### 2015-04-02 manuscript.tex
manuscript

\documentclass[conference]{IEEEtran}
\usepackage{colortbl}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{tabulary}
\usepackage{bigstrut}
\setlength\fboxsep{1pt}
\setlength\fboxrule{1pt}
\usepackage{multicol}
\bstctlcite{IEEEexample:BSTcontrol}
\usepackage[table]{xcolor}
\usepackage{picture}
\newcommand{\quart}[4]{\begin{picture}(100,3)
  {\color{black}\put(#3,3){\circle*{4}}\put(#1,3){\line(1,0){#2}}}\end{picture}}
\usepackage{amsmath}
\usepackage{balance}
\usepackage{flushend}
\usepackage[english]{babel}
\usepackage{blindtext}
\usepackage{times}
\usepackage{cite}
\usepackage{hyperref}
\hypersetup{
  colorlinks = false,
  hidelinks = true
}
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}

\begin{document}
  \title{Contrast Set Learning using WHAT}

  \author{\IEEEauthorblockN{Rahul Krishna}
    \IEEEauthorblockA{
      North Carolina State University, USA\\
      rkrish11@ncsu.edu}
    \and
    \IEEEauthorblockN{Tim Menzies}
    \IEEEauthorblockA{North Carolina State University, USA\\
      tim.menzies@gmail.com}}

  % make the title area
  \maketitle

  \begin{abstract}

  \end{abstract}
  \begin{keywords}
    defect prediction, CART
  \end{keywords}

\section{Introduction}
\section{Background}
\section{Experimental Design}
\subsection{The Planning Algorithm}

\section{Experimental Results}
\section{Discussion}
\section{Threats to validity}
\section{Conclusion}
\section*{Acknowledgements}
\begin{thebibliography}{10}
\bibitem{test}
\end{thebibliography}
\end{document}

### 2015-04-05 manuscript.tex
Manuscripy

@@
 \section{Background}
+\subsection{The Planning Algorithm}
+The planning scheme makes use of WHERE to recursively split the data into smaller clusters.
+Following this, a nearest neighbour scheme is applied to identify pairs of nearby clusters.
+A projective plane is constructed with these clusters at the vertices to characterize the cluster pairs.
+
+The mutation policy works by projecting the test instance onto the projective planes and identifying the the plane on which the test instance has the largest scalar projection.
+WHAT reflects over the vertices of the chosen hyperplane,  identifying the \textit{better} vertex among the two.
+A new instance is generated by mutating the attributes of the test instance towards the better vertex and away from the worse vertex.
+This process is repeated for all the test instance that are considered defective.
 \section{Experimental Design}
-\subsection{The Planning Algorithm}
 
@@
 \section*{Acknowledgements}
-\begin{thebibliography}{10}
-\bibitem{test}
-\end{thebibliography}
+%\begin{thebibliography}{10}
+%\bibitem{test}
+%\end{thebibliography}
 \end{document}

### 2015-04-05 manuscript.tex
Updates from ShareLaTeX

@@
 \usepackage{picture}
+\newcommand{\keyword}[1]{\textit{#1}}
 \newcommand{\quart}[4]{\begin{picture}(100,3)
@@
   \end{abstract}
-  \begin{keywords}
+  \begin{IEEEkeywords}
     defect prediction, CART
-  \end{keywords}
+  \end{IEEEkeywords}
 
@@
 A new instance is generated by mutating the attributes of the test instance towards the better vertex and away from the worse vertex.
-This process is repeated for all the test instance that are considered defective.
+This process is repeated for all the test instances that are considered defective.
 \section{Experimental Design}
-
+The following section describes the experiments used to measure the performance of WHAT on 10 defect data sets and 6 performance prediction data sets.
+\subsection{Data sets}
+The defect data was obtained from the PROMISE repository. We investigated 32 releases from 11 open source Java projects defined by the metrics highlighted in: \textit{Ant} (1.5-1.7) 
 \section{Experimental Results}

### 2015-04-05 manuscript.tex
Updates from ShareLaTeX

@@
 \section{Introduction}
+\section{Motivating Example}
 \section{Background}
+\section{Contrast Set Learning using WHAT}
+\subsection{Overview}
 \subsection{The Planning Algorithm}
@@
 \subsection{Data sets}
-The defect data was obtained from the PROMISE repository. We investigated 32 releases from 11 open source Java projects defined by the metrics highlighted in: \textit{Ant} (1.5-1.7) 
-\section{Experimental Results}
-\section{Discussion}
-\section{Threats to validity}
-\section{Conclusion}
-\section*{Acknowledgements}
+The data was obtained from the PROMISE repository.
+For the defect data we investigated 32 releases from 11 open source Java projects defined by the metrics highlighted in \ref{}: \keyword{Apache Ant} (1.5 -- 1.7), \keyword{Apache Camel} (1.2 -- 1.6), \keyword{Apache Ivy} (1.1 -- 2.0), \keyword{JEdit} (4.1 -- 4.3), \keyword{Apache Log4j} (1.0 -- 1.2), \keyword{Apache Lucene} (2.0 -- 2.2), \keyword{PBeans} (1.0 and 2.0), \keyword{Apache POI} (2.0 -- 3.0), \keyword{Apache Synapse} (1.0 -- 1.2), \keyword{Apache Velocity} (1.4 -- 1.6), and \keyword{Apache Xalan-Java} (2.5 -- 2.7).
+Given the empirical nature of the data, it is important to design an experiment such that the planning phase uses only the \keyword{past} data to learn trends which can then be applied to the \keyword{future} data.
+Thus for our experiment we use data sets that have at least two consecutive releases.
+\begin{itemize}
+\item To generate recommendations for a release $i$, the planner uses releases releases $(i-1)$ and $(i-2)$.
+\item The predictor also uses releases $(i-1)$ and $(i-2)$.
+However, we use SMOTE with re-sampling in order to handle the class imbalance in the data and to prevent the predictor from using the same training data as the planner.
+\end{itemize}
+
+The performance prediction data set was obtained from \cite{}.
+The data set contains six examples of real world configurable systems: \keyword{Apache}, \keyword{LLVM}, \keyword{x264}, \keyword{Berkeley DB (written in C and Java}, and \keyword{SQLite}.
+The systems have different characteristics, different implementation languages, and different configuration mechanisms.
+The data set is a collection of all possible configurations (with SQLITE being a exception with only 4653 configurations).
+We performed a 5-fold cross validation study on this data set.
+
+\subsection{Performance Assessment}
+
+In order to assess the performance of the planner for the defect data set, we use the Cliffs Delta score to measure the probability that the number of bugs in test data before applying the planner is larger than after.
+In other words, we use the delta score to measure the ability of the planner to effective reduce the number of defects.
+
+% \section{Experimental Results}
+% \section{Discussion}
+% \section{Threats to validity}
+% \section{Conclusion}
+% \section*{Acknowledgements}
 %\begin{thebibliography}{10}

### 2015-04-05 manuscript.tex
Updates from ShareLaTeX

@@
 
-In order to assess the performance of the planner for the defect data set, we use the Cliffs Delta score to measure the probability that the number of bugs in test data before applying the planner is larger than after.
+In order to assess the performance of the planner for the defect data set, we use the Cliffs Delta score to measure the probability that the number of bugs in test data before applying the planner is larger than after doing so.
 In other words, we use the delta score to measure the ability of the planner to effective reduce the number of defects.

### 2015-04-07 manuscript.tex
Updates from ShareLaTeX

@@
 \begin{document}
-  \title{Contrast Set Learning using WHAT}
+  \title{An Instance Based Approach for Empirical Transfer Learning}
 
@@
 \section{Background}
-\section{Contrast Set Learning using WHAT}
-\subsection{Overview}
+\section{Instance Based Learning}
+Assessing the performance of certain techniques can be extremely hard.
+In several applications we have models that can emulate the performance of systems.
+Using these models it is possible to examine several scenarios in a reproducible manner.
+However, models aren't always the solution, as we shall see.
+
+There exists several problems where models are hard to obtain, or the input and output are related by complex connections that simply cannot be modeled in a reliable manner, or generation of reliable models take prohibitively long.
+Software defect prediction is an excellent example of such a case.
+Models that incorporate all the intricate issues that may lead defects in a product is extremely hard to come by.
+In this paper we propose the use of an instance based approach in place of the conventional model based approach.
+
+\subsection{Spectral Learning using WHERE}
+The algorithm uses WHERE to recursively cluster the input data to identify subsets in the training data that a test instance can learn from.
+WHERE is a spectral learner which uses the FastMap heuristic to estimate the first principal component.
+It then recursively partitions the data into two halves along the median point of the projection on the first principal component, terminating when a half has less than $\sqrt{N}$ items.
+
 \subsection{The Planning Algorithm}
-The planning scheme makes use of WHERE to recursively split the data into smaller clusters.
+The planning scheme makes use of the clusters generated using the WHERE algorithm discussed above.
 Following this, a nearest neighbour scheme is applied to identify pairs of nearby clusters.
@@
 The mutation policy works by projecting the test instance onto the projective planes and identifying the the plane on which the test instance has the largest scalar projection.
-WHAT reflects over the vertices of the chosen hyperplane,  identifying the \textit{better} vertex among the two.
-A new instance is generated by mutating the attributes of the test instance towards the better vertex and away from the worse vertex.
+The planner then reflects over the vertices of the chosen hyperplane, identifying the \textit{better} vertex among the two.
+Now, a new instance is generated by mutating the attributes of the test instance towards the better vertex and away from the worse vertex.
 This process is repeated for all the test instances that are considered defective.
@@
 In other words, we use the delta score to measure the ability of the planner to effective reduce the number of defects.
+Given the untreated test instance labeled \textit{Before} of length \textit{M} and the treated instances labeled \textit{After}, the delta score is obtained as follows:
+\begin{equation}
+\delta = \frac{\#(Before>After) - \#(Before<After)}{M^2}
+\end{equation}
 
+In the context of our application, the $\delta$ attains a value of 1 if the number of defects after applying the treatments has reduced to zero, and 0 if there is no change.
+
+For the performance prediction data set on the other hand, Cliff's delta measure is not directly applicable.
+We therefore assess the performance by measuring the gain, given by $\frac{Before}{After}$.
+The gain takes a value larger than 1 if the run times have been reduced, a value of 1 if there is no change, and a value less than 1 if run times have increased after applying the recommended changes.
+
+In addition to the above, we rank the different variants of the planning scheme to identify the best approach.
+We make use of the Scott-Knott procedure, recommended by \cite{} to compute the ranks.
+It works as follows: A list of treatments \textit{l} is sorted by the median score.
+The list \textit{l} is then split into sub-lists m, n in order to maximize the expected value of the differences in the observed performance before and after division.
+A statistical hypothesis test \textit{H} is applied on the splits \textit{m, n} to check if they are statistically different.
+If so, Skott-Knott then recurses on each division.
+In our paper, we use the A12 test and a non-parametric bootstrap sampling for hypothesis testing.
 % \section{Experimental Results}

### 2015-04-07 manuscript.tex
Stuff

@@
 \section{Instance Based Learning}
-Assessing the performance of certain techniques can be extremely hard.
-In several applications we have models that can emulate the performance of systems.
-Using these models it is possible to examine several scenarios in a reproducible manner.
+
+Assessing the quality of solutions to a real-world problem can be extremely hard.
+In several applications, researchers have models that can emulate the problem.
+Using these models it is possible to examine several scenarios in a short period of time, and this can be done in a reproducible manner.
 However, models aren't always the solution, as we shall see.
 
-There exists several problems where models are hard to obtain, or the input and output are related by complex connections that simply cannot be modeled in a reliable manner, or generation of reliable models take prohibitively long.
+There exist several problems where models are hard to obtain, or the input and output are related by complex connections that simply cannot be modeled in a reliable manner, or generation of reliable models take prohibitively long.
 Software defect prediction is an excellent example of such a case.
 Models that incorporate all the intricate issues that may lead defects in a product is extremely hard to come by.
+Moreover, it has been shown that models for different regions within the same data can have very different properties \cite{}.
+
 In this paper we propose the use of an instance based approach in place of the conventional model based approach.

### 2015-04-08 manuscript.tex
CC Metrics

@@
 \begin{document}
-  \title{An Instance Based Approach for Empirical Transfer Learning}
+  \title{An Instance Based Reasoning for Empirical Transfer Learning}
 
@@
 In this paper we propose the use of an instance based approach in place of the conventional model based approach.
+Instead of generating solutions and going back to a model to see if the solution has any value, we
 
@@
 This process is repeated for all the test instances that are considered defective.
+\begin{figure*}[htbp!]
+  \renewcommand{\baselinestretch}{0.8}\begin{center}
+    {\scriptsize
+      \begin{tabular}{c|l|p{4.7in}}
+        amc & average method complexity & e.g. number of JAVA byte codes\\\hline
+        avg\_cc & average McCabe & average McCabe's cyclomatic complexity seen
+        in class\\\hline
+        ca & afferent couplings & how many other classes use the specific
+        class. \\\hline
+        cam & cohesion amongst classes & summation of number of different
+        types of method parameters in every method divided by a multiplication
+        of number of different method parameter types in whole class and
+        number of methods. \\\hline
+        cbm &coupling between methods &  total number of new/redefined methods
+        to which all the inherited methods are coupled\\\hline
+        cbo & coupling between objects & increased when the methods of one
+        class access services of another.\\\hline
+        ce & efferent couplings & how many other classes is used by the
+        specific class. \\\hline
+        dam & data access & ratio of the number of private (protected)
+        attributes to the total number of attributes\\\hline
+        dit & depth of inheritance tree &\\\hline
+        ic & inheritance coupling &  number of parent classes to which a given
+        class is coupled (includes counts of methods and variables inherited)
+        \\\hline
+        lcom & lack of cohesion in methods &number of pairs of methods that do
+        not share a reference to an instance variable.\\\hline
+        locm3 & another lack of cohesion measure & if $m,a$ are  the number of
+        $methods,attributes$
+        in a class number and $\mu(a)$  is the number of methods accessing an
+        attribute, 
+        then
+        $lcom3=((\frac{1}{a} \sum_j^a \mu(a_j)) - m)/ (1-m)$.
+        \\\hline
+        loc & lines of code &\\\hline
+        max\_cc & maximum McCabe & maximum McCabe's cyclomatic complexity seen
+        in class\\\hline
+        mfa & functional abstraction & number of methods inherited by a class
+        plus number of methods accessible by member methods of the
+        class\\\hline
+        moa &  aggregation &  count of the number of data declarations (class
+        fields) whose types are user defined classes\\\hline
+        noc &  number of children &\\\hline
+        npm & number of public methods & \\\hline
+        rfc & response for a class &number of  methods invoked in response to
+        a message to the object.\\\hline
+        wmc & weighted methods per class &\\\hline
+        \rowcolor{lightgray}
+        defect & defect & Boolean: where defects found in post-release bug-tracking systems.
+      \end{tabular}
+    }
+  \end{center}
+  \caption{OO measures used in our defect data sets.  Last line is
+    the dependent attribute (whether a defect is reported to  a
+    post-release bug-tracking system).}\label{fig:ck}
+\end{figure*}
+
 \section{Experimental Design}

### 2015-04-08 manuscript.tex
results

@@
 \usepackage{booktabs}
-\usepackage{subcaption}
+\usepackage{subfig}
 \usepackage{algorithm}
@@
 \usepackage[table]{xcolor}
+\definecolor{darkgray}{gray}{0.6}
+\definecolor{Gray}{gray}{0.9}
 \usepackage{picture}
@@
 In our paper, we use the A12 test and a non-parametric bootstrap sampling for hypothesis testing.
-% \section{Experimental Results}
+\section{Experimental Results}
+\begin{figure}[!t]
+
+\begin{minipage}{0.5\textwidth}
+\renewcommand{\baselinestretch}{}
+{\bf \scriptsize Ant:}
+
+{\scriptsize \begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
+      \arrayrulecolor{darkgray}
+      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
+    1 &     Baseline &    0.03  &  0.0 & \quart{0}{0}{0}{62} \\
+    \hline  2 & $\alpha=0.25$, Prune=50\% &    0.15  &  0.09 & \quart{4}{6}{7}{62} \\
+    \hline  3 & $\alpha=0.5$, Prune=50\% &    0.25  &  0.1 & \quart{12}{6}{14}{62} \\
+    \hline  4 &     $\alpha=0.25$ &    0.34  &  0.05 & \quart{18}{4}{20}{62} \\
+    4 &   $\alpha=0.25$, weight &    0.36  &  0.08 & \quart{18}{5}{21}{62} \\
+    4 & $\alpha=0.75$, Prune=50\% &    0.41  &  0.13 & \quart{21}{8}{24}{62} \\
+    \hline  5 &    $\alpha=0.5$, weight &    0.46  &  0.18 & \quart{24}{12}{27}{62} \\
+    5 &      $\alpha=0.5$ &    0.53  &  0.15 & \quart{27}{10}{32}{62} \\
+    \hline  6 &     $\alpha=0.75$ &    0.64  &  0.17 & \quart{34}{11}{39}{62} \\
+    6 &   $\alpha=0.75$, weight &    0.73  &  0.17 & \quart{38}{11}{45}{62} \\
+    \hline \end{tabular}\\}
+
+{\bf \scriptsize Camel}
+
+{\scriptsize \begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
+    \arrayrulecolor{darkgray}
+    \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
+1 &   Baseline &    0.16  &  0.03 & \quart{0}{3}{1}{111} \\
+1 &   $\alpha=0.25$ &    0.17  &  0.06 & \quart{0}{7}{2}{111} \\
+1 & $\alpha=0.25$, weight &    0.17  &  0.06 & \quart{0}{7}{2}{111} \\
+\hline  2 & $\alpha=0.25$, Prune=50\% &    0.22  &  0.06 & \quart{5}{8}{9}{111} \\
+\hline  3 &    $\alpha=0.5$ &    0.25  &  0.1 & \quart{3}{14}{13}{111} \\
+3 &  $\alpha=0.5$, weight &    0.26  &  0.14 & \quart{7}{19}{14}{111} \\
+\hline  4 & $\alpha=0.5$, Prune=50\% &    0.32  &  0.16 & \quart{10}{21}{22}{111} \\
+\hline  5 & $\alpha=0.75$, weight &    0.38  &  0.19 & \quart{14}{25}{30}{111} \\
+5 &   $\alpha=0.75$ &    0.4  &  0.12 & \quart{23}{16}{32}{111} \\
+\hline  6 & $\alpha=0.75$, Prune=50\% &    0.47  &  0.15 & \quart{30}{19}{42}{111} \\
+\hline \end{tabular}}\\
+
+{\bf \scriptsize Ivy}
+
+    {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
+        \arrayrulecolor{darkgray}
+        \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
+        1 &     Baseline &    0.06  &  0.0 & \quart{0}{0}{0}{79} \\
+        \hline  2 & $\alpha=0.25$, Prune=50\% &    0.14  &  0.04 & \quart{4}{3}{6}{79} \\
+        \hline  3 & $\alpha=0.5$, Prune=50\% &    0.2  &  0.06 & \quart{9}{5}{11}{79} \\
+        \hline  4 & $\alpha=0.75$, Prune=50\% &    0.27  &  0.14 & \quart{10}{12}{17}{79} \\
+        \hline  5 &     $\alpha=0.25$ &    0.41  &  0.06 & \quart{27}{5}{29}{79} \\
+        5 &   $\alpha=0.25$, weight &    0.42  &  0.06 & \quart{27}{6}{30}{79} \\
+        \hline  6 &    $\alpha=0.5$, weight &    0.55  &  0.11 & \quart{35}{9}{41}{79} \\
+        6 &      $\alpha=0.5$ &    0.57  &  0.09 & \quart{37}{7}{43}{79} \\
+        \hline  7 &   $\alpha=0.75$, weight &    0.61  &  0.08 & \quart{42}{7}{46}{79} \\
+        7 &     $\alpha=0.75$ &    0.62  &  0.04 & \quart{46}{3}{47}{79} \\
+        \hline \end{tabular}}\\
+
+{\bf \scriptsize Jedit}
+
+  {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
+      \arrayrulecolor{darkgray}
+      \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
+      1 &   Baseline &    0.05  &  0.0 & \quart{0}{0}{0}{75} \\
+      \hline  2 & $\alpha=0.25$, Prune=50\% &    0.11  &  0.05 & \quart{2}{4}{4}{75} \\
+      \hline  3 & $\alpha=0.5$, Prune=50\% &    0.16  &  0.1 & \quart{3}{8}{8}{75} \\
+      \hline  4 &   $\alpha=0.25$ &    0.2  &  0.08 & \quart{10}{6}{11}{75} \\
+      4 & $\alpha=0.25$, weight &    0.21  &  0.1 & \quart{7}{8}{12}{75} \\
+      \hline  5 & $\alpha=0.75$, Prune=50\% &    0.32  &  0.15 & \quart{15}{11}{21}{75} \\
+      5 &  $\alpha=0.5$, weight &    0.33  &  0.05 & \quart{19}{4}{22}{75} \\
+      5 &    $\alpha=0.5$ &    0.34  &  0.18 & \quart{18}{14}{23}{75} \\
+      \hline  6 &   $\alpha=0.75$ &    0.56  &  0.2 & \quart{27}{16}{40}{75} \\
+      6 & $\alpha=0.75$, weight &    0.56  &  0.26 & \quart{29}{20}{40}{75} \\
+      \hline \end{tabular}}\\
+\end{minipage}
+\end{figure}
+\begin{figure}
+\begin{minipage}{0.5\textwidth}
+  \renewcommand{\baselinestretch}{}
+{\bf \scriptsize Log4j}
+
+  {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
+      \arrayrulecolor{darkgray}
+      \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
+      1 & $\alpha=0.5$, Prune=50\% &    0.1  &  0.06 & \quart{1}{11}{5}{172} \\
+      1 & $\alpha=0.25$, Prune=50\% &    0.11  &  0.04 & \quart{1}{8}{7}{172} \\
+      1 & $\alpha=0.25$, weight &    0.1  &  0.03 & \quart{3}{6}{5}{172} \\
+      1 &  $\alpha=0.5$, weight &    0.1  &  0.13 & \quart{0}{24}{5}{172} \\
+      1 &   Baseline &    0.11  &  0.04 & \quart{0}{7}{7}{172} \\
+      1 &   $\alpha=0.25$ &    0.12  &  0.06 & \quart{1}{11}{9}{172} \\
+      \hline  2 &    $\alpha=0.5$ &    0.15  &  0.09 & \quart{3}{17}{14}{172} \\
+      2 & $\alpha=0.75$, Prune=50\% &    0.15  &  0.05 & \quart{9}{9}{14}{172} \\
+      2 & $\alpha=0.75$, weight &    0.17  &  0.22 & \quart{9}{40}{18}{172} \\
+      2 &   $\alpha=0.75$ &    0.22  &  0.16 & \quart{14}{30}{27}{172} \\
+      \hline \end{tabular}}\\
+
+{\bf \scriptsize Lucene}
+
+{\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
+    \arrayrulecolor{darkgray}
+    \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
+    1 & $\alpha=0.25$, weight &    0.03  &  0.03 & \quart{0}{4}{1}{148} \\
+    1 &  $\alpha=0.25$ &    0.05  &  0.04 & \quart{1}{6}{4}{148} \\
+    \hline  2 &   $\alpha=0.5$ &    0.09  &  0.09 & \quart{6}{13}{10}{148} \\
+    2 & $\alpha=0.25$, Prune=50\% &    0.09  &  0.03 & \quart{7}{5}{10}{148} \\
+    2 &  Baseline &    0.1  &  0.01 & \quart{10}{2}{12}{148} \\
+    2 & $\alpha=0.5$, weight &    0.14  &  0.06 & \quart{10}{9}{18}{148} \\
+    \hline  3 & $\alpha=0.5$, Prune=50\% &    0.19  &  0.08 & \quart{21}{12}{25}{148} \\
+    \hline  4 & $\alpha=0.75$, weight &    0.23  &  0.15 & \quart{22}{23}{31}{148} \\
+    4 &  $\alpha=0.75$ &    0.26  &  0.1 & \quart{27}{15}{36}{148} \\
+    4 & $\alpha=0.75$, Prune=50\% &    0.28  &  0.13 & \quart{30}{19}{39}{148} \\\hline \end{tabular}}\\
+
+{\bf \scriptsize Poi}
+
+{\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
+    \arrayrulecolor{darkgray}
+    \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
+    1 & $\alpha=0.25$, Prune=50\% &    0.09  &  0.15 & \quart{0}{9}{3}{62} \\
+    1 &     Baseline &    0.09  &  0.05 & \quart{2}{3}{3}{62} \\
+    1 & $\alpha=0.5$, Prune=50\% &    0.12  &  0.13 & \quart{1}{8}{5}{62} \\
+    \hline  2 &     $\alpha=0.25$ &    0.24  &  0.3 & \quart{5}{19}{13}{62} \\
+    2 &   $\alpha=0.25$, weight &    0.25  &  0.32 & \quart{4}{20}{14}{62} \\
+    \hline  3 & $\alpha=0.75$, Prune=50\% &    0.37  &  0.45 & \quart{4}{29}{21}{62} \\
+    3 &    $\alpha=0.5$, weight &    0.49  &  0.5 & \quart{9}{32}{29}{62} \\
+    \hline  4 &     $\alpha=0.75$ &    0.53  &  0.47 & \quart{16}{30}{32}{62} \\
+    4 &      $\alpha=0.5$ &    0.53  &  0.28 & \quart{18}{18}{32}{62} \\
+    4 &   $\alpha=0.75$, weight &    0.61  &  0.43 & \quart{22}{27}{37}{62} \\
+    \hline \end{tabular}}  \\
+
+{\bf \scriptsize Velocity}
+
+  {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
+      \arrayrulecolor{darkgray}
+      \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
+      1 & $\alpha=0.25$ &    0.08  &  0.03 & \quart{0}{4}{1}{140} \\
+      1 & $\alpha=0.25$, weight &    0.09  &  0.05 & \quart{0}{7}{3}{140} \\
+      \hline  2 & Baseline &    0.13  &  0.04 & \quart{6}{6}{9}{140} \\
+      \hline  3 & $\alpha=0.5$ &    0.16  &  0.09 & \quart{9}{13}{13}{140} \\
+      3 & $\alpha=0.25$, Prune=50\% &    0.17  &  0.04 & \quart{13}{6}{15}{140} \\
+      3 & $\alpha=0.5$, weight &    0.19  &  0.09 & \quart{12}{13}{18}{140} \\
+      \hline  4 & $\alpha=0.5$, Prune=50\% &    0.22  &  0.11 & \quart{15}{16}{22}{140} \\
+      4 & $\alpha=0.75$, weight &    0.25  &  0.1 & \quart{19}{15}{27}{140} \\
+      4 & $\alpha=0.75$ &    0.28  &  0.2 & \quart{19}{30}{31}{140} \\
+      4 & $\alpha=0.75$, Prune=50\% &    0.28  &  0.09 & \quart{24}{13}{31}{140} \\
+      \hline \end{tabular}}\\
+
+{\bf \scriptsize Xalan}
+
+  {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
+      \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
+      1 & $\alpha=0.75$, weight &    0.31  &  0.14 & \quart{0}{31}{13}{170} \\
+      1 & $\alpha=0.25$, weight &    0.32  &  0.1 & \quart{2}{22}{15}{170} \\
+      1 &   $\alpha=0.25$ &    0.32  &  0.06 & \quart{13}{14}{15}{170} \\
+      \hline  2 &    $\alpha=0.5$ &    0.34  &  0.11 & \quart{6}{25}{20}{170} \\
+      2 &   Baseline &    0.36  &  0.13 & \quart{4}{30}{24}{170} \\
+      2 &  $\alpha=0.5$, weight &    0.35  &  0.12 & \quart{6}{28}{22}{170} \\
+      2 & $\alpha=0.5$, Prune=50\% &    0.36  &  0.12 & \quart{11}{27}{24}{170} \\
+      2 & $\alpha=0.25$, Prune=50\% &    0.38  &  0.1 & \quart{13}{23}{29}{170} \\
+      2 & $\alpha=0.75$, Prune=50\% &    0.37  &  0.21 & \quart{2}{47}{27}{170} \\
+      2 &   $\alpha=0.75$ &    0.38  &  0.17 & \quart{6}{39}{29}{170} \\
+      \hline \end{tabular}}
+ \end{minipage}  
+   \end{figure}
+
 % \section{Discussion}

### 2015-04-08 manuscript.tex
Updates from ShareLaTeX

@@
 \newcommand{\keyword}[1]{\textit{#1}}
-\newcommand{\quart}[4]{\begin{picture}(100,3)
+\newcommand{\quart}[4]{\begin{picture}(50,3)
   {\color{black}\put(#3,3){\circle*{4}}\put(#1,3){\line(1,0){#2}}}\end{picture}}
@@
 This process is repeated for all the test instances that are considered defective.
+
+\begin{figure}[!b]
+\small
+\begin{tabular}{|p{.95\linewidth}|}\hline
+WHAT begins by \textit{clustering} the training data into similar subsets using WHERE. It works as follows:
+\begin{enumerate}
+\item Find two distant points in that population; call them the {\em east} and {\em west} poles. 
+\item Draw an axis of length $c$ between the poles. 
+\item Let each point be at distance $a,b$ to the {\em east,west} poles.  Using the cosine rule, project each point onto the  axis  at $x=(a^2 + c^2 - b^2)/(2c)$.  
+\item Using the median $x$ value, divide the population.
+\item For each half that is larger than $\sqrt{N}$ of the original population, go to step 1.
+\end{enumerate}
+
+Note that the above requires a distance measure between sets of decisions: GALE uses the standard case-based reasoning measure defined by Aha et al.~\cite{aha91}.
+Note also that GALE implements step1 via  the FASTMAP~\cite{Faloutsos1995} linear-time
+heuristic:
+\begin{itemize}
+\item Pick any point at random; 
+\item Let {\em east} be the point furthest from that point; 
+\item Let {\em west} be the point furthest from {\em east}.
+\end{itemize}
+
+These final sub-divisions found by this process are the {\em neighborhoods} that GALE will {\em perturb} as follows:
+\begin{itemize}
+\item Find the objective scores of the {\em east,west} poles in each neighborhood.
+\item Using the continuous domination predicate of \fig{moea}, find  the {\em better} pole. 
+\item Perturb all points in that neighborhood by pushing them towards the better pole, by a distance  $c/2$ (recall that  $c$ is the distance between the poles).
+\item Let generation $i+1$ be the combination of all pushed points from all neighborhoods.
+\end{itemize}
+
+From a formal perspective, GALE is an active learner~\cite{Dasgupta2005} that builds a piecewise linear approximation to the Pareto frontier~\cite{Zuluaga:13}.
+For each piece, it then pushes the neighborhood up the local gradient.
+This  approximation is built in the reduced dimensional space found the FASTMAP  Nystr\"om approximation to the first component of PCA~\cite{platt05}.
+\\\hline
+\end{tabular}
+\caption{Inside GALE}\label{fig:gale}
+\end{figure}
+
+\subsection{Defect Prediction}
+
 \begin{figure*}[htbp!]
@@
 \begin{figure}[!t]
-
+  \centering
 \begin{minipage}{0.5\textwidth}

### 2015-04-09 manuscript.tex
stufff....

@@
 \usepackage{algpseudocode}
-\usepackage{tabulary}
-\usepackage{bigstrut}
 \setlength\fboxsep{1pt}
@@
 \usepackage{flushend}
-\usepackage[english]{babel}
-\usepackage{blindtext}
 \usepackage{times}
@@
 \begin{tabular}{|p{.95\linewidth}|}\hline
-WHAT begins by \textit{clustering} the training data into similar subsets using WHERE. It works as follows:
+WHAT begins by \textit{clustering} the training data into similar subsets using WHERE which works as follows:
 \begin{enumerate}
@@
 \item Find the objective scores of the {\em east,west} poles in each neighborhood.
-\item Using the continuous domination predicate of \fig{moea}, find  the {\em better} pole. 
+\item Using the continuous domination predicate of MOEA, find  the {\em better} pole. 
 \item Perturb all points in that neighborhood by pushing them towards the better pole, by a distance  $c/2$ (recall that  $c$ is the distance between the poles).

### 2015-04-09 manuscript.tex
stufff....

@@
 \begin{tabular}{|p{.95\linewidth}|}\hline
-WHAT begins by \textit{clustering} the training data into similar subsets using WHERE which works as follows:
+WHAT begins by \textit{clustering} the training data into similar subsets using WHERE, which works as follows:
 \begin{enumerate}
@@
 
-Note that the above requires a distance measure between sets of decisions: GALE uses the standard case-based reasoning measure defined by Aha et al.~\cite{aha91}.
-Note also that GALE implements step1 via  the FASTMAP~\cite{Faloutsos1995} linear-time
-heuristic:
+There are couple of things to note: firstly, the above algorithm requires a distance measure between sets of decisions, for this WHERE uses case-based reasoning measure defined by Aha et al.~\cite{aha91}; secondly, in step-1 a linear time heuristic called FASTMAP~\cite{Faloutsos1995} is used to find the two most distant points, this procedure is listed below:
 \begin{itemize}
-\item Pick any point at random; 
+\item Pick a point at random; 
 \item Let {\em east} be the point furthest from that point; 
-\item Let {\em west} be the point furthest from {\em east}.
+\item Then {\em west} be the point furthest from {\em east}.
 \end{itemize}
 
-These final sub-divisions found by this process are the {\em neighborhoods} that GALE will {\em perturb} as follows:
+The final clusters that are found by WHERE are then used by WHAT as follows:
 \begin{itemize}

### 2015-04-09 manuscript.tex
Stuff...

@@
 \usepackage{booktabs}
+\usepackage{epstopdf}
 \usepackage{subfig}
@@
 \usepackage{algpseudocode}
+\usepackage{graphicx}
 \setlength\fboxsep{1pt}
@@
 \usepackage{picture}
-\newcommand{\keyword}[1]{\textit{#1}}
+\newcommand{\kw}[1]{\textit{#1}}
 \newcommand{\quart}[4]{\begin{picture}(50,3)
@@
 \setlength{\parskip}{1em}
+
+% New Commands
+\newcommand{\bi}{\begin{itemize}}
+\newcommand{\ei}{\end{itemize}}
+\newcommand{\be}{\begin{enumerate}}
+\newcommand{\ee}{\end{enumerate}}
 
@@
 Models that incorporate all the intricate issues that may lead defects in a product is extremely hard to come by.
-Moreover, it has been shown that models for different regions within the same data can have very different properties \cite{}.
+Moreover, it has been shown that models for different regions within the same data can have very different properties \cite{localvsglobal}.
 
@@
 
-\subsection{The Planning Algorithm}
-The planning scheme makes use of the clusters generated using the WHERE algorithm discussed above.
+\subsection{Planning changes using WHAT}
+We propose the WHAT algorithm as a tool to plan changes in the original test data.
+Figure~\ref{fig:what} highlights the procedure by which WHAT operates.
+It begins by creating clusters which are generated using the WHERE algorithm discussed above.
 Following this, a nearest neighbour scheme is applied to identify pairs of nearby clusters.
@@
 Now, a new instance is generated by mutating the attributes of the test instance towards the better vertex and away from the worse vertex.
-This process is repeated for all the test instances that are considered defective.
+This process is repeated for all the test instances that are considered defective by the defect prediction scheme, discussed below.
 
-\begin{figure}[!b]
+\begin{figure}[htbp!]
 \small
 \begin{tabular}{|p{.95\linewidth}|}\hline
-WHAT begins by \textit{clustering} the training data into similar subsets using WHERE, which works as follows:
+WHAT begins by \textit{clustering} the training data into similar subsets using WHERE. WHERE works as follows:
 \begin{enumerate}
@@
 
-There are couple of things to note: firstly, the above algorithm requires a distance measure between sets of decisions, for this WHERE uses case-based reasoning measure defined by Aha et al.~\cite{aha91}; secondly, in step-1 a linear time heuristic called FASTMAP~\cite{Faloutsos1995} is used to find the two most distant points, this procedure is listed below:
+There are couple of things to note: firstly, the above algorithm requires a distance measure between sets of decisions, for this WHERE uses case-based reasoning measure defined by Aha et al.~\cite{aha91}; secondly, in step-1 a linear time heuristic called FASTMAP~\cite{fastmap} is used to find the two most distant points, this procedure is listed below:
 \begin{itemize}
@@
 \begin{itemize}
-\item Find the objective scores of the {\em east,west} poles in each neighborhood.
-\item Using the continuous domination predicate of MOEA, find  the {\em better} pole. 
-\item Perturb all points in that neighborhood by pushing them towards the better pole, by a distance  $c/2$ (recall that  $c$ is the distance between the poles).
-\item Let generation $i+1$ be the combination of all pushed points from all neighborhoods.
+\item For each cluster find its nearest neighbor.
+\item Construct a projective plane for each cluster pair. Label the cluster pairs as {\em Good} and {\em Bad}.
+\item For a test instance, project it onto the planes generated above and pick the one on which the test case has the largest projection.
+\item Mutate the attributes of the test case towards the {\em Good Cluster} in that projective plane. 
 \end{itemize}
 
-From a formal perspective, GALE is an active learner~\cite{Dasgupta2005} that builds a piecewise linear approximation to the Pareto frontier~\cite{Zuluaga:13}.
-For each piece, it then pushes the neighborhood up the local gradient.
-This  approximation is built in the reduced dimensional space found the FASTMAP  Nystr\"om approximation to the first component of PCA~\cite{platt05}.
+Formally, WHAT can be considered as an instance based  learning scheme.
+And that's beacuse it builds a set of recommendations based on a given test case based on the clusters formed at the training stage.
+This is unlike a model based approach, which would have used a model to do the same~\cite{xomo}.
 \\\hline
 \end{tabular}
-\caption{Inside GALE}\label{fig:gale}
+\caption{Inside WHAT}\label{fig:what}
 \end{figure}
@@
 \subsection{Defect Prediction}
+
+To validate the treatments that have been suggested by our planner, we need to have defect predictors that capable of identifying if a certain module may (or may not) have a defect.
+A recent IEEE TSE paper by Lessmann et al.~\cite{lessmann} compared 21 different leaners for software defect prediction:
+\bi
+\item
+{\em Statistical classifiers:}
+Linear    discriminant analysis,
+Quadratic discriminant analysis,
+Logistic regression,
+Naive Bayes,
+Bayesian networks,
+Least-angle regression,
+Relevance vector machine,
+
+\item
+{\em Nearest neighbor methods:}
+k-nearest neighbor,
+K-Star
+
+\item
+{\em Neural networks:}
+Multi-Layer Perceptron,
+Radial bias functions,
+
+\item
+{\em Support vector machine-based classifiers:}
+Support vector machine,
+Lagrangian SVM
+Least squares SVM,
+Linear programming,
+Voted perceptron,
+
+\item
+{\em Decision-tree approaches:}
+C4.5,
+CART,
+Alternating DTs
+\item
+{\em Ensemble methods:}
+\textbf{Random Forest},
+Logistic Model Tree.
+\ei
+
+They concluded that Random Forrest was the best method, CART being the worst.
+
+Random Forest is an ensemble learning scheme that constructs a number of decision trees at the training time, for a test instance it outputs the mode of the classes of individual tree.
+It's patent from how random forest operates that the prediction will suffer if there is an imbalance in classes during the training.
+Unfortunately, the data sets explored here do suffer from severe skewness, as highlighted in~\ref{fig:classimb}.
+A study conducted by Pelayo and Dick~\cite{smote2} inspected this issue.
+They showed that the SMOTE technique~\cite{smote} can be used to improve recognition of defect-prone modules.
+
+In short, SMOTE works by under-sampling the majority class and oversampling all the minority classes in the training data.
+We use a similar approach with one minor addition to the original algorithm.
+In our implementation of SMOTE we have introduced an additional step called \textit{resampling}, wherein we ensure that after we do the over/under sampling, the new training data does not have any of the original rows.
+The new training data merely resembles the original data.
+This is done as a precautionary measure, so as not to have WHAT and Random Forest train on the same training data.
+%Its worth noting that both WHAT and Random Forest require some data to train.
+In order to prevent the two from using the same data to train, we run SMOTE by  \textit{resampling} the classes.
+Re-sampling
 
@@
 \section{Experimental Design}
-The following section describes the experiments used to measure the performance of WHAT on 10 defect data sets and 6 performance prediction data sets.
+The following section describes the experimental rig and the experiments used to measure the performance of WHAT on 10 defect data sets and 6 performance prediction data sets.
+
+\begin{figure}[tbp!]
+  \subfloat[][\label{oracle}]{\includegraphics[width=\linewidth]{./_figs/Oracle}}\\
+  \subfloat[][\label{what}]{\includegraphics[width=\linewidth]{./_figs/WHAT}}
+  \caption{(a) The defect prediction oracle, (b) The Planning scheme}
+  \label{fig:rig}
+\end{figure}
+
+%involves two key components. Firstly, there is the oracle (Random Forest with SMOTE) which is used to make predictions. Then we have the 
 \subsection{Data sets}
 The data was obtained from the PROMISE repository.
-For the defect data we investigated 32 releases from 11 open source Java projects defined by the metrics highlighted in \ref{}: \keyword{Apache Ant} (1.5 -- 1.7), \keyword{Apache Camel} (1.2 -- 1.6), \keyword{Apache Ivy} (1.1 -- 2.0), \keyword{JEdit} (4.1 -- 4.3), \keyword{Apache Log4j} (1.0 -- 1.2), \keyword{Apache Lucene} (2.0 -- 2.2), \keyword{PBeans} (1.0 and 2.0), \keyword{Apache POI} (2.0 -- 3.0), \keyword{Apache Synapse} (1.0 -- 1.2), \keyword{Apache Velocity} (1.4 -- 1.6), and \keyword{Apache Xalan-Java} (2.5 -- 2.7).
-Given the empirical nature of the data, it is important to design an experiment such that the planning phase uses only the \keyword{past} data to learn trends which can then be applied to the \keyword{future} data.
+For the defect data we investigated 32 releases from 11 open source Java projects defined by the metrics highlighted in Fig.~\ref{fig:ck}: \kw{Apache Ant} (1.5 -- 1.7), \kw{Apache Camel} (1.2 -- 1.6), \kw{Apache Ivy} (1.1 -- 2.0), \kw{JEdit} (4.1 -- 4.3), \kw{Apache Log4j} (1.0 -- 1.2), \kw{Apache Lucene} (2.0 -- 2.2), \kw{PBeans} (1.0 and 2.0), \kw{Apache POI} (2.0 -- 3.0), \kw{Apache Synapse} (1.0 -- 1.2), \kw{Apache Velocity} (1.4 -- 1.6), and \kw{Apache Xalan-Java} (2.5 -- 2.7).
+Given the empirical nature of the data, it is important to design an experiment such that the planning phase uses only the \kw{past} data to learn trends which can then be applied to the \kw{future} data.
 Thus for our experiment we use data sets that have at least two consecutive releases.
@@
 
-The performance prediction data set was obtained from \cite{}.
-The data set contains six examples of real world configurable systems: \keyword{Apache}, \keyword{LLVM}, \keyword{x264}, \keyword{Berkeley DB (written in C and Java}, and \keyword{SQLite}.
+The performance prediction data set was obtained from~\cite{}.
+The data set contains six examples of real world configurable systems: \kw{Apache}, \kw{LLVM}, \kw{x264}, \kw{Berkeley DB (written in C and Java}, and \kw{SQLite}.
 The systems have different characteristics, different implementation languages, and different configuration mechanisms.
@@
 We performed a 5-fold cross validation study on this data set.
+
+\subsection{The Rig}
+
+The experimental rig is shown in Figure \ref{fig:rig}.
+It uses an \textit{oracle} to determine wether a certain test case is defective or not.
+If the oracle suggests that an instance is defective, then we use WHAT to apply the recommendations to that test instance.
+The oracle is used to check if the recommendation helped subdue the defect.
 
@@
 In addition to the above, we rank the different variants of the planning scheme to identify the best approach.
-We make use of the Scott-Knott procedure, recommended by \cite{} to compute the ranks.
+We make use of the Scott-Knott procedure, recommended by Mittas \& Angelis in their 2013 IEEE TSE paper~\cite{sk}, to compute the ranks.
 It works as follows: A list of treatments \textit{l} is sorted by the median score.
@@
 If so, Skott-Knott then recurses on each division.
-In our paper, we use the A12 test and a non-parametric bootstrap sampling for hypothesis testing.
+
+The research conducted by Shepperd and MacDonell~\cite{}, Kampenes~\cite{} and Kocaguenli et al.~\cite{}, highlighted that an ``effect size'' in lieu of a mere hypothesis test is required in order to verfiy if two populations are ``significantly'' different.
+An ICSE'11 paper by Arcuri~\cite{} endorsed the use of Vargha and Delaney's A12 effect size for reporting results in software engineering.
+Thus, for hypothesis testing H in Skott-Knott, we use the A12 test and a non-parametric bootstrap sampling~\cite{}.
+
 \section{Experimental Results}
@@
 % \section*{Acknowledgements}
-%\begin{thebibliography}{10}
-%\bibitem{test}
-%\end{thebibliography}
+
+\bibliography{References}{}
+\bibliographystyle{IEEEtran}
 \end{document}

### 2015-04-09 manuscript.tex
Updates from ShareLaTeX

--- 2015-04-09 manuscript.tex
@@
 \usepackage{algpseudocode}
+\usepackage{tabulary}
+\usepackage{bigstrut}
 \setlength\fboxsep{1pt}
@@
 \usepackage{flushend}
+\usepackage[english]{babel}
+\usepackage{blindtext}
 \usepackage{times}
@@
 \begin{tabular}{|p{.95\linewidth}|}\hline
-WHAT begins by \textit{clustering} the training data into similar subsets using WHERE which works as follows:
+WHAT begins by \textit{clustering} the training data into similar subsets using WHERE. It works as follows:
 \begin{enumerate}
-\item Find two distant points in that population; call them the {\em east} and {\em west} poles. 
+\item Find the two most distant points in a given population; say {\em east} and {\em west}. 
 \item Draw an axis of length $c$ between the poles. 
@@
 \item Find the objective scores of the {\em east,west} poles in each neighborhood.
-\item Using the continuous domination predicate of MOEA, find  the {\em better} pole. 
+\item Using the continuous domination predicate of \fig{moea}, find  the {\em better} pole. 
 \item Perturb all points in that neighborhood by pushing them towards the better pole, by a distance  $c/2$ (recall that  $c$ is the distance between the poles).

### 2015-04-10 manuscript.tex
Updates from ShareLaTeX

--- 2015-04-09 manuscript.tex
@@
 \usepackage{subfig}
+\usepackage{times}
 \usepackage{algorithm}
@@
 \begin{document}
-  \title{An Instance Based Reasoning for Empirical Transfer Learning}
+  \title{``Don't tell me what is, tell me what to do'':\\Instance-Based Planning for Actionable Analytics}
 
-  \author{\IEEEauthorblockN{Rahul Krishna}
+  \author{\IEEEauthorblockN{Rahul Krishna, Tim Menzies, Xipeng Sheng}
     \IEEEauthorblockA{
-      North Carolina State University, USA\\
-      rkrish11@ncsu.edu}
-    \and
-    \IEEEauthorblockN{Tim Menzies}
-    \IEEEauthorblockA{North Carolina State University, USA\\
-      tim.menzies@gmail.com}}
+      Computer Science, North Carolina State University, USA\\
+  i.m.ralk, tim.menzies, xipengshen@gmail.com}\and
+  \IEEEauthorblockN{Andrian Marcus}
+   \IEEEauthorblockA{
+      Computer Science, University of Texas, Dallas,  USA\\
+  amarcus@utdallas.edu}}
 
@@
 \begin{enumerate}
-\item Find two distant points in that population; call them the {\em east} and {\em west} poles. 
+\item Find the two most distant points in a given population; say {\em east} and {\em west}. 
 \item Draw an axis of length $c$ between the poles. 

### 2015-04-12 manuscript.tex
Updates from ShareLaTeX

@@
   \title{``Don't tell me what is, tell me what to do'':\\Instance-Based Planning for Actionable Analytics}
-
-  \author{\IEEEauthorblockN{Rahul Krishna, Tim Menzies, Xipeng Sheng}
-    \IEEEauthorblockA{
-      Computer Science, North Carolina State University, USA\\
-  i.m.ralk, tim.menzies, xipengshen@gmail.com}\and
-  \IEEEauthorblockN{Andrian Marcus}
-   \IEEEauthorblockA{
-      Computer Science, University of Texas, Dallas,  USA\\
-  amarcus@utdallas.edu}}
 
@@
     1 &     Baseline &    0.03  &  0.0 & \quart{0}{0}{0}{62} \\
-    \hline  2 & $\alpha=0.25$, Prune=50\% &    0.15  &  0.09 & \quart{4}{6}{7}{62} \\
-    \hline  3 & $\alpha=0.5$, Prune=50\% &    0.25  &  0.1 & \quart{12}{6}{14}{62} \\
-    \hline  4 &     $\alpha=0.25$ &    0.34  &  0.05 & \quart{18}{4}{20}{62} \\
-    4 &   $\alpha=0.25$, weight &    0.36  &  0.08 & \quart{18}{5}{21}{62} \\
-    4 & $\alpha=0.75$, Prune=50\% &    0.41  &  0.13 & \quart{21}{8}{24}{62} \\
-    \hline  5 &    $\alpha=0.5$, weight &    0.46  &  0.18 & \quart{24}{12}{27}{62} \\
-    5 &      $\alpha=0.5$ &    0.53  &  0.15 & \quart{27}{10}{32}{62} \\
-    \hline  6 &     $\alpha=0.75$ &    0.64  &  0.17 & \quart{34}{11}{39}{62} \\
-    6 &   $\alpha=0.75$, weight &    0.73  &  0.17 & \quart{38}{11}{45}{62} \\
+    \hline  2 & $0.25$, Prune=50\% &    0.15  &  0.09 & \quart{4}{6}{7}{62} \\
+    \hline  3 & $0.5$, Prune=50\% &    0.25  &  0.1 & \quart{12}{6}{14}{62} \\
+    \hline  4 &     $0.25$ &    0.34  &  0.05 & \quart{18}{4}{20}{62} \\
+    4 &   $0.25$, weight &    0.36  &  0.08 & \quart{18}{5}{21}{62} \\
+    4 & $0.75$, Prune=50\% &    0.41  &  0.13 & \quart{21}{8}{24}{62} \\
+    \hline  5 &    $0.5$, weight &    0.46  &  0.18 & \quart{24}{12}{27}{62} \\
+    5 &      $0.5$ &    0.53  &  0.15 & \quart{27}{10}{32}{62} \\
+    \hline  6 &     $0.75$ &    0.64  &  0.17 & \quart{34}{11}{39}{62} \\
+    6 &   $0.75$, weight &    0.73  &  0.17 & \quart{38}{11}{45}{62} \\
     \hline \end{tabular}\\}
@@
 1 &   Baseline &    0.16  &  0.03 & \quart{0}{3}{1}{111} \\
-1 &   $\alpha=0.25$ &    0.17  &  0.06 & \quart{0}{7}{2}{111} \\
-1 & $\alpha=0.25$, weight &    0.17  &  0.06 & \quart{0}{7}{2}{111} \\
-\hline  2 & $\alpha=0.25$, Prune=50\% &    0.22  &  0.06 & \quart{5}{8}{9}{111} \\
-\hline  3 &    $\alpha=0.5$ &    0.25  &  0.1 & \quart{3}{14}{13}{111} \\
-3 &  $\alpha=0.5$, weight &    0.26  &  0.14 & \quart{7}{19}{14}{111} \\
-\hline  4 & $\alpha=0.5$, Prune=50\% &    0.32  &  0.16 & \quart{10}{21}{22}{111} \\
-\hline  5 & $\alpha=0.75$, weight &    0.38  &  0.19 & \quart{14}{25}{30}{111} \\
-5 &   $\alpha=0.75$ &    0.4  &  0.12 & \quart{23}{16}{32}{111} \\
-\hline  6 & $\alpha=0.75$, Prune=50\% &    0.47  &  0.15 & \quart{30}{19}{42}{111} \\
+1 &   $0.25$ &    0.17  &  0.06 & \quart{0}{7}{2}{111} \\
+1 & $0.25$, weight &    0.17  &  0.06 & \quart{0}{7}{2}{111} \\
+\hline  2 & $0.25$, Prune=50\% &    0.22  &  0.06 & \quart{5}{8}{9}{111} \\
+\hline  3 &    $0.5$ &    0.25  &  0.1 & \quart{3}{14}{13}{111} \\
+3 &  $0.5$, weight &    0.26  &  0.14 & \quart{7}{19}{14}{111} \\
+\hline  4 & $0.5$, Prune=50\% &    0.32  &  0.16 & \quart{10}{21}{22}{111} \\
+\hline  5 & $0.75$, weight &    0.38  &  0.19 & \quart{14}{25}{30}{111} \\
+5 &   $0.75$ &    0.4  &  0.12 & \quart{23}{16}{32}{111} \\
+\hline  6 & $0.75$, Prune=50\% &    0.47  &  0.15 & \quart{30}{19}{42}{111} \\
 \hline \end{tabular}}\\
@@
         1 &     Baseline &    0.06  &  0.0 & \quart{0}{0}{0}{79} \\
-        \hline  2 & $\alpha=0.25$, Prune=50\% &    0.14  &  0.04 & \quart{4}{3}{6}{79} \\
-        \hline  3 & $\alpha=0.5$, Prune=50\% &    0.2  &  0.06 & \quart{9}{5}{11}{79} \\
-        \hline  4 & $\alpha=0.75$, Prune=50\% &    0.27  &  0.14 & \quart{10}{12}{17}{79} \\
-        \hline  5 &     $\alpha=0.25$ &    0.41  &  0.06 & \quart{27}{5}{29}{79} \\
-        5 &   $\alpha=0.25$, weight &    0.42  &  0.06 & \quart{27}{6}{30}{79} \\
-        \hline  6 &    $\alpha=0.5$, weight &    0.55  &  0.11 & \quart{35}{9}{41}{79} \\
-        6 &      $\alpha=0.5$ &    0.57  &  0.09 & \quart{37}{7}{43}{79} \\
-        \hline  7 &   $\alpha=0.75$, weight &    0.61  &  0.08 & \quart{42}{7}{46}{79} \\
-        7 &     $\alpha=0.75$ &    0.62  &  0.04 & \quart{46}{3}{47}{79} \\
+        \hline  2 & $0.25$, Prune=50\% &    0.14  &  0.04 & \quart{4}{3}{6}{79} \\
+        \hline  3 & $0.5$, Prune=50\% &    0.2  &  0.06 & \quart{9}{5}{11}{79} \\
+        \hline  4 & $0.75$, Prune=50\% &    0.27  &  0.14 & \quart{10}{12}{17}{79} \\
+        \hline  5 &     $0.25$ &    0.41  &  0.06 & \quart{27}{5}{29}{79} \\
+        5 &   $0.25$, weight &    0.42  &  0.06 & \quart{27}{6}{30}{79} \\
+        \hline  6 &    $0.5$, weight &    0.55  &  0.11 & \quart{35}{9}{41}{79} \\
+        6 &      $0.5$ &    0.57  &  0.09 & \quart{37}{7}{43}{79} \\
+        \hline  7 &   $0.75$, weight &    0.61  &  0.08 & \quart{42}{7}{46}{79} \\
+        7 &     $0.75$ &    0.62  &  0.04 & \quart{46}{3}{47}{79} \\
         \hline \end{tabular}}\\
@@
       1 &   Baseline &    0.05  &  0.0 & \quart{0}{0}{0}{75} \\
-      \hline  2 & $\alpha=0.25$, Prune=50\% &    0.11  &  0.05 & \quart{2}{4}{4}{75} \\
-      \hline  3 & $\alpha=0.5$, Prune=50\% &    0.16  &  0.1 & \quart{3}{8}{8}{75} \\
-      \hline  4 &   $\alpha=0.25$ &    0.2  &  0.08 & \quart{10}{6}{11}{75} \\
-      4 & $\alpha=0.25$, weight &    0.21  &  0.1 & \quart{7}{8}{12}{75} \\
-      \hline  5 & $\alpha=0.75$, Prune=50\% &    0.32  &  0.15 & \quart{15}{11}{21}{75} \\
-      5 &  $\alpha=0.5$, weight &    0.33  &  0.05 & \quart{19}{4}{22}{75} \\
-      5 &    $\alpha=0.5$ &    0.34  &  0.18 & \quart{18}{14}{23}{75} \\
-      \hline  6 &   $\alpha=0.75$ &    0.56  &  0.2 & \quart{27}{16}{40}{75} \\
-      6 & $\alpha=0.75$, weight &    0.56  &  0.26 & \quart{29}{20}{40}{75} \\
+      \hline  2 & $0.25$, Prune=50\% &    0.11  &  0.05 & \quart{2}{4}{4}{75} \\
+      \hline  3 & $0.5$, Prune=50\% &    0.16  &  0.1 & \quart{3}{8}{8}{75} \\
+      \hline  4 &   $0.25$ &    0.2  &  0.08 & \quart{10}{6}{11}{75} \\
+      4 & $0.25$, weight &    0.21  &  0.1 & \quart{7}{8}{12}{75} \\
+      \hline  5 & $0.75$, Prune=50\% &    0.32  &  0.15 & \quart{15}{11}{21}{75} \\
+      5 &  $0.5$, weight &    0.33  &  0.05 & \quart{19}{4}{22}{75} \\
+      5 &    $0.5$ &    0.34  &  0.18 & \quart{18}{14}{23}{75} \\
+      \hline  6 &   $0.75$ &    0.56  &  0.2 & \quart{27}{16}{40}{75} \\
+      6 & $0.75$, weight &    0.56  &  0.26 & \quart{29}{20}{40}{75} \\
       \hline \end{tabular}}\\
@@
       \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
-      1 & $\alpha=0.5$, Prune=50\% &    0.1  &  0.06 & \quart{1}{11}{5}{172} \\
-      1 & $\alpha=0.25$, Prune=50\% &    0.11  &  0.04 & \quart{1}{8}{7}{172} \\
-      1 & $\alpha=0.25$, weight &    0.1  &  0.03 & \quart{3}{6}{5}{172} \\
-      1 &  $\alpha=0.5$, weight &    0.1  &  0.13 & \quart{0}{24}{5}{172} \\
+      1 & $0.5$, Prune=50\% &    0.1  &  0.06 & \quart{1}{11}{5}{172} \\
+      1 & $0.25$, Prune=50\% &    0.11  &  0.04 & \quart{1}{8}{7}{172} \\
+      1 & $0.25$, weight &    0.1  &  0.03 & \quart{3}{6}{5}{172} \\
+      1 &  $0.5$, weight &    0.1  &  0.13 & \quart{0}{24}{5}{172} \\
       1 &   Baseline &    0.11  &  0.04 & \quart{0}{7}{7}{172} \\
-      1 &   $\alpha=0.25$ &    0.12  &  0.06 & \quart{1}{11}{9}{172} \\
-      \hline  2 &    $\alpha=0.5$ &    0.15  &  0.09 & \quart{3}{17}{14}{172} \\
-      2 & $\alpha=0.75$, Prune=50\% &    0.15  &  0.05 & \quart{9}{9}{14}{172} \\
-      2 & $\alpha=0.75$, weight &    0.17  &  0.22 & \quart{9}{40}{18}{172} \\
-      2 &   $\alpha=0.75$ &    0.22  &  0.16 & \quart{14}{30}{27}{172} \\
+      1 &   $0.25$ &    0.12  &  0.06 & \quart{1}{11}{9}{172} \\
+      \hline  2 &    $0.5$ &    0.15  &  0.09 & \quart{3}{17}{14}{172} \\
+      2 & $0.75$, Prune=50\% &    0.15  &  0.05 & \quart{9}{9}{14}{172} \\
+      2 & $0.75$, weight &    0.17  &  0.22 & \quart{9}{40}{18}{172} \\
+      2 &   $0.75$ &    0.22  &  0.16 & \quart{14}{30}{27}{172} \\
       \hline \end{tabular}}\\
@@
     \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
-    1 & $\alpha=0.25$, weight &    0.03  &  0.03 & \quart{0}{4}{1}{148} \\
-    1 &  $\alpha=0.25$ &    0.05  &  0.04 & \quart{1}{6}{4}{148} \\
-    \hline  2 &   $\alpha=0.5$ &    0.09  &  0.09 & \quart{6}{13}{10}{148} \\
-    2 & $\alpha=0.25$, Prune=50\% &    0.09  &  0.03 & \quart{7}{5}{10}{148} \\
+    1 & $0.25$, weight &    0.03  &  0.03 & \quart{0}{4}{1}{148} \\
+    1 &  $0.25$ &    0.05  &  0.04 & \quart{1}{6}{4}{148} \\
+    \hline  2 &   $0.5$ &    0.09  &  0.09 & \quart{6}{13}{10}{148} \\
+    2 & $0.25$, Prune=50\% &    0.09  &  0.03 & \quart{7}{5}{10}{148} \\
     2 &  Baseline &    0.1  &  0.01 & \quart{10}{2}{12}{148} \\
-    2 & $\alpha=0.5$, weight &    0.14  &  0.06 & \quart{10}{9}{18}{148} \\
-    \hline  3 & $\alpha=0.5$, Prune=50\% &    0.19  &  0.08 & \quart{21}{12}{25}{148} \\
-    \hline  4 & $\alpha=0.75$, weight &    0.23  &  0.15 & \quart{22}{23}{31}{148} \\
-    4 &  $\alpha=0.75$ &    0.26  &  0.1 & \quart{27}{15}{36}{148} \\
-    4 & $\alpha=0.75$, Prune=50\% &    0.28  &  0.13 & \quart{30}{19}{39}{148} \\\hline \end{tabular}}\\
+    2 & $0.5$, weight &    0.14  &  0.06 & \quart{10}{9}{18}{148} \\
+    \hline  3 & $0.5$, Prune=50\% &    0.19  &  0.08 & \quart{21}{12}{25}{148} \\
+    \hline  4 & $0.75$, weight &    0.23  &  0.15 & \quart{22}{23}{31}{148} \\
+    4 &  $0.75$ &    0.26  &  0.1 & \quart{27}{15}{36}{148} \\
+    4 & $0.75$, Prune=50\% &    0.28  &  0.13 & \quart{30}{19}{39}{148} \\\hline \end{tabular}}\\
 
@@
     \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
-    1 & $\alpha=0.25$, Prune=50\% &    0.09  &  0.15 & \quart{0}{9}{3}{62} \\
+    1 & $0.25$, Prune=50\% &    0.09  &  0.15 & \quart{0}{9}{3}{62} \\
     1 &     Baseline &    0.09  &  0.05 & \quart{2}{3}{3}{62} \\
-    1 & $\alpha=0.5$, Prune=50\% &    0.12  &  0.13 & \quart{1}{8}{5}{62} \\
-    \hline  2 &     $\alpha=0.25$ &    0.24  &  0.3 & \quart{5}{19}{13}{62} \\
-    2 &   $\alpha=0.25$, weight &    0.25  &  0.32 & \quart{4}{20}{14}{62} \\
-    \hline  3 & $\alpha=0.75$, Prune=50\% &    0.37  &  0.45 & \quart{4}{29}{21}{62} \\
-    3 &    $\alpha=0.5$, weight &    0.49  &  0.5 & \quart{9}{32}{29}{62} \\
-    \hline  4 &     $\alpha=0.75$ &    0.53  &  0.47 & \quart{16}{30}{32}{62} \\
-    4 &      $\alpha=0.5$ &    0.53  &  0.28 & \quart{18}{18}{32}{62} \\
-    4 &   $\alpha=0.75$, weight &    0.61  &  0.43 & \quart{22}{27}{37}{62} \\
+    1 & $0.5$, Prune=50\% &    0.12  &  0.13 & \quart{1}{8}{5}{62} \\
+    \hline  2 &     $0.25$ &    0.24  &  0.3 & \quart{5}{19}{13}{62} \\
+    2 &   $0.25$, weight &    0.25  &  0.32 & \quart{4}{20}{14}{62} \\
+    \hline  3 & $0.75$, Prune=50\% &    0.37  &  0.45 & \quart{4}{29}{21}{62} \\
+    3 &    $0.5$, weight &    0.49  &  0.5 & \quart{9}{32}{29}{62} \\
+    \hline  4 &     $0.75$ &    0.53  &  0.47 & \quart{16}{30}{32}{62} \\
+    4 &      $0.5$ &    0.53  &  0.28 & \quart{18}{18}{32}{62} \\
+    4 &   $0.75$, weight &    0.61  &  0.43 & \quart{22}{27}{37}{62} \\
     \hline \end{tabular}}  \\
@@
       \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
-      1 & $\alpha=0.25$ &    0.08  &  0.03 & \quart{0}{4}{1}{140} \\
-      1 & $\alpha=0.25$, weight &    0.09  &  0.05 & \quart{0}{7}{3}{140} \\
+      1 & $0.25$ &    0.08  &  0.03 & \quart{0}{4}{1}{140} \\
+      1 & $0.25$, weight &    0.09  &  0.05 & \quart{0}{7}{3}{140} \\
       \hline  2 & Baseline &    0.13  &  0.04 & \quart{6}{6}{9}{140} \\
-      \hline  3 & $\alpha=0.5$ &    0.16  &  0.09 & \quart{9}{13}{13}{140} \\
-      3 & $\alpha=0.25$, Prune=50\% &    0.17  &  0.04 & \quart{13}{6}{15}{140} \\
-      3 & $\alpha=0.5$, weight &    0.19  &  0.09 & \quart{12}{13}{18}{140} \\
-      \hline  4 & $\alpha=0.5$, Prune=50\% &    0.22  &  0.11 & \quart{15}{16}{22}{140} \\
-      4 & $\alpha=0.75$, weight &    0.25  &  0.1 & \quart{19}{15}{27}{140} \\
-      4 & $\alpha=0.75$ &    0.28  &  0.2 & \quart{19}{30}{31}{140} \\
-      4 & $\alpha=0.75$, Prune=50\% &    0.28  &  0.09 & \quart{24}{13}{31}{140} \\
+      \hline  3 & $0.5$ &    0.16  &  0.09 & \quart{9}{13}{13}{140} \\
+      3 & $0.25$, Prune=50\% &    0.17  &  0.04 & \quart{13}{6}{15}{140} \\
+      3 & $0.5$, weight &    0.19  &  0.09 & \quart{12}{13}{18}{140} \\
+      \hline  4 & $0.5$, Prune=50\% &    0.22  &  0.11 & \quart{15}{16}{22}{140} \\
+      4 & $0.75$, weight &    0.25  &  0.1 & \quart{19}{15}{27}{140} \\
+      4 & $0.75$ &    0.28  &  0.2 & \quart{19}{30}{31}{140} \\
+      4 & $0.75$, Prune=50\% &    0.28  &  0.09 & \quart{24}{13}{31}{140} \\
       \hline \end{tabular}}\\
@@
       \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
-      1 & $\alpha=0.75$, weight &    0.31  &  0.14 & \quart{0}{31}{13}{170} \\
-      1 & $\alpha=0.25$, weight &    0.32  &  0.1 & \quart{2}{22}{15}{170} \\
-      1 &   $\alpha=0.25$ &    0.32  &  0.06 & \quart{13}{14}{15}{170} \\
-      \hline  2 &    $\alpha=0.5$ &    0.34  &  0.11 & \quart{6}{25}{20}{170} \\
+      1 & $0.75$, weight &    0.31  &  0.14 & \quart{0}{31}{13}{170} \\
+      1 & $0.25$, weight &    0.32  &  0.1 & \quart{2}{22}{15}{170} \\
+      1 &   $0.25$ &    0.32  &  0.06 & \quart{13}{14}{15}{170} \\
+      \hline  2 &    $0.5$ &    0.34  &  0.11 & \quart{6}{25}{20}{170} \\
       2 &   Baseline &    0.36  &  0.13 & \quart{4}{30}{24}{170} \\
-      2 &  $\alpha=0.5$, weight &    0.35  &  0.12 & \quart{6}{28}{22}{170} \\
-      2 & $\alpha=0.5$, Prune=50\% &    0.36  &  0.12 & \quart{11}{27}{24}{170} \\
-      2 & $\alpha=0.25$, Prune=50\% &    0.38  &  0.1 & \quart{13}{23}{29}{170} \\
-      2 & $\alpha=0.75$, Prune=50\% &    0.37  &  0.21 & \quart{2}{47}{27}{170} \\
-      2 &   $\alpha=0.75$ &    0.38  &  0.17 & \quart{6}{39}{29}{170} \\
+      2 &  $0.5$, weight &    0.35  &  0.12 & \quart{6}{28}{22}{170} \\
+      2 & $0.5$, Prune=50\% &    0.36  &  0.12 & \quart{11}{27}{24}{170} \\
+      2 & $0.25$, Prune=50\% &    0.38  &  0.1 & \quart{13}{23}{29}{170} \\
+      2 & $0.75$, Prune=50\% &    0.37  &  0.21 & \quart{2}{47}{27}{170} \\
+      2 &   $0.75$ &    0.38  &  0.17 & \quart{6}{39}{29}{170} \\
       \hline \end{tabular}}

### 2015-04-14 manuscript.tex
Updates from ShareLaTeX

@@
 \newcommand{\kw}[1]{\textit{#1}}
-\newcommand{\quart}[4]{\begin{picture}(50,3)
+\newcommand{\quart}[4]{\begin{picture}(75,6)
   {\color{black}\put(#3,3){\circle*{4}}\put(#1,3){\line(1,0){#2}}}\end{picture}}
@@
 \begin{document}
-  \title{``Don't tell me what is, tell me what to do'':\\Instance-Based Planning for Actionable Analytics}
+  \title{``Don't tell me what it is, tell me what to do'':\\Instance-Based Planning for Actionable Analytics}
 
@@
 WHERE is a spectral learner which uses the FastMap heuristic to estimate the first principal component.
-It then recursively partitions the data into two halves along the median point of the projection on the first principal component, terminating when a half has less than $\sqrt{N}$ items.
+It then recursively partitions the data into two halves along the Medianian point of the projection on the first principal component, terminating when a half has less than $\sqrt{N}$ items.
 
@@
 \item Let each point be at distance $a,b$ to the {\em east,west} poles.  Using the cosine rule, project each point onto the  axis  at $x=(a^2 + c^2 - b^2)/(2c)$.  
-\item Using the median $x$ value, divide the population.
+\item Using the Medianian $x$ value, divide the population.
 \item For each half that is larger than $\sqrt{N}$ of the original population, go to step 1.
@@
 Formally, WHAT can be considered as an instance based  learning scheme.
-And that's beacuse it builds a set of recommendations based on a given test case based on the clusters formed at the training stage.
+And that's beacuse it builds a set of recommendations based on a given test case based on the clusters forMedian at the training stage.
 This is unlike a model based approach, which would have used a model to do the same~\cite{xomo}.
@@
 The data set is a collection of all possible configurations (with SQLITE being a exception with only 4653 configurations).
-We performed a 5-fold cross validation study on this data set.
+We perforMedian a 5-fold cross validation study on this data set.
 
@@
 We make use of the Scott-Knott procedure, recommended by Mittas \& Angelis in their 2013 IEEE TSE paper~\cite{sk}, to compute the ranks.
-It works as follows: A list of treatments \textit{l} is sorted by the median score.
+It works as follows: A list of treatments \textit{l} is sorted by the Medianian score.
 The list \textit{l} is then split into sub-lists m, n in order to maximize the expected value of the differences in the observed performance before and after division.
@@
 \centering
-\begin{minipage}{0.5\textwidth}
-\renewcommand{\baselinestretch}{}
-{\bf \scriptsize Ant:}
+\includegraphics[width=\linewidth]{_figs/Histogram}
+\caption{Caption}
+\label{fig:bugs}
+\end{figure}
 
-{\scriptsize \begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
+\begin{figure*}[!t]
+
+\noindent\begin{minipage}{0.5\textwidth}
+  {\scriptsize \textbf{Ant}\\}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
       \arrayrulecolor{darkgray}
-      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
-    1 &     Baseline &    0.03  &  0.0 & \quart{0}{0}{0}{62} \\
-    \hline  2 & $0.25$, Prune=50\% &    0.15  &  0.09 & \quart{4}{6}{7}{62} \\
-    \hline  3 & $0.5$, Prune=50\% &    0.25  &  0.1 & \quart{12}{6}{14}{62} \\
-    \hline  4 &     $0.25$ &    0.34  &  0.05 & \quart{18}{4}{20}{62} \\
-    4 &   $0.25$, weight &    0.36  &  0.08 & \quart{18}{5}{21}{62} \\
-    4 & $0.75$, Prune=50\% &    0.41  &  0.13 & \quart{21}{8}{24}{62} \\
-    \hline  5 &    $0.5$, weight &    0.46  &  0.18 & \quart{24}{12}{27}{62} \\
-    5 &      $0.5$ &    0.53  &  0.15 & \quart{27}{10}{32}{62} \\
-    \hline  6 &     $0.75$ &    0.64  &  0.17 & \quart{34}{11}{39}{62} \\
-    6 &   $0.75$, weight &    0.73  &  0.17 & \quart{38}{11}{45}{62} \\
-    \hline \end{tabular}\\}
-
-{\bf \scriptsize Camel}
-
-{\scriptsize \begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
-    \arrayrulecolor{darkgray}
-    \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
-1 &   Baseline &    0.16  &  0.03 & \quart{0}{3}{1}{111} \\
-1 &   $0.25$ &    0.17  &  0.06 & \quart{0}{7}{2}{111} \\
-1 & $0.25$, weight &    0.17  &  0.06 & \quart{0}{7}{2}{111} \\
-\hline  2 & $0.25$, Prune=50\% &    0.22  &  0.06 & \quart{5}{8}{9}{111} \\
-\hline  3 &    $0.5$ &    0.25  &  0.1 & \quart{3}{14}{13}{111} \\
-3 &  $0.5$, weight &    0.26  &  0.14 & \quart{7}{19}{14}{111} \\
-\hline  4 & $0.5$, Prune=50\% &    0.32  &  0.16 & \quart{10}{21}{22}{111} \\
-\hline  5 & $0.75$, weight &    0.38  &  0.19 & \quart{14}{25}{30}{111} \\
-5 &   $0.75$ &    0.4  &  0.12 & \quart{23}{16}{32}{111} \\
-\hline  6 & $0.75$, Prune=50\% &    0.47  &  0.15 & \quart{30}{19}{42}{111} \\
-\hline \end{tabular}}\\
-
-{\bf \scriptsize Ivy}
-
-    {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
-        \arrayrulecolor{darkgray}
-        \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
-        1 &     Baseline &    0.06  &  0.0 & \quart{0}{0}{0}{79} \\
-        \hline  2 & $0.25$, Prune=50\% &    0.14  &  0.04 & \quart{4}{3}{6}{79} \\
-        \hline  3 & $0.5$, Prune=50\% &    0.2  &  0.06 & \quart{9}{5}{11}{79} \\
-        \hline  4 & $0.75$, Prune=50\% &    0.27  &  0.14 & \quart{10}{12}{17}{79} \\
-        \hline  5 &     $0.25$ &    0.41  &  0.06 & \quart{27}{5}{29}{79} \\
-        5 &   $0.25$, weight &    0.42  &  0.06 & \quart{27}{6}{30}{79} \\
-        \hline  6 &    $0.5$, weight &    0.55  &  0.11 & \quart{35}{9}{41}{79} \\
-        6 &      $0.5$ &    0.57  &  0.09 & \quart{37}{7}{43}{79} \\
-        \hline  7 &   $0.75$, weight &    0.61  &  0.08 & \quart{42}{7}{46}{79} \\
-        7 &     $0.75$ &    0.62  &  0.04 & \quart{46}{3}{47}{79} \\
-        \hline \end{tabular}}\\
-
-{\bf \scriptsize Jedit}
-
-  {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
-      \arrayrulecolor{darkgray}
-      \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
-      1 &   Baseline &    0.05  &  0.0 & \quart{0}{0}{0}{75} \\
-      \hline  2 & $0.25$, Prune=50\% &    0.11  &  0.05 & \quart{2}{4}{4}{75} \\
-      \hline  3 & $0.5$, Prune=50\% &    0.16  &  0.1 & \quart{3}{8}{8}{75} \\
-      \hline  4 &   $0.25$ &    0.2  &  0.08 & \quart{10}{6}{11}{75} \\
-      4 & $0.25$, weight &    0.21  &  0.1 & \quart{7}{8}{12}{75} \\
-      \hline  5 & $0.75$, Prune=50\% &    0.32  &  0.15 & \quart{15}{11}{21}{75} \\
-      5 &  $0.5$, weight &    0.33  &  0.05 & \quart{19}{4}{22}{75} \\
-      5 &    $0.5$ &    0.34  &  0.18 & \quart{18}{14}{23}{75} \\
-      \hline  6 &   $0.75$ &    0.56  &  0.2 & \quart{27}{16}{40}{75} \\
-      6 & $0.75$, weight &    0.56  &  0.26 & \quart{29}{20}{40}{75} \\
-      \hline \end{tabular}}\\
-\end{minipage}
-\end{figure}
-\begin{figure}
-\begin{minipage}{0.5\textwidth}
-  \renewcommand{\baselinestretch}{}
-{\bf \scriptsize Log4j}
-
-  {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
-      \arrayrulecolor{darkgray}
-      \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
-      1 & $0.5$, Prune=50\% &    0.1  &  0.06 & \quart{1}{11}{5}{172} \\
-      1 & $0.25$, Prune=50\% &    0.11  &  0.04 & \quart{1}{8}{7}{172} \\
-      1 & $0.25$, weight &    0.1  &  0.03 & \quart{3}{6}{5}{172} \\
-      1 &  $0.5$, weight &    0.1  &  0.13 & \quart{0}{24}{5}{172} \\
-      1 &   Baseline &    0.11  &  0.04 & \quart{0}{7}{7}{172} \\
-      1 &   $0.25$ &    0.12  &  0.06 & \quart{1}{11}{9}{172} \\
-      \hline  2 &    $0.5$ &    0.15  &  0.09 & \quart{3}{17}{14}{172} \\
-      2 & $0.75$, Prune=50\% &    0.15  &  0.05 & \quart{9}{9}{14}{172} \\
-      2 & $0.75$, weight &    0.17  &  0.22 & \quart{9}{40}{18}{172} \\
-      2 &   $0.75$ &    0.22  &  0.16 & \quart{14}{30}{27}{172} \\
-      \hline \end{tabular}}\\
-
-{\bf \scriptsize Lucene}
-
-{\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
-    \arrayrulecolor{darkgray}
-    \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
-    1 & $0.25$, weight &    0.03  &  0.03 & \quart{0}{4}{1}{148} \\
-    1 &  $0.25$ &    0.05  &  0.04 & \quart{1}{6}{4}{148} \\
-    \hline  2 &   $0.5$ &    0.09  &  0.09 & \quart{6}{13}{10}{148} \\
-    2 & $0.25$, Prune=50\% &    0.09  &  0.03 & \quart{7}{5}{10}{148} \\
-    2 &  Baseline &    0.1  &  0.01 & \quart{10}{2}{12}{148} \\
-    2 & $0.5$, weight &    0.14  &  0.06 & \quart{10}{9}{18}{148} \\
-    \hline  3 & $0.5$, Prune=50\% &    0.19  &  0.08 & \quart{21}{12}{25}{148} \\
-    \hline  4 & $0.75$, weight &    0.23  &  0.15 & \quart{22}{23}{31}{148} \\
-    4 &  $0.75$ &    0.26  &  0.1 & \quart{27}{15}{36}{148} \\
-    4 & $0.75$, Prune=50\% &    0.28  &  0.13 & \quart{30}{19}{39}{148} \\\hline \end{tabular}}\\
-
-{\bf \scriptsize Poi}
-
-{\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
-    \arrayrulecolor{darkgray}
-    \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
-    1 & $0.25$, Prune=50\% &    0.09  &  0.15 & \quart{0}{9}{3}{62} \\
-    1 &     Baseline &    0.09  &  0.05 & \quart{2}{3}{3}{62} \\
-    1 & $0.5$, Prune=50\% &    0.12  &  0.13 & \quart{1}{8}{5}{62} \\
-    \hline  2 &     $0.25$ &    0.24  &  0.3 & \quart{5}{19}{13}{62} \\
-    2 &   $0.25$, weight &    0.25  &  0.32 & \quart{4}{20}{14}{62} \\
-    \hline  3 & $0.75$, Prune=50\% &    0.37  &  0.45 & \quart{4}{29}{21}{62} \\
-    3 &    $0.5$, weight &    0.49  &  0.5 & \quart{9}{32}{29}{62} \\
-    \hline  4 &     $0.75$ &    0.53  &  0.47 & \quart{16}{30}{32}{62} \\
-    4 &      $0.5$ &    0.53  &  0.28 & \quart{18}{18}{32}{62} \\
-    4 &   $0.75$, weight &    0.61  &  0.43 & \quart{22}{27}{37}{62} \\
-    \hline \end{tabular}}  \\
-
-{\bf \scriptsize Velocity}
-
-  {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
-      \arrayrulecolor{darkgray}
-      \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
-      1 & $0.25$ &    0.08  &  0.03 & \quart{0}{4}{1}{140} \\
-      1 & $0.25$, weight &    0.09  &  0.05 & \quart{0}{7}{3}{140} \\
-      \hline  2 & Baseline &    0.13  &  0.04 & \quart{6}{6}{9}{140} \\
-      \hline  3 & $0.5$ &    0.16  &  0.09 & \quart{9}{13}{13}{140} \\
-      3 & $0.25$, Prune=50\% &    0.17  &  0.04 & \quart{13}{6}{15}{140} \\
-      3 & $0.5$, weight &    0.19  &  0.09 & \quart{12}{13}{18}{140} \\
-      \hline  4 & $0.5$, Prune=50\% &    0.22  &  0.11 & \quart{15}{16}{22}{140} \\
-      4 & $0.75$, weight &    0.25  &  0.1 & \quart{19}{15}{27}{140} \\
-      4 & $0.75$ &    0.28  &  0.2 & \quart{19}{30}{31}{140} \\
-      4 & $0.75$, Prune=50\% &    0.28  &  0.09 & \quart{24}{13}{31}{140} \\
-      \hline \end{tabular}}\\
-
-{\bf \scriptsize Xalan}
-
-  {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
-      \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
-      1 & $0.75$, weight &    0.31  &  0.14 & \quart{0}{31}{13}{170} \\
-      1 & $0.25$, weight &    0.32  &  0.1 & \quart{2}{22}{15}{170} \\
-      1 &   $0.25$ &    0.32  &  0.06 & \quart{13}{14}{15}{170} \\
-      \hline  2 &    $0.5$ &    0.34  &  0.11 & \quart{6}{25}{20}{170} \\
-      2 &   Baseline &    0.36  &  0.13 & \quart{4}{30}{24}{170} \\
-      2 &  $0.5$, weight &    0.35  &  0.12 & \quart{6}{28}{22}{170} \\
-      2 & $0.5$, Prune=50\% &    0.36  &  0.12 & \quart{11}{27}{24}{170} \\
-      2 & $0.25$, Prune=50\% &    0.38  &  0.1 & \quart{13}{23}{29}{170} \\
-      2 & $0.75$, Prune=50\% &    0.37  &  0.21 & \quart{2}{47}{27}{170} \\
-      2 &   $0.75$ &    0.38  &  0.17 & \quart{6}{39}{29}{170} \\
+      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+      1 &     Base &    0.13  &  0.03 & \quart{0}{1}{1}{48}\\
+      \hline  2 & 0.25, weighting,  iP=50\% &    0.2  &  0.05 & \quart{3}{3}{4}{48}\\
+      \hline  3 & 0.5, weighting,  iP=50\% &    0.26  &  0.06 & \quart{6}{3}{8}{48}\\
+      \hline  4 &     0.25 &    0.3  &  0.1 & \quart{7}{6}{10}{48}\\
+      4 &   0.25&    0.3  &  0.08 & \quart{8}{4}{10}{48}\\
+      \hline  5 & 0.75, weighting,  iP=50\% &    0.42  &  0.13 & \quart{13}{7}{17}{48}\\
+      5 &      0.5 &    0.43  &  0.1 & \quart{14}{6}{17}{48}\\
+      5 &    0.5&    0.43  &  0.1 & \quart{15}{5}{17}{48}\\
+      \hline  6 &   0.75&    0.64  &  0.19 & \quart{22}{10}{29}{48}\\
+      6 &     0.75 &    0.63  &  0.08 & \quart{26}{4}{28}{48}\\
       \hline \end{tabular}}
 \end{minipage}
-   \end{figure}
+\noindent\begin{minipage}{0.5\textwidth}
+  \flushleft
+  {\scriptsize \textbf{Camel}\\}
+{\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+  1 &   Base &    0.15  &  0.05 & \quart{0}{4}{1}{75}\\
+\hline  2 &   0.25 &    0.18  &  0.06 & \quart{1}{5}{4}{75}\\
+  2 & 0.25&    0.2  &  0.06 & \quart{2}{5}{6}{75}\\
+  2 & 0.25, weighting,  iP=50\% &    0.2  &  0.04 & \quart{4}{3}{6}{75}\\
+\hline  3 &  0.5&    0.25  &  0.1 & \quart{6}{9}{10}{75}\\
+  3 &    0.5 &    0.26  &  0.12 & \quart{6}{11}{11}{75}\\
+  3 & 0.5, weighting,  iP=50\% &    0.28  &  0.11 & \quart{10}{9}{13}{75}\\
+\hline  4 & 0.75&    0.39  &  0.16 & \quart{19}{13}{22}{75}\\
+  4 &   0.75 &    0.42  &  0.17 & \quart{15}{15}{25}{75}\\
+  4 & 0.75, weighting,  iP=50\% &    0.42  &  0.1 & \quart{20}{9}{25}{75}\\
+\hline \end{tabular}}
+\end{minipage}
+
+\noindent\begin{minipage}{0.5\textwidth}
+  \flushleft
+  {\scriptsize \textbf{Ivy}\\[-0.05cm]}
+{\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+  1 & 0.25, weighting,  iP=50\% &    0.15  &  0.04 & \quart{0}{2}{0}{55}\\
+\hline  2 &     Base &    0.16  &  0.0 & \quart{1}{0}{1}{55}\\
+  2 &     0.25 &    0.18  &  0.06 & \quart{1}{4}{2}{55}\\
+  2 &   0.25&    0.2  &  0.06 & \quart{1}{4}{3}{55}\\
+\hline  3 & 0.5, weighting,  iP=50\% &    0.28  &  0.08 & \quart{7}{5}{9}{55}\\
+\hline  4 &      0.5 &    0.33  &  0.11 & \quart{8}{7}{12}{55}\\
+  4 &    0.5&    0.37  &  0.09 & \quart{10}{6}{14}{55}\\
+\hline  5 & 0.75, weighting,  iP=50\% &    0.38  &  0.16 & \quart{12}{10}{15}{55}\\
+\hline  6 &   0.75&    0.56  &  0.08 & \quart{25}{5}{27}{55}\\
+  6 &     0.75 &    0.57  &  0.12 & \quart{25}{7}{27}{55}\\[-0.01cm]
+\hline \end{tabular}}
+\end{minipage}
+\noindent\begin{minipage}{0.5\textwidth}
+  \flushleft
+  {\scriptsize \textbf{Jedit}\\}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+  1 &   Base &    0.06  &  0.01 & \quart{0}{0}{0}{64}\\
+\hline  2 & 0.25&    0.08  &  0.06 & \quart{0}{4}{1}{64}\\
+  2 &   0.25 &    0.09  &  0.05 & \quart{0}{3}{2}{64}\\
+\hline  3 & 0.25, weighting,  iP=50\% &    0.12  &  0.08 & \quart{1}{5}{4}{64}\\
+\hline  4 &  0.5&    0.16  &  0.09 & \quart{4}{6}{6}{64}\\
+  4 &    0.5 &    0.17  &  0.09 & \quart{4}{6}{7}{64}\\
+\hline  5 & 0.5, weighting,  iP=50\% &    0.22  &  0.11 & \quart{8}{8}{10}{64}\\
+  5 & 0.75&    0.26  &  0.18 & \quart{9}{12}{13}{64}\\
+\hline  6 &   0.75 &    0.38  &  0.31 & \quart{11}{21}{21}{64}\\
+  6 & 0.75, weighting,  iP=50\% &    0.41  &  0.17 & \quart{17}{12}{24}{64}\\
+\hline \end{tabular}}
+\end{minipage}
+
+\noindent\begin{minipage}{0.5\textwidth}
+  \flushleft
+  {\scriptsize \textbf{Log4j}\\}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+  1 &   Base &    0.06  &  0.03 & \quart{0}{4}{4}{139}\\
+\hline  2 & 0.25&    0.09  &  0.04 & \quart{4}{6}{8}{139}\\
+  2 &   0.25 &    0.09  &  0.06 & \quart{4}{8}{8}{139}\\
+  2 & 0.25, weighting,  iP=50\% &    0.09  &  0.04 & \quart{4}{6}{8}{139}\\
+  2 &    0.5 &    0.1  &  0.07 & \quart{4}{10}{10}{139}\\
+\hline  3 &  0.5&    0.12  &  0.03 & \quart{10}{4}{12}{139}\\
+\hline  4 & 0.75&    0.13  &  0.11 & \quart{10}{15}{14}{139}\\
+  4 &   0.75 &    0.13  &  0.06 & \quart{12}{9}{14}{139}\\
+  4 & 0.5, weighting,  iP=50\% &    0.13  &  0.06 & \quart{10}{8}{14}{139}\\
+\hline  5 & 0.75, weighting,  iP=50\% &    0.19  &  0.11 & \quart{17}{15}{22}{139}\\
+\hline \end{tabular}}
+\end{minipage}
+\noindent\begin{minipage}{0.5\textwidth}
+  \flushleft
+  {\scriptsize \textbf{Lucene}\\}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+  1 &  0.25 &    0.05  &  0.02 & \quart{1}{4}{3}{188}\\
+  1 & 0.25&    0.05  &  0.04 & \quart{0}{7}{3}{188}\\
+\hline  2 &   0.5 &    0.07  &  0.04 & \quart{3}{8}{7}{188}\\
+  2 & 0.25, weighting,  iP=50\% &    0.07  &  0.04 & \quart{3}{8}{7}{188}\\
+  2 & 0.5&    0.08  &  0.05 & \quart{5}{10}{9}{188}\\
+\hline  3 & 0.5, weighting,  iP=50\% &    0.1  &  0.03 & \quart{9}{6}{13}{188}\\
+  3 &  Base &    0.1  &  0.03 & \quart{7}{6}{13}{188}\\
+\hline  4 & 0.75, weighting,  iP=50\% &    0.13  &  0.09 & \quart{9}{18}{19}{188}\\
+  4 &  0.75 &    0.15  &  0.08 & \quart{13}{16}{23}{188}\\
+  4 & 0.75&    0.15  &  0.11 & \quart{11}{21}{23}{188}\\
+\hline \end{tabular}}
+\end{minipage}
+
+\noindent\begin{minipage}{0.5\textwidth}
+  \flushleft
+  {\scriptsize \textbf{Poi}\\}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
+      \arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+  1 &     Base &    0.1  &  0.03 & \quart{0}{2}{1}{61}\\
+\hline  2 & 0.25, weighting,  iP=50\% &    0.14  &  0.1 & \quart{0}{6}{4}{61}\\
+\hline  3 &   0.25&    0.18  &  0.14 & \quart{4}{9}{6}{61}\\
+  3 &     0.25 &    0.19  &  0.11 & \quart{4}{7}{7}{61}\\
+  3 & 0.5, weighting,  iP=50\% &    0.2  &  0.19 & \quart{4}{13}{8}{61}\\
+\hline  4 & 0.75, weighting,  iP=50\% &    0.26  &  0.2 & \quart{8}{13}{12}{61}\\
+  4 &      0.5 &    0.28  &  0.2 & \quart{6}{14}{13}{61}\\
+  4 &    0.5&    0.33  &  0.22 & \quart{10}{14}{16}{61}\\
+\hline  5 &     0.75 &    0.47  &  0.22 & \quart{18}{14}{26}{61}\\
+  5 &   0.75&    0.46  &  0.11 & \quart{22}{7}{25}{61}\\
+\hline \end{tabular}}
+\end{minipage}
+\noindent\begin{minipage}{0.5\textwidth}
+  \flushleft
+  {\scriptsize \textbf{Synapse}\\}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+  1 & Base &    0.15  &  0.0 & \quart{1}{0}{1}{44}\\
+  1 & 0.5, weighting,  iP=50\% &    0.15  &  0.08 & \quart{1}{4}{1}{44}\\
+  1 & 0.25, weighting,  iP=50\% &    0.17  &  0.08 & \quart{0}{4}{2}{44}\\
+\hline  2 & 0.75, weighting,  iP=50\% &    0.21  &  0.08 & \quart{1}{4}{4}{44}\\
+  2 & 0.25 &    0.23  &  0.18 & \quart{2}{9}{5}{44}\\
+  2 & 0.25&    0.23  &  0.11 & \quart{2}{5}{5}{44}\\
+\hline  3 & 0.5&    0.38  &  0.19 & \quart{7}{10}{12}{44}\\
+  3 &  0.5 &    0.42  &  0.27 & \quart{6}{14}{14}{44}\\
+\hline  4 & 0.75 &    0.5  &  0.39 & \quart{12}{20}{19}{44}\\
+  4 & 0.75&    0.56  &  0.25 & \quart{17}{12}{22}{44}\\
+\hline \end{tabular}}
+\end{minipage}
+
+\noindent\begin{minipage}{0.50\textwidth}
+  \flushleft
+  {\scriptsize \textbf{Velocity}\\}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+  1 & 0.25, weighting,  iP=50\% &    0.03  &  0.06 & \quart{0}{5}{1}{98}\\
+  1 & 0.25 &    0.04  &  0.02 & \quart{1}{2}{2}{98}\\
+  1 & 0.25&    0.05  &  0.03 & \quart{2}{3}{3}{98}\\
+  1 & Base &    0.05  &  0.06 & \quart{0}{5}{3}{98}\\
+\hline  2 & 0.5, weighting,  iP=50\% &    0.07  &  0.11 & \quart{3}{11}{5}{98}\\
+  2 & 0.5&    0.1  &  0.08 & \quart{5}{8}{8}{98}\\
+\hline  3 & 0.5 &    0.13  &  0.12 & \quart{5}{12}{11}{98}\\
+\hline  4 & 0.75 &    0.16  &  0.24 & \quart{8}{24}{14}{98}\\
+  4 & 0.75, weighting,  iP=50\% &    0.17  &  0.15 & \quart{9}{15}{15}{98}\\
+  4 & 0.75&    0.22  &  0.22 & \quart{9}{22}{20}{98}\\
+\hline \end{tabular}}
+\end{minipage}
+\noindent\begin{minipage}{0.50\textwidth}
+  \flushleft
+  {\scriptsize \textbf{Xalan}\\}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+  1 &   Base &    0.08  &  0.02 & \quart{0}{1}{0}{80}\\
+\hline  2 & 0.5, weighting,  iP=50\% &    0.14  &  0.05 & \quart{3}{4}{6}{80}\\
+  2 & 0.75, weighting,  iP=50\% &    0.15  &  0.06 & \quart{5}{5}{6}{80}\\
+  2 & 0.25, weighting,  iP=50\% &    0.15  &  0.06 & \quart{3}{5}{6}{80}\\
+\hline  3 &   0.25 &    0.23  &  0.11 & \quart{8}{10}{13}{80}\\
+  3 & 0.25&    0.23  &  0.09 & \quart{10}{8}{13}{80}\\
+\hline  4 &  0.5&    0.28  &  0.06 & \quart{16}{5}{18}{80}\\
+\hline  5 &    0.5 &    0.3  &  0.13 & \quart{15}{11}{19}{80}\\
+  5 & 0.75&    0.34  &  0.19 & \quart{16}{16}{23}{80}\\
+  5 &   0.75 &    0.38  &  0.11 & \quart{21}{10}{26}{80}\\
+\hline \end{tabular}}
+\end{minipage}
+   \end{figure*}
 
@@
 % \section{Conclusion}
-% \section*{Acknowledgements}
-
+% \section*{Acknoweightingledgements}
+\newpage
 \bibliography{References}{}

### 2015-04-17 manuscript.tex
Updates from ShareLaTeX

@@
  \documentclass[conference]{IEEEtran}
-\usepackage{colortbl}
-\usepackage{booktabs}
-\usepackage{epstopdf}
 \usepackage{subfig}
-\usepackage{times}
-\usepackage{algorithm}
+\usepackage{wrapfig}
+ \usepackage{amsmath}
+ \usepackage{url}
+ \usepackage{pifont}
+\usepackage{rotating}
+%\usepackage{balance} 
+\usepackage{color, colortbl}
+\usepackage{graphicx}
 \usepackage{algorithmicx}
-\usepackage{algpseudocode}
-\usepackage{graphicx}
-\setlength\fboxsep{1pt}
-\setlength\fboxrule{1pt}
-\usepackage{multicol}
-\bstctlcite{IEEEexample:BSTcontrol}
-\usepackage[table]{xcolor}
-\definecolor{darkgray}{gray}{0.6}
-\definecolor{Gray}{gray}{0.9}
-\usepackage{picture}
-\newcommand{\kw}[1]{\textit{#1}}
-\newcommand{\quart}[4]{\begin{picture}(75,6)
-  {\color{black}\put(#3,3){\circle*{4}}\put(#1,3){\line(1,0){#2}}}\end{picture}}
-\usepackage{amsmath}
-\usepackage{balance}
-\usepackage{flushend}
-\usepackage{times}
+\usepackage{program}
 \usepackage{cite}
-\usepackage{hyperref}
-\hypersetup{
-  colorlinks = false,
-  hidelinks = true
-}
-\setlength{\parindent}{0em}
-\setlength{\parskip}{1em}
-
-% New Commands
+\usepackage{alltt}
+\newcommand{\eq}[1]{Equation~\ref{eq:#1}}
 \newcommand{\bi}{\begin{itemize}}
@@
 \newcommand{\ee}{\end{enumerate}}
+\newcommand{\tion}[1]{\textsection\ref{sec:#1}}
+\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
+\definecolor{lightgray}{gray}{0.975}
+\usepackage{fancyvrb}
+\usepackage{stfloats}
+\usepackage{multirow}
+\usepackage{listings}
+\usepackage{amsmath} 
+\DeclareMathOperator*{\argmin}{arg\,min} 
+\DeclareMathOperator*{\argmax}{arg\,max}
+
+\definecolor{darkgreen}{rgb}{0,0.3,0}
+
+\usepackage[table]{xcolor}
+\definecolor{Gray}{rgb}{0.88,1,1}
+\definecolor{Gray}{gray}{0.85}
+\definecolor{Blue}{RGB}{0,29,193}
+\newcommand{\G}{\cellcolor{green}}
+\newcommand{\Y}{\cellcolor{yellow}}
+
+\definecolor{MyDarkBlue}{rgb}{0,0.08,0.45} 
+\newenvironment{changed}{\par\color{MyDarkBlue}}{\par}
+
+\newcommand{\ADD}[1]{\textcolor{MyDarkBlue}{{\bf #1}}}
+\newcommand{\addit}[1]{\begin{changed}\input{#1}\end{changed}}
+
+\usepackage{color}
+\usepackage{listings}
+\usepackage{setspace}
+
+\definecolor{Gray}{gray}{0.9}
+\newcommand{\kw}[1]{\textit{#1}}
+\newcommand{\quart}[4]{\begin{picture}(75,6)
+  {\color{black}\put(#3,3){\circle*{4}}\put(#1,3){\line(1,0){#2}}}\end{picture}}
+% New Commands
+
+\definecolor{Code}{rgb}{0,0,0}
+\definecolor{Decorators}{rgb}{0.5,0.5,0.5}
+\definecolor{Numbers}{rgb}{0.5,0,0}
+\definecolor{MatchingBrackets}{rgb}{0.25,0.5,0.5}
+\definecolor{Keywords}{rgb}{0,0,1}
+\definecolor{self}{rgb}{0,0,0}
+\definecolor{Strings}{rgb}{0,0.63,0}
+\definecolor{Comments}{rgb}{0,0.63,1}
+\definecolor{Backquotes}{rgb}{0,0,0}
+\definecolor{Classname}{rgb}{0,0,0}
+\definecolor{FunctionName}{rgb}{0,0,0}
+\definecolor{Operators}{rgb}{0,0,0}
+\definecolor{Background}{rgb}{1,1,1}
+
+\lstnewenvironment{python}[1][]{
+\lstset{
+mathescape,
+numbers=#1,
+numberstyle=\footnotesize,
+numbersep=0.5em,
+xleftmargin=0em,
+framextopmargin=2em,
+framexbottommargin=2em,
+showspaces=false,
+showtabs=false,
+showstringspaces=false,
+tabsize=2,
+% Basic
+basicstyle=\ttfamily\small\setstretch{0.8},
+backgroundcolor=\color{Background},
+language=Python,
+% Comments
+commentstyle=\color{Comments}\slshape,
+% Strings
+stringstyle=\color{Strings},
+morecomment=[s][\color{Strings}]{"""}{"""},
+morecomment=[s][\color{Strings}]{'''}{'''},
+% keywords
+morekeywords={[1]import,from,class,def,for,while,if,is,in,elif,else,not,and,or,print,break,continue,return,True,False,None,access,as,,del,except,exec,finally,global,import,lambda,pass,print,raise,try,assert, dot, norm, zip, sorted},
+keywordstyle={[1]\color{Code}\bfseries},
+% additional keywords
+morekeywords={[3]fastmap, project, furthest, split, where,clusterer, getExemplar, projection, mutate, WHAT, knn},
+keywordstyle={[3]\color{Keywords}\bfseries},
+morekeywords={[2]@invariant},
+keywordstyle={[2]\color{Decorators}\slshape},
+emph={self},
+emphstyle={\color{self}\slshape},
+%
+}}{}
 
@@
 \section{Introduction}
+{\bf RQ1: Can Instance-based Learning techniques be used to create Planning tools that can better analyse software defect?}
+
+{\bf RQ2: Can lessons learnt from local search operators be useful for generating solutions that can be used to mitigate defects in software systems?}
+
+{\bf RQ3: Can such instance-based planners be applied to other software engineering paradigms?}
+We check if the proposed instance-based planner is applicable to performance prediction.
+
 \section{Motivating Example}
@@
 
-Assessing the quality of solutions to a real-world problem can be extremely hard.
-In several applications, researchers have models that can emulate the problem.
+Assessing the quality of solutions to a real-world problem can be extremely hard~\cite{menzies2005xomo}.
+In several software engineering applications, researchers have models that can emulate the problem, for instance there is the COCOMO effort model~\cite[p29-57]{boehm2009software}, the COQUALMO defect model~\cite[p254-268]{boehm2009software}, Madachy’s schedule risk model~\cite[p284-291]{boehm2009software}, to name a few.
 Using these models it is possible to examine several scenarios in a short period of time, and this can be done in a reproducible manner.
@@
 
-There exist several problems where models are hard to obtain, or the input and output are related by complex connections that simply cannot be modeled in a reliable manner, or generation of reliable models take prohibitively long.
+There exist several problems where models are hard to obtain, or the input and output are related by complex connections that simply cannot be modeled in a reliable manner, or generation of reliable models take prohibitively long ~\cite{Ludewig2003}.
 Software defect prediction is an excellent example of such a case.
@@
 Moreover, it has been shown that models for different regions within the same data can have very different properties \cite{localvsglobal}.
+This makes it extremely hard for one to design planning systems that are capable of mitigating these defects.
 
-In this paper we propose the use of an instance based approach in place of the conventional model based approach.
-Instead of generating solutions and going back to a model to see if the solution has any value, we
+In this paper we propose the use of an instance based approach, an example of case based reasoning strategy, in place of the conventional model based approach.
+Instance based approaches have been used extensively by the effort estimation community, see~\cite{keung2008analogy, 6600685, walkerden1999empirical, shepperd1997estimating, kocaguneli2010use, some more form p1703 line 2}.
+This approach has been proposed as an alternative to closed form mathematical models of other modeling methods such as regression \cite{keung2008analogy}.
+There are several other reasons for instance based approaches being a useful tool, see~\cite{6600685}.
+As pointed out by~\cite{walkerden1999empirical} it can be used with partial knowledge of the target project at an early stage which could be a very useful tool in preventing software defects.
+Instance based approaches are also rather robust in handling cases with sparse samples \cite{1438374}.
+All these features are desirable and suggest that instance-based approach is a useful adjunct to traditional model based approach.
+
+We would like to stress that the purpose of our work is not to promote instance-based planning over model based analytics, rather it is to suggest an alternative when model based approaches cannot be used.
 
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{_figs/WHAT-Clusters2.pdf}
+\caption{WHAT}
+\label{fig:whatflow}
+\end{figure}
+
+\begin{figure}[!b]
+\begin{python}[right]
+def fastmap(data): 
+  """Project data on a line 
+     between 2 distant points
+  """
+  z          = random.choose(data)
+  east       = furthest(z, data)
+  west       = furthest(east, data)
+  data.poles = (west,east)
+  c          = dist(west,east)     
+  for one in data.members: 
+    one.pos = project(west,east,c,one)
+  data = sorted(data) # sorted by 'pos'
+  return split(data)
+
+def project(west, east, c, x): 
+  "Project x onto line east to west"
+  a = dist(x,west)
+  b = dist(x,east)
+  return (a*a + c*c - b*b)/(2*c) #cosine rule
+
+def furthest(x,data): 
+  # what is furthest from x?
+  out, max = x,0
+  for y in data:
+    d = dist(x,y)
+    if d > max: out, max = y, d
+  return out
+
+def split(data): # Split at median
+   mid = len(data)/2; 
+  return data[mid:], data[:mid]
+
+def where(data, scores={}, 
+          lvl=10000, prune=True):  
+  "Recursively split data into 2 equal sizes."
+  if lvl < 1: 
+     return data # stop if out of levels
+  leafs      = [] # Empty Set
+  left,right = fastmap(data)
+  west, east = data.poles
+  $\omega=\sqrt{\mu}$ # enough data for recursion
+  goWest = len(left) > $\omega$  
+  goEast = len(right) > $\omega$ 
+  if prune: # if not pruning, ignore this step
+    if goEast and better(west,east,scores): 
+       goEast = False 
+    if goWest and better(east,west,scores): 
+       goWest = False 
+  if goWest:  
+     leafs += where(left,  lvl - 1, prune)  
+  if goEast:  
+     leafs += where(right, lvl - 1, prune) 
+  return leafs
+
+\end{python}
+\caption{Clustering with WHERE}
+\label{fig:fastmapCode}   
+\end{figure}
+
+\begin{figure}[!t]
+\begin{python}[left]
+def clusterer():
+ "Create clusters using WHERE"
+
+def getExemplar():
+  """
+  Identify the contour that exemplifies
+  the test Instance the most
+  """
+  contours = []
+  ClusterRows = clusterer()
+  while ClusterRows:
+    one = ClusterRows.pop()
+    two = knn(one, ClusterRows)[1]
+    contours.append([one, two])
+  return contours
+
+def projection(one, two, three):
+  "Compute projection of three on one & two"
+  if one.score() > two.score():
+    bad, good = one, two
+  else:
+    bad, good = two, one
+  plane = [b - a for a, b in zip(
+            bad.rep(), good.rep())]
+  Norm = norm(plane)
+  unitVect = [p / Norm for p in plane]
+  proj = dot(three - bad.rep(), unitVect)
+  return proj
+
+def mutate(me, others):
+  "Mutate 'me' towards 'others'"
+  return [my + ext * (good - my) 
+    	 for my, good in zip(me, others)]
+
+def WHAT():
+  contours = getExemplar()
+  for rows in defectiveRows:
+    vtx = sorted(
+        contours,
+        key=lambda F: projection(
+        F[0], F[1], rows), reverse=True)[0]
+
+    [good, bad] = sorted(vtx
+            , key=lambda F: F.score())
+    newRows.append(mutate(rows, good))
+  return newRows
+\end{python}
+\caption{Instance-based Planning using WHAT}
+\label{fig:WHAT}   
+\end{figure}
+
 \subsection{Defect Prediction}
@@
 To validate the treatments that have been suggested by our planner, we need to have defect predictors that capable of identifying if a certain module may (or may not) have a defect.
-A recent IEEE TSE paper by Lessmann et al.~\cite{lessmann} compared 21 different leaners for software defect prediction:
+A recent IEEE TSE paper by Lessmann et al.~\cite{lessmann} compared 21 different learners for software defect prediction:
 \bi
@@
 
+\begin{figure}[!tb]
+  \renewcommand{\baselinestretch}{0.8}\begin{center}
+{\scriptsize
+\begin{tabular}{l@{~~~}l@{~~~}l@{~~~}l@{~~~}l@{~~~}l@{~~~}l@{~~}}
+  \hline
+  \rowcolor{lightgray}
+  Data & Symbol & Training & Testing & Training Samples& Defective &\% Defective \\\hline
+
+Ant & ant & 1.5, 1.6  &1.7 & 644&124&19.25\\
+
+Camel & cam & 1.2, 1.4 & 1.6 & 1480&361 & 24.39\\
+
+Ivy & ivy & 1.1, 1.4 & 2.0  & 352 & 79 & 22.44\\
+
+Jedit & jed & 4.1, 4.2 & 4.3 & 679 & 127 & 18.70\\
+
+Log4j & log & 1.0, 1.1 & 1.2 & 244 & 71 & 29.09\\
+
+Lucene & luc & 2.0, 2.2 & 2.4 & 442 & 235 & 53.16\\
+
+Poi & poi & 2.0, 2.5 & 3.0 & 699 & 285 & 40.77\\
+
+Synapse & syn & 1.0, 1.1 & 1.2 & 379 & 76 & 20.05\\
+
+Velocity & vel & 1.4, 1.5 & 1.6 & 410& 289 & 70.48\\
+
+Xalan & xal &2.5, 2.6 &2.7 & 1688 & 798 & 47.27\\\hline
+\end{tabular}}
+\end{center}
+\caption{Attributes of the defect datasets}\label{fig:ck}
+\end{figure}
+
 \section{Experimental Design}
@@
 \begin{figure}[tbp!]
-  \subfloat[][\label{oracle}]{\includegraphics[width=\linewidth]{./_figs/Oracle}}\\
-  \subfloat[][\label{what}]{\includegraphics[width=\linewidth]{./_figs/WHAT}}
-  \caption{(a) The defect prediction oracle, (b) The Planning scheme}
-  \label{fig:rig}
+%   \subfloat[\label{oracle}]{\includegraphics[width=\linewidth]{./_figs/Oracle}}\\
+  \includegraphics[width=\linewidth]{./_figs/WHAT}
+  \caption{The Planning scheme}
+  \label{fig:what}
 \end{figure}
@@
 
-The performance prediction data set was obtained from~\cite{}.
+In order to answer {\bfseries RQ4}, we have used the performance prediction data set was obtained from the PROMISE repository~\cite{}.
 The data set contains six examples of real world configurable systems: \kw{Apache}, \kw{LLVM}, \kw{x264}, \kw{Berkeley DB (written in C and Java}, and \kw{SQLite}.
@@
 The data set is a collection of all possible configurations (with SQLITE being a exception with only 4653 configurations).
-We perforMedian a 5-fold cross validation study on this data set.
 
@@
 
-The research conducted by Shepperd and MacDonell~\cite{}, Kampenes~\cite{} and Kocaguenli et al.~\cite{}, highlighted that an ``effect size'' in lieu of a mere hypothesis test is required in order to verfiy if two populations are ``significantly'' different.
+The research conducted by Shepperd and MacDonell~\cite{shepperd12a}, Kampenes~\cite{kampenes07} and Kocaguenli et al.~\cite{}, highlighted that an ``effect size'' in lieu of a mere hypothesis test is required in order to verfiy if two populations are ``significantly'' different.
 An ICSE'11 paper by Arcuri~\cite{} endorsed the use of Vargha and Delaney's A12 effect size for reporting results in software engineering.
@@
 \centering
-\includegraphics[width=\linewidth]{_figs/Histogram}
+\includegraphics[width=\linewidth]{_figs/histograms.pdf}
 \caption{Caption}
@@
 
-\begin{figure*}[!t]
+\begin{figure*}[htbp!]
 
@@
       \hline  4 &     0.25 &    0.3  &  0.1 & \quart{7}{6}{10}{48}\\
-      4 &   0.25&    0.3  &  0.08 & \quart{8}{4}{10}{48}\\
+      4 &   0.25, weighting&    0.3  &  0.08 & \quart{8}{4}{10}{48}\\
       \hline  5 & 0.75, weighting,  iP=50\% &    0.42  &  0.13 & \quart{13}{7}{17}{48}\\
       5 &      0.5 &    0.43  &  0.1 & \quart{14}{6}{17}{48}\\
-      5 &    0.5&    0.43  &  0.1 & \quart{15}{5}{17}{48}\\
-      \hline  6 &   0.75&    0.64  &  0.19 & \quart{22}{10}{29}{48}\\
+      5 &    0.5, weighting&    0.43  &  0.1 & \quart{15}{5}{17}{48}\\
+      \hline  6 &   0.75, weighting&    0.64  &  0.19 & \quart{22}{10}{29}{48}\\
       6 &     0.75 &    0.63  &  0.08 & \quart{26}{4}{28}{48}\\
@@
 \hline  2 &   0.25 &    0.18  &  0.06 & \quart{1}{5}{4}{75}\\
-  2 & 0.25&    0.2  &  0.06 & \quart{2}{5}{6}{75}\\
+  2 & 0.25, weighting&    0.2  &  0.06 & \quart{2}{5}{6}{75}\\
   2 & 0.25, weighting,  iP=50\% &    0.2  &  0.04 & \quart{4}{3}{6}{75}\\
-\hline  3 &  0.5&    0.25  &  0.1 & \quart{6}{9}{10}{75}\\
+\hline  3 &  0.5, weighting&    0.25  &  0.1 & \quart{6}{9}{10}{75}\\
   3 &    0.5 &    0.26  &  0.12 & \quart{6}{11}{11}{75}\\
   3 & 0.5, weighting,  iP=50\% &    0.28  &  0.11 & \quart{10}{9}{13}{75}\\
-\hline  4 & 0.75&    0.39  &  0.16 & \quart{19}{13}{22}{75}\\
+\hline  4 & 0.75, weighting&    0.39  &  0.16 & \quart{19}{13}{22}{75}\\
   4 &   0.75 &    0.42  &  0.17 & \quart{15}{15}{25}{75}\\
@@
   2 &     0.25 &    0.18  &  0.06 & \quart{1}{4}{2}{55}\\
-  2 &   0.25&    0.2  &  0.06 & \quart{1}{4}{3}{55}\\
+  2 &   0.25, weighting&    0.2  &  0.06 & \quart{1}{4}{3}{55}\\
 \hline  3 & 0.5, weighting,  iP=50\% &    0.28  &  0.08 & \quart{7}{5}{9}{55}\\
 \hline  4 &      0.5 &    0.33  &  0.11 & \quart{8}{7}{12}{55}\\
-  4 &    0.5&    0.37  &  0.09 & \quart{10}{6}{14}{55}\\
+  4 &    0.5, weighting&    0.37  &  0.09 & \quart{10}{6}{14}{55}\\
 \hline  5 & 0.75, weighting,  iP=50\% &    0.38  &  0.16 & \quart{12}{10}{15}{55}\\
-\hline  6 &   0.75&    0.56  &  0.08 & \quart{25}{5}{27}{55}\\
+\hline  6 &   0.75, weighting&    0.56  &  0.08 & \quart{25}{5}{27}{55}\\
   6 &     0.75 &    0.57  &  0.12 & \quart{25}{7}{27}{55}\\[-0.01cm]
@@
   1 &   Base &    0.06  &  0.01 & \quart{0}{0}{0}{64}\\
-\hline  2 & 0.25&    0.08  &  0.06 & \quart{0}{4}{1}{64}\\
+\hline  2 & 0.25, weighting&    0.08  &  0.06 & \quart{0}{4}{1}{64}\\
   2 &   0.25 &    0.09  &  0.05 & \quart{0}{3}{2}{64}\\
 \hline  3 & 0.25, weighting,  iP=50\% &    0.12  &  0.08 & \quart{1}{5}{4}{64}\\
-\hline  4 &  0.5&    0.16  &  0.09 & \quart{4}{6}{6}{64}\\
+\hline  4 &  0.5, weighting&    0.16  &  0.09 & \quart{4}{6}{6}{64}\\
   4 &    0.5 &    0.17  &  0.09 & \quart{4}{6}{7}{64}\\
 \hline  5 & 0.5, weighting,  iP=50\% &    0.22  &  0.11 & \quart{8}{8}{10}{64}\\
-  5 & 0.75&    0.26  &  0.18 & \quart{9}{12}{13}{64}\\
+  5 & 0.75, weighting&    0.26  &  0.18 & \quart{9}{12}{13}{64}\\
 \hline  6 &   0.75 &    0.38  &  0.31 & \quart{11}{21}{21}{64}\\
@@
   1 &   Base &    0.06  &  0.03 & \quart{0}{4}{4}{139}\\
-\hline  2 & 0.25&    0.09  &  0.04 & \quart{4}{6}{8}{139}\\
+\hline  2 & 0.25, weighting&    0.09  &  0.04 & \quart{4}{6}{8}{139}\\
   2 &   0.25 &    0.09  &  0.06 & \quart{4}{8}{8}{139}\\
@@
   2 &    0.5 &    0.1  &  0.07 & \quart{4}{10}{10}{139}\\
-\hline  3 &  0.5&    0.12  &  0.03 & \quart{10}{4}{12}{139}\\
-\hline  4 & 0.75&    0.13  &  0.11 & \quart{10}{15}{14}{139}\\
+\hline  3 &  0.5, weighting&    0.12  &  0.03 & \quart{10}{4}{12}{139}\\
+\hline  4 & 0.75, weighting&    0.13  &  0.11 & \quart{10}{15}{14}{139}\\
   4 &   0.75 &    0.13  &  0.06 & \quart{12}{9}{14}{139}\\
@@
   1 &  0.25 &    0.05  &  0.02 & \quart{1}{4}{3}{188}\\
-  1 & 0.25&    0.05  &  0.04 & \quart{0}{7}{3}{188}\\
+  1 & 0.25, weighting&    0.05  &  0.04 & \quart{0}{7}{3}{188}\\
 \hline  2 &   0.5 &    0.07  &  0.04 & \quart{3}{8}{7}{188}\\
   2 & 0.25, weighting,  iP=50\% &    0.07  &  0.04 & \quart{3}{8}{7}{188}\\
-  2 & 0.5&    0.08  &  0.05 & \quart{5}{10}{9}{188}\\
+  2 & 0.5, weighting&    0.08  &  0.05 & \quart{5}{10}{9}{188}\\
 \hline  3 & 0.5, weighting,  iP=50\% &    0.1  &  0.03 & \quart{9}{6}{13}{188}\\
@@
   4 &  0.75 &    0.15  &  0.08 & \quart{13}{16}{23}{188}\\
-  4 & 0.75&    0.15  &  0.11 & \quart{11}{21}{23}{188}\\
+  4 & 0.75, weighting&    0.15  &  0.11 & \quart{11}{21}{23}{188}\\
 \hline \end{tabular}}
@@
 \hline  2 & 0.25, weighting,  iP=50\% &    0.14  &  0.1 & \quart{0}{6}{4}{61}\\
-\hline  3 &   0.25&    0.18  &  0.14 & \quart{4}{9}{6}{61}\\
+\hline  3 &   0.25, weighting&    0.18  &  0.14 & \quart{4}{9}{6}{61}\\
   3 &     0.25 &    0.19  &  0.11 & \quart{4}{7}{7}{61}\\
@@
   4 &      0.5 &    0.28  &  0.2 & \quart{6}{14}{13}{61}\\
-  4 &    0.5&    0.33  &  0.22 & \quart{10}{14}{16}{61}\\
+  4 &    0.5, weighting&    0.33  &  0.22 & \quart{10}{14}{16}{61}\\
 \hline  5 &     0.75 &    0.47  &  0.22 & \quart{18}{14}{26}{61}\\
-  5 &   0.75&    0.46  &  0.11 & \quart{22}{7}{25}{61}\\
+  5 &   0.75, weighting&    0.46  &  0.11 & \quart{22}{7}{25}{61}\\
 \hline \end{tabular}}
@@
   2 & 0.25 &    0.23  &  0.18 & \quart{2}{9}{5}{44}\\
-  2 & 0.25&    0.23  &  0.11 & \quart{2}{5}{5}{44}\\
-\hline  3 & 0.5&    0.38  &  0.19 & \quart{7}{10}{12}{44}\\
+  2 & 0.25, weighting&    0.23  &  0.11 & \quart{2}{5}{5}{44}\\
+\hline  3 & 0.5, weighting&    0.38  &  0.19 & \quart{7}{10}{12}{44}\\
   3 &  0.5 &    0.42  &  0.27 & \quart{6}{14}{14}{44}\\
 \hline  4 & 0.75 &    0.5  &  0.39 & \quart{12}{20}{19}{44}\\
-  4 & 0.75&    0.56  &  0.25 & \quart{17}{12}{22}{44}\\
+  4 & 0.75, weighting&    0.56  &  0.25 & \quart{17}{12}{22}{44}\\
 \hline \end{tabular}}
@@
   1 & 0.25 &    0.04  &  0.02 & \quart{1}{2}{2}{98}\\
-  1 & 0.25&    0.05  &  0.03 & \quart{2}{3}{3}{98}\\
+  1 & 0.25, weighting&    0.05  &  0.03 & \quart{2}{3}{3}{98}\\
   1 & Base &    0.05  &  0.06 & \quart{0}{5}{3}{98}\\
 \hline  2 & 0.5, weighting,  iP=50\% &    0.07  &  0.11 & \quart{3}{11}{5}{98}\\
-  2 & 0.5&    0.1  &  0.08 & \quart{5}{8}{8}{98}\\
+  2 & 0.5, weighting&    0.1  &  0.08 & \quart{5}{8}{8}{98}\\
 \hline  3 & 0.5 &    0.13  &  0.12 & \quart{5}{12}{11}{98}\\
@@
   4 & 0.75, weighting,  iP=50\% &    0.17  &  0.15 & \quart{9}{15}{15}{98}\\
-  4 & 0.75&    0.22  &  0.22 & \quart{9}{22}{20}{98}\\
+  4 & 0.75, weighting&    0.22  &  0.22 & \quart{9}{22}{20}{98}\\
 \hline \end{tabular}}
@@
 \hline  3 &   0.25 &    0.23  &  0.11 & \quart{8}{10}{13}{80}\\
-  3 & 0.25&    0.23  &  0.09 & \quart{10}{8}{13}{80}\\
-\hline  4 &  0.5&    0.28  &  0.06 & \quart{16}{5}{18}{80}\\
+  3 & 0.25, weighting&    0.23  &  0.09 & \quart{10}{8}{13}{80}\\
+\hline  4 &  0.5, weighting&    0.28  &  0.06 & \quart{16}{5}{18}{80}\\
 \hline  5 &    0.5 &    0.3  &  0.13 & \quart{15}{11}{19}{80}\\
-  5 & 0.75&    0.34  &  0.19 & \quart{16}{16}{23}{80}\\
+  5 & 0.75, weighting&    0.34  &  0.19 & \quart{16}{16}{23}{80}\\
   5 &   0.75 &    0.38  &  0.11 & \quart{21}{10}{26}{80}\\
@@
 % \section{Conclusion}
-% \section*{Acknoweightingledgements}
+% \section*{Acknowledgements}
 \newpage

### 2015-04-29 manuscript.tex
Updates from ShareLaTeX

@@
 \newcommand{\quart}[4]{\begin{picture}(75,6)
-  {\color{black}\put(#3,3){\circle*{4}}\put(#1,3){\line(1,0){#2}}}\end{picture}}
+  {\color{black}\put(#3,3){\circle*{2.5}}\put(#1,3){\line(1,0){#2}}}\end{picture}}
 % New Commands
@@
 % additional keywords
-morekeywords={[3]fastmap, project, furthest, split, where,clusterer, getExemplar, projection, mutate, WHAT, knn},
+morekeywords={[3]fastmap, project, furthest, split, WHERE,clusterer, getContours, envied, fWeight, nearestContour, projection, mutate, WHAT, knn},
 keywordstyle={[3]\color{Keywords}\bfseries},
-morekeywords={[2]@invariant},
+morekeywords={[2]@invari},
 keywordstyle={[2]\color{Decorators}\slshape},
@@
 
-In this paper we propose the use of an instance based approach, an example of case based reasoning strategy, in place of the conventional model based approach.
-Instance based approaches have been used extensively by the effort estimation community, see~\cite{keung2008analogy, 6600685, walkerden1999empirical, shepperd1997estimating, kocaguneli2010use, some more form p1703 line 2}.
-This approach has been proposed as an alternative to closed form mathematical models of other modeling methods such as regression \cite{keung2008analogy}.
+An alternative approach would be to make use of an instance based approach, an example of case based reasoning strategy, in place of the conventional model based approach.
+Instance based approaches have been used extensively by the effort estimation community, see~\cite{keung2008analogy, 6600685, walkerden1999empirical, shepperd1997estimating, kocaguneli2010use}.
+This approach has been proposed as an alternative to closed form mathematical models or other modeling methods such as regression \cite{keung2008analogy}.
 There are several other reasons for instance based approaches being a useful tool, see~\cite{6600685}.
@@
 
+In this paper the instance based learning principle is used to first cluster the training data and then create contours in the data.
+These contours can then be used by test cases to infer meaningful information in order to improve it.
+The entire process is described in greater detail in the following sections.
 We would like to stress that the purpose of our work is not to promote instance-based planning over model based analytics, rather it is to suggest an alternative when model based approaches cannot be used.
@@
 WHERE is a spectral learner which uses the FastMap heuristic to estimate the first principal component.
-It then recursively partitions the data into two halves along the Medianian point of the projection on the first principal component, terminating when a half has less than $\sqrt{N}$ items.
+It then recursively partitions the data into two halves along the Median point of the projection on the first principal component, terminating when a half has less than $\sqrt{N}$ items.
 
@@
 The planner then reflects over the vertices of the chosen hyperplane, identifying the \textit{better} vertex among the two.
-Now, a new instance is generated by mutating the attributes of the test instance towards the better vertex and away from the worse vertex.
+Now, a new instance is generated by \textit{mutating the attributes} of the test instance towards the better vertex and away from the worse vertex.
 This process is repeated for all the test instances that are considered defective by the defect prediction scheme, discussed below.
 
+\subsection{Feature Weighting}
+The algorithm also allows for a feature weighting and pruning scheme.
+We have employed a simple (and fast) attribute ranking method where the features are sorted based on their ability to find meaningful splits in the dependent class of the data, see ~\cite{hall03}.
+Features that can find splits with the \textit{lesser variance} in the dependent variable are \textit{ranked higher} than features that don't.
+
+We reason that the most informative feature must undergo a larger change as compared to other features.
+Therefore, when feature weighting is employed, the higher ranked features are mutated by a larger extent.
+Additionally, we have also included information pruning.
+Here we mutate only the top X\% of the features in each test instance.
+The remaining features remain unaltered.
 \begin{figure}[htbp!]
@@
 \begin{enumerate}
-\item Find the two most distant points in a given population; say {\em east} and {\em west}. 
+\item Find the two most dist points in a given population; say {\em east} and {\em west}. 
 \item Draw an axis of length $c$ between the poles. 
@@
 
-There are couple of things to note: firstly, the above algorithm requires a distance measure between sets of decisions, for this WHERE uses case-based reasoning measure defined by Aha et al.~\cite{aha91}; secondly, in step-1 a linear time heuristic called FASTMAP~\cite{fastmap} is used to find the two most distant points, this procedure is listed below:
+There are couple of things to note: firstly, the above algorithm requires a distance measure between sets of decisions, for this WHERE uses case-based reasoning measure defined by Aha et al.~\cite{aha91}; secondly, in step-1 a linear time heuristic called FASTMAP~\cite{fastmap} is used to find the two most dist points, this procedure is listed below:
 \begin{itemize}
@@
 Formally, WHAT can be considered as an instance based  learning scheme.
-And that's beacuse it builds a set of recommendations based on a given test case based on the clusters forMedian at the training stage.
+And that's because it builds a set of recommendations based on a given test case based on the clusters for Median at the training stage.
 This is unlike a model based approach, which would have used a model to do the same~\cite{xomo}.
@@
 \begin{figure}[!b]
-\begin{python}[right]
+\begin{python}[left]
 def fastmap(data): 
   """Project data on a line 
-     between 2 distant points
+     between 2 dist points
   """
@@
   b = dist(x,east)
-  return (a*a + c*c - b*b)/(2*c) #cosine rule
+  #cosine rule
+  return (a*a + c*c - b*b)/(2*c)
 
@@
 
-def where(data, scores={}, 
+def WHERE(data, scores={}, 
           lvl=10000, prune=True):  
-  "Recursively split data into 2 equal sizes."
+  "Recursively split data."
   if lvl < 1: 
@@
   goEast = len(right) > $\omega$ 
-  if prune: # if not pruning, ignore this step
+  if prune: 
     if goEast and better(west,east,scores): 
@@
 \begin{figure}[!t]
-\begin{python}[left]
-def clusterer():
- "Create clusters using WHERE"
+\begin{python}[right]
+def envied(leaves):
+  """
+  Returns a single exemplary row from 
+  a cluster.
+  """
 
-def getExemplar():
+def fWeight(train, prune = 0):
   """
-  Identify the contour that exemplifies
-  the test Instance the most
+  Find the feature weights & prune features
+  """
+
+def getContours(train):
+  """
+  Identify the pairs of clusters
+  that can form a contour
   """
   contours = []
-  ClusterRows = clusterer()
-  while ClusterRows:
-    one = ClusterRows.pop()
-    two = knn(one, ClusterRows)[1]
-    contours.append([one, two])
+  # Clustering with where
+  clusters = WHERE(train) 
+  near = lambda x: knn(x, clusters)[1]
+  for c in clusters:
+    one = envied(c)
+    two = envied(near(one, clusters))
+    contours += [one, two]
   return contours
 
-def projection(one, two, three):
-  "Compute projection of three on one & two"
-  if one.score() > two.score():
-    bad, good = one, two
+def project(a, b, test):
+  if score(a) > score(b):
+    good, bad = a,b 
   else:
-    bad, good = two, one
-  plane = [b - a for a, b in zip(
-            bad.rep(), good.rep())]
-  Norm = norm(plane)
-  unitVect = [p / Norm for p in plane]
-  proj = dot(three - bad.rep(), unitVect)
-  return proj
+    good, bad = b,a
+  AB = dist(bad,test)
+  BC = dist(good,test)
+  AC = dist(good,bad)
+  # Cosine rule
+  y = (AB$^2$ + BC$^2$ - AC$^2$)/(2*AC)
+  return $\sqrt{AB^2 - y^2}$
 
-def mutate(me, others):
+def mutate(me, others, weights = None):
   "Mutate 'me' towards 'others'"
+  if weights:
+    return [my + ext * f * (good - my) for 
+    f, my, good in zip(wights, me, others)]
+  else:
     return [my + ext * (good - my) 
@@
 
+def nearestContour(contours, instance):
+  "Find the nearest contour to an instance"
+  return sorted(
+        contours,
+        key=lambda F: project(
+        F[0], F[1], instance), 
+        reverse=True)[0]
+
 def WHAT():
-  contours = getExemplar()
+  contours = getContours()
+  weights = fWeight(train)
   for rows in defectiveRows:
-    vtx = sorted(
-        contours,
-        key=lambda F: projection(
-        F[0], F[1], rows), reverse=True)[0]
-
+    vtx = nearestContour(contours, rows)
     [good, bad] = sorted(vtx
-            , key=lambda F: F.score())
-    newRows.append(mutate(rows, good))
-  return newRows
+            , key=lambda F: score(F))
+    new += mutate(rows, good, weights)
+  return new
 \end{python}
@@
 {\em Statistical classifiers:}
-Linear    discriminant analysis,
-Quadratic discriminant analysis,
+Linear    discrimin analysis,
+Quadratic discrimin analysis,
 Logistic regression,
@@
         ca & afferent couplings & how many other classes use the specific
+        class. \\\hline
 class. \\\hline
@@
 
-\section{Experimental Design}
-The following section describes the experimental rig and the experiments used to measure the performance of WHAT on 10 defect data sets and 6 performance prediction data sets.
+\begin{figure}[!hbp]
+  \renewcommand{\baselinestretch}{1}\begin{center}
+{\scriptsize
+\begin{tabular}{llllll}
+  \hline
+  \rowcolor{lightgray}
+Project & Domain & Lang. & LOC & Features & Config\\\hline
+
+Berkeley DB CE & Database & C & 219,811 & 18 & 2560\\
+
+Berkeley DB JE & Database & Java & 42,596 & 32  & 400\\
+
+Apache & Web Server & C & 230,277 & 9 & 192\\
+
+SQLite & Database & C & 312,625 & 39 & 3,932,160\textsuperscript{*}\\
+
+LLVM & Compiler & C++ & 47,549 & 11 & 1024\\
+
+x264 & Video Enc. & C& 45,743 & 16 & 1152\\\hline
+\end{tabular}}\par\medskip
+
+{ \footnotesize $^*$ Dataset contains 4, 553 configurations for prediction modeling and 100 additional random configurations for prediction evaluation, see \cite{vapp}.}
+\end{center}
+
+\caption{Attributes of the Performance Prediction datasets}\label{fig:cpm}
+\end{figure}
 
@@
 \includegraphics[width=\linewidth]{./_figs/WHAT}
-  \caption{The Planning scheme}
-  \label{fig:what}
+\caption{Experimental Rig}
+\label{fig:rig}
+
+%   \subfloat[Experimental Rig for Defect Prediction]{  \includegraphics[width=\linewidth]{./_figs/WHAT}
+%   \label{fig:rig2}}
+
 \end{figure}
@@
 %involves two key components. Firstly, there is the oracle (Random Forest with SMOTE) which is used to make predictions. Then we have the 
-\subsection{Data sets}
-The data was obtained from the PROMISE repository.
-For the defect data we investigated 32 releases from 11 open source Java projects defined by the metrics highlighted in Fig.~\ref{fig:ck}: \kw{Apache Ant} (1.5 -- 1.7), \kw{Apache Camel} (1.2 -- 1.6), \kw{Apache Ivy} (1.1 -- 2.0), \kw{JEdit} (4.1 -- 4.3), \kw{Apache Log4j} (1.0 -- 1.2), \kw{Apache Lucene} (2.0 -- 2.2), \kw{PBeans} (1.0 and 2.0), \kw{Apache POI} (2.0 -- 3.0), \kw{Apache Synapse} (1.0 -- 1.2), \kw{Apache Velocity} (1.4 -- 1.6), and \kw{Apache Xalan-Java} (2.5 -- 2.7).
-Given the empirical nature of the data, it is important to design an experiment such that the planning phase uses only the \kw{past} data to learn trends which can then be applied to the \kw{future} data.
+\section{Data sets}
+
+The following section describes the experimental rig and the experiments used to measure the performance of WHAT on 10 defect data sets and 6 performance prediction data sets.
+
+\subsection{Defect Data Set}
+The data was obtained from the PROMISE repository\footnote{Promise Repository: \url{http://openscience.us/repo}}.
+For the defect data we investigated 32 releases from 11 open source Java projects defined by the metrics highlighted in figure ~\ref{fig:ck}: \kw{Apache } (1.5 -- 1.7), \kw{Apache Camel} (1.2 -- 1.6), \kw{Apache Ivy} (1.1 -- 2.0), \kw{JEdit} (4.1 -- 4.3), \kw{Apache Log4j} (1.0 -- 1.2), \kw{Apache Lucene} (2.0 -- 2.2), \kw{PBeans} (1.0 and 2.0), \kw{Apache POI} (2.0 -- 3.0), \kw{Apache Synapse} (1.0 -- 1.2), \kw{Apache Velocity} (1.4 -- 1.6), and \kw{Apache Xalan-Java} (2.5 -- 2.7).
+
+Given the empirical nature of the data, it is import to design an experiment such that the planning phase uses only the \kw{past} data to learn trends which can then be applied to the \kw{future} data.
 Thus for our experiment we use data sets that have at least two consecutive releases.
@@
 
-In order to answer {\bfseries RQ4}, we have used the performance prediction data set was obtained from the PROMISE repository~\cite{}.
-The data set contains six examples of real world configurable systems: \kw{Apache}, \kw{LLVM}, \kw{x264}, \kw{Berkeley DB (written in C and Java}, and \kw{SQLite}.
-The systems have different characteristics, different implementation languages, and different configuration mechanisms.
-The data set is a collection of all possible configurations (with SQLITE being a exception with only 4653 configurations).
+\subsection{Performance Prediction Data Set}
+
+{\bfseries RQ3} asks if the aforementioned method can be expanded to other kinds of data.
+To answer this, we have used the performance prediction data set collected by Siegmund et al.
+for their ICSE '12 paper~\cite{sven12}.
+The data sets have been deployed as a part of the \textsc{SPLConqueror} tool\footnote{\url{http://fosd.de/SPLConqueror}}.
+This data set contains six examples of real world configurable systems that cover a broad spectrum of scenarios, see figure \ref{fig:cpm} for a summary.
+The systems have different characteristics (lines of code: 40 thousand to 300 thousand; Valid configurations: 192 to about 3.9 million), different implementation languages (C, C++, and Java), different mechanism (conditional compilation, configuration files, and command-line options), and different domains (Web servers, compilers, encoders, and databases).
+The data contains a measurement of all the configurations that are invoked by the benchmarking tool.
+The measurements were conducted 5 to 20 times and the mean of all measurements for each configuration was recoded.
+
+For our experiments, we randomly split the data sets into two equal halves, one for training and the other for testing.
+The planning phase learns configuration settings from the training half and plans for changes in the test half aiming to optimize the performance of the test instances.
+We repeat our measurements 20 to 25 times to overcome measurement bias.
+\section{Experimental Design}
 
@@
 
-The experimental rig is shown in Figure \ref{fig:rig}.
-It uses an \textit{oracle} to determine wether a certain test case is defective or not.
-If the oracle suggests that an instance is defective, then we use WHAT to apply the recommendations to that test instance.
-The oracle is used to check if the recommendation helped subdue the defect.
+The experimental rig for defect prediction is shown in Figure \ref{fig:rig}. It works as follows: 
+\bi
+\item We use an {oracle} (Random Forest + SMOTE) to determine whether a certain test case is defective or not. 
+\item If the oracle suggests that an instance is defective, then we use WHAT to apply the recommendations to that test instance. 
+\item The oracle is then used to predict the attributes in the modified instance.
+\item The statistical significance of the changes are verified using the cliffs delta measure described below.
+\ei
+
+For run time optimization, we use a similar rig.
+The oracle is Random Forest, and it predicts for run times of specific configuration.
+WHAT is used to generate a recommended configuration to reduce the run times.
+The run time is measured by the oracle.
+The reduction of run times are expressed as fractions of the original (also referred to as baseline) run time.
+
+Note that we report the performance scores as a comparison between the oracle's prediction \textit{before} and that \textit{after}.
+We refrain from using the \textit{actual} defects in the data sets to perform the same comparison.
+This is because the oracle is limited in its ability to predict defects, there are instances that are inherently misclassified.
+These misclassifications however are not affected by the planner.
+Therefore, by comparing the defect counts before and after applying the planner and doing so with a the same oracle would give us an accurate albeit relativistic measure of performance.
 
@@
 \begin{equation}
-\delta = \frac{\#(Before>After) - \#(Before<After)}{M^2}
+\delta = \frac{\#(Before<After) - \#(Before>After)}{M^2}
 \end{equation}
 
-In the context of our application, the $\delta$ attains a value of 1 if the number of defects after applying the treatments has reduced to zero, and 0 if there is no change.
+In the context of our application, the $\delta$ attains a value of -1 if the number of defects after applying the treatments has reduced to zero.
+On the other hand $\delta$ will be 0 if there is no change at all.
+Thus, most of the values reported will lie between 0 and -1.
+It needs to be highlighted that although $\delta$ can lie between -1 and +1, the in our application the range is limited to -1 and 0.
+And this is because we only apply the treatments to defective cases.
 
@@
 
-In addition to the above, we rank the different variants of the planning scheme to identify the best approach.
+In addition to the above, we rank the different varis of the planning scheme to identify the best approach.
 We make use of the Scott-Knott procedure, recommended by Mittas \& Angelis in their 2013 IEEE TSE paper~\cite{sk}, to compute the ranks.
-It works as follows: A list of treatments \textit{l} is sorted by the Medianian score.
+It works as follows: A list of treatments \textit{l} is sorted by the Median score.
 The list \textit{l} is then split into sub-lists m, n in order to maximize the expected value of the differences in the observed performance before and after division.
@@
 
-The research conducted by Shepperd and MacDonell~\cite{shepperd12a}, Kampenes~\cite{kampenes07} and Kocaguenli et al.~\cite{}, highlighted that an ``effect size'' in lieu of a mere hypothesis test is required in order to verfiy if two populations are ``significantly'' different.
+The research conducted by Shepperd and MacDonell~\cite{shepperd12a}, Kampenes~\cite{kampenes07} and Kocaguenli et al.~\cite{}, highlighted that an ``effect size'' in lieu of a mere hypothesis test is required in order to verfiy if two populations are ``significly'' different.
 An ICSE'11 paper by Arcuri~\cite{} endorsed the use of Vargha and Delaney's A12 effect size for reporting results in software engineering.
@@
 \includegraphics[width=\linewidth]{_figs/histograms.pdf}
-\caption{Caption}
+\caption{Comparison of defects before and after planning.}
 \label{fig:bugs}
 \end{figure}
+
+\begin{figure*}[htbp!]
+\centering
+\begin{minipage}{0.30\linewidth}
+\includegraphics[width=\linewidth]{_figs/Apache.pdf}
+\end{minipage}
+\begin{minipage}{0.30\linewidth}
+\includegraphics[width=\linewidth]{_figs/BDBJ.pdf}
+\end{minipage}
+\begin{minipage}{0.30\linewidth}
+\includegraphics[width=\linewidth]{_figs/BDBC.pdf}
+\end{minipage}
+
+\begin{minipage}{0.30\linewidth}
+\includegraphics[width=\linewidth]{_figs/LLVM.pdf}
+\end{minipage}
+\begin{minipage}{0.30\linewidth}
+\includegraphics[width=\linewidth]{_figs/SQL.pdf}
+\end{minipage}
+\begin{minipage}{0.30\linewidth}
+\includegraphics[width=\linewidth]{_figs/X264.pdf}
+\end{minipage}
+\caption{Run time optimization using WHAT.
+Blue curve represents a mutation probability of 0.75 with feature weighting and information pruning; Red curve represents a mutation probability of 0.25 with feature weighting, but no information pruning; Black curve represents the raw test data used as baseline for the comparision.}
+\label{fig:pp}
+\end{figure*}
+
+\begin{figure*}[htbp!]
+\noindent\begin{minipage}{0.5\textwidth}
+  {\scriptsize \textbf{Apache}\\}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
+      \arrayrulecolor{darkgray}
+      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+  1 & 75, weighting, Prune=25\% &    0.77  &  0.05 & \quart{0}{9}{3}{49} \\
+  1 &   75 &    0.79  &  0.08 & \quart{1}{16}{7}{49} \\
+\hline  2 & 75, weighting &    0.85  &  0.07 & \quart{9}{14}{19}{49} \\
+  2 & 50, weighting, Prune=25\% &    0.85  &  0.04 & \quart{15}{8}{19}{49} \\
+  2 &  50 &    0.85  &  0.05 & \quart{17}{10}{19}{49} \\
+\hline  3 & 50, weighting &    0.91  &  0.05 & \quart{25}{10}{31}{49} \\
+  3 &  25 &    0.92  &  0.04 & \quart{29}{8}{33}{49} \\
+  3 & 25, weighting, Prune=25\% &    0.93  &  0.02 & \quart{33}{4}{35}{49} \\
+\hline  4 & 25, weighting &    0.96  &  0.03 & \quart{37}{6}{41}{49} \\
+\hline  5 & baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
+\hline \end{tabular}}
+\end{minipage}
+\noindent\begin{minipage}{0.5\textwidth}
+  \flushleft
+  {\scriptsize \textbf{BDBC}\\}
+{\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+  1 &     75 &    0.22  &  0.05 & \quart{0}{3}{1}{49} \\
+  1 &  75, weighting, Prune=25\% &    0.21  &  0.04 & \quart{0}{2}{0}{49} \\
+\hline  2 &  75, weighting &    0.24  &  0.1 & \quart{0}{6}{2}{49} \\
+\hline  3 &     50 &    0.4  &  0.04 & \quart{11}{2}{12}{49} \\
+  3 &  50, weighting, Prune=25\% &    0.4  &  0.05 & \quart{10}{3}{12}{49} \\
+\hline  4 &  50, weighting &    0.47  &  0.09 & \quart{14}{5}{16}{49} \\
+\hline  5 &     25 &    0.66  &  0.03 & \quart{28}{1}{28}{49} \\
+  5 &  25, weighting, Prune=25\% &    0.67  &  0.06 & \quart{28}{3}{29}{49} \\
+\hline  6 &  25, weighting &    0.69  &  0.06 & \quart{29}{4}{30}{49} \\
+\hline  7 &  baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
+\hline \end{tabular}}
+\end{minipage}
+
+\noindent\begin{minipage}{0.5\textwidth}
+  \flushleft
+  {\scriptsize \textbf{BDBJ}\\}
+{\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+  1 &     75 &    0.63  &  0.16 & \quart{0}{19}{3}{49} \\
+  1 &  75, weighting, Prune=25\% &    0.68  &  0.17 & \quart{1}{21}{9}{49} \\
+  1 &  75, weighting &    0.74  &  0.11 & \quart{8}{14}{17}{49} \\
+\hline  2 &  50, weighting, Prune=25\% &    0.75  &  0.09 & \quart{14}{12}{18}{49} \\
+  2 &     50 &    0.79  &  0.13 & \quart{16}{16}{23}{49} \\
+\hline  3 &  50, weighting &    0.82  &  0.09 & \quart{23}{11}{27}{49} \\
+\hline  4 &  25, weighting, Prune=25\% &    0.87  &  0.07 & \quart{29}{9}{33}{49} \\
+\hline  5 &     25 &    0.88  &  0.06 & \quart{33}{8}{34}{49} \\
+  5 &  25, weighting &    0.92  &  0.06 & \quart{36}{7}{39}{49} \\
+\hline  6 &  baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
+\hline \end{tabular}}
+\end{minipage}
+\noindent\begin{minipage}{0.5\textwidth}
+  \flushleft
+  {\scriptsize \textbf{LLVM}\\}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+  1 &     75 &    0.92  &  0.01 & \quart{5}{6}{5}{49} \\
+  1 &  75, weighting, Prune=25\% &    0.92  &  0.02 & \quart{0}{11}{5}{49} \\
+  1 &  75, weighting &    0.93  &  0.02 & \quart{5}{11}{11}{49} \\
+\hline  2 &     50 &    0.94  &  0.01 & \quart{16}{6}{16}{49} \\
+  2 &  50, weighting, Prune=25\% &    0.95  &  0.0 & \quart{22}{0}{22}{49} \\
+  2 &  50, weighting &    0.96  &  0.02 & \quart{22}{11}{27}{49} \\
+\hline  3 &     25 &    0.98  &  0.01 & \quart{33}{5}{38}{49} \\
+  3 &  25, weighting, Prune=25\% &    0.98  &  0.01 & \quart{33}{5}{38}{49} \\
+  3 &  25, weighting &    0.98  &  0.0 & \quart{38}{0}{38}{49} \\
+\hline  4 &  baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
+\hline \end{tabular}}
+\end{minipage}
+
+\noindent\begin{minipage}{0.5\textwidth}
+  \flushleft
+  {\scriptsize \textbf{SQL}\\}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+  1 &      75 &    0.98  &  0.01 & \quart{0}{16}{16}{49} \\
+  1 &  75, weighting, Prune=25\% &    0.98  &  0.0 & \quart{16}{0}{16}{49} \\
+  1 &  75, weighting &    0.99  &  0.01 & \quart{16}{17}{33}{49} \\
+  1 &  50, weighting, Prune=25\% &    0.99  &  0.0 & \quart{33}{0}{33}{49} \\
+  1 &      50 &    0.99  &  0.0 & \quart{33}{0}{33}{49} \\
+  1 &  50, weighting &    0.99  &  0.01 & \quart{33}{16}{33}{49} \\
+  1 &  25, weighting, Prune=25\% &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
+  1 &      25 &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
+  1 &  25, weighting &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
+  1 &  baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
+  \hline \end{tabular}}
+\end{minipage}
+\noindent\begin{minipage}{0.5\textwidth}
+  \flushleft
+  {\scriptsize \textbf{X264}\\}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+  1 &  75, weighting, Prune=25\% &    0.73  &  0.05 & \quart{1}{9}{3}{49} \\
+  1 &     75 &    0.74  &  0.05 & \quart{0}{8}{5}{49} \\
+\hline  2 &  75, weighting &    0.81  &  0.04 & \quart{13}{7}{17}{49} \\
+  2 &  50, weighting, Prune=25\% &    0.82  &  0.04 & \quart{17}{7}{18}{49} \\
+  2 &     50 &    0.83  &  0.03 & \quart{17}{5}{20}{49} \\
+\hline  3 &  50, weighting &    0.88  &  0.03 & \quart{25}{6}{29}{49} \\
+\hline  4 &     25 &    0.9  &  0.03 & \quart{31}{5}{32}{49} \\
+  4 &  25, weighting, Prune=25\% &    0.91  &  0.03 & \quart{32}{5}{34}{49} \\
+\hline  5 &  25, weighting &    0.93  &  0.02 & \quart{36}{3}{37}{49} \\
+\hline  6 &  baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
+\hline \end{tabular}}
+\end{minipage}
+\end{figure*}
 
@@
       \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-      1 &     Base &    0.13  &  0.03 & \quart{0}{1}{1}{48}\\
-      \hline  2 & 0.25, weighting,  iP=50\% &    0.2  &  0.05 & \quart{3}{3}{4}{48}\\
-      \hline  3 & 0.5, weighting,  iP=50\% &    0.26  &  0.06 & \quart{6}{3}{8}{48}\\
-      \hline  4 &     0.25 &    0.3  &  0.1 & \quart{7}{6}{10}{48}\\
-      4 &   0.25, weighting&    0.3  &  0.08 & \quart{8}{4}{10}{48}\\
-      \hline  5 & 0.75, weighting,  iP=50\% &    0.42  &  0.13 & \quart{13}{7}{17}{48}\\
-      5 &      0.5 &    0.43  &  0.1 & \quart{14}{6}{17}{48}\\
-      5 &    0.5, weighting&    0.43  &  0.1 & \quart{15}{5}{17}{48}\\
-      \hline  6 &   0.75, weighting&    0.64  &  0.19 & \quart{22}{10}{29}{48}\\
-      6 &     0.75 &    0.63  &  0.08 & \quart{26}{4}{28}{48}\\
+  1 & ant,  0.25,  weight &    -0.33  &  0.05 & \quart{1}{5}{3}{149}\\
+  1 &   ant,  0.25 &    -0.31  &  0.06 & \quart{2}{6}{5}{149}\\
+  1 &    ant,  0.5 &    -0.28  &  0.15 & \quart{1}{16}{8}{149}\\
+\hline  2 & ant,  0.5,  weight &    -0.26  &  0.19 & \quart{0}{20}{10}{149}\\
+  2 & ant,  0.5,  weight,  iP= 50\\% &    -0.26  &  0.11 & \quart{5}{12}{10}{149}\\
+  2 & ant,  0.75,  weight &    -0.25  &  0.3 & \quart{0}{32}{12}{149}\\
+  2 &   ant,  0.75 &    -0.23  &  0.23 & \quart{1}{25}{14}{149}\\
+  2 & ant,  0.25,  weight,  iP= 50\\% &    -0.22  &  0.08 & \quart{8}{9}{15}{149}\\
+  2 & ant,  0.75,  weight,  iP= 50\\% &    -0.21  &  0.13 & \quart{8}{15}{16}{149}\\
+\hline  3 &   ant,  Base &    -0.13  &  0.03 & \quart{24}{3}{25}{149}\\
 \hline \end{tabular}}
@@
 \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-  1 &   Base &    0.15  &  0.05 & \quart{0}{4}{1}{75}\\
-\hline  2 &   0.25 &    0.18  &  0.06 & \quart{1}{5}{4}{75}\\
-  2 & 0.25, weighting&    0.2  &  0.06 & \quart{2}{5}{6}{75}\\
-  2 & 0.25, weighting,  iP=50\% &    0.2  &  0.04 & \quart{4}{3}{6}{75}\\
-\hline  3 &  0.5, weighting&    0.25  &  0.1 & \quart{6}{9}{10}{75}\\
-  3 &    0.5 &    0.26  &  0.12 & \quart{6}{11}{11}{75}\\
-  3 & 0.5, weighting,  iP=50\% &    0.28  &  0.11 & \quart{10}{9}{13}{75}\\
-\hline  4 & 0.75, weighting&    0.39  &  0.16 & \quart{19}{13}{22}{75}\\
-  4 &   0.75 &    0.42  &  0.17 & \quart{15}{15}{25}{75}\\
-  4 & 0.75, weighting,  iP=50\% &    0.42  &  0.1 & \quart{20}{9}{25}{75}\\
+  1 & camel_0.75_w_iP(50\%) &    -0.45  &  0.17 & \quart{0}{21}{8}{189}\\
+\hline  2 &   camel_0.75 &    -0.39  &  0.21 & \quart{8}{26}{16}{189}\\
+  2 & camel_0.75_w &    -0.37  &  0.19 & \quart{9}{24}{18}{189}\\
+\hline  3 & camel_0.5_w_iP(50\%) &    -0.28  &  0.13 & \quart{19}{17}{29}{189}\\
+\hline  4 &  camel_0.5_w &    -0.26  &  0.1 & \quart{27}{12}{32}{189}\\
+  4 &    camel_0.5 &    -0.24  &  0.1 & \quart{29}{13}{34}{189}\\
+\hline  5 & camel_0.25_w_iP(50\%) &    -0.22  &  0.07 & \quart{33}{9}{37}{189}\\
+\hline  6 &   camel_0.25 &    -0.17  &  0.08 & \quart{39}{10}{43}{189}\\
+  6 & camel_0.25_w &    -0.17  &  0.06 & \quart{38}{8}{43}{189}\\
+  6 &   camel_Base &    -0.16  &  0.02 & \quart{43}{3}{44}{189}\\
 \hline \end{tabular}}
@@
 \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-  1 & 0.25, weighting,  iP=50\% &    0.15  &  0.04 & \quart{0}{2}{0}{55}\\
-\hline  2 &     Base &    0.16  &  0.0 & \quart{1}{0}{1}{55}\\
-  2 &     0.25 &    0.18  &  0.06 & \quart{1}{4}{2}{55}\\
-  2 &   0.25, weighting&    0.2  &  0.06 & \quart{1}{4}{3}{55}\\
-\hline  3 & 0.5, weighting,  iP=50\% &    0.28  &  0.08 & \quart{7}{5}{9}{55}\\
-\hline  4 &      0.5 &    0.33  &  0.11 & \quart{8}{7}{12}{55}\\
-  4 &    0.5, weighting&    0.37  &  0.09 & \quart{10}{6}{14}{55}\\
-\hline  5 & 0.75, weighting,  iP=50\% &    0.38  &  0.16 & \quart{12}{10}{15}{55}\\
-\hline  6 &   0.75, weighting&    0.56  &  0.08 & \quart{25}{5}{27}{55}\\
-  6 &     0.75 &    0.57  &  0.12 & \quart{25}{7}{27}{55}\\[-0.01cm]
+  1 &     ivy_0.75 &    -0.62  &  0.05 & \quart{0}{4}{1}{141}\\
+  1 &   ivy_0.75_w &    -0.61  &  0.09 & \quart{0}{7}{2}{141}\\
+\hline  2 &      ivy_0.5 &    -0.56  &  0.09 & \quart{4}{8}{6}{141}\\
+  2 &    ivy_0.5_w &    -0.53  &  0.12 & \quart{4}{10}{9}{141}\\
+\hline  3 &   ivy_0.25_w &    -0.41  &  0.06 & \quart{17}{5}{19}{141}\\
+  3 &     ivy_0.25 &    -0.39  &  0.06 & \quart{18}{6}{21}{141}\\
+\hline  4 & ivy_0.75_w_iP(50\%) &    -0.27  &  0.14 & \quart{27}{12}{31}{141}\\
+\hline  5 & ivy_0.5_w_iP(50\%) &    -0.18  &  0.06 & \quart{35}{5}{39}{141}\\
+\hline  6 & ivy_0.25_w_iP(50\%) &    -0.12  &  0.04 & \quart{42}{3}{44}{141}\\
+\hline  7 &     ivy_Base &    -0.06  &  0.0 & \quart{49}{0}{49}{141}\\
 \hline \end{tabular}}
@@
 \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-  1 &   Base &    0.06  &  0.01 & \quart{0}{0}{0}{64}\\
-\hline  2 & 0.25, weighting&    0.08  &  0.06 & \quart{0}{4}{1}{64}\\
-  2 &   0.25 &    0.09  &  0.05 & \quart{0}{3}{2}{64}\\
-\hline  3 & 0.25, weighting,  iP=50\% &    0.12  &  0.08 & \quart{1}{5}{4}{64}\\
-\hline  4 &  0.5, weighting&    0.16  &  0.09 & \quart{4}{6}{6}{64}\\
-  4 &    0.5 &    0.17  &  0.09 & \quart{4}{6}{7}{64}\\
-\hline  5 & 0.5, weighting,  iP=50\% &    0.22  &  0.11 & \quart{8}{8}{10}{64}\\
-  5 & 0.75, weighting&    0.26  &  0.18 & \quart{9}{12}{13}{64}\\
-\hline  6 &   0.75 &    0.38  &  0.31 & \quart{11}{21}{21}{64}\\
-  6 & 0.75, weighting,  iP=50\% &    0.41  &  0.17 & \quart{17}{12}{24}{64}\\
+  1 &   jedit_0.75 &    -0.55  &  0.19 & \quart{2}{17}{6}{142}\\
+  1 & jedit_0.75_w &    -0.55  &  0.35 & \quart{0}{30}{6}{142}\\
+\hline  2 &    jedit_0.5 &    -0.34  &  0.19 & \quart{14}{16}{24}{142}\\
+  2 &  jedit_0.5_w &    -0.31  &  0.08 & \quart{23}{7}{27}{142}\\
+  2 & jedit_0.75_w_iP(50\%) &    -0.32  &  0.17 & \quart{21}{14}{26}{142}\\
+\hline  3 & jedit_0.25_w &    -0.21  &  0.1 & \quart{33}{9}{35}{142}\\
+  3 &   jedit_0.25 &    -0.2  &  0.07 & \quart{32}{6}{36}{142}\\
+\hline  4 & jedit_0.5_w_iP(50\%) &    -0.16  &  0.11 & \quart{37}{10}{40}{142}\\
+\hline  5 & jedit_0.25_w_iP(50\%) &    -0.11  &  0.06 & \quart{42}{6}{44}{142}\\
+\hline  6 &   jedit_Base &    -0.05  &  0.0 & \quart{49}{0}{49}{142}\\
 \hline \end{tabular}}
@@
 \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-  1 &   Base &    0.06  &  0.03 & \quart{0}{4}{4}{139}\\
-\hline  2 & 0.25, weighting&    0.09  &  0.04 & \quart{4}{6}{8}{139}\\
-  2 &   0.25 &    0.09  &  0.06 & \quart{4}{8}{8}{139}\\
-  2 & 0.25, weighting,  iP=50\% &    0.09  &  0.04 & \quart{4}{6}{8}{139}\\
-  2 &    0.5 &    0.1  &  0.07 & \quart{4}{10}{10}{139}\\
-\hline  3 &  0.5, weighting&    0.12  &  0.03 & \quart{10}{4}{12}{139}\\
-\hline  4 & 0.75, weighting&    0.13  &  0.11 & \quart{10}{15}{14}{139}\\
-  4 &   0.75 &    0.13  &  0.06 & \quart{12}{9}{14}{139}\\
-  4 & 0.5, weighting,  iP=50\% &    0.13  &  0.06 & \quart{10}{8}{14}{139}\\
-\hline  5 & 0.75, weighting,  iP=50\% &    0.19  &  0.11 & \quart{17}{15}{22}{139}\\
+  1 &   log4j_0.75 &    -0.19  &  0.2 & \quart{0}{41}{24}{272}\\
+  1 & log4j_0.75_w &    -0.15  &  0.16 & \quart{6}{33}{33}{272}\\
+  1 & log4j_0.75_w_iP(50\%) &    -0.15  &  0.05 & \quart{29}{10}{33}{272}\\
+  1 &    log4j_0.5 &    -0.15  &  0.09 & \quart{27}{18}{33}{272}\\
+\hline  2 &   log4j_0.25 &    -0.12  &  0.07 & \quart{35}{14}{39}{272}\\
+  2 &   log4j_Base &    -0.11  &  0.04 & \quart{41}{8}{41}{272}\\
+  2 & log4j_0.25_w &    -0.1  &  0.03 & \quart{39}{6}{43}{272}\\
+  2 &  log4j_0.5_w &    -0.1  &  0.13 & \quart{22}{27}{43}{272}\\
+  2 & log4j_0.25_w_iP(50\%) &    -0.09  &  0.04 & \quart{39}{8}{45}{272}\\
+  2 & log4j_0.5_w_iP(50\%) &    -0.09  &  0.05 & \quart{39}{10}{45}{272}\\
 \hline \end{tabular}}
@@
 \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-  1 &  0.25 &    0.05  &  0.02 & \quart{1}{4}{3}{188}\\
-  1 & 0.25, weighting&    0.05  &  0.04 & \quart{0}{7}{3}{188}\\
-\hline  2 &   0.5 &    0.07  &  0.04 & \quart{3}{8}{7}{188}\\
-  2 & 0.25, weighting,  iP=50\% &    0.07  &  0.04 & \quart{3}{8}{7}{188}\\
-  2 & 0.5, weighting&    0.08  &  0.05 & \quart{5}{10}{9}{188}\\
-\hline  3 & 0.5, weighting,  iP=50\% &    0.1  &  0.03 & \quart{9}{6}{13}{188}\\
-  3 &  Base &    0.1  &  0.03 & \quart{7}{6}{13}{188}\\
-\hline  4 & 0.75, weighting,  iP=50\% &    0.13  &  0.09 & \quart{9}{18}{19}{188}\\
-  4 &  0.75 &    0.15  &  0.08 & \quart{13}{16}{23}{188}\\
-  4 & 0.75, weighting&    0.15  &  0.11 & \quart{11}{21}{23}{188}\\
+  1 & lucene_0.75_w_iP(50\%) &    -0.27  &  0.16 & \quart{0}{24}{10}{209}\\
+  1 &  lucene_0.75 &    -0.25  &  0.1 & \quart{6}{15}{14}{209}\\
+  1 & lucene_0.75_w &    -0.22  &  0.14 & \quart{6}{22}{18}{209}\\
+\hline  2 & lucene_0.5_w_iP(50\%) &    -0.18  &  0.09 & \quart{15}{14}{24}{209}\\
+\hline  3 & lucene_0.5_w &    -0.11  &  0.08 & \quart{29}{13}{35}{209}\\
+\hline  4 &  lucene_Base &    -0.1  &  0.01 & \quart{37}{2}{37}{209}\\
+  4 &   lucene_0.5 &    -0.09  &  0.07 & \quart{32}{11}{39}{209}\\
+  4 & lucene_0.25_w_iP(50\%) &    -0.09  &  0.03 & \quart{37}{5}{39}{209}\\
+\hline  5 &  lucene_0.25 &    -0.05  &  0.04 & \quart{42}{6}{45}{209}\\
+  5 & lucene_0.25_w &    -0.03  &  0.03 & \quart{45}{4}{48}{209}\\
 \hline \end{tabular}}
@@
 \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-  1 &     Base &    0.1  &  0.03 & \quart{0}{2}{1}{61}\\
-\hline  2 & 0.25, weighting,  iP=50\% &    0.14  &  0.1 & \quart{0}{6}{4}{61}\\
-\hline  3 &   0.25, weighting&    0.18  &  0.14 & \quart{4}{9}{6}{61}\\
-  3 &     0.25 &    0.19  &  0.11 & \quart{4}{7}{7}{61}\\
-  3 & 0.5, weighting,  iP=50\% &    0.2  &  0.19 & \quart{4}{13}{8}{61}\\
-\hline  4 & 0.75, weighting,  iP=50\% &    0.26  &  0.2 & \quart{8}{13}{12}{61}\\
-  4 &      0.5 &    0.28  &  0.2 & \quart{6}{14}{13}{61}\\
-  4 &    0.5, weighting&    0.33  &  0.22 & \quart{10}{14}{16}{61}\\
-\hline  5 &     0.75 &    0.47  &  0.22 & \quart{18}{14}{26}{61}\\
-  5 &   0.75, weighting&    0.46  &  0.11 & \quart{22}{7}{25}{61}\\
+  1 &   poi_0.75_w &    -0.59  &  0.36 & \quart{0}{26}{9}{123}\\
+  1 &      poi_0.5 &    -0.5  &  0.28 & \quart{12}{20}{16}{123}\\
+  1 &     poi_0.75 &    -0.5  &  0.47 & \quart{0}{33}{16}{123}\\
+\hline  2 &    poi_0.5_w &    -0.37  &  0.51 & \quart{4}{37}{25}{123}\\
+  2 & poi_0.75_w_iP(50\%) &    -0.34  &  0.41 & \quart{15}{29}{27}{123}\\
+\hline  3 &   poi_0.25_w &    -0.25  &  0.31 & \quart{23}{22}{34}{123}\\
+  3 &     poi_0.25 &    -0.23  &  0.29 & \quart{24}{20}{35}{123}\\
+\hline  4 & poi_0.5_w_iP(50\%) &    -0.11  &  0.12 & \quart{39}{9}{44}{123}\\
+  4 &     poi_Base &    -0.09  &  0.06 & \quart{43}{4}{45}{123}\\
+  4 & poi_0.25_w_iP(50\%) &    -0.08  &  0.15 & \quart{39}{10}{46}{123}\\
 \hline \end{tabular}}

### 2015-04-29 manuscript.tex
Updates from ShareLaTeX

@@
 \begin{document}
-  \title{``Don't tell me what it is, tell me what to do'':\\Instance-Based Planning for Actionable Analytics}
+  \title{Temporal Transfer Learning with ``HERE'':\\ Local Policy Generation (in Near Linear Time)}
 
@@
   \maketitle
+  \pagestyle{plain}
 
   \begin{abstract}
-
+ Busy project managers grow impatient with analytcs
   \end{abstract}
@@
 \section{Introduction}
+
+In the $21^{st}$ century, it is now impossible to manually browse all
+the available software defect data.  For example, as of April 2015,
+Mozilla Firefox has over a million bug reports on software projects.  While it is
+now possible to automatically analyze such data with data miners, at
+some stage a group of business users will have to convene to {\em
+  interpret the results} (e.g., to decide if it is wise to deploy the
+results as a defect reduction method within an organization).
+These business  users are now demanding that data mining tools
+be augmented with tools to support  business-level
+interpretation of that data. For example,
+at a  panel on software analytics at ICSE'12,
+industrial practitioners lamented the state of the art in data mining
+and software engineering~\cite{menzies12a}. Panelists commented that
+``prediction is all well and good, but what about decision
+making?''. That is, these panelists are more interested in the interpretations
+that follow the mining, rather than just  the mining.
+
+In order to satisfy these panelists, w  explore the generation of {\em policies} in the context
+of software analytics. Such {\em policies} are recommendations of what
+to change in order to better achieve some goal. In this paper the two
+case studies are:
+\bi
+\item Learning code changes to static code features that reduce
+the number of defects;
+\item Learning reconfigurations of Makefiles such that, when the code
+is compiled, that code runs faster.
+\ei
+Note that {\em policy generation} is different to the standard
+data mining tasks of prediction or classification.  Predictors
+and classifiers only tell us what {\em is} while policy 
+generators tell us {\em what to do}.
+
+The tool used to generate these policies is ``HERE'', an instance-based
+local search algorithm that looks for improvement trends in the data,
+then adjusting examples to nudge them along that improvement. While
+our case studies are defect and runtime reduction, HERE is a general
+purpose algorithm that could be applied to any table of data with at least
+one column whose values can be sorted from ``desired'' to ``undesired''.
+
+\section{Related Work}
+Policy generation is different to standard data mining in that the 
+latter is most concerned with what {\em is} rather than {\em what to do}.
+For example, a classification or prediction system such as C4.5~\cite{quinlan92} or CART~\cite{breiman84} can predict for a discrete or continuous class variable
+(respectively). As such, they can be used as a sub-routine within a
+policy generator. For example, later in this paper we will use the CART
+prediction system to assess the policies generated by HERE.
+
+Policy generation with HERE is different to the recommendor systems.
+As described by Robillard and Walker~\cite{rob14}, recommendor systems
+in software engineering
+are less {\em directive} and more    {\em collaborative} than policy
+generators:
+\bi
+\item
+Directive systems such as HERE tell developers exactly what to do
+(e.g. ``use these settings in a Makefile'') 
+\item
+Collaborative systems are more suggestive guides that
+help (e.g.) programmers focus on very small sets
+with  very large libraries of code of documentation.
+\ei
+Collaborative systems may not presume to know what to do
+in that smaller set (while the directive systems would issue an edict
+such as  ``change this to that'').
+
+We also distinguish HERE's policy generation fro the multi-objective optimization methods explored by Harman and Krall and Menzies and 
+and many ithers.
+
+Previous with have explored model-based policy generation with STAR,
+NOVA, and instance-based policy generation with  W2.
+
+refactoring XXX
+
+Finally, we note that HERE is a temporal transfer learner.
+
 {\bf RQ1: Can Instance-based Learning techniques be used to create Planning tools that can better analyse software defect?}
@@
         amc & average method complexity & e.g. number of JAVA byte codes\\\hline
-        avg\_cc & average McCabe & average McCabe's cyclomatic complexity seen
+        avg\, cc & average McCabe & average McCabe's cyclomatic complexity seen
         in class\\\hline
@@
         then
-        $lcom3=((\frac{1}{a} \sum_j^a \mu(a_j)) - m)/ (1-m)$.
+        $lcom3=((\frac{1}{a} \sum, j^a \mu(a, j)) - m)/ (1-m)$.
         \\\hline
         loc & lines of code &\\\hline
-        max\_cc & maximum McCabe & maximum McCabe's cyclomatic complexity seen
+        max\, cc & maximum McCabe & maximum McCabe's cyclomatic complexity seen
         in class\\\hline
@@
 \begin{figure}[tbp!]
-% \subfloat[\label{oracle}]{\includegraphics[width=\linewidth]{./_figs/Oracle}}\\
-\includegraphics[width=\linewidth]{./_figs/WHAT}
+% \subfloat[\label{oracle}]{\includegraphics[width=\linewidth]{{_figs//Oracle}}\\
+\includegraphics[width=\linewidth]{_figs/WHAT}
 \caption{Experimental Rig}
@@
 
-%   \subfloat[Experimental Rig for Defect Prediction]{  \includegraphics[width=\linewidth]{./_figs/WHAT}
+%   \subfloat[Experimental Rig for Defect Prediction]{  \includegraphics[width=\linewidth]{_figs/WHAT}
 %   \label{fig:rig2}}
@@
   {\scriptsize \textbf{Ant}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-      \arrayrulecolor{darkgray}
-      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-  1 & ant,  0.25,  weight &    -0.33  &  0.05 & \quart{1}{5}{3}{149}\\
-  1 &   ant,  0.25 &    -0.31  &  0.06 & \quart{2}{6}{5}{149}\\
-  1 &    ant,  0.5 &    -0.28  &  0.15 & \quart{1}{16}{8}{149}\\
-\hline  2 & ant,  0.5,  weight &    -0.26  &  0.19 & \quart{0}{20}{10}{149}\\
-  2 & ant,  0.5,  weight,  iP= 50\\% &    -0.26  &  0.11 & \quart{5}{12}{10}{149}\\
-  2 & ant,  0.75,  weight &    -0.25  &  0.3 & \quart{0}{32}{12}{149}\\
-  2 &   ant,  0.75 &    -0.23  &  0.23 & \quart{1}{25}{14}{149}\\
-  2 & ant,  0.25,  weight,  iP= 50\\% &    -0.22  &  0.08 & \quart{8}{9}{15}{149}\\
-  2 & ant,  0.75,  weight,  iP= 50\\% &    -0.21  &  0.13 & \quart{8}{15}{16}{149}\\
-\hline  3 &   ant,  Base &    -0.13  &  0.03 & \quart{24}{3}{25}{149}\\
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
+      \arrayrulecolor{darkgray}
+      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+  1 & 0.75 &    -0.63  &  0.08 & \quart{2}{7}{5}{144} \\
+  1 & 0.75, weighting &    -0.6  &  0.2 & \quart{0}{16}{8}{144} \\
+\hline  2 & 0.5, weighting &    -0.42  &  0.11 & \quart{17}{10}{23}{144} \\
+  2 & 0.5 &    -0.42  &  0.11 & \quart{19}{9}{23}{144} \\
+  2 & 0.75, weighting, Prune=50\% &    -0.4  &  0.11 & \quart{20}{9}{25}{144} \\
+\hline  3 & 0.25 &    -0.28  &  0.09 & \quart{31}{7}{35}{144} \\
+  3 & 0.25, weighting &    -0.28  &  0.08 & \quart{31}{7}{35}{144} \\
+\hline  4 & 0.5, weighting, Prune=50\% &    -0.25  &  0.06 & \quart{35}{5}{38}{144} \\
+\hline  5 & 0.25, weighting, Prune=50\% &    -0.19  &  0.05 & \quart{41}{4}{43}{144} \\
+\hline  6 & Baseline &    -0.11  &  0.03 & \quart{47}{2}{49}{144} \\
 \hline \end{tabular}}
@@
   {\scriptsize \textbf{Camel}\\}
-{\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-  1 & camel_0.75_w_iP(50\%) &    -0.45  &  0.17 & \quart{0}{21}{8}{189}\\
-\hline  2 &   camel_0.75 &    -0.39  &  0.21 & \quart{8}{26}{16}{189}\\
-  2 & camel_0.75_w &    -0.37  &  0.19 & \quart{9}{24}{18}{189}\\
-\hline  3 & camel_0.5_w_iP(50\%) &    -0.28  &  0.13 & \quart{19}{17}{29}{189}\\
-\hline  4 &  camel_0.5_w &    -0.26  &  0.1 & \quart{27}{12}{32}{189}\\
-  4 &    camel_0.5 &    -0.24  &  0.1 & \quart{29}{13}{34}{189}\\
-\hline  5 & camel_0.25_w_iP(50\%) &    -0.22  &  0.07 & \quart{33}{9}{37}{189}\\
-\hline  6 &   camel_0.25 &    -0.17  &  0.08 & \quart{39}{10}{43}{189}\\
-  6 & camel_0.25_w &    -0.17  &  0.06 & \quart{38}{8}{43}{189}\\
-  6 &   camel_Base &    -0.16  &  0.02 & \quart{43}{3}{44}{189}\\
+{\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+  1 &  0.75, weighting, Prune=50\% &    -0.41  &  0.1 & \quart{2}{14}{9}{205} \\
+  1 &  0.75 &    -0.41  &  0.23 & \quart{1}{32}{9}{205} \\
+  1 &  0.75, weighting &    -0.39  &  0.16 & \quart{0}{22}{12}{205} \\
+\hline  2 &  0.5, weighting, Prune=50\% &    -0.27  &  0.09 & \quart{19}{12}{29}{205} \\
+  2 &  0.5 &    -0.26  &  0.12 & \quart{20}{17}{30}{205} \\
+  2 &  0.5, weighting &    -0.24  &  0.09 & \quart{24}{13}{33}{205} \\
+\hline  3 &  0.25, weighting, Prune=50\% &    -0.2  &  0.05 & \quart{36}{7}{38}{205} \\
+  3 &  0.25, weighting &    -0.19  &  0.07 & \quart{36}{9}{40}{205} \\
+  3 &  0.25 &    -0.17  &  0.06 & \quart{37}{8}{43}{205} \\
+\hline  4 &  Baseline &    -0.15  &  0.06 & \quart{41}{8}{45}{205} \\
 \hline \end{tabular}}
@@
   {\scriptsize \textbf{Ivy}\\[-0.05cm]}
-{\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-  1 &     ivy_0.75 &    -0.62  &  0.05 & \quart{0}{4}{1}{141}\\
-  1 &   ivy_0.75_w &    -0.61  &  0.09 & \quart{0}{7}{2}{141}\\
-\hline  2 &      ivy_0.5 &    -0.56  &  0.09 & \quart{4}{8}{6}{141}\\
-  2 &    ivy_0.5_w &    -0.53  &  0.12 & \quart{4}{10}{9}{141}\\
-\hline  3 &   ivy_0.25_w &    -0.41  &  0.06 & \quart{17}{5}{19}{141}\\
-  3 &     ivy_0.25 &    -0.39  &  0.06 & \quart{18}{6}{21}{141}\\
-\hline  4 & ivy_0.75_w_iP(50\%) &    -0.27  &  0.14 & \quart{27}{12}{31}{141}\\
-\hline  5 & ivy_0.5_w_iP(50\%) &    -0.18  &  0.06 & \quart{35}{5}{39}{141}\\
-\hline  6 & ivy_0.25_w_iP(50\%) &    -0.12  &  0.04 & \quart{42}{3}{44}{141}\\
-\hline  7 &     ivy_Base &    -0.06  &  0.0 & \quart{49}{0}{49}{141}\\
+{\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+  1 &     0.75 &    -0.57  &  0.17 & \quart{0}{16}{6}{163} \\
+  1 &   0.75, weighting &    -0.55  &  0.11 & \quart{3}{11}{8}{163} \\
+\hline  2 &   0.75, weighting, Prune=50\% &    -0.38  &  0.11 & \quart{19}{11}{25}{163} \\
+  2 &    0.5, weighting &    -0.36  &  0.12 & \quart{23}{12}{27}{163} \\
+  2 &   0.5 &    -0.33  &  0.11 & \quart{25}{11}{30}{163} \\
+\hline  3 &   0.5, weighting, Prune=50\% &    -0.27  &  0.08 & \quart{30}{8}{36}{163} \\
+\hline  4 &   0.25, weighting &    -0.2  &  0.07 & \quart{41}{7}{43}{163} \\
+  4 &     0.25 &    -0.16  &  0.04 & \quart{43}{4}{47}{163} \\
+  4 &     Baseline &    -0.16  &  0.0 & \quart{47}{0}{47}{163} \\
+\hline  5 &   0.25, weighting, Prune=50\% &    -0.15  &  0.04 & \quart{45}{4}{48}{163} \\
 \hline \end{tabular}}
@@
   {\scriptsize \textbf{Jedit}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-  1 &   jedit_0.75 &    -0.55  &  0.19 & \quart{2}{17}{6}{142}\\
-  1 & jedit_0.75_w &    -0.55  &  0.35 & \quart{0}{30}{6}{142}\\
-\hline  2 &    jedit_0.5 &    -0.34  &  0.19 & \quart{14}{16}{24}{142}\\
-  2 &  jedit_0.5_w &    -0.31  &  0.08 & \quart{23}{7}{27}{142}\\
-  2 & jedit_0.75_w_iP(50\%) &    -0.32  &  0.17 & \quart{21}{14}{26}{142}\\
-\hline  3 & jedit_0.25_w &    -0.21  &  0.1 & \quart{33}{9}{35}{142}\\
-  3 &   jedit_0.25 &    -0.2  &  0.07 & \quart{32}{6}{36}{142}\\
-\hline  4 & jedit_0.5_w_iP(50\%) &    -0.16  &  0.11 & \quart{37}{10}{40}{142}\\
-\hline  5 & jedit_0.25_w_iP(50\%) &    -0.11  &  0.06 & \quart{42}{6}{44}{142}\\
-\hline  6 &   jedit_Base &    -0.05  &  0.0 & \quart{49}{0}{49}{142}\\
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+  1 &  0.75, weighting, Prune=50\% &    -0.41  &  0.18 & \quart{0}{20}{8}{172} \\
+  1 &  0.75 &    -0.35  &  0.26 & \quart{0}{30}{15}{172} \\
+\hline  2 &  0.75, weighting &    -0.25  &  0.17 & \quart{16}{20}{26}{172} \\
+  2 &  0.5, weighting, Prune=50\% &    -0.21  &  0.1 & \quart{23}{11}{31}{172} \\
+\hline  3 &   0.5 &    -0.17  &  0.08 & \quart{32}{9}{36}{172} \\
+  3 &  0.5, weighting &    -0.14  &  0.09 & \quart{31}{10}{39}{172} \\
+\hline  4 &  0.25, weighting, Prune=50\% &    -0.12  &  0.06 & \quart{39}{7}{41}{172} \\
+\hline  5 &  0.25 &    -0.08  &  0.05 & \quart{43}{5}{46}{172} \\
+  5 &  0.25, weighting &    -0.08  &  0.06 & \quart{43}{6}{46}{172} \\
+\hline  6 &  Baseline &    -0.06  &  0.01 & \quart{47}{1}{48}{172} \\
 \hline \end{tabular}}
@@
   {\scriptsize \textbf{Log4j}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-  1 &   log4j_0.75 &    -0.19  &  0.2 & \quart{0}{41}{24}{272}\\
-  1 & log4j_0.75_w &    -0.15  &  0.16 & \quart{6}{33}{33}{272}\\
-  1 & log4j_0.75_w_iP(50\%) &    -0.15  &  0.05 & \quart{29}{10}{33}{272}\\
-  1 &    log4j_0.5 &    -0.15  &  0.09 & \quart{27}{18}{33}{272}\\
-\hline  2 &   log4j_0.25 &    -0.12  &  0.07 & \quart{35}{14}{39}{272}\\
-  2 &   log4j_Base &    -0.11  &  0.04 & \quart{41}{8}{41}{272}\\
-  2 & log4j_0.25_w &    -0.1  &  0.03 & \quart{39}{6}{43}{272}\\
-  2 &  log4j_0.5_w &    -0.1  &  0.13 & \quart{22}{27}{43}{272}\\
-  2 & log4j_0.25_w_iP(50\%) &    -0.09  &  0.04 & \quart{39}{8}{45}{272}\\
-  2 & log4j_0.5_w_iP(50\%) &    -0.09  &  0.05 & \quart{39}{10}{45}{272}\\
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+  1 &  0.75, weighting, Prune=50\% &    -0.19  &  0.13 & \quart{0}{28}{15}{273} \\
+\hline  2 &  0.75 &    -0.13  &  0.06 & \quart{23}{13}{28}{273} \\
+  2 &  0.5, weighting, Prune=50\% &    -0.13  &  0.05 & \quart{23}{11}{28}{273} \\
+  2 &  0.75, weighting &    -0.12  &  0.1 & \quart{15}{21}{30}{273} \\
+\hline  3 &  0.5, weighting &    -0.1  &  0.03 & \quart{28}{6}{34}{273} \\
+\hline  4 &   0.5 &    -0.1  &  0.07 & \quart{28}{15}{34}{273} \\
+  4 &  0.25 &    -0.09  &  0.04 & \quart{34}{9}{36}{273} \\
+  4 &  0.25, weighting, Prune=50\% &    -0.09  &  0.04 & \quart{34}{9}{36}{273} \\
+  4 &  0.25, weighting &    -0.06  &  0.04 & \quart{34}{9}{43}{273} \\
+\hline  5 &  Baseline &    -0.06  &  0.03 & \quart{43}{6}{43}{273} \\
 \hline \end{tabular}}
@@
   {\scriptsize \textbf{Lucene}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-  1 & lucene_0.75_w_iP(50\%) &    -0.27  &  0.16 & \quart{0}{24}{10}{209}\\
-  1 &  lucene_0.75 &    -0.25  &  0.1 & \quart{6}{15}{14}{209}\\
-  1 & lucene_0.75_w &    -0.22  &  0.14 & \quart{6}{22}{18}{209}\\
-\hline  2 & lucene_0.5_w_iP(50\%) &    -0.18  &  0.09 & \quart{15}{14}{24}{209}\\
-\hline  3 & lucene_0.5_w &    -0.11  &  0.08 & \quart{29}{13}{35}{209}\\
-\hline  4 &  lucene_Base &    -0.1  &  0.01 & \quart{37}{2}{37}{209}\\
-  4 &   lucene_0.5 &    -0.09  &  0.07 & \quart{32}{11}{39}{209}\\
-  4 & lucene_0.25_w_iP(50\%) &    -0.09  &  0.03 & \quart{37}{5}{39}{209}\\
-\hline  5 &  lucene_0.25 &    -0.05  &  0.04 & \quart{42}{6}{45}{209}\\
-  5 & lucene_0.25_w &    -0.03  &  0.03 & \quart{45}{4}{48}{209}\\
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+  1 &  0.75, weighting &    -0.15  &  0.09 & \quart{0}{29}{9}{393} \\
+  1 &  0.75 &    -0.13  &  0.09 & \quart{0}{29}{16}{393} \\
+  1 &  0.75, weighting, Prune=50\% &    -0.12  &  0.08 & \quart{6}{27}{19}{393} \\
+\hline  2 &  Baseline &    -0.1  &  0.03 & \quart{26}{10}{26}{393} \\
+  2 &  0.5, weighting, Prune=50\% &    -0.1  &  0.03 & \quart{23}{10}{26}{393} \\
+\hline  3 &  0.5, weighting &    -0.08  &  0.06 & \quart{23}{20}{33}{393} \\
+  3 &  0.25, weighting, Prune=50\% &    -0.07  &  0.03 & \quart{33}{10}{36}{393} \\
+  3 &  0.5 &    -0.07  &  0.05 & \quart{29}{17}{36}{393} \\
+\hline  4 &  0.25, weighting &    -0.04  &  0.04 & \quart{36}{13}{46}{393} \\
+  4 &  0.25 &    -0.04  &  0.02 & \quart{39}{7}{46}{393} \\
 \hline \end{tabular}}
@@
   {\scriptsize \textbf{Poi}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-      \arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-  1 &   poi_0.75_w &    -0.59  &  0.36 & \quart{0}{26}{9}{123}\\
-  1 &      poi_0.5 &    -0.5  &  0.28 & \quart{12}{20}{16}{123}\\
-  1 &     poi_0.75 &    -0.5  &  0.47 & \quart{0}{33}{16}{123}\\
-\hline  2 &    poi_0.5_w &    -0.37  &  0.51 & \quart{4}{37}{25}{123}\\
-  2 & poi_0.75_w_iP(50\%) &    -0.34  &  0.41 & \quart{15}{29}{27}{123}\\
-\hline  3 &   poi_0.25_w &    -0.25  &  0.31 & \quart{23}{22}{34}{123}\\
-  3 &     poi_0.25 &    -0.23  &  0.29 & \quart{24}{20}{35}{123}\\
-\hline  4 & poi_0.5_w_iP(50\%) &    -0.11  &  0.12 & \quart{39}{9}{44}{123}\\
-  4 &     poi_Base &    -0.09  &  0.06 & \quart{43}{4}{45}{123}\\
-  4 & poi_0.25_w_iP(50\%) &    -0.08  &  0.15 & \quart{39}{10}{46}{123}\\
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
+      \arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+  1 & 0.75, weighting &    -0.45  &  0.1 & \quart{6}{10}{11}{162} \\
+  1 &  0.75 &    -0.44  &  0.23 & \quart{0}{23}{12}{162} \\
+\hline  2 & 0.5, weighting &    -0.32  &  0.23 & \quart{12}{24}{24}{162} \\
+  2 & 0.5 &    -0.26  &  0.23 & \quart{18}{24}{31}{162} \\
+  2 & 0.75, weighting, Prune=50\% &    -0.25  &  0.19 & \quart{17}{20}{32}{162} \\
+\hline  3 & 0.5, weighting, Prune=50\% &    -0.19  &  0.09 & \quart{34}{9}{38}{162} \\
+  3 &  0.25 &    -0.19  &  0.11 & \quart{32}{11}{38}{162} \\
+  3 & 0.25, weighting &    -0.17  &  0.14 & \quart{30}{14}{40}{162} \\
+\hline  4 & 0.25, weighting, Prune=50\% &    -0.12  &  0.09 & \quart{40}{9}{45}{162} \\
+\hline  5 &  Baseline &    -0.09  &  0.03 & \quart{46}{3}{48}{162} \\
 \hline \end{tabular}}
@@
   {\scriptsize \textbf{Synapse}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-  1 & Base &    0.15  &  0.0 & \quart{1}{0}{1}{44}\\
-  1 & 0.5, weighting,  iP=50\% &    0.15  &  0.08 & \quart{1}{4}{1}{44}\\
-  1 & 0.25, weighting,  iP=50\% &    0.17  &  0.08 & \quart{0}{4}{2}{44}\\
-\hline  2 & 0.75, weighting,  iP=50\% &    0.21  &  0.08 & \quart{1}{4}{4}{44}\\
-  2 & 0.25 &    0.23  &  0.18 & \quart{2}{9}{5}{44}\\
-  2 & 0.25, weighting&    0.23  &  0.11 & \quart{2}{5}{5}{44}\\
-\hline  3 & 0.5, weighting&    0.38  &  0.19 & \quart{7}{10}{12}{44}\\
-  3 &  0.5 &    0.42  &  0.27 & \quart{6}{14}{14}{44}\\
-\hline  4 & 0.75 &    0.5  &  0.39 & \quart{12}{20}{19}{44}\\
-  4 & 0.75, weighting&    0.56  &  0.25 & \quart{17}{12}{22}{44}\\
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+  1 & 0.75, weighting &    -0.56  &  0.2 & \quart{7}{18}{11}{148} \\
+  1 & 0.75 &    -0.48  &  0.34 & \quart{0}{29}{18}{148} \\
+\hline  2 & 0.5 &    -0.4  &  0.27 & \quart{14}{24}{25}{148} \\
+  2 & 0.5, weighting &    -0.37  &  0.17 & \quart{21}{15}{28}{148} \\
+\hline  3 & 0.25 &    -0.23  &  0.16 & \quart{31}{14}{40}{148} \\
+  3 & 0.25, weighting &    -0.23  &  0.1 & \quart{38}{9}{40}{148} \\
+  3 & 0.75, weighting, Prune=50\% &    -0.19  &  0.08 & \quart{40}{7}{43}{148} \\
+\hline  4 & 0.25, weighting, Prune=50\% &    -0.17  &  0.08 & \quart{42}{7}{45}{148} \\
+  4 & Baseline &    -0.15  &  0.0 & \quart{47}{0}{47}{148} \\
+  4 & 0.5, weighting, Prune=50\% &    -0.15  &  0.11 & \quart{40}{9}{47}{148} \\
 \hline \end{tabular}}
@@
   \flushleft
-  {\scriptsize \textbf{Velocity}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-  1 & 0.25, weighting,  iP=50\% &    0.03  &  0.06 & \quart{0}{5}{1}{98}\\
-  1 & 0.25 &    0.04  &  0.02 & \quart{1}{2}{2}{98}\\
-  1 & 0.25, weighting&    0.05  &  0.03 & \quart{2}{3}{3}{98}\\
-  1 & Base &    0.05  &  0.06 & \quart{0}{5}{3}{98}\\
-\hline  2 & 0.5, weighting,  iP=50\% &    0.07  &  0.11 & \quart{3}{11}{5}{98}\\
-  2 & 0.5, weighting&    0.1  &  0.08 & \quart{5}{8}{8}{98}\\
-\hline  3 & 0.5 &    0.13  &  0.12 & \quart{5}{12}{11}{98}\\
-\hline  4 & 0.75 &    0.16  &  0.24 & \quart{8}{24}{14}{98}\\
-  4 & 0.75, weighting,  iP=50\% &    0.17  &  0.15 & \quart{9}{15}{15}{98}\\
-  4 & 0.75, weighting&    0.22  &  0.22 & \quart{9}{22}{20}{98}\\
+  {\scriptsize \textbf{Velocity}\\
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+  1 & 0.75, weighting &    -0.19  &  0.22 & \quart{1}{34}{21}{207} \\
+  1 & 0.75, weighting, Prune=50\% &    -0.15  &  0.13 & \quart{14}{20}{28}{207} \\
+  1 & 0.75 &    -0.14  &  0.23 & \quart{0}{35}{29}{207} \\
+\hline  2 & 0.5 &    -0.13  &  0.11 & \quart{23}{17}{31}{207} \\
+\hline  3 & 0.5, weighting &    -0.1  &  0.08 & \quart{29}{13}{35}{207} \\
+  3 & 0.5, weighting, Prune=50\% &    -0.07  &  0.07 & \quart{32}{11}{40}{207} \\
+\hline  4 & Baseline &    -0.05  &  0.04 & \quart{43}{6}{43}{207} \\
+  4 & 0.25, weighting &    -0.05  &  0.03 & \quart{40}{5}{43}{207} \\
+  4 & 0.25 &    -0.04  &  0.02 & \quart{43}{3}{45}{207} \\
+  4 & 0.25, weighting, Prune=50\% &    -0.01  &  0.04 & \quart{43}{6}{49}{207} \\
 \hline \end{tabular}}
@@
   {\scriptsize \textbf{Xalan}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-  1 &   Base &    0.08  &  0.02 & \quart{0}{1}{0}{80}\\
-\hline  2 & 0.5, weighting,  iP=50\% &    0.14  &  0.05 & \quart{3}{4}{6}{80}\\
-  2 & 0.75, weighting,  iP=50\% &    0.15  &  0.06 & \quart{5}{5}{6}{80}\\
-  2 & 0.25, weighting,  iP=50\% &    0.15  &  0.06 & \quart{3}{5}{6}{80}\\
-\hline  3 &   0.25 &    0.23  &  0.11 & \quart{8}{10}{13}{80}\\
-  3 & 0.25, weighting&    0.23  &  0.09 & \quart{10}{8}{13}{80}\\
-\hline  4 &  0.5, weighting&    0.28  &  0.06 & \quart{16}{5}{18}{80}\\
-\hline  5 &    0.5 &    0.3  &  0.13 & \quart{15}{11}{19}{80}\\
-  5 & 0.75, weighting&    0.34  &  0.19 & \quart{16}{16}{23}{80}\\
-  5 &   0.75 &    0.38  &  0.11 & \quart{21}{10}{26}{80}\\
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+  1 & 0.75 &    -0.36  &  0.12 & \quart{0}{16}{9}{198} \\
+  1 & 0.75, weighting &    -0.3  &  0.17 & \quart{4}{23}{18}{198} \\
+  1 &    0.5 &    -0.3  &  0.12 & \quart{9}{17}{18}{198} \\
+\hline  2 & 0.5, weighting &    -0.28  &  0.09 & \quart{16}{13}{20}{198} \\
+\hline  3 & 0.25, weighting &    -0.23  &  0.1 & \quart{20}{14}{27}{198} \\
+  3 & 0.25 &    -0.23  &  0.12 & \quart{20}{17}{27}{198} \\
+\hline  4 & 0.25, weighting, Prune=50\% &    -0.14  &  0.07 & \quart{36}{9}{40}{198} \\
+  4 & 0.75, weighting, Prune=50\% &    -0.14  &  0.07 & \quart{33}{10}{40}{198} \\
+  4 & 0.5, weighting, Prune=50\% &    -0.12  &  0.06 & \quart{37}{8}{43}{198} \\
+\hline  5 & Baseline &    -0.08  &  0.02 & \quart{47}{2}{48}{198} \\
 \hline \end{tabular}}

### 2015-05-01 manuscript.tex
Updates from ShareLaTeX

@@
  \usepackage{pifont}
+ \usepackage{times}
 \usepackage{rotating}
@@
 % additional keywords
-morekeywords={[3]fastmap, project, furthest, split, WHERE,clusterer, getContours, envied, fWeight, nearestContour, projection, mutate, WHAT, knn},
+morekeywords={[3]fastmap, project, furthest, split, WHERE,clusterer, getContours, envied, fWeight, nearestContour, projection, mutate, HERE, knn},
 keywordstyle={[3]\color{Keywords}\bfseries},
@@
 
+\author{
+% You can go ahead and credit any number of authors here,
+% e.g. one 'row of three' or two rows (consisting of one row of three
+% and a second row of one, two or three).
+%
+% The command \alignauthor (no curly braces needed) should
+% precede each author name, affiliation/snail-mail address and
+% e-mail address. Additionally, tag each line of
+% affiliation/address with \affaddr, and tag the
+% e-mail address with \email.
+%
+% 1st. author
+Rahul Krishna, Tim Menzies, Xipeng Shen\\
+       \affaddr{Computer Science, NcState, USA}\\
+       \{i.m.ralk, tim.menzies, xipengshen\}@gmail.com
+% 3rd. author
+ % use '\and' if you need 'another row' of author names
+% 4th. author
+\and
+ Andrian Marcus\\
+       \affaddr{Computer Science, UtDallas, USA}\\
+       {amarcus@utdallas.edu} }
+
 \begin{document}
-  \title{Temporal Transfer Learning with ``HERE'':\\ Local Policy Generation (in Near Linear Time)}
+  \title{Learning Actionable Analytics 
+ (with Applications for Reducing Defects and Reducing Runtimes)}
 
@@
   \begin{abstract}
- Busy project managers grow impatient with analytcs
+ As business users demand more insightful
+ analytics, data scientists need to change
+ their tools. Instead of merely predicting 
+ some result, they also need tools that generate ``policy advice'';
+ i.e. suggestions on  how to change values in order to
+ improve on some predicted value.
+
+ This paper proposes one such policy
+ generator. ``HOW'' is a near-linear-time
+ tool for proposing changes to independent
+ variables in order to improve on 
+ the predictions of the dependent variables. Unlike other approaches
+ for learning optimizations to software does not require
+ an underlying of the domain (rather, HOW automatically
+ learns that model as part of its operation).
+
+ This paper uses  HOW to learn methods
+ to reduce defects and decrease program runtime.
+ For the test data used in this paper,
+ we have observed that the improvements generated by HERE can reduce
+ defect prediction and runtimes by up to
+ 50\% of their original values.
   \end{abstract}
   \begin{IEEEkeywords}
-    defect prediction, CART
+Instance-based reasoning, defect prediction, random forest, optimization.
   \end{IEEEkeywords}
@@
 \section{Introduction}
-
 In the $21^{st}$ century, it is now impossible to manually browse all
@@
 results as a defect reduction method within an organization).
+
 These business  users are now demanding that data mining tools
@@
 making?''. That is, these panelists are more interested in the interpretations
-that follow the mining, rather than just  the mining.
-
-In order to satisfy these panelists, w  explore the generation of {\em policies} in the context
+that follow the mining, rather than just  the mining. For example:
+\bi
+\item Instead of just accepting  {\em predictions} on how many 
+ software defects
+to expect,  business users now demand {\em policies} that
+reduce the likelihood of those defects;
+\item Instead of just accepting {\em predictions} on the runtime
+time of their software, business users might now demand
+{\em policies} that reduce that runtime.
+\ei
+In order to satisfy the demands of this new kind of business user, we  explore the generation of {\em policies} in the context
 of software analytics. Such {\em policies} are recommendations of what
-to change in order to better achieve some goal. In this paper the two
-case studies are:
+to change in order to better achieve some goal. 
+Note that such {\em policy generation} is very different to the standard
+data mining tasks of prediction some discrete or numeric class.
+Predictors
+and classifiers only tell us what {\em is} while policy 
+generators tell us {\em what to change}. For the kind of business user
+discussed above, policy generators are the prefeered tool since,
+as one gruff user once shouted at us ``don't tell me what \underline{is};
+tell me what to \underline{change}''.
+
+This paper presents the following general framework for extending  predictor systems
+such that they become 
+policy generators:
+\begin{small}
+\[
+project\;data \rightarrow \left\{\begin{array}{l}\mathit{train}
+\rightarrow \left\{\begin{array}{l}\mathit{predictor\;(e.g.\;CART\;or\; RF)}\\
+\mathit{policy\; generator\; (e.g.\; HOW)}\end{array}\right.
+\\
+~\\
+\mathit{test}  \rightarrow  \left\{\begin{array}{r@{~}l}
+\mathit{before}& =\mathit{predictor}(\mathit{test})\\
+\mathit{after}& =\mathit{predictor}(\; \mathit{policy}(\mathit{test})\;)\\
+\Delta& =\mathit{after} / \mathit{before}
+\end{array}\right.
+\end{array} \right.
+\]
+\end{small}
+In the above:
 \bi
-\item Learning code changes to static code features that reduce
-the number of defects;
-\item Learning reconfigurations of Makefiles such that, when the code
-is compiled, that code runs faster.
+\item
+Project data is divided into a train and test set.
+\item
+From the train set, we learn {\em both} a policy generator as well
+as a predictor using (e.g.)
+CART (for making numeric predictions~\cite{Breiman1984}) or Random Forests (for making predictions
+about symbolic classes~\cite{Breiman2001}). 
+\item
+The test data is then studied to generate two predictions:
+a {\em before} prediction (on the raw test data); then an {\em after}
+prediction (after applying the policies learned from the training data).
+\item
+The improvement delta $\Delta$ is then computed by dividing {\em after} and {\em before}.
 \ei
-Note that {\em policy generation} is different to the standard
-data mining tasks of prediction or classification.  Predictors
-and classifiers only tell us what {\em is} while policy 
-generators tell us {\em what to do}.
-
-The tool used to generate these policies is ``HERE'', an instance-based
+This paper presents a novel policy generator called ``HOW''.
+HOW is a near-linear time  instance-based
 local search algorithm that looks for improvement trends in the data,
-then adjusting examples to nudge them along that improvement. While
+then adjusting examples to nudge them along that trend.
+The experiments of this paper apply HOW to learning policies for 
+software defect reduction and for compiling software that runs faster.
+At least for the data explored here, HOW's reductions in defects and runtimes
+are very large-- up to 50\% fewer defects and up to 50\% faster runtimes.
+
+The rest of this paper is structured as follows.
+
+\section{Releated Work}
+
+Our prior work in generating policies relied upon a Monte Carlo
+analysis of an underlying model~\cite{me07f}. This approach had three major problems.
+Firstly, enough domain knowledge had to be collected to build that model
+and this can take a long time. For example, in our previous work we used three software process models from
+the Unviersity of Southern California that were initially
+developed and updated for nearly two decades from 1981~\cite{boehm81} to 2000~\cite{boehm00b}.
+
+Secondly, there is the computational cost of running those models.
+While
+
+~\cite{}-- which suffered from the problem of (a)~the effort required to collect the domain knowledge to build
+problem in certifying the underlying model;
+ (b)~the computational problem of running that model enough
+times to learn patterns in that data; and (c)~ requrearea used large scale simulations or large
+
+While
 our case studies are defect and runtime reduction, HERE is a general
@@
 We also distinguish HERE's policy generation fro the multi-objective optimization methods explored by Harman and Krall and Menzies and 
-and many ithers.
+and many others.
 
@@
 
-{\bf RQ2: Can lessons learnt from local search operators be useful for generating solutions that can be used to mitigate defects in software systems?}
+{\bf RQ2: Can lessons learnt from local policy generators be useful for generating solutions that can be used to mitigate defects in software systems?}
 
@@
 Instance based approaches have been used extensively by the effort estimation community, see~\cite{keung2008analogy, 6600685, walkerden1999empirical, shepperd1997estimating, kocaguneli2010use}.
+
 This approach has been proposed as an alternative to closed form mathematical models or other modeling methods such as regression \cite{keung2008analogy}.
@@
 
-\subsection{Planning changes using WHAT}
-We propose the WHAT algorithm as a tool to plan changes in the original test data.
-Figure~\ref{fig:what} highlights the procedure by which WHAT operates.
+\subsection{Planning changes using HERE}
+We propose the HERE algorithm as a tool to plan changes in the original test data.
+Figure~\ref{fig:what} highlights the procedure by which HERE operates.
 It begins by creating clusters which are generated using the WHERE algorithm discussed above.
 Following this, a nearest neighbour scheme is applied to identify pairs of nearby clusters.
-A projective plane is constructed with these clusters at the vertices to characterize the cluster pairs.
-
-The mutation policy works by projecting the test instance onto the projective planes and identifying the the plane on which the test instance has the largest scalar projection.
-The planner then reflects over the vertices of the chosen hyperplane, identifying the \textit{better} vertex among the two.
+A contour is constructed with these clusters at the vertices to characterize the cluster pairs.
+
+The mutation policy works by projecting the test instance onto the contours and identifying the the contour on which the test instance has the largest scalar projection.
+The planner then reflects over the vertices of the chosen contour, identifying the \textit{better} vertex among the two.
 Now, a new instance is generated by \textit{mutating the attributes} of the test instance towards the better vertex and away from the worse vertex.
@@
 
-\subsection{Feature Weighting}
+\subsection{Feature Weighting} \label{fwt}
 The algorithm also allows for a feature weighting and pruning scheme.
@@
 \begin{tabular}{|p{.95\linewidth}|}\hline
-WHAT begins by \textit{clustering} the training data into similar subsets using WHERE. WHERE works as follows:
+HERE begins by \textit{clustering} the training data into similar subsets using WHERE. WHERE works as follows:
 \begin{enumerate}
@@
 \item Let each point be at distance $a,b$ to the {\em east,west} poles.  Using the cosine rule, project each point onto the  axis  at $x=(a^2 + c^2 - b^2)/(2c)$.  
-\item Using the Medianian $x$ value, divide the population.
+\item Using the Median $x$ value, divide the population.
 \item For each half that is larger than $\sqrt{N}$ of the original population, go to step 1.
@@
 
-The final clusters that are found by WHERE are then used by WHAT as follows:
+The final clusters that are found by WHERE are then used by HERE as follows:
 \begin{itemize}
@@
 
-Formally, WHAT can be considered as an instance based  learning scheme.
+Formally, HERE can be considered as an instance based  learning scheme.
 And that's because it builds a set of recommendations based on a given test case based on the clusters for Median at the training stage.
@@
 \end{tabular}
-\caption{Inside WHAT}\label{fig:what}
+\caption{Inside HERE}\label{fig:what}
 \end{figure}
@@
 \includegraphics[width=\linewidth]{_figs/WHAT-Clusters2.pdf}
-\caption{WHAT}
+\caption{HERE}
 \label{fig:whatflow}
@@
 
-def project(west, east, c, x): 
+def project(west, east, AC, x): 
   "Project x onto line east to west"
-  a = dist(x,west)
-  b = dist(x,east)
+  AB = dist(x,west)
+  BC = dist(x,east)
   #cosine rule
-  return (a*a + c*c - b*b)/(2*c)
+  return (AB$^2$ + AC$^2$ - AB$^2$)/(2*AC)
 
@@
     two = envied(near(one, clusters))
-    contours += [one, two]
+    contours += [(one, two)]
   return contours
@@
   # Cosine rule
-  y = (AB$^2$ + BC$^2$ - AC$^2$)/(2*AC)
-  return $\sqrt{AB^2 - y^2}$
+  x = (AB$^2$ + AC$^2$ - BC$^2$)/(2*AC)
+  return $\sqrt{AB^2 - x^2}$
 
@@
 
-def WHAT():
+def HERE():
   contours = getContours()
@@
 \end{python}
-\caption{Instance-based Planning using WHAT}
-\label{fig:WHAT}   
+\caption{Instance-based Planning using HERE}
+\label{fig:HERE}   
 \end{figure}
@@
 The new training data merely resembles the original data.
-This is done as a precautionary measure, so as not to have WHAT and Random Forest train on the same training data.
-%Its worth noting that both WHAT and Random Forest require some data to train.
+This is done as a precautionary measure, so as not to have HERE and Random Forest train on the same training data.
+%Its worth noting that both HERE and Random Forest require some data to train.
 In order to prevent the two from using the same data to train, we run SMOTE by  \textit{resampling} the classes.
@@
 
-\caption{Attributes of the Performance Prediction datasets}\label{fig:cpm}
+\caption{Attributes of the Performance Prediction data sets}\label{fig:cpm}
 \end{figure}
@@
 
-%   \subfloat[Experimental Rig for Defect Prediction]{  \includegraphics[width=\linewidth]{_figs/WHAT}
+%   \subfloat[Experimental Rig for Defect Prediction]{  \includegraphics[width=\linewidth]{_figs/HERE}
 %   \label{fig:rig2}}
@@
 
-The following section describes the experimental rig and the experiments used to measure the performance of WHAT on 10 defect data sets and 6 performance prediction data sets.
+The following section describes the experimental rig and the experiments used to measure the performance of HERE on 10 defect data sets and 6 performance prediction data sets.
 
@@
 The data was obtained from the PROMISE repository\footnote{Promise Repository: \url{http://openscience.us/repo}}.
-For the defect data we investigated 32 releases from 11 open source Java projects defined by the metrics highlighted in figure ~\ref{fig:ck}: \kw{Apache } (1.5 -- 1.7), \kw{Apache Camel} (1.2 -- 1.6), \kw{Apache Ivy} (1.1 -- 2.0), \kw{JEdit} (4.1 -- 4.3), \kw{Apache Log4j} (1.0 -- 1.2), \kw{Apache Lucene} (2.0 -- 2.2), \kw{PBeans} (1.0 and 2.0), \kw{Apache POI} (2.0 -- 3.0), \kw{Apache Synapse} (1.0 -- 1.2), \kw{Apache Velocity} (1.4 -- 1.6), and \kw{Apache Xalan-Java} (2.5 -- 2.7).
+For the defect data we investigated 32 releases from 11 open source Java projects defined by the metrics highlighted in figure ~\ref{fig:ck}: \kw{Apache Ant} (1.5 -- 1.7), \kw{Apache Camel} (1.2 -- 1.6), \kw{Apache Ivy} (1.1 -- 2.0), \kw{JEdit} (4.1 -- 4.3), \kw{Apache Log4j} (1.0 -- 1.2), \kw{Apache Lucene} (2.0 -- 2.2), \kw{PBeans} (1.0 and 2.0), \kw{Apache POI} (2.0 -- 3.0), \kw{Apache Synapse} (1.0 -- 1.2), \kw{Apache Velocity} (1.4 -- 1.6), and \kw{Apache Xalan-Java} (2.5 -- 2.7).
 
@@
 \item We use an {oracle} (Random Forest + SMOTE) to determine whether a certain test case is defective or not. 
-\item If the oracle suggests that an instance is defective, then we use WHAT to apply the recommendations to that test instance. 
+\item If the oracle suggests that an instance is defective, then we use HERE to apply the recommendations to that test instance. 
 \item The oracle is then used to predict the attributes in the modified instance.
@@
 The oracle is Random Forest, and it predicts for run times of specific configuration.
-WHAT is used to generate a recommended configuration to reduce the run times.
+HERE is used to generate a recommended configuration to reduce the run times.
 The run time is measured by the oracle.
@@
 \delta = \frac{\#(Before<After) - \#(Before>After)}{M^2}
+\label{eq:cliffs}
 \end{equation}
@@
 
-In addition to the above, we rank the different varis of the planning scheme to identify the best approach.
+In addition to the above, we rank the different various of the planning scheme to identify the best approach.
 We make use of the Scott-Knott procedure, recommended by Mittas \& Angelis in their 2013 IEEE TSE paper~\cite{sk}, to compute the ranks.
@@
 \section{Experimental Results}
-\begin{figure}[!t]
+
+\subsection{Defect Data Set}
+This sections explores \textbf{RQ2: Can lessons learnt from local policy generators be useful for generating solutions that can be used to mitigate defects in software systems?}
+
+Figure \ref{fig:bugs} compares the number of defects before and after applying "HERE".
+The graphs represent the median scores, with the inter-quartile ranges represented by the error bars.
+The results seem to show that in all data sets under consideration, the number of defects have reduced, some more so than others.
+Large differences were notice in certain data sets namely, \textit{ant}, \textit{camel}, \textit{jedit}, \textit{poi,} and \textit{xalan}, on close examination it was noticed that these data sets had comparatively large training data, which translates to more samples for the planner to learn from.
+
+In addition to this, to study the statistical significance of the changes, the results were statistically verified using the Skott-Knott procedure.
+In order to do this we computed the Cliff's Delta score.
+As highlighted previously, HERE is applied only for test instances that are considered defective by the oracle.
+Using \eq{cliffs} we can expect to see the following results:
+
+\bi
+\item $\lt$ 0 if defects have been suppressed.
+\item = 0 if no change has been made.
+\item $\gt$ 0 if new defects have been introduced.
+This is not applicable to our case because we only apply HERE to defective cases; either the defects are suppressed or they remain unaltered, introduction of new defects is not possible.
+\ei
+
+\begin{figure}[tbp]
 \centering
@@
 \end{figure}
+With this in mind, it is easy to note that lower cliffs delta score translates to better the performance.
+
+The results are tabulated in figure \ref{tab:ant}. For the sake of completeness, we have introduced three basic configurations in HERE: 
+\bi
+\item \textit{Extent of Mutation:} Denotes the extent by which a test instant is \textit{mutated} towards the best cluster in the contour.
+It is a fraction that lies between 0 and 1.
+The baseline study requires no change be made, and thus extent of mutation is set to zero.
+\item \textit{Feature Weighting:} The importance of feature weighting has already been discussed in section \ref{fwt}.
+It is a fraction that lies between 0 and 1, with 0 being the least important and 1 the most important feature.
+The extent of mutation is multiplied by this fraction to determine how much a specific feature changes by.
+Generally, we would like to make the largest change to the most crucial feature.
+\item \textit{Information Pruning:} In addition to the weighting the features, we explored the possibility of mutating only the most important features.
+The feature weights are already known to us, we sort the features in descending order of their weights and mutate only the first X\%.
+\ei
+It is to be noted however that
+
+\begin{figure*}[htbp!]
+
+\noindent\begin{minipage}{0.5\textwidth}
+  {\scriptsize \textbf{Ant}\\}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
+      \arrayrulecolor{darkgray}
+      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
+  1 & 0.75 &    -0.63  &  0.08 & \quart{2}{7}{5}{144} \\
+  1 & 0.75, weighting &    -0.6  &  0.2 & \quart{0}{16}{8}{144} \\
+\hline  2 & 0.5, weighting &    -0.42  &  0.11 & \quart{17}{10}{23}{144} \\
+  2 & 0.5 &    -0.42  &  0.11 & \quart{19}{9}{23}{144} \\
+  2 & 0.75, weighting, Prune=50\% &    -0.4  &  0.11 & \quart{20}{9}{25}{144} \\
+\hline  3 & 0.25 &    -0.28  &  0.09 & \quart{31}{7}{35}{144} \\
+  3 & 0.25, weighting &    -0.28  &  0.08 & \quart{31}{7}{35}{144} \\
+\hline  4 & 0.5, weighting, Prune=50\% &    -0.25  &  0.06 & \quart{35}{5}{38}{144} \\
+\hline  5 & 0.25, weighting, Prune=50\% &    -0.19  &  0.05 & \quart{41}{4}{43}{144} \\
+\hline  6 & Baseline &    -0.11  &  0.03 & \quart{47}{2}{49}{144} \\
+\hline \end{tabular}}
+\end{minipage}
+\noindent\begin{minipage}{0.5\textwidth}
+  \flushleft
+  {\scriptsize \textbf{Camel}\\}
+{\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
+  1 &  0.75, weighting, Prune=50\% &    -0.41  &  0.1 & \quart{2}{14}{9}{205} \\
+  1 &  0.75 &    -0.41  &  0.23 & \quart{1}{32}{9}{205} \\
+  1 &  0.75, weighting &    -0.39  &  0.16 & \quart{0}{22}{12}{205} \\
+\hline  2 &  0.5, weighting, Prune=50\% &    -0.27  &  0.09 & \quart{19}{12}{29}{205} \\
+  2 &  0.5 &    -0.26  &  0.12 & \quart{20}{17}{30}{205} \\
+  2 &  0.5, weighting &    -0.24  &  0.09 & \quart{24}{13}{33}{205} \\
+\hline  3 &  0.25, weighting, Prune=50\% &    -0.2  &  0.05 & \quart{36}{7}{38}{205} \\
+  3 &  0.25, weighting &    -0.19  &  0.07 & \quart{36}{9}{40}{205} \\
+  3 &  0.25 &    -0.17  &  0.06 & \quart{37}{8}{43}{205} \\
+\hline  4 &  Baseline &    -0.15  &  0.06 & \quart{41}{8}{45}{205} \\
+\hline \end{tabular}}
+\end{minipage}
+
+\noindent\begin{minipage}{0.5\textwidth}
+  \flushleft
+  {\scriptsize \textbf{Ivy}\\[-0.05cm]}
+{\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
+  1 &     0.75 &    -0.57  &  0.17 & \quart{0}{16}{6}{163} \\
+  1 &   0.75, weighting &    -0.55  &  0.11 & \quart{3}{11}{8}{163} \\
+\hline  2 &   0.75, weighting, Prune=50\% &    -0.38  &  0.11 & \quart{19}{11}{25}{163} \\
+  2 &    0.5, weighting &    -0.36  &  0.12 & \quart{23}{12}{27}{163} \\
+  2 &   0.5 &    -0.33  &  0.11 & \quart{25}{11}{30}{163} \\
+\hline  3 &   0.5, weighting, Prune=50\% &    -0.27  &  0.08 & \quart{30}{8}{36}{163} \\
+\hline  4 &   0.25, weighting &    -0.2  &  0.07 & \quart{41}{7}{43}{163} \\
+  4 &     0.25 &    -0.16  &  0.04 & \quart{43}{4}{47}{163} \\
+  4 &     Baseline &    -0.16  &  0.0 & \quart{47}{0}{47}{163} \\
+\hline  5 &   0.25, weighting, Prune=50\% &    -0.15  &  0.04 & \quart{45}{4}{48}{163} \\
+\hline \end{tabular}}
+\end{minipage}
+\noindent\begin{minipage}{0.5\textwidth}
+  \flushleft
+  {\scriptsize \textbf{Jedit}\\}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
+  1 &  0.75, weighting, Prune=50\% &    -0.41  &  0.18 & \quart{0}{20}{8}{172} \\
+  1 &  0.75 &    -0.35  &  0.26 & \quart{0}{30}{15}{172} \\
+\hline  2 &  0.75, weighting &    -0.25  &  0.17 & \quart{16}{20}{26}{172} \\
+  2 &  0.5, weighting, Prune=50\% &    -0.21  &  0.1 & \quart{23}{11}{31}{172} \\
+\hline  3 &   0.5 &    -0.17  &  0.08 & \quart{32}{9}{36}{172} \\
+  3 &  0.5, weighting &    -0.14  &  0.09 & \quart{31}{10}{39}{172} \\
+\hline  4 &  0.25, weighting, Prune=50\% &    -0.12  &  0.06 & \quart{39}{7}{41}{172} \\
+\hline  5 &  0.25 &    -0.08  &  0.05 & \quart{43}{5}{46}{172} \\
+  5 &  0.25, weighting &    -0.08  &  0.06 & \quart{43}{6}{46}{172} \\
+\hline  6 &  Baseline &    -0.06  &  0.01 & \quart{47}{1}{48}{172} \\
+\hline \end{tabular}}
+\end{minipage}
+
+\noindent\begin{minipage}{0.5\textwidth}
+  \flushleft
+  {\scriptsize \textbf{Log4j}\\}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
+  1 &  0.75, weighting, Prune=50\% &    -0.19  &  0.13 & \quart{0}{28}{15}{273} \\
+\hline  2 &  0.75 &    -0.13  &  0.06 & \quart{23}{13}{28}{273} \\
+  2 &  0.5, weighting, Prune=50\% &    -0.13  &  0.05 & \quart{23}{11}{28}{273} \\
+  2 &  0.75, weighting &    -0.12  &  0.1 & \quart{15}{21}{30}{273} \\
+\hline  3 &  0.5, weighting &    -0.1  &  0.03 & \quart{28}{6}{34}{273} \\
+\hline  4 &   0.5 &    -0.1  &  0.07 & \quart{28}{15}{34}{273} \\
+  4 &  0.25 &    -0.09  &  0.04 & \quart{34}{9}{36}{273} \\
+  4 &  0.25, weighting, Prune=50\% &    -0.09  &  0.04 & \quart{34}{9}{36}{273} \\
+  4 &  0.25, weighting &    -0.06  &  0.04 & \quart{34}{9}{43}{273} \\
+\hline  5 &  Baseline &    -0.06  &  0.03 & \quart{43}{6}{43}{273} \\
+\hline \end{tabular}}
+\end{minipage}
+\noindent\begin{minipage}{0.5\textwidth}
+  \flushleft
+  {\scriptsize \textbf{Lucene}\\}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
+  1 &  0.75, weighting &    -0.15  &  0.09 & \quart{0}{29}{9}{393} \\
+  1 &  0.75 &    -0.13  &  0.09 & \quart{0}{29}{16}{393} \\
+  1 &  0.75, weighting, Prune=50\% &    -0.12  &  0.08 & \quart{6}{27}{19}{393} \\
+\hline  2 &  Baseline &    -0.1  &  0.03 & \quart{26}{10}{26}{393} \\
+  2 &  0.5, weighting, Prune=50\% &    -0.1  &  0.03 & \quart{23}{10}{26}{393} \\
+\hline  3 &  0.5, weighting &    -0.08  &  0.06 & \quart{23}{20}{33}{393} \\
+  3 &  0.25, weighting, Prune=50\% &    -0.07  &  0.03 & \quart{33}{10}{36}{393} \\
+  3 &  0.5 &    -0.07  &  0.05 & \quart{29}{17}{36}{393} \\
+\hline  4 &  0.25, weighting &    -0.04  &  0.04 & \quart{36}{13}{46}{393} \\
+  4 &  0.25 &    -0.04  &  0.02 & \quart{39}{7}{46}{393} \\
+\hline \end{tabular}}
+\end{minipage}
+
+\noindent\begin{minipage}{0.5\textwidth}
+  \flushleft
+  {\scriptsize \textbf{Poi}\\}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
+      \arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
+  1 & 0.75, weighting &    -0.45  &  0.1 & \quart{6}{10}{11}{162} \\
+  1 &  0.75 &    -0.44  &  0.23 & \quart{0}{23}{12}{162} \\
+\hline  2 & 0.5, weighting &    -0.32  &  0.23 & \quart{12}{24}{24}{162} \\
+  2 & 0.5 &    -0.26  &  0.23 & \quart{18}{24}{31}{162} \\
+  2 & 0.75, weighting, Prune=50\% &    -0.25  &  0.19 & \quart{17}{20}{32}{162} \\
+\hline  3 & 0.5, weighting, Prune=50\% &    -0.19  &  0.09 & \quart{34}{9}{38}{162} \\
+  3 &  0.25 &    -0.19  &  0.11 & \quart{32}{11}{38}{162} \\
+  3 & 0.25, weighting &    -0.17  &  0.14 & \quart{30}{14}{40}{162} \\
+\hline  4 & 0.25, weighting, Prune=50\% &    -0.12  &  0.09 & \quart{40}{9}{45}{162} \\
+\hline  5 &  Baseline &    -0.09  &  0.03 & \quart{46}{3}{48}{162} \\
+\hline \end{tabular}}
+\end{minipage}
+\noindent\begin{minipage}{0.5\textwidth}
+  \flushleft
+  {\scriptsize \textbf{Synapse}\\}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
+  1 & 0.75, weighting &    -0.56  &  0.2 & \quart{7}{18}{11}{148} \\
+  1 & 0.75 &    -0.48  &  0.34 & \quart{0}{29}{18}{148} \\
+\hline  2 & 0.5 &    -0.4  &  0.27 & \quart{14}{24}{25}{148} \\
+  2 & 0.5, weighting &    -0.37  &  0.17 & \quart{21}{15}{28}{148} \\
+\hline  3 & 0.25 &    -0.23  &  0.16 & \quart{31}{14}{40}{148} \\
+  3 & 0.25, weighting &    -0.23  &  0.1 & \quart{38}{9}{40}{148} \\
+  3 & 0.75, weighting, Prune=50\% &    -0.19  &  0.08 & \quart{40}{7}{43}{148} \\
+\hline  4 & 0.25, weighting, Prune=50\% &    -0.17  &  0.08 & \quart{42}{7}{45}{148} \\
+  4 & Baseline &    -0.15  &  0.0 & \quart{47}{0}{47}{148} \\
+  4 & 0.5, weighting, Prune=50\% &    -0.15  &  0.11 & \quart{40}{9}{47}{148} \\
+\hline \end{tabular}}
+\end{minipage}
+
+\noindent\begin{minipage}{0.50\textwidth}
+  \flushleft
+  {\scriptsize \textbf{Velocity}\\}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
+  1 & 0.75, weighting &    -0.19  &  0.22 & \quart{1}{34}{21}{207} \\
+  1 & 0.75, weighting, Prune=50\% &    -0.15  &  0.13 & \quart{14}{20}{28}{207} \\
+  1 & 0.75 &    -0.14  &  0.23 & \quart{0}{35}{29}{207} \\
+\hline  2 & 0.5 &    -0.13  &  0.11 & \quart{23}{17}{31}{207} \\
+\hline  3 & 0.5, weighting &    -0.1  &  0.08 & \quart{29}{13}{35}{207} \\
+  3 & 0.5, weighting, Prune=50\% &    -0.07  &  0.07 & \quart{32}{11}{40}{207} \\
+\hline  4 & Baseline &    -0.05  &  0.04 & \quart{43}{6}{43}{207} \\
+  4 & 0.25, weighting &    -0.05  &  0.03 & \quart{40}{5}{43}{207} \\
+  4 & 0.25 &    -0.04  &  0.02 & \quart{43}{3}{45}{207} \\
+  4 & 0.25, weighting, Prune=50\% &    -0.01  &  0.04 & \quart{43}{6}{49}{207} \\
+\hline \end{tabular}}
+\end{minipage}
+\noindent\begin{minipage}{0.50\textwidth}
+  \flushleft
+  {\scriptsize \textbf{Xalan}\\}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
+  1 & 0.75 &    -0.36  &  0.12 & \quart{0}{16}{9}{198} \\
+  1 & 0.75, weighting &    -0.3  &  0.17 & \quart{4}{23}{18}{198} \\
+  1 &    0.5 &    -0.3  &  0.12 & \quart{9}{17}{18}{198} \\
+\hline  2 & 0.5, weighting &    -0.28  &  0.09 & \quart{16}{13}{20}{198} \\
+\hline  3 & 0.25, weighting &    -0.23  &  0.1 & \quart{20}{14}{27}{198} \\
+  3 & 0.25 &    -0.23  &  0.12 & \quart{20}{17}{27}{198} \\
+\hline  4 & 0.25, weighting, Prune=50\% &    -0.14  &  0.07 & \quart{36}{9}{40}{198} \\
+  4 & 0.75, weighting, Prune=50\% &    -0.14  &  0.07 & \quart{33}{10}{40}{198} \\
+  4 & 0.5, weighting, Prune=50\% &    -0.12  &  0.06 & \quart{37}{8}{43}{198} \\
+\hline  5 & Baseline &    -0.08  &  0.02 & \quart{47}{2}{48}{198} \\
+\hline \end{tabular}}
+\end{minipage}
+\caption{Cliffs Delta Scores for the defect data set.
+The Treatment column, has 3 possible configurations, the first (0.25, 0.50, and 0.75) represents the extent of mutation; weighting represents feature weighting; Prune represents the extent of information pruning.}
+\label{tab:ant}
+\end{figure*}
 
@@
 \end{minipage}
-\caption{Run time optimization using WHAT.
-Blue curve represents a mutation probability of 0.75 with feature weighting and information pruning; Red curve represents a mutation probability of 0.25 with feature weighting, but no information pruning; Black curve represents the raw test data used as baseline for the comparision.}
+\caption{Run time optimization using HERE.
+Blue curve represents a mutation probability of 0.75 with feature weighting and information pruning; Red curve represents a mutation probability of 0.25 with feature weighting, but no information pruning; Black curve represents the raw test data used as baseline for the comparison.}
 \label{fig:pp}
@@
 
+\subsection{Performance Prediction Data set}
+
+In this section, 
 \begin{figure*}[htbp!]
@@
       \arrayrulecolor{darkgray}
-      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
   1 & 75, weighting, Prune=25\% &    0.77  &  0.05 & \quart{0}{9}{3}{49} \\
@@
 \arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
   1 &     75 &    0.22  &  0.05 & \quart{0}{3}{1}{49} \\
@@
 \arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
   1 &     75 &    0.63  &  0.16 & \quart{0}{19}{3}{49} \\
@@
 \arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
   1 &     75 &    0.92  &  0.01 & \quart{5}{6}{5}{49} \\
@@
 \arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
   1 &      75 &    0.98  &  0.01 & \quart{0}{16}{16}{49} \\
@@
 \arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
   1 &  75, weighting, Prune=25\% &    0.73  &  0.05 & \quart{1}{9}{3}{49} \\
@@
 
-\begin{figure*}[htbp!]
-
-\noindent\begin{minipage}{0.5\textwidth}
-  {\scriptsize \textbf{Ant}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-      \arrayrulecolor{darkgray}
-      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-  1 & 0.75 &    -0.63  &  0.08 & \quart{2}{7}{5}{144} \\
-  1 & 0.75, weighting &    -0.6  &  0.2 & \quart{0}{16}{8}{144} \\
-\hline  2 & 0.5, weighting &    -0.42  &  0.11 & \quart{17}{10}{23}{144} \\
-  2 & 0.5 &    -0.42  &  0.11 & \quart{19}{9}{23}{144} \\
-  2 & 0.75, weighting, Prune=50\% &    -0.4  &  0.11 & \quart{20}{9}{25}{144} \\
-\hline  3 & 0.25 &    -0.28  &  0.09 & \quart{31}{7}{35}{144} \\
-  3 & 0.25, weighting &    -0.28  &  0.08 & \quart{31}{7}{35}{144} \\
-\hline  4 & 0.5, weighting, Prune=50\% &    -0.25  &  0.06 & \quart{35}{5}{38}{144} \\
-\hline  5 & 0.25, weighting, Prune=50\% &    -0.19  &  0.05 & \quart{41}{4}{43}{144} \\
-\hline  6 & Baseline &    -0.11  &  0.03 & \quart{47}{2}{49}{144} \\
-\hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Camel}\\}
-{\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-  1 &  0.75, weighting, Prune=50\% &    -0.41  &  0.1 & \quart{2}{14}{9}{205} \\
-  1 &  0.75 &    -0.41  &  0.23 & \quart{1}{32}{9}{205} \\
-  1 &  0.75, weighting &    -0.39  &  0.16 & \quart{0}{22}{12}{205} \\
-\hline  2 &  0.5, weighting, Prune=50\% &    -0.27  &  0.09 & \quart{19}{12}{29}{205} \\
-  2 &  0.5 &    -0.26  &  0.12 & \quart{20}{17}{30}{205} \\
-  2 &  0.5, weighting &    -0.24  &  0.09 & \quart{24}{13}{33}{205} \\
-\hline  3 &  0.25, weighting, Prune=50\% &    -0.2  &  0.05 & \quart{36}{7}{38}{205} \\
-  3 &  0.25, weighting &    -0.19  &  0.07 & \quart{36}{9}{40}{205} \\
-  3 &  0.25 &    -0.17  &  0.06 & \quart{37}{8}{43}{205} \\
-\hline  4 &  Baseline &    -0.15  &  0.06 & \quart{41}{8}{45}{205} \\
-\hline \end{tabular}}
-\end{minipage}
-
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Ivy}\\[-0.05cm]}
-{\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-  1 &     0.75 &    -0.57  &  0.17 & \quart{0}{16}{6}{163} \\
-  1 &   0.75, weighting &    -0.55  &  0.11 & \quart{3}{11}{8}{163} \\
-\hline  2 &   0.75, weighting, Prune=50\% &    -0.38  &  0.11 & \quart{19}{11}{25}{163} \\
-  2 &    0.5, weighting &    -0.36  &  0.12 & \quart{23}{12}{27}{163} \\
-  2 &   0.5 &    -0.33  &  0.11 & \quart{25}{11}{30}{163} \\
-\hline  3 &   0.5, weighting, Prune=50\% &    -0.27  &  0.08 & \quart{30}{8}{36}{163} \\
-\hline  4 &   0.25, weighting &    -0.2  &  0.07 & \quart{41}{7}{43}{163} \\
-  4 &     0.25 &    -0.16  &  0.04 & \quart{43}{4}{47}{163} \\
-  4 &     Baseline &    -0.16  &  0.0 & \quart{47}{0}{47}{163} \\
-\hline  5 &   0.25, weighting, Prune=50\% &    -0.15  &  0.04 & \quart{45}{4}{48}{163} \\
-\hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Jedit}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-  1 &  0.75, weighting, Prune=50\% &    -0.41  &  0.18 & \quart{0}{20}{8}{172} \\
-  1 &  0.75 &    -0.35  &  0.26 & \quart{0}{30}{15}{172} \\
-\hline  2 &  0.75, weighting &    -0.25  &  0.17 & \quart{16}{20}{26}{172} \\
-  2 &  0.5, weighting, Prune=50\% &    -0.21  &  0.1 & \quart{23}{11}{31}{172} \\
-\hline  3 &   0.5 &    -0.17  &  0.08 & \quart{32}{9}{36}{172} \\
-  3 &  0.5, weighting &    -0.14  &  0.09 & \quart{31}{10}{39}{172} \\
-\hline  4 &  0.25, weighting, Prune=50\% &    -0.12  &  0.06 & \quart{39}{7}{41}{172} \\
-\hline  5 &  0.25 &    -0.08  &  0.05 & \quart{43}{5}{46}{172} \\
-  5 &  0.25, weighting &    -0.08  &  0.06 & \quart{43}{6}{46}{172} \\
-\hline  6 &  Baseline &    -0.06  &  0.01 & \quart{47}{1}{48}{172} \\
-\hline \end{tabular}}
-\end{minipage}
-
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Log4j}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-  1 &  0.75, weighting, Prune=50\% &    -0.19  &  0.13 & \quart{0}{28}{15}{273} \\
-\hline  2 &  0.75 &    -0.13  &  0.06 & \quart{23}{13}{28}{273} \\
-  2 &  0.5, weighting, Prune=50\% &    -0.13  &  0.05 & \quart{23}{11}{28}{273} \\
-  2 &  0.75, weighting &    -0.12  &  0.1 & \quart{15}{21}{30}{273} \\
-\hline  3 &  0.5, weighting &    -0.1  &  0.03 & \quart{28}{6}{34}{273} \\
-\hline  4 &   0.5 &    -0.1  &  0.07 & \quart{28}{15}{34}{273} \\
-  4 &  0.25 &    -0.09  &  0.04 & \quart{34}{9}{36}{273} \\
-  4 &  0.25, weighting, Prune=50\% &    -0.09  &  0.04 & \quart{34}{9}{36}{273} \\
-  4 &  0.25, weighting &    -0.06  &  0.04 & \quart{34}{9}{43}{273} \\
-\hline  5 &  Baseline &    -0.06  &  0.03 & \quart{43}{6}{43}{273} \\
-\hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Lucene}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-  1 &  0.75, weighting &    -0.15  &  0.09 & \quart{0}{29}{9}{393} \\
-  1 &  0.75 &    -0.13  &  0.09 & \quart{0}{29}{16}{393} \\
-  1 &  0.75, weighting, Prune=50\% &    -0.12  &  0.08 & \quart{6}{27}{19}{393} \\
-\hline  2 &  Baseline &    -0.1  &  0.03 & \quart{26}{10}{26}{393} \\
-  2 &  0.5, weighting, Prune=50\% &    -0.1  &  0.03 & \quart{23}{10}{26}{393} \\
-\hline  3 &  0.5, weighting &    -0.08  &  0.06 & \quart{23}{20}{33}{393} \\
-  3 &  0.25, weighting, Prune=50\% &    -0.07  &  0.03 & \quart{33}{10}{36}{393} \\
-  3 &  0.5 &    -0.07  &  0.05 & \quart{29}{17}{36}{393} \\
-\hline  4 &  0.25, weighting &    -0.04  &  0.04 & \quart{36}{13}{46}{393} \\
-  4 &  0.25 &    -0.04  &  0.02 & \quart{39}{7}{46}{393} \\
-\hline \end{tabular}}
-\end{minipage}
-
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Poi}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-      \arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-  1 & 0.75, weighting &    -0.45  &  0.1 & \quart{6}{10}{11}{162} \\
-  1 &  0.75 &    -0.44  &  0.23 & \quart{0}{23}{12}{162} \\
-\hline  2 & 0.5, weighting &    -0.32  &  0.23 & \quart{12}{24}{24}{162} \\
-  2 & 0.5 &    -0.26  &  0.23 & \quart{18}{24}{31}{162} \\
-  2 & 0.75, weighting, Prune=50\% &    -0.25  &  0.19 & \quart{17}{20}{32}{162} \\
-\hline  3 & 0.5, weighting, Prune=50\% &    -0.19  &  0.09 & \quart{34}{9}{38}{162} \\
-  3 &  0.25 &    -0.19  &  0.11 & \quart{32}{11}{38}{162} \\
-  3 & 0.25, weighting &    -0.17  &  0.14 & \quart{30}{14}{40}{162} \\
-\hline  4 & 0.25, weighting, Prune=50\% &    -0.12  &  0.09 & \quart{40}{9}{45}{162} \\
-\hline  5 &  Baseline &    -0.09  &  0.03 & \quart{46}{3}{48}{162} \\
-\hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Synapse}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-  1 & 0.75, weighting &    -0.56  &  0.2 & \quart{7}{18}{11}{148} \\
-  1 & 0.75 &    -0.48  &  0.34 & \quart{0}{29}{18}{148} \\
-\hline  2 & 0.5 &    -0.4  &  0.27 & \quart{14}{24}{25}{148} \\
-  2 & 0.5, weighting &    -0.37  &  0.17 & \quart{21}{15}{28}{148} \\
-\hline  3 & 0.25 &    -0.23  &  0.16 & \quart{31}{14}{40}{148} \\
-  3 & 0.25, weighting &    -0.23  &  0.1 & \quart{38}{9}{40}{148} \\
-  3 & 0.75, weighting, Prune=50\% &    -0.19  &  0.08 & \quart{40}{7}{43}{148} \\
-\hline  4 & 0.25, weighting, Prune=50\% &    -0.17  &  0.08 & \quart{42}{7}{45}{148} \\
-  4 & Baseline &    -0.15  &  0.0 & \quart{47}{0}{47}{148} \\
-  4 & 0.5, weighting, Prune=50\% &    -0.15  &  0.11 & \quart{40}{9}{47}{148} \\
-\hline \end{tabular}}
-\end{minipage}
-
-\noindent\begin{minipage}{0.50\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Velocity}\\
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-  1 & 0.75, weighting &    -0.19  &  0.22 & \quart{1}{34}{21}{207} \\
-  1 & 0.75, weighting, Prune=50\% &    -0.15  &  0.13 & \quart{14}{20}{28}{207} \\
-  1 & 0.75 &    -0.14  &  0.23 & \quart{0}{35}{29}{207} \\
-\hline  2 & 0.5 &    -0.13  &  0.11 & \quart{23}{17}{31}{207} \\
-\hline  3 & 0.5, weighting &    -0.1  &  0.08 & \quart{29}{13}{35}{207} \\
-  3 & 0.5, weighting, Prune=50\% &    -0.07  &  0.07 & \quart{32}{11}{40}{207} \\
-\hline  4 & Baseline &    -0.05  &  0.04 & \quart{43}{6}{43}{207} \\
-  4 & 0.25, weighting &    -0.05  &  0.03 & \quart{40}{5}{43}{207} \\
-  4 & 0.25 &    -0.04  &  0.02 & \quart{43}{3}{45}{207} \\
-  4 & 0.25, weighting, Prune=50\% &    -0.01  &  0.04 & \quart{43}{6}{49}{207} \\
-\hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.50\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Xalan}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
-  1 & 0.75 &    -0.36  &  0.12 & \quart{0}{16}{9}{198} \\
-  1 & 0.75, weighting &    -0.3  &  0.17 & \quart{4}{23}{18}{198} \\
-  1 &    0.5 &    -0.3  &  0.12 & \quart{9}{17}{18}{198} \\
-\hline  2 & 0.5, weighting &    -0.28  &  0.09 & \quart{16}{13}{20}{198} \\
-\hline  3 & 0.25, weighting &    -0.23  &  0.1 & \quart{20}{14}{27}{198} \\
-  3 & 0.25 &    -0.23  &  0.12 & \quart{20}{17}{27}{198} \\
-\hline  4 & 0.25, weighting, Prune=50\% &    -0.14  &  0.07 & \quart{36}{9}{40}{198} \\
-  4 & 0.75, weighting, Prune=50\% &    -0.14  &  0.07 & \quart{33}{10}{40}{198} \\
-  4 & 0.5, weighting, Prune=50\% &    -0.12  &  0.06 & \quart{37}{8}{43}{198} \\
-\hline  5 & Baseline &    -0.08  &  0.02 & \quart{47}{2}{48}{198} \\
-\hline \end{tabular}}
-\end{minipage}
-   \end{figure*}
-
 % \section{Discussion}

### 2015-05-02 manuscript.tex
Updates from ShareLaTeX

@@
   \title{Learning Actionable Analytics 
- (with Applications for Reducing Defects and Reducing Runtimes)}
+ (with applications for reducing defects and reducing runtimes)}
 
@@
  to reduce defects and decrease program runtime.
- For the test data used in this paper,
- we have observed that the improvements generated by HERE can reduce
- defect prediction and runtimes by up to
+ For the test data of this paper, the improvements generated by HERE can reduce
+ defect counts as well as runtimes by up to
  50\% of their original values.
@@
 \section{Introduction}
-In the $21^{st}$ century, it is now impossible to manually browse all
-the available software defect data.  For example, as of April 2015,
-Mozilla Firefox has over a million bug reports on software projects.  While it is
-now possible to automatically analyze such data with data miners, at
-some stage a group of business users will have to convene to {\em
-  interpret the results} (e.g., to decide if it is wise to deploy the
-results as a defect reduction method within an organization).
-
-These business  users are now demanding that data mining tools
+Business  users are now demanding that data mining tools
 be augmented with tools to support  business-level
@@
  software defects
-to expect,  business users now demand {\em policies} that
+to expect,  business users might now demand a {\em plan} to
 reduce the likelihood of those defects;
@@
 time of their software, business users might now demand
-{\em policies} that reduce that runtime.
+a {\em plan} to reduce that runtime.
 \ei
-In order to satisfy the demands of this new kind of business user, we  explore the generation of {\em policies} in the context
-of software analytics. Such {\em policies} are recommendations of what
-to change in order to better achieve some goal. 
-Note that such {\em policy generation} is very different to the standard
-data mining tasks of prediction some discrete or numeric class.
+In these two points, we say that a ``plan'' is a  set of proposed changes in order to better achieve some goal. 
+Generating {\em plans} is a  very different task the standard
+data mining tasks of {\em predicting} some discrete or numeric class.
 Predictors
-and classifiers only tell us what {\em is} while policy 
-generators tell us {\em what to change}. For the kind of business user
-discussed above, policy generators are the prefeered tool since,
-as one gruff user once shouted at us ``don't tell me what \underline{is};
-tell me what to \underline{change}''.
+and classifiers only tell us what {\em is} while planners 
+  tell us {\em what to change}. For the kind of business user
+discussed above, planners are the preferred to mere prediction systems
+since, as one gruff user once shouted at us:
+\begin{quote}
+{\em ``Don't tell me what \underline{is};
+tell me what to \underline{change}.''}
+\end{quote}
+In order to satisfy the demands of this new kind of business user, we  study the generation of {\em plans} in the context
+of software analytics.  
+As reported in this paper, that study makes five contributions:
+\be
+\item A general framework for augmenting a prediction system such that
+it becomes a planning system;
+\item A  test that recognizes  when we should {\em not}  plan: in summary, our kind of planning is
+not recommended in domains that  generate poorly performing predictors;
+\item A general verification rig for assessing the value of plans generated within this rig.
+\item A novel near-linear-time instance-based planner called ``HOW''. 
+\item An experimental validation that the HOW planner is useful for reducing the
+expected values of 
+\bi
+\item Software defects in certain object-oriented JAVA systems listed in \tion{oo}:  Ant Camel, Ivy, Jedit, Log4, Lucene, Poi, Synapse, Velocity, Xalan;
+\item The runtime of the software systems discussed in \tion{cpu}: Berkeley DB, Apache, SQLite, LLVM, 
+  x264.
+\ei
+\ei
+HOW is an {\em instance-based planner} in that it make its conclusions by
+studying the space of examples. This is a very different approach to
+{\em model-based planners} that use the model
+as sub-routine within a Monte Carlo~\cite{me07f} or evolutionary 
+programming rig~\cite{krall14,harman12dec}. 
+We prefer HOW's instance-based approach since
+it is not dependent on any underlying model.
+This is important since:
+\bi
+\item
+When some models are hard to access or slow to run (see examples, below),
+then it useful to reason from historical logs rather than from hard-to-collect
+model output.
+\item
+For reasons of confidentionality or priorpiarty restrictions, 
+It can be harder to access 
+\item
+Building and certifying a model   can take years. For example, in previous work~\cite{me07f} we used models
+developed by Boehm's group at the University of Southern California.
+Some of those models took decades to develop and mature (from 1981~\cite{boehm81} to 2000~\cite{boehm00b}). 
+\ei
+The rest of this paepr is structued as follows.
+
+\section{From ``Prediction'' to ``Planning''}
+
+approach if the underlying model
 
@@
 policy generators:
+
 \begin{small}
 \[
-project\;data \rightarrow \left\{\begin{array}{l}\mathit{train}
-\rightarrow \left\{\begin{array}{l}\mathit{predictor\;(e.g.\;CART\;or\; RF)}\\
-\mathit{policy\; generator\; (e.g.\; HOW)}\end{array}\right.
+\begin{array}{r}
+project\\
+data
+\end{array}\rightarrow \left\{\begin{array}{l}\mathit{train}
+\rightarrow \left\{\begin{array}{l}\mathit{build\;predictor\;(e.g.\;CART\;or\; RF)}\\
+\mathit{build\;planner\; (e.g.\; HOW)}\end{array}\right.
 \\
 ~\\
-\mathit{test}  \rightarrow  \left\{\begin{array}{r@{~}l}
+\mathit{test}  \rightarrow  \left\{\begin{array}{l@{~}l}
 \mathit{before}& =\mathit{predictor}(\mathit{test})\\
-\mathit{after}& =\mathit{predictor}(\; \mathit{policy}(\mathit{test})\;)\\
+\mathit{if\; before} & \ge  \mathif{satisfactory\; then}\\
+ &
+\begin{array}{l@{~}l}
+
+\mathit{test'}& = \mathit{planner}(\mathit{test})\\
+\mathit{after}& =\mathit{predictor}(\mathit{test'})\\ 
 \Delta& =\mathit{after} / \mathit{before}
+\end{array}
 \end{array}\right.

### 2015-05-02 manuscript.tex
Updates from ShareLaTeX

@@
 
+\title{Learning Actionable Analytics 
+ (with applications for reducing defects and reducing runtimes)}
 \author{
@@
 
+  \pagestyle{plain}
 \begin{document}
-  \title{Learning Actionable Analytics 
- (with applications for reducing defects and reducing runtimes)}
+  \maketitle
 
   % make the title area
-  \maketitle
-  \pagestyle{plain}
 
@@
 of software analytics.  
-As reported in this paper, that study makes five contributions:
+This paper presents
+HOW, a novel  {\em instance-based planner} that runs in near-linear time.
+In the experiments shown below, we see that HOW's plans can
+significantly reduce the expected
+value of:
+\bi
+\item Software defects in certain object-oriented JAVA systems listed in \tion{oo}:  Ant Camel, Ivy, Jedit, JBeans, Log4, Lucene, Poi, Synapse, Velocity, Xalan, Xerces;
+\item The runtime of the software systems discussed in \tion{cpu}: Berkeley DB, Apache, SQLite, LLVM, 
+  x264.
+\ei
+HOW's instance-based reasoning  makes its conclusions by
+studying the space of examples. This is a very different approach to
+{\em model-based planners} that use the model
+as sub-routine within a Monte Carlo simulation~\cite{me07f} or the evolutionary 
+programming methods explored by the search-based software
+engineering community~\cite{krall14,harman12dec}. 
+We find   HOW's instance-based approach useful since it can be applied
+to domains that lack a model, but possess a historical log of observed behaviours.
+
+Instance-based reasoning is also useful if building and certifying a model   takes a long time.
+Such slow-to-build models exist in software engineering.
+For  example, in previous work~\cite{me07f} we used models
+developed by Boehm's group at the University of Southern California.
+Some of those models took decades to develop and mature (from 1981~\cite{boehm81} to 2000~\cite{boehm00b}).
+This is not an isolated example.
+One of us (Menzies) teaches a graduate class in automated model-based software engineering.
+Students in that class are asked to find (or build) a non-trivial model of
+some software process (where ``non-trivial'' means something that processes
+a  model at least an order of magnitude more complex than Brooks' Law). 
+While the  number of such models has been growing in recent years\footnote{See the
+catalogue at goo.gl/nv2AVK.}, 
+the total number remains very small-- which is an observation consistent with
+SE models typically require  much effort to build and certify.
+
+Finally, even when there is an existing model, instance-based reasoning can be useful.
+Sometimes  it is easier to access instances of a model's behaviour than the model
+itself. For example, in prior work with Martin  Feather from the Jet Propulsion 
+Laboratory~\cite{fea02a},  our research partner could not share a
+propriety model from within the NASA firewalls. However, they could share 
+logs of the input/output of that model.
+
+In summary, this paper makes five contributions:
 \be
@@
 \item A general verification rig for assessing the value of plans generated within this rig.
-\item A novel near-linear-time instance-based planner called ``HOW''. 
+\item The HOW  instance-based planner.
+\item A proof that HOW runs in near-linear time.
 \item An experimental validation that the HOW planner is useful for reducing the
-expected values of 
-\bi
-\item Software defects in certain object-oriented JAVA systems listed in \tion{oo}:  Ant Camel, Ivy, Jedit, Log4, Lucene, Poi, Synapse, Velocity, Xalan;
-\item The runtime of the software systems discussed in \tion{cpu}: Berkeley DB, Apache, SQLite, LLVM, 
-  x264.
-\ei
-\ei
-HOW is an {\em instance-based planner} in that it make its conclusions by
-studying the space of examples. This is a very different approach to
-{\em model-based planners} that use the model
-as sub-routine within a Monte Carlo~\cite{me07f} or evolutionary 
-programming rig~\cite{krall14,harman12dec}. 
-We prefer HOW's instance-based approach since
-it is not dependent on any underlying model.
-This is important since:
-\bi
-\item
-When some models are hard to access or slow to run (see examples, below),
-then it useful to reason from historical logs rather than from hard-to-collect
-model output.
-\item
-For reasons of confidentionality or priorpiarty restrictions, 
-It can be harder to access 
-\item
-Building and certifying a model   can take years. For example, in previous work~\cite{me07f} we used models
-developed by Boehm's group at the University of Southern California.
-Some of those models took decades to develop and mature (from 1981~\cite{boehm81} to 2000~\cite{boehm00b}). 
-\ei
+expected values of software defects and software runtimes (at least, for the data sets studied here).
+\ee
 The rest of this paepr is structued as follows.
@@
 \section{From ``Prediction'' to ``Planning''}
-
-approach if the underlying model
-
-This paper presents the following general framework for extending  predictor systems
-such that they become 
-policy generators:
-
-\begin{small}
+A major  problem with building a planning mechanism in software engineering is ``how to verify the generated
+plans?''. For example,  in the experiments shown below,  HOW comments  on how to reduce
+software defects by adjusting certain static code parameters of the code\footnote{Such parameters can be automatically adjusted using code refactoring
+tools, as shown by Binkely et al. in 2006~\cite{Binkley2006} and more recently by Mkaouer et al. in 2015~\cite{Mkaouer15}.}. How are we to verify that HOW's recommendations actually work?
+
+Some organizations have the resources to 
+run repeated trials to assess the effect of different treatments.
+For example, in one remarkable recent study, Bente et al. report results
+were the same specification was developed into a product by four different organizations~\cite{Anda2009}. Given those kind of resources, it would be possible
+to (say) take a code base, assign it to $N$ different teams, apply
+HOW's plans the code used by  $N/2$ teams, then check in 12 months time
+if those halves of the teams have fewer defects than the other.
+
+Very few industrial or research groups have access
+to the kinds of resources using by Bente et al. (evidence: in the size years since the
+publication of that work, we know of only one of two similar studies). Hence, it
+we wish to verify HOW's plans, then some other approach is required that is less
+resource intensive.
+
+We propose using prediction systems (built by data mining) as a verification
+tool for planners. In domains with data, from which data miners can build
+predictors of adequate performance, then those predictors can assess the value
+of the changes proposed by HOW.
+As shown in \fig{work}, 
+project data is divided into two disjoint sets {\em train} and {\em test}
+(so {\em train} $\cup$ {\em test} $=\;\emptyset$).
+Next, from the train set, we build both a {\em planner} as well
+as a {\em predictor}. Our general framework does not   commit to any particular  choice
+of {\em planner} or {\em predictor}. For the purposes of this discussion 
+our {\em planner}
+will be HOW (discussed below)and our
+our {\em predictors} will be the Random Forest and Random Forest
+Regressor\footnote{Decision tree learners find the attribute whose value's
+select for for sections of the data with least variation in the class
+variable. Decision tree learners then recurse on each selection~\cite{breiman84}. A random forest is a set of decision trees, each built
+from some random subset of the rows and columns. The conclusions
+of the forest are a ``vote'' generated by all the trees~\cite{Breiman2001}. 
+A standard Random Forest predicts for a discrete class variable while
+a Random Forest Regressor generates numeric predictions.} taken from the SciKit
+Learn toolkit~\cite{Pedregosa2012}.
+
+Turning now to the {\em test} data, this is based to the {\em predictor}
+to generate a baseline {\em before} performance score.
+Note that if our {\em predictors} fail to perform adequately on the test data,
+then we cannot trust them to comment on our plans. Accordingly,
+if that performance is unsatisfactory, we abort.
+Else, we (1)~apply the {\em planner} to alter the {\em test} data;
+then (2)~apply the {\em predictor} to the altered data {\em test'};
+then (3)~return the performance delta $\Delta$.
+
+The clear advantage of this approach is that it can be readily and automatically
+applied to domains with historical data. That said, the drawback with this approach
+is that our assessment of the plans is only as good as the predictor. To 
+mitigate for this {\em problem of poor planners}, it is wise to demand high standards form the {\em
+satisfactory} threshold used in this \fig{frame}.
+
+\begin{figure}[!t]
+\small
 \[  
@@
 data
-\end{array}\rightarrow \left\{\begin{array}{l}\mathit{train}
-\rightarrow \left\{\begin{array}{l}\mathit{build\;predictor\;(e.g.\;CART\;or\; RF)}\\
-\mathit{build\;planner\; (e.g.\; HOW)}\end{array}\right.
+\end{array} 
+\left\{\begin{array}{l}\mathit{train}
+        \left\{\begin{array}{l}
+                \mathrm{learn\;a\;}\mathrm{predictor\;}\mathrm{e.g.\;Random\;Forest}\\
+                \mathrm{learn\;a\;}\mathrm{planner\;}\mathrm{e.g.\; HOW}
+              \end{array}\right.
        \\
       ~\\
-\mathit{test}  \rightarrow  \left\{\begin{array}{l@{~}l}
-\mathit{before}& =\mathit{predictor}(\mathit{test})\\
-\mathit{if\; before} & \ge  \mathif{satisfactory\; then}\\
- &
-\begin{array}{l@{~}l}
-
-\mathit{test'}& = \mathit{planner}(\mathit{test})\\
-\mathit{after}& =\mathit{predictor}(\mathit{test'})\\ 
-\Delta& =\mathit{after} / \mathit{before}
+\mathit{test}  
+    \left\{\begin{array}{l@{~}l}
+           \mathit{before}& =\mathrm{predictor}(\mathit{test})\\
+           \mathrm{\bf if\;}\mathit{before} & <  \mathit{satisfactory}\\
+           \mathrm{\bf then}  & \mathrm{{\bf return}\; 0}\\~\\
+           \mathrm{\bf else} &
+           \left\{
+            \begin{array}{l}
+                \mathit{test'} = \mathrm{planner}(\mathit{test})\\
+                \mathit{after} =\mathrm{predictor}(\mathit{test'})\\ 
+                \mathrm{{\bf return}\;} \mathit{after} /  \mathit{before}
             \end{array}
+          \right.
    \end{array}\right.
@@
 \]
-\end{small}
-In the above:
+
+\caption{How to use {\em predictors} for {\em planning}.}\label{fig:work}
+\end{figure}
+
+This study explores data sets from two types of domains:
 \bi
 \item
-Project data is divided into a train and test set.
+In one type, we 
+build plans to change static code attributes in order to reduce defects in
+Java classes.  Here,,
+performance can be measured in terms of recall (percent of faulty classes in
+the test data detected
+by the {\em predictor}). Using engineering judgement, we define satisfactory recall as anything less than 70\%. 
 \item 
-From the train set, we learn {\em both} a policy generator as well
-as a predictor using (e.g.)
-CART (for making numeric predictions~\cite{Breiman1984}) or Random Forests (for making predictions
-about symbolic classes~\cite{Breiman2001}). 
-\item
-The test data is then studied to generate two predictions:
-a {\em before} prediction (on the raw test data); then an {\em after}
-prediction (after applying the policies learned from the training data).
-\item
-The improvement delta $\Delta$ is then computed by dividing {\em after} and {\em before}.
+In the other type, we   build
+plans to change configurations settings within a Makefile such that the resulting compiled
+code will run faster. Here, performance can be measured in terms of difference
+between the predicted runtime $p$ of test case items and their actual runtimes $a$
+using  $s= 1- \frac{abs(a - p)}{a}$.
+Using engineering judgement, we define satisfactory $s$ as anything less than 70\%. 
 \ei
+This paper explores 12 static code data sets
+Ant, Camel, Ivy, Jedit, JBeans, Log4, Lucene, Poi, Synapse, Velocity, Xalan, Xerces\footnote{Available from the object-oriented defects section of the PROMISE respository openscience.us/repo/defect/ck.} and five configuration data sets Berkeley DB, Apache, SQLite, LLVM,
+  x264\footnote{Available from the performance prediction section of PROMISE
+  http://openscience.us/repo/performance-predict.}. For each of these data sets,
+  we generated 25 {\em before} scores from
+  random split train:test splits in the ratio 4:1 train.
+ The median {\em before} recalls from  the static code data sets was:
+%issue24
+\[\mathrm{recall}=\{98,88,86,84,82,81,79,78,78,\overbrace{55,23,20}^{\mathrm{JBeans,Poi,Xalan}}\}\]
+The median {\em before} $e$  scores from  the configuration data was
+%issue 24
+\[s=\{98,97,95,88,92\}\]
+Note that we need to abort planning in only $3/17$ of our data sets.
+
+This paper also explores five configuration data sets Berkeley DB, Apache, SQLite, LLVM,
+  x264. The median {\em before} scores from these data sets (generated in 
+-- which means we cannot generate plans for $3/12$ of our data sets. However, as shown
+below, we were able to generate useful plans for the other $9/12$ of the data.
+
+In the other type,
+
+then studied to generate a prediction
+on the test data. If the performance on that test data is not
+satisfactory, thempredictions:
+a {\em before} prediction (on the raw test data); and  an {\em after}
+prediction (that is  applying the policies learned from the training data).
+
+The improvement delta $\Delta$ is then computed by dividing {\em after} and {\em before}
+
 This paper presents a novel policy generator called ``HOW''.
@@
 \subsection{Defect Data Set}
-The data was obtained from the PROMISE repository\footnote{Promise Repository: \url{http://openscience.us/repo}}.
+The data was obtained from the PROMISE repository\footnote{Promise Repository: \url{openscience.us/repo}}.
 For the defect data we investigated 32 releases from 11 open source Java projects defined by the metrics highlighted in figure ~\ref{fig:ck}: \kw{Apache Ant} (1.5 -- 1.7), \kw{Apache Camel} (1.2 -- 1.6), \kw{Apache Ivy} (1.1 -- 2.0), \kw{JEdit} (4.1 -- 4.3), \kw{Apache Log4j} (1.0 -- 1.2), \kw{Apache Lucene} (2.0 -- 2.2), \kw{PBeans} (1.0 and 2.0), \kw{Apache POI} (2.0 -- 3.0), \kw{Apache Synapse} (1.0 -- 1.2), \kw{Apache Velocity} (1.4 -- 1.6), and \kw{Apache Xalan-Java} (2.5 -- 2.7).
@@
 for their ICSE '12 paper~\cite{sven12}.
-The data sets have been deployed as a part of the \textsc{SPLConqueror} tool\footnote{\url{http://fosd.de/SPLConqueror}}.
+The data sets have been deployed as a part of the \textsc{SPLConqueror} tool\footnote{\url{fosd.de/SPLConqueror}}.
 This data set contains six examples of real world configurable systems that cover a broad spectrum of scenarios, see figure \ref{fig:cpm} for a summary.

### 2015-05-03 how.tex
Updates from ShareLaTeX

--- 2015-05-02 manuscript.tex
@@
 
+\subsection{Proposed Framework}
+
 We propose using prediction systems (built by data mining) as a verification
@@
 then (2)~apply the {\em predictor} to the altered data {\em test'};
-then (3)~return the performance delta $\Delta$.
+then (3)~return the performance delta.
+
+\subsection{When Not to Plan: Problem of Poor Planner}
 
@@
 mitigate for this {\em problem of poor planners}, it is wise to demand high standards form the {\em
-satisfactory} threshold used in this \fig{frame}.
+satisfactory} threshold used in this \fig{work}.
 
@@
 
-This study explores data sets from two types of domains:
+How prevalent is the problem of poor planners? While
+this is hard to answer in the general case, we can say that for the 17 data
+sets explored in this study, only 3 suffer from this problem.
+This study's    data   from two  types of domains:
 \bi
@@
 the test data detected
-by the {\em predictor}). Using engineering judgement, we define satisfactory recall as anything less than 70\%. 
+by the {\em predictor}). Using engineering judgement, we define satisfactory recall as anything over   70\%. 
 \item 
@@
 using  $s= 1- \frac{abs(a - p)}{a}$.
-Using engineering judgement, we define satisfactory $s$ as anything less than 70\%. 
+Using engineering judgement, we define satisfactory $s$ as anything over   70\%. 
 \ei
@@
   random split train:test splits in the ratio 4:1 train.
- The median {\em before} recalls from  the static code data sets was:
+ The median {\em before} scores from  the static code data sets were:
 %issue24
 \[\mathrm{recall}=\{98,88,86,84,82,81,79,78,78,\overbrace{55,23,20}^{\mathrm{JBeans,Poi,Xalan}}\}\]
-The median {\em before} $e$  scores from  the configuration data was
+The median {\em before}   scores from  the configuration data were:
 %issue 24
@@
 
-This paper also explores five configuration data sets Berkeley DB, Apache, SQLite, LLVM,
-  x264. The median {\em before} scores from these data sets (generated in 
--- which means we cannot generate plans for $3/12$ of our data sets. However, as shown
-below, we were able to generate useful plans for the other $9/12$ of the data.
-
-In the other type,
-
-then studied to generate a prediction
-on the test data. If the performance on that test data is not
-satisfactory, thempredictions:
-a {\em before} prediction (on the raw test data); and  an {\em after}
-prediction (that is  applying the policies learned from the training data).
-
-The improvement delta $\Delta$ is then computed by dividing {\em after} and {\em before}
-
-This paper presents a novel policy generator called ``HOW''.
-HOW is a near-linear time  instance-based
-local search algorithm that looks for improvement trends in the data,
-then adjusting examples to nudge them along that trend.
-The experiments of this paper apply HOW to learning policies for 
-software defect reduction and for compiling software that runs faster.
-At least for the data explored here, HOW's reductions in defects and runtimes
-are very large-- up to 50\% fewer defects and up to 50\% faster runtimes.
-
-The rest of this paper is structured as follows.
+\subsection{Testing for Grainer Causality}
+With one small variation,  the above framework can be used to check if the learned
+plans can be said to {\em cause} a change in the domain being explored.
+
+In the literature, there are two main definitions of causality: Hill's H-causality
+and Grainer's G-casualty. 
+Of the two, Hill's definition is the most strict. An effect
+is H-causal if it satisfies nine criteria including:
+\be
+\item
+Plausibility;
+\item
+Strength of the effect; 
+\item
+Specificity: locality of the effect
+to specialized groups;
+\item
+Support by experimental evidence;
+\item
+Coherence between cause-effects noted
+in the field and in laboratory samples;
+\item
+Temporally: the effect has to follow the cause;
+\item
+Analogy: similar causes have similar effects;
+\item
+Biological gradient: more exposure to the cause leads to more of an
+effect)
+\item
+Consistency: the same cause-effect pairings have been seen by different persons
+in different places.
+\ee
+It is hard to demonstrate H-causality in software. For example, Hill's criteria emphasises repeatability and laboratory studies-- both of which are
+hard to perform in software engineering (e.g. see the continued debate about
+the value of using undergraduate students to surrogates for industrial
+practitioners in software engineering research~\cite{Carver2003}). Also, Hill's requirement
+for consistency is easier to achieve in studies of small closed systems (e.g. bacteria in a petri dish)
+than in large socio-technical systems (e.g. open source projects). As Lofti Zadeh
+commented: ``as complexity rises, precise statements lose meaning and meaningful statements lose precision''~\cite{zadeh.
+
+Granger causality is a statistical concept of causality that is based on prediction.
+According to Granger causality, if a signal X1 "Granger-causes" (or "G-causes") a signal X2, then past values of X1 should contain information that helps predict X2 above and beyond the information contained in past values of X2 alone.
+Its mathematical formulation is based on linear regression modeling of stochastic processes (Granger 1969).
+
+Hill1965
+
+\cite{Seth2007,granger80}
 

### 2015-05-03 how.tex
Updates from ShareLaTeX

@@
 \ee
-The rest of this paepr is structued as follows.
+The rest of this paper is structured as follows.
 
@@
 
-\subsection{Testing for Grainer Causality}
+\subsection{Are These Plans ``Causal''?}
 With one small variation,  the above framework can be used to check if the learned
@@
 
-In the literature, there are two main definitions of causality: Hill's H-causality
-and Grainer's G-casualty. 
+In the literature, there are two main definitions of causality: Hill's H-causality~\cite{Hill1965}
+and Granger's G-casualty~\cite{granger80}. 
 Of the two, Hill's definition is the most strict. An effect
@@
 \ee
-It is hard to demonstrate H-causality in software. For example, Hill's criteria emphasises repeatability and laboratory studies-- both of which are
+It is hard to demonstrate H-causality in software engineering.
+For example, Hill's criteria emphasises repeatability and laboratory studies-- both of which are
 hard to perform in software engineering (e.g. see the continued debate about
@@
 practitioners in software engineering research~\cite{Carver2003}). Also, Hill's requirement
-for consistency is easier to achieve in studies of small closed systems (e.g. bacteria in a petri dish)
-than in large socio-technical systems (e.g. open source projects). As Lofti Zadeh
-commented: ``as complexity rises, precise statements lose meaning and meaningful statements lose precision''~\cite{zadeh.
-
-Granger causality is a statistical concept of causality that is based on prediction.
-According to Granger causality, if a signal X1 "Granger-causes" (or "G-causes") a signal X2, then past values of X1 should contain information that helps predict X2 above and beyond the information contained in past values of X2 alone.
-Its mathematical formulation is based on linear regression modeling of stochastic processes (Granger 1969).
-
-Hill1965
-
-\cite{Seth2007,granger80}
+for consistency is far easier to achieve in studies of small closed systems (e.g. bacteria in a petri dish)
+than in large socio-technical systems (e.g. open source projects).
+
+The practical difficulties associated with Hill's criteria lead Granger~\cite{granger80}
+to propose another criteria\footnote{Granger  notes that
+his proposal was based on earlier work by Norbert Weiner~\cite{Seth2007}.}.
+G-causality is based on building predictions based on {\em past} data,
+then showing that this works for {\em future} data~\cite{granger80}.
+
+Note that the standard 10-way cross-validation
+procedure  in data mining does {\em not} demonstrate G-causality.  In a N-way cross-val experiments, the data is divided into $N$ bins.  
+$N-1$ bins are used for learning and the results are tested
+on the  remaining bin.
+Cross-validation is then repeated $N$ times, each time using a different bin for the test set.
+This approach can not be used to demonstrate causality since, if the initial data is collected
+over (say) $N$ months, then it is possible that the test set contains observations collected
+{\em before}   items seen in the training set.
+
+Jiang et al.~\cite{me11f} and Lumpe et al.~\cite{me11f} propose a modification to cross-validation which lets them
+demonstate G-causal defect effects in softwrare engineering.
+They divide project data  into $N$ bins, each of with contain data collected at similar times.
+They then sort those bins (on the collection date) and use bins $i,j$ to predict for $k$ where 
+$i<j<k$.
+
+We adapt the work of Jiang,Lumpe et al.  as follows. In  \fig{work}, we demand that the {\em test}
+data is not collected before the {\em train} data.  With that change,
+we can reasonably claim that the plan's generating by HOW are G-causal.
 
@@
 \newpage
-\bibliography{References}{}
+\bibliography{how}{}
 \bibliographystyle{IEEEtran}

### 2015-05-03 how.tex
Updates from ShareLaTeX

@@
 \usepackage{algorithmicx}
+
+\usepackage[running]{lineno}
 \usepackage{program}
@@
 \bi
-\item Software defects in certain object-oriented JAVA systems listed in \tion{oo}:  Ant Camel, Ivy, Jedit, JBeans, Log4, Lucene, Poi, Synapse, Velocity, Xalan, Xerces;
-\item The runtime of the software systems discussed in \tion{cpu}: Berkeley DB, Apache, SQLite, LLVM, 
-  x264.
+\item The software defects found in  twelve object-oriented JAVA systems explored in 2010 by Jureczko et al.~\cite{jureczko10};
+\item The runtime of the six software systems whose configurations
+are explored in 2013 by Seigmund et al.~\cite{sven12};
 \ei
+Many papers use this above data to build {\em predictors} for defects and runtimes.
+However, none of those papers then go on to use this data to build {\em planners}.
+
 HOW's instance-based reasoning  makes its conclusions by
@@
 \item An experimental validation that the HOW planner is useful for reducing the
-expected values of software defects and software runtimes (at least, for the data sets studied here).
+expected values of the Jureczko software defects and the Seigmund software runtimes.
 \ee
@@
 plans?''. For example,  in the experiments shown below,  HOW comments  on how to reduce
-software defects by adjusting certain static code parameters of the code\footnote{Such parameters can be automatically adjusted using code refactoring
+software defects by adjusting certain static code parameters of the code\footnote{Such parameters can be mnaually adjusted by programmers or (for large scale changes) automatically adjusted using code refactoring
 tools, as shown by Binkely et al. in 2006~\cite{Binkley2006} and more recently by Mkaouer et al. in 2015~\cite{Mkaouer15}.}. How are we to verify that HOW's recommendations actually work?
@@
 project data is divided into two disjoint sets {\em train} and {\em test}
-(so {\em train} $\cup$ {\em test} $=\;\emptyset$).
+(so \mbox{{\em train} $\cup$ {\em test} $=\;\emptyset$}).
 Next, from the train set, we build both a {\em planner} as well
@@
 
-Turning now to the {\em test} data, this is based to the {\em predictor}
+Turning now to the {\em test} data, this is passed to the {\em predictor}
 to generate a baseline {\em before} performance score.
@@
 
-\subsection{When Not to Plan: Problem of Poor Planner}
-
-The clear advantage of this approach is that it can be readily and automatically
-applied to domains with historical data. That said, the drawback with this approach
-is that our assessment of the plans is only as good as the predictor. To 
-mitigate for this {\em problem of poor planners}, it is wise to demand high standards form the {\em
-satisfactory} threshold used in this \fig{work}.
-
 \begin{figure}[!t]
@@
 \begin{array}{r}
-project\\
-data
+\mathrm{project}\\
+\mathrm{data}
 \end{array} 
@@
         \left\{\begin{array}{l}
-                \mathrm{learn\;a\;}\mathrm{predictor\;}\mathrm{e.g.\;Random\;Forest}\\
-                \mathrm{learn\;a\;}\mathrm{planner\;}\mathrm{e.g.\; HOW}
+                \mathrm{learn\;a\;}\mathrm{predictor\;}\mathrm{(e.g.\;via \;Random\;Forest)}\\
+                \mathrm{learn\;a\;}\mathrm{planner\;}\mathrm{(e.g.\;via \; HOW)}
               \end{array}\right.
@@
 
-How prevalent is the problem of poor planners? While
-this is hard to answer in the general case, we can say that for the 17 data
-sets explored in this study, only 3 suffer from this problem.
-This study's    data   from two  types of domains:
-\bi
-\item
-In one type, we 
-build plans to change static code attributes in order to reduce defects in
-Java classes.  Here,,
-performance can be measured in terms of recall (percent of faulty classes in
-the test data detected
-by the {\em predictor}). Using engineering judgement, we define satisfactory recall as anything over   70\%. 
-\item 
-In the other type, we   build
-plans to change configurations settings within a Makefile such that the resulting compiled
-code will run faster. Here, performance can be measured in terms of difference
-between the predicted runtime $p$ of test case items and their actual runtimes $a$
-using  $s= 1- \frac{abs(a - p)}{a}$.
-Using engineering judgement, we define satisfactory $s$ as anything over   70\%. 
-\ei
-This paper explores 12 static code data sets
-Ant, Camel, Ivy, Jedit, JBeans, Log4, Lucene, Poi, Synapse, Velocity, Xalan, Xerces\footnote{Available from the object-oriented defects section of the PROMISE respository openscience.us/repo/defect/ck.} and five configuration data sets Berkeley DB, Apache, SQLite, LLVM,
-  x264\footnote{Available from the performance prediction section of PROMISE
-  http://openscience.us/repo/performance-predict.}. For each of these data sets,
-  we generated 25 {\em before} scores from
-  random split train:test splits in the ratio 4:1 train.
- The median {\em before} scores from  the static code data sets were:
-%issue24
-\[\mathrm{recall}=\{98,88,86,84,82,81,79,78,78,\overbrace{55,23,20}^{\mathrm{JBeans,Poi,Xalan}}\}\]
-The median {\em before}   scores from  the configuration data were:
-%issue 24
-\[s=\{98,97,95,88,92\}\]
-Note that we need to abort planning in only $3/17$ of our data sets.
-
 \subsection{Are These Plans ``Causal''?}
-With one small variation,  the above framework can be used to check if the learned
+With one additional stipulation,   this framework can be used to check if the learned
 plans can be said to {\em cause} a change in the domain being explored.
@@
 Of the two, Hill's definition is the most strict. An effect
-is H-causal if it satisfies nine criteria including:
-\be
-\item
-Plausibility;
-\item
-Strength of the effect; 
-\item
-Specificity: locality of the effect
+is H-causal if it satisfies nine criteria including
+{\em  plausibility};
+{\em strength} of the effect;
+{\em 
+specificity}, i.e. locality of the effect
 to specialized groups;
-\item
-Support by experimental evidence;
-\item
-Coherence between cause-effects noted
+{\em
+support} by experimental evidence;
+{\em 
+coherence} between cause-effects noted
 in the field and in laboratory samples;
-\item
-Temporally: the effect has to follow the cause;
-\item
-Analogy: similar causes have similar effects;
-\item
-Biological gradient: more exposure to the cause leads to more of an
-effect)
-\item
-Consistency: the same cause-effect pairings have been seen by different persons
+{\em
+temporally} i.e. the effect has to follow the cause;
+{\em 
+analogy}, i.e.  similar causes have similar effects;
+{\em
+biological gradient}, i.e.  more exposure to the cause leads to more of an
+effect; and
+{\em
+consistency}, i.e.  the same cause-effect pairings have been seen by different persons
 in different places.
-\ee
+
 It is hard to demonstrate H-causality in software engineering.
@@
 for consistency is far easier to achieve in studies of small closed systems (e.g. bacteria in a petri dish)
-than in large socio-technical systems (e.g. open source projects).
-
-The practical difficulties associated with Hill's criteria lead Granger~\cite{granger80}
-to propose another criteria\footnote{Granger  notes that
+than in large socio-technical systems (e.g. open source projects). In the latter,
+effects are more {\em probabilistic} than {\em categorical}-- by which we mean that 
+some cause tends to cause some effect at some probability $p$ less that one.
+This in turn means that at some probability $q$ (where $0 \le q < p \le 1$)
+that we will find examples of {\em inconsistency} where some cause does {\em not} lead
+to some effect (thus violating one of Hill's criteria for demonstrating causality).
+
+The  difficulties associated with Hill's criteria lead Granger~\cite{granger80}
+to propose another more practical criteria\footnote{Granger  himself comments that
 his proposal was based on earlier work by Norbert Weiner~\cite{Seth2007}.}.
-G-causality is based on building predictions based on {\em past} data,
+\mbox{G-causality} is based on building predictions based on {\em past} data,
 then showing that this works for {\em future} data~\cite{granger80}. 
-
-Note that the standard 10-way cross-validation
-procedure  in data mining does {\em not} demonstrate G-causality.  In a N-way cross-val experiments, the data is divided into $N$ bins.  
+In should be noted  that the standard 10-way cross-validation
+procedure used  in data mining does not necessarily demonstrate G-causality.  In a N-way cross-val experiments, the data is divided into $N$ bins.  
 $N-1$ bins are used for learning and the results are tested
 on the  remaining bin.
-Cross-validation is then repeated $N$ times, each time using a different bin for the test set.
+This is repeated $N$ times, each time using a different bin for the test set.
 This approach can not be used to demonstrate causality since, if the initial data is collected
@@
 
-Jiang et al.~\cite{me11f} and Lumpe et al.~\cite{me11f} propose a modification to cross-validation which lets them
-demonstate G-causal defect effects in softwrare engineering.
-They divide project data  into $N$ bins, each of with contain data collected at similar times.
-They then sort those bins (on the collection date) and use bins $i,j$ to predict for $k$ where 
-$i<j<k$.
+Jiang et al.~\cite{me11f} and Lumpe et al.~\cite{me11f} propose a modification to cross-validation.
+which lets a researcher
+demonstrate G-causal defect effects in software engineering.
+In this modification, we  divide project data  into $N$ bins, each of with contain data collected at similar times.
+They then sort those bins (on the collection date) and use bins $i,j$ to build models that
+are applied to bin  $k$ where 
+$i<j<k$. Note that this procedure ensures that we are building theories on data seen
+before the test data.
 
 We adapt the work of Jiang,Lumpe et al.  as follows. In  \fig{work}, we demand that the {\em test}
-data is not collected before the {\em train} data.  With that change,
+data is not necessarily collected before the {\em train} data:
+\bi
+\item[\#1:] For data collected from software released in multiple versions, we should hence use  versions  $i,j$ to build models that are applied to version  $k$ where $i<j<k$.
+\item[\#2:] For data collected from Monte Carlo simulations (where inputs are selected at random)
+then as long as simulation $i$ is not used to adjust simulation $j> i$, then any item in that
+data could be generated before any other. For this kind of data, we  can use the first $X\%$
+of the simulation for training, and the remaining data for testing.
+\ee
+In the two case studies of this paper, the Jureczko object-oriented defect data comes from software
+released in multiple versions while the Seigmund configuration data comes from Monte Carlo simulations.
+Hence, we use procedure \#1 for the defect data and procedure \#2 for the configuration data.
+
+With these changes,
 we can reasonably claim that the plan's generating by HOW are G-causal.
+
+\subsection{When Not to Plan: the Problem of Poor Predictors}
+
+The clear advantage of the approach of \fig{work} is that it can be readily and automatically
+applied to domains with historical data. That said, the obvious drawback with this approach
+is that our assessment of the plans is only as good as the predictor. To 
+mitigate for this {\em problem of poor predictors}, it is hence wise to demand high standards for the {\em
+satisfactory} threshold used in this \fig{work}.
+
+How prevalent is the problem of poor planners? 
+In the general case, this is hard to answer. However, as discussed in this section, for the 17 data
+sets explored in this study, only 
+%XXX 
+3 suffer from this problem.
+
+This study's data from two types of domains: the Jureczko   object-oriented data  
+and the Seigmund configuration data. 
+For the Seigmund data, the plans generated by HOW advise on how  to change the   configurations settings within a Makefile
+(in order to make resulting compiled
+code  run faster). Here, performance can be measured in terms of  difference
+between the predicted runtime $p$ of test case items and their actual runtimes $a$
+using  $s= 100*(1- \frac{abs(a - p)}{a})$.
+Using engineering judgement, we define satisfactory $s$ as anything over   70\%. 
+This paper  explores    six Seigmund configuration data sets:  Berkeley DB (Java and Windows versions), Apache, SQLite, LLVM, and
+  x264\footnote{Available from the performance prediction section of PROMISE
+  http://openscience.us/repo/performance-predict.}. 
+  After splitting that data into equal sized train:test groups, a Random Forest
+  Regressor trained on one half, then applied to the other, achieved nearly perfect scores of
+%issue 24
+\[s=\{99.9, 99.8, 99.4, 99.1, 96,1\}\]
+(Aside: if the reader doubts that such high scores are achievable, we note that these scores are 
+consistent with those achieved by predictors built by Seigmund et al.~\cite{sven12}.)
+
+For the  Jureczko   object-oriented data,
+the plans generated by HOW advise   how to change static code attributes in order to reduce defects in
+Java classes.  Here,
+performance can be measured in terms of recall (percent of faulty classes in
+the test data detected
+by the {\em predictor}). Using engineering judgement, we define satisfactory recall as anything over   70\%. 
+This paper explores 12 of the Jureczko   object-oriented static code data sets: Ant, Camel, Ivy, Jedit, JBeans, Log4, Lucene, Poi, Synapse, Velocity, Xalan, Xerces\footnote{Available from the object-oriented defects section of the PROMISE respository openscience.us/repo/defect/ck.}.
+For each of these data sets, we generated  {\em before} scores  by finding the latest
+version $k$, then training  a predictor on versions $k-2$ and $k-1$. As reported below,
+our initial recall scores from this data were unpromising (very low recall values). However,
+after applying certain data pre-processing steps (described below), a Random Forest generated
+on the $k-2,k-1$ versions achieved recalls on version $k$ of
+%issue24
+\[\mathrm{recall}=\{98,88,86,84,82,81,79,78,78,\overbrace{55,23,20}^{\mathrm{JBeans,Poi,Xalan}}\}\]
+From the above, we conclude that all the Seigmund configuration data and most of the Jureczko data
+avoids the problem of poor predictors. Hence, we can use that data for the planning
+experiments described below.
+
+\section{Experimental Methods}
+
+blah blah data. algorithms. statistics
 

### 2015-05-03 _figs/s.sh
typo

@@ -1,0 +1,51 @@
+data() { cat<<EOF
+ant        a 0.54 0.13
+camel      c 0.45 0.38
+ivy        i 0.8  0.41
+jedit      j 0.64 0.3
+log4j      l 0.8  0.19
+luncene    L 0,6  0.3
+pbeans(rf) P 0.9  0.32 
+poi        p 0.57 0.33
+synapse    s 0.63 0.49
+velocity   v 0.86 0.66
+xalan      x 0.44 0
+xerces     X 0.22 0.4
+EOF
+}
+
+data | sed 's/[ ]+/	/g' > /tmp/s.dat
+points() {
+    data | gawk '{
+      print "set label \"" $2 "\" at  " $3 "," $4 ";\n" }'
+}
+
+eps2pdf() {
+ gs -dSAFER -dNOPLATFONTS -dNOPAUSE -dBATCH \
+  -sDEVICE=pdfwrite -sPAPERSIZE=letter -dCompatibilityLevel=1.4 \
+  -dPDFSETTINGS=/printer -dCompatibilityLevel=1.4 -dMaxSubsetPct=100 \
+  -dSubsetFonts=true -dEmbedAllFonts=true -dEPSCrop -sOutputFile="$1.pdf" \
+  -f "$1.eps"
+}
+
+plot(){
+    gnuplot<<EOF
+set terminal postscript eps color "Helvetica" 15
+set size 0.5,0.5
+set output "s.eps
+set xrange [0:1]
+set yrange [-0.05:1]
+set xlabel "recall (pd)"
+set ylabel "\% false alarms"
+set arrow 1 from 0.6,0.4 to 1,0.4 nohead
+set arrow 2 from 0.6,0.4 to 0.6,-0.05 nohead
+
+$(points)
+plot "/tmp/s.dat" using ($$3+0.05):4 title "" with points lt 1 pt 6
+EOF
+eps2pdf s
+}
+
+plot
+open s.pdf
+

### 2015-05-03 how.tex
Updates from ShareLaTeX

@@
 Many papers use this above data to build {\em predictors} for defects and runtimes.
-However, none of those papers then go on to use this data to build {\em planners}.
-
-HOW's instance-based reasoning  makes its conclusions by
-studying the space of examples. This is a very different approach to
-{\em model-based planners} that use the model
-as sub-routine within a Monte Carlo simulation~\cite{me07f} or the evolutionary 
-programming methods explored by the search-based software
-engineering community~\cite{krall14,harman12dec}. 
-We find   HOW's instance-based approach useful since it can be applied
-to domains that lack a model, but possess a historical log of observed behaviours.
-
-Instance-based reasoning is also useful if building and certifying a model   takes a long time.
-Such slow-to-build models exist in software engineering.
-For  example, in previous work~\cite{me07f} we used models
-developed by Boehm's group at the University of Southern California.
-Some of those models took decades to develop and mature (from 1981~\cite{boehm81} to 2000~\cite{boehm00b}).
-This is not an isolated example.
-One of us (Menzies) teaches a graduate class in automated model-based software engineering.
-Students in that class are asked to find (or build) a non-trivial model of
-some software process (where ``non-trivial'' means something that processes
-a  model at least an order of magnitude more complex than Brooks' Law). 
-While the  number of such models has been growing in recent years\footnote{See the
-catalogue at goo.gl/nv2AVK.}, 
-the total number remains very small-- which is an observation consistent with
-SE models typically require  much effort to build and certify.
-
-Finally, even when there is an existing model, instance-based reasoning can be useful.
-Sometimes  it is easier to access instances of a model's behaviour than the model
-itself. For example, in prior work with Martin  Feather from the Jet Propulsion 
-Laboratory~\cite{fea02a},  our research partner could not share a
-propriety model from within the NASA firewalls. However, they could share 
-logs of the input/output of that model.
+However, aside from work by the authors of this paper,
+none of those papers then go on to use this data to build {\em planners}.
 
@@
 The rest of this paper is structured as follows.
-
-\section{From ``Prediction'' to ``Planning''}
+HOW's instance-based reasoning  makes its conclusions by
+studying the space of examples. As discussed in \tion{mm},
+this is a very different approach to
+{\em model-based planners} that use the model
+as sub-routine within a Monte Carlo simulation~\cite{me07f} or the evolutionary 
+programming methods explored by the search-based software
+engineering community~\cite{krall14,harman12dec}.
+
+\section{HOW: Motivation and Methods}\label{sec:mm}
+
+ \subsectuion{Why ``HOW''?}
+
+HOW was inspired by some recent work by Krall and Menzies and Davis on 
+the GALE optimizer~\cite{krall14}. A well-known effect in machine learning (and, in computer vision
+and compression~\cite{levina04}) is that the $n$ dimensions of a data set can be represented by a  much
+lower-dimensional approximation. GALE finds those $m << n$ dimensions then mutates examples
+towards the better end of each dimension $m_i$.
+
+A limitation with GALE is that whenever it adjusts an instance, some model has to be called
+to re-evaluate the new objective scores for the new examples. This can be a limitation
+since, in some domains, no such model exists or is readily accessible.
+Building and certifying a model   takes a long time. Such slow-to-build models exist in software engineering. For  example, in previous work~\cite{me07f} we used models
+developed by Boehm's group at the University of Southern California.
+Some of those models took decades to develop and mature (from 1981~\cite{boehm81} to 2000~\cite{boehm00b}).
+This is not an isolated example.
+One of us (Menzies) teaches a graduate class in automated model-based software engineering.
+Students in that class are asked to find (or build) a non-trivial model of
+some software process (where ``non-trivial'' means something that processes
+a  model at least an order of magnitude more complex than Brooks' Law). 
+While the  number of such models has been growing in recent years\footnote{See the
+catalogue at goo.gl/nv2AVK.}, 
+the total number remains very small-- which is an observation consistent with
+SE models typically require  much effort to build and certify.
+
+Finally, even when there is an existing model, instance-based reasoning can be useful.
+Sometimes  it is easier to access instances of a model's behaviour than the model
+itself. For example, in prior work with Martin  Feather from the Jet Propulsion 
+Laboratory~\cite{fea02a},  our research partner could not share a
+propriety model from within the NASA firewalls. However, they could share 
+logs of the input/output of that model.
+
+Depending on the audience, we can
+might call HOW a spectral learner, 
+a response surface method, or  a local search operator.
+{\em Spectral learners}~\cite{kamvar03} reason across $m$ dimensions synthesized
+using (say) PCA~\cite{pearson1901}. For example,
+algorithms like PDDP~\cite{boley98} use PCA to
+recursively divide data into smaller regions where each level of recursion needs an   $O(N^2)$ analysis
+to infer the principle components. HOW performs an analogous procedure using a   $O(2N)$ analysis
+based on a heuristic proposed by
+Faloutsos and Lin~\cite{Faloutsos1995} (see above, the ``FASTMAP'' algorithm).
+
+{\em Response surface methods}  build a fast approximation to the function being optimized,
+then uses that  approximation to take intelligent guesses about useful mutations. HOW
+is a non-parametric response surface method that finds its response surface via recursive
+clustering. For an example of a parametric response surface method, that uses Gaussian process
+models, see Zuluaga et al.~\cite{zuluaga13}.
+
+A {\em local search operator} that a some probability $p$, nudges  instance variables
+along a dimension that improves its objective scores. HOW's recursive clustering methods
+combine $n$ dimensions into $m \ll n$ so its ``nudges'' are simultaneous
+adjustments along multiple dimensions. For an example of other kinds of local search algorithms, that only adjust
+one variable at a time, see the literature on WALKSAT~\cite{Selman1992} and MAXWALKSAT~\cite{kautz97}.
+See also the literature on local search methods in multi-objective optimization.
+
+\be
+\item Take  a population $P$ of examples
+\item Separate all $p \in P$ examples into their $n$ independent variables and 
+their $o$ scores;
+\item Find $m \ll n$ lower dimensional approximations for the $n$ independent variables;
+\item Look for the worst and best ends of each $m$  dimension (where the better ends
+have better objective scores);
+\item Find the $q \subseteq P$ subset of the population with ``better'' objective scores;
+\item Generate the next population $P'$ by adjust the independent variables
+of the $q$  examples
+by a random amount (in the direction of  the  better ends of each dimension).
+\item Apply some model to discover all the objective scores of $P'$
+\item Set $P=P'$ and go to step 1
+\ee
+
+PCA explores the $e$
+eigenvectors of the correlation matrix between $d$
+variables~\cite{pearson1901}.  Usually,
+only a few $e \ll d$ eigenvectors are required
+since multiple inter-related variables $i,j,k \subseteq d$ can be represented
+by a single  eigenvector.
+Also, noisy variables from $d$ are
+ignored since they  do not contribute to the signal in the data.
+Further,
+redundant  variables  become (approximately) parallel lines
+in $e$ space. For all such redundancies \mbox{$i,j \in d$}, we
+can ignore $j$
+since effects that change over $j$ also
+change in the same way over $i$.
+
+Algorithms like PDDP~\cite{boley98} use PCA to
+recursively divide data into smaller regions. Each
+step of that process requires an $O(N^2)$ analysis
+of the data to compute the components~\cite{ilin10}. Worse, it requires an evaluation of every example.
+Using WHERE, competitive results can be achieved
+using an $O(2N)$ analysis.
+WHERE uses a heuristic proposed by
+Faloutsos and Lin~\cite{Faloutsos1995}
+(which
+Platt has
+  shown computes a Nystr\"om
+  approximation to the first component of
+  PCA~\cite{platt05}).
+In step one, WHERE inputs
+$N$
+examples $N_1,N_2,..$. Secondly, WHERE
+picks any
+point $N_i$ at random. Thirdly, WHERE
+finds the point  {\em West}~$\in N$ that is
+furthest\footnote{
+ For this work, we use the standard Euclidean measure recommended for
+instance-based reasoning by Aha et al.~\cite{aha91};
+i.e. $\sqrt{\sum_i(x_i-y_i)^2}$ where $x_i,y_i$
+are values normalized 0..1 for the range min..max.}
+from $N_i$.
+Finally, WHERE
+
+$m \ll n$
+dimension
+
+HOW divide training into regions where the training
+data has similar properties. Each region is then examined and divided into ``west'' and ``east''
+where the region's ``west'' end has examples with worst performance stores than the east
+end (mnemoc: west starts with ``w'' and is short for ``worst' and east starts with ``e;;]which is shirt
+for excellent).so the ``e'' in
+
+\be
+\item Clustering the training data 
+\item 
+(c) finding which end of the cluster has better performance scores.
+(d) find
+
+\section{Methodological Comments:\\ from ``Prediction'' to ``Planning''}
 A major  problem with building a planning mechanism in software engineering is ``how to verify the generated

### 2015-05-04 how.tex
Updates from ShareLaTeX

@@
 \ei
-Many papers use this above data to build {\em predictors} for defects and runtimes.
+In summary, this paper makes six contributions that are significantly different to
+prior work:
+\be
+\item Many software analytics papers use data to build {\em predictors} for (e.g.) defects and runtimes.
 However, aside from work by the authors of this paper,
-none of those papers then go on to use this data to build {\em planners}.
-
-In summary, this paper makes five contributions:
-\be
-\item A general framework for augmenting a prediction system such that
+none of those papers then go further to use that data to build {\em planners}.
+\item This paper offers a general framework for augmenting a prediction system such that
 it becomes a planning system;
-\item A  test that recognizes  when we should {\em not}  plan: in summary, our kind of planning is
+\item This paper offers a  test that recognizes  when we should {\em not}  plan: in summary, our kind of planning is
 not recommended in domains that  generate poorly performing predictors;
-\item A general verification rig for assessing the value of plans generated within this rig.
-\item The HOW  instance-based planner.
-\item A proof that HOW runs in near-linear time.
-\item An experimental validation that the HOW planner is useful for reducing the
+\item This paper offers a general verification rig for assessing the value of plans generated within this rig.
+\item The HOW  instance-based planner of this paper has not been presented before.
+\item The experiments of this paper show that HOW planner is useful for real-world tasks;
+e.g. reducing the
 expected values of the Jureczko software defects and the Seigmund software runtimes.
@@
 
- \subsectuion{Why ``HOW''?}
-
+ \subsection{Motivation: Why ``HOW''?}
 HOW was inspired by some recent work by Krall and Menzies and Davis on 
@@
 lower-dimensional approximation. GALE finds those $m << n$ dimensions then mutates examples
-towards the better end of each dimension $m_i$.
-
-A limitation with GALE is that whenever it adjusts an instance, some model has to be called
-to re-evaluate the new objective scores for the new examples. This can be a limitation
-since, in some domains, no such model exists or is readily accessible.
-Building and certifying a model   takes a long time. Such slow-to-build models exist in software engineering. For  example, in previous work~\cite{me07f} we used models
+towards the better end of each dimension $m_i$. Since it explores $m \ll n$ dimensions,
+GALE terminates much faster than standard optimiser (e.g. for one large model, 4 minutes versus 7 hours~\cite{krall14}).
+Better yet, GALE's rapdily generated  solutions are competitive (or better) than those found by 
+slower optimizers.
+
+A limitation with GALE is that it makes extensive use of
+an underlying domain model to asses generations of newly mutated instances.  This is an issue since
+in some domains, no such model exists or is readily accessible. For example, this whole paper
+began when, after briefing a business client on GALE, they asked:
+\begin{quote}
+{\em ``But what if I do not have a model of my business?''}
+\end{quote}
+This is a legitimate concern.
+Building and certifying a model  can  takes  long time, especially in software engineering. For  example, in previous work~\cite{me07f} we used models
 developed by Boehm's group at the University of Southern California.
@@
 
-Finally, even when there is an existing model, instance-based reasoning can be useful.
-Sometimes  it is easier to access instances of a model's behaviour than the model
+Also, even when there is an existing model, instance-based reasoning can be useful.
+Models need maintenance lest they become out-dated. Elsewhere, we have described our
+extensions to the USC models to enable reasoning about agile software developments. 
+It took many months to implement and certify those extensions~\cite{me09i,me09j}.
+The problem of model maintenance is another
+motivation to look for alternate methods that can be automateically updated whenever new data arrives.
+
+Finally, sometimes  it is easier to access instances of a model's behaviour than the model
 itself. For example, in prior work with Martin  Feather from the Jet Propulsion 
@@
 
-Depending on the audience, we can
-might call HOW a spectral learner, 
-a response surface method, or  a local search operator.
-{\em Spectral learners}~\cite{kamvar03} reason across $m$ dimensions synthesized
-using (say) PCA~\cite{pearson1901}. For example,
-algorithms like PDDP~\cite{boley98} use PCA to
-recursively divide data into smaller regions where each level of recursion needs an   $O(N^2)$ analysis
-to infer the principle components. HOW performs an analogous procedure using a   $O(2N)$ analysis
-based on a heuristic proposed by
-Faloutsos and Lin~\cite{Faloutsos1995} (see above, the ``FASTMAP'' algorithm).
-
-{\em Response surface methods}  build a fast approximation to the function being optimized,
-then uses that  approximation to take intelligent guesses about useful mutations. HOW
-is a non-parametric response surface method that finds its response surface via recursive
-clustering. For an example of a parametric response surface method, that uses Gaussian process
-models, see Zuluaga et al.~\cite{zuluaga13}.
-
-A {\em local search operator} that a some probability $p$, nudges  instance variables
-along a dimension that improves its objective scores. HOW's recursive clustering methods
-combine $n$ dimensions into $m \ll n$ so its ``nudges'' are simultaneous
-adjustments along multiple dimensions. For an example of other kinds of local search algorithms, that only adjust
-one variable at a time, see the literature on WALKSAT~\cite{Selman1992} and MAXWALKSAT~\cite{kautz97}.
-See also the literature on local search methods in multi-objective optimization.
+Note that this lack of access to a workable model is not just fatal for GALE, but also for every
+other model-based optimization algorithm such as simulated
+annealling or evolutuionary methods such as   
+NSGA-II, NSGA-III, SPEA2, IBEA, PSO, DE, MOEA/D, etc.~\cite{deb00a,zit02,zit04,%
+deb14,Cui2005a,storn97,zhang07:TEC}. Accordingly, this paper seeks
+an optimization methods that avoids the problem of models that are missing, slow
+to build, hard to maintain, or difficult to access.
+
+\subsection{Methods: How to Build ``HOW''?}
+HOW is a variant of GALE that does not need a underlying domain model.
+
+When designing HOW, our premises were:
+\bi
+\item
+This is no domain model; (b)~we have some
+labelled data and (b)~we seek minimal
+disrupttion
+HOW divide training into regions where the training
+data has similar properties. Each region is then examined and divided into ``west'' and ``east''
+where the region's ``west'' end has examples with worst performance stores than the east
+end (mnemoc: west starts with ``w'' and is short for ``worst' and east starts with ``e;;]which is shirt
+for excellent).so the ``e'' in
 
@@
 
-HOW divide training into regions where the training
-data has similar properties. Each region is then examined and divided into ``west'' and ``east''
-where the region's ``west'' end has examples with worst performance stores than the east
-end (mnemoc: west starts with ``w'' and is short for ``worst' and east starts with ``e;;]which is shirt
-for excellent).so the ``e'' in
-
 \be
@@
 (d) find
+\ee
 
@@
 one column whose values can be sorted from ``desired'' to ``undesired''.
-
-\section{Related Work}
-Policy generation is different to standard data mining in that the 
-latter is most concerned with what {\em is} rather than {\em what to do}.
-For example, a classification or prediction system such as C4.5~\cite{quinlan92} or CART~\cite{breiman84} can predict for a discrete or continuous class variable
-(respectively). As such, they can be used as a sub-routine within a
-policy generator. For example, later in this paper we will use the CART
-prediction system to assess the policies generated by HERE.
-
-Policy generation with HERE is different to the recommendor systems.
-As described by Robillard and Walker~\cite{rob14}, recommendor systems
-in software engineering
-are less {\em directive} and more    {\em collaborative} than policy
-generators:
-\bi
-\item
-Directive systems such as HERE tell developers exactly what to do
-(e.g. ``use these settings in a Makefile'') 
-\item
-Collaborative systems are more suggestive guides that
-help (e.g.) programmers focus on very small sets
-with  very large libraries of code of documentation.
-\ei
-Collaborative systems may not presume to know what to do
-in that smaller set (while the directive systems would issue an edict
-such as  ``change this to that'').
-
-We also distinguish HERE's policy generation fro the multi-objective optimization methods explored by Harman and Krall and Menzies and 
-and many others.
-
-Previous with have explored model-based policy generation with STAR,
-NOVA, and instance-based policy generation with  W2.
-
-refactoring XXX
-
-Finally, we note that HERE is a temporal transfer learner.
 
@@
 % \section{Discussion}
-% \section{Threats to validity}
-% \section{Conclusion}
+\section{Threats to validity}
+\input{related}
+
+\section{Conclusion}
 % \section*{Acknowledgements}

### 2015-05-04 related.tex
Updates from ShareLaTeX

\section{Related Work}
The connection of HOW to model-based evolutionary programming was discussed above.
In summary,   model-based tools such as NSGA-III~\cite{deb14} or MOEA/D~\cite{zhang07:TEC}
use some domain model as part of extensive Monte Carlo studies (augmented with some
evolution of selected best instances).
The premise of HOW is that we have access to domain data, but not a domain model.
Also, the results shown above were obtained without evolving/updating some current population
multiple times.

Planning with HERE is somewhat different to the recommendor systems.
As described by Robillard and Walker~\cite{rob14}, recommendor systems
in software engineering
are less {\em directive} and more    {\em collaborative} than policy
generators:
\bi
\item
Directive systems such as HERE tell developers exactly what to do
(e.g. ``use these settings in a Makefile'') 
\item
The collaborative systems discussed by Robillard and Walker
are more suggestive guides that
help (e.g.) programmers focus on very small sets
with  very large libraries of code of documentation.
\ei
One difference between directive and collaborative systems is that
the latter may not presume to suggest exactly what to do next.
However, planning systems like HOW are much more ardent: then make precise recommendations
of how to change all items in the test suite.

HOW is more a data mining method than a model-based optimizer. It represents our next attempt
to develop model-less instance-based optimizers.  Our previous attempts in this area
were the W2, WHERE, and IDEA systems~~\cite{menzies13:brady,Menzies2013:local,me12c}.
W2 was developed with Brady et al.~\cite{menzies13:brady}. 
W2 reasoned over deltas in the the raw
attributes values (and not the synthesized attributes used by HOW). 
The results of  adjusting values via those deltas was assessed via an SQL-like
query that selected all examples in the database that satisfied the newly adjusted
values. W2 suffers from two problems that are resolved
in this paper: {\em optimization failure} and {\em instance exhastion}.
\bi
\item 
As reported in that paper, W2
had a large number of {\em optimization failures}; i.e. after applying its recommendations,
the objective scores actually got worse. We recommend HOW's approach (of reasoning
over the synthesized attributes) to W2 since {\em in none of the above
results} do we observe that {\em after} we treat the data, that the objective scores are worse.
\item
As to {\em instance exhaustion}, W2 was a simple case-based reasoning system that never generalized
over its instances. Hence, the SQl-like query used to asses W2's plans often returned
a vanishingly small number of instances. To avoid this problem, we strongly recommend
combining a planning system with a prediction system (as done in this paper) such that we can
generalize to adjusted examples not seen on the original sample.
\ei
The WHERE tool~\cite{Menzies2013:local} developed the recursive clustering method over synthesized attributes
  used in this paper. WHERE was   a prediction
system since reported current patterns in the data, rather than proposing plans
on how to improve those patterns. Nor did that tool offer guidance on how to assess
the results of stepping along those patterns to guide changes to the system.

The problems of W2 and the success of WHERE suggested in might be useful to combine
WHERE's synthesized attributes with W2. The result was the IDEA tool~\cite{me12c}. 
While the initial prototype seemed promising~\cite{me12c}, we made the mistake of using
the tree structure of the recursive clusters to generate plans (in IDEA, the plan to
move an instance from one poorly performing cluster $C_1$ to another $C_2$ was computed
from the different in the  median
values of the instances in the two  branches that lead to $C_1$ and $C_2$).  When
that approach was applied to the data used in this paper, the results were quite weak
(very little net improvement). However, we abandoned the tree-query approach
and went for the pure instance-based approach discussed at the start of this paper.

Moving on to other releated work, depending on the audience  we would
 call HOW a {\em spectral learner}, 
a {\em response surface method}, or  a {\em local search operator}.
According to
Kamvar et al~\cite{kamvar03}
{\em spectral learners}reason across $m$ underlying dimensions synthesized
using (say) PCA~\cite{pearson1901}. For example,
algorithms like PDDP~\cite{boley98} use PCA to
recursively divide data into smaller regions where each level of recursion needs an   $O(N^2)$ analysis
to infer the principle components. HOW performs an analogous procedure using a   $O(2N)$ analysis
based on a heuristic proposed by
Faloutsos and Lin~\cite{Faloutsos1995} (see above, the ``FASTMAP'' algorithm).

{\em Response surface methods}  build a fast approximation to the function being optimized,
then uses that  approximation to take intelligent guesses about useful mutations. HOW
is a non-parametric response surface method that finds its response surface via recursive
clustering. For an example of a parametric response surface method, that uses Gaussian process
models, see Zuluaga et al.~\cite{zuluaga13}.

A {\em local search operator} that a some probability $p$, nudges  instance variables
along a dimension that improves its objective scores. HOW's recursive clustering methods
combine $n$ dimensions into $m \ll n$ so its ``nudges'' are simultaneous
adjustments along multiple dimensions. For an example of other kinds of local search algorithms, that only adjust
one variable at a time, see the literature on WALKSAT~\cite{Selman1992} and MAXWALKSAT~\cite{kautz97}.
See also the literature on local search methods in multi-objective optimization.
For example,
Peng et al.~\cite{peng09:ls} have augmented MOEAs with
local search  (i.e. applying a problem-specific repair/improvement
heuristic on some current solution).
Also, Igel et al.'s~\cite{igel07} multi-objective
covariance matrix adaptation evolution strategy
can run the mutations along  ``ridges'' in the search space.

Note that the above response surface methods and local search operators cannot be compared to HOW
since, unlike HOW, they assume the presence of some model that can evaluate generations of newly mutated
instances. Recall from the above that the goal of HOW is to offer an optimization method without
using the evolutionary methods that make extensive demands on an underlying domain model.

### 2015-05-05 how.tex
Updates from ShareLaTeX

@@
  \usepackage{pifont}
- \usepackage{times}
+ %\usepackage{times}
 \usepackage{rotating}
@@
 \definecolor{Comments}{rgb}{0,0.63,1}
+\definecolor{Comments}{rgb}{0.5,0.5,0.5}
 \definecolor{Backquotes}{rgb}{0,0,0}
@@
 numbers=#1,
-numberstyle=\footnotesize,
+numberstyle=\scriptsize,
 numbersep=0.5em,
@@
 % Basic
-basicstyle=\ttfamily\small\setstretch{0.8},
+basicstyle=\ttfamily\scriptsize\setstretch{0.8},
 backgroundcolor=\color{Background},
@@
  \subsection{Motivation: Why ``HOW''?}
-HOW was inspired by some recent work by Krall and Menzies and Davis on 
-the GALE optimizer~\cite{krall14}. A well-known effect in machine learning (and, in computer vision
+HOW was inspired by certain  limits observed in 
+the GALE optimizer~\cite{krall14}. 
+A well-known effect in machine learning (and, in computer vision
 and compression~\cite{levina04}) is that the $n$ dimensions of a data set can be represented by a  much
@@
 an underlying domain model to asses generations of newly mutated instances.  This is an issue since
-in some domains, no such model exists or is readily accessible. For example, this whole paper
+in some domains, no such model exists or is readily accessible. For example, this   paper
 began when, after briefing a business client on GALE, they asked:
@@
 \subsection{Methods: How to Build ``HOW''?}
-HOW is a variant of GALE that does not need a underlying domain model.
-
+
+A general model for {\em predictors} is as follows. 
+During testing, each test instance gains a  prediction 
+by finding which region of the data it falls into.
+During training, those regions are inferred from
+divisions that ``chunk'' together regions with instances
+with similar properties. These dividers can be categorical (as in the case of decision trees) or probabilistic (as in the
+case of Naive Bayes) or learned via some distance minimization
+process 
+(as in the case of support vector machines) or generated
+directly by some clustering algorithm.
+
+Those same regions can be used for instance-based 
+{\em planning}-- but instead of leaving test instances in the regions
+found during training, we displace them towards regions
+with better objective scores. 
+Two important design decision with HOW 
+is how to determine the {\em magnitude} and {\em direction} of the
+displacement.
+
+For HOW v1.0 (reported in this paper), we committed to a policy
+of {\em minimal displacement}  since we do not wish to alarm developers and managers
+with large scale change requests.
+Note that minimal displacement makes HOW very different
+to evolutionary optimizers.
+Those algorithms, which include  
+GALE, NSGA-II, NSGA-III, SPEA2, IBEA, PSO, DE and  MOEA/D~\cite{krall14,deb00a,zit02,zit04,%
+deb14,Cui2005a,storn97,zhang07:TEC} can make large scale
+displacements to the original population.
+
+Accordingly, HOW v1.0  executes by:
+\be
+\item Dividing the $N$ training examples into many small clusters (each of size of , at most, $\sqrt{N}$);
+\item
+For a test instance that falls into cluster $C_i$,
+never displace more than the boundary of that  cluster.
+\ee
+For the purposes of clustering, we use the WHERE recursive
+descent procedure~\cite{me
+WHERE is a spectral clusterer; i.e. it
+executes over   synthesized dimensions discovered
+by a 
+principle components analysis (PCA)
+
+Having  limiting the displacement {\em distance} to within one cluster,
+there is still the issue of how to select the displacement 
+{\em direction}.
+
+Let the training and test instances comprise pair of independent and objective values. For example:
+\bi 
+\item
+For the Seigmund data,
+the objective score is the runtime of the test suite of some compiled program;
+\item
+For the Jureczko data, the objective score
+is a boolean that is true if defects have been noted
+for that class.
+\ei
+Let $X,Y$ be particular  training and test instance.
+Further, 
+let the training data be clustered and $X$
+comes from a cluster $C_i$ that is near the test instance $Y$
+and has objective scores better than those seen in $Y$.
+We call $X$  the {\em exemplar} of $C_i$ since it
+holds independent values that best characterize that cluster:
+\bi
+\item
+For
+instances with numeric objectives (e.g. the Seigmund data), 
+the exemplar of a cluster is the instance
+with the best objective score.
+\item
+For instances with discrete objectives (e.g. Jureczko data),
+there is less differentiation between the objective scores.
+Hence, for this kind of the data, the exemplar of a cluster is
+an instance synthesized from the median values of the instances
+in that cluster.
+\ei
+Given the above, we can now define a {\em plan} to be
+a set of values to be added to a test instance in order
+to reduce the distance between that instance and the exemplar: 
+\[Y_j = Y_j + f*(X_j - Y_j)\]
+In the above, $Y_j$ is an independent variable within the
+test instance $Y$; $X$ is the exemplar found at training time;
+and  $f$ is a constant that controls
+how far we  move an instance (which is tuned for different data
+sets).
+
+A core design principle for HOW was ``minimal change'';
+i.e. make very small changes to the current instance.
+\ei
+There are many ways to find those regions 
 When designing HOW, our premises were:
@@
 eigenvectors of the correlation matrix between $d$
-variables~\cite{pearson1901}.  Usually,
+variables~\cite{pearson1901}.  
+This is a useful approach since, usually,
 only a few $e \ll d$ eigenvectors are required
@@
 Algorithms like PDDP~\cite{boley98} use PCA to
-recursively divide data into smaller regions. Each
+recursively cluster data into smaller regions. Each
 step of that process requires an $O(N^2)$ analysis
@@
   PCA~\cite{platt05}).
-In step one, WHERE inputs
+Initially, WHERE inputs
 $N$
-examples $N_1,N_2,..$. Secondly, WHERE
+instances $N_1,N_2,..$. Secondly, WHERE
 picks any
-point $N_i$ at random. Thirdly, WHERE
-finds the point  {\em West}~$\in N$ that is
-furthest\footnote{
- For this work, we use the standard Euclidean measure recommended for
+instance $N_i$ at random. Thirdly, WHERE
+finds the instance  {\em West}~$\in N$ that is
+furthest from $N_i$. Finally,
+if funds the point {\em East}~$\in N$ 
+that is furthest from {\em West}. To computer these distances,
+we use the standard Euclidean measure recommended for
 instance-based reasoning by Aha et al.~\cite{aha91};
 i.e. $\sqrt{\sum_i(x_i-y_i)^2}$ where $x_i,y_i$
-are values normalized 0..1 for the range min..max.}
-from $N_i$.
-Finally, WHERE
-
-$m \ll n$
-dimension
+are values normalized 0..1 for the range min..max.
 

### 2015-05-05 how.tex
Updates from ShareLaTeX

@@
 The problem of model maintenance is another
-motivation to look for alternate methods that can be automateically updated whenever new data arrives.
+motivation to look for alternate methods that can be automatically updated whenever new data arrives.
 
@@
 with large scale change requests.
+HOW's minimal displacement policy is to generate
+many small clusters, then limit displacement to the distance
+to the nearest cluster.
 Note that minimal displacement makes HOW very different
@@
 
-Accordingly, HOW v1.0  executes by:
-\be
-\item Dividing the $N$ training examples into many small clusters (each of size of , at most, $\sqrt{N}$);
-\item
-For a test instance that falls into cluster $C_i$,
-never displace more than the boundary of that  cluster.
-\ee
 For the purposes of clustering, we use the WHERE recursive
-descent procedure~\cite{me
-WHERE is a spectral clusterer; i.e. it
-executes over   synthesized dimensions discovered
-by a 
-principle components analysis (PCA)
-
-Having  limiting the displacement {\em distance} to within one cluster,
+descent procedure of \fig{where} that converts
+$N$ instances into $\sqrt{N}$ clusters.
+WHERE is a spectral clusterer~\cite{kamvar03}; i.e. it
+executes in near linear time to generate
+cluster using dimensions  discovered
+by a  PCA-like analysis (PCA=principle components analysis).
+
+\begin{figure}[t!]
+\small
+\begin{tabular}{|p{.95\linewidth}|}\hline
+WHERE recursive divides data as follows.
+It finds the two   distance instances,  $X,Y$
+by picking any instance $W$ at random, then setting $X$ to its most
+distant instance, then setting $Y$ to the instance most distant from
+$X$. 
+Note that finding $X,Y$ requires only $O(2N)$ comparisons
+of $N$ instances.
+
+Let $c=dist(X,Y)$. Using $c$, we next  project each instance $Z$
+onto a line that  runs between $X,Y$ as follows. If $a=dist(Z,X)$ and
+$b=dist(Z,Y)$, the $Z$'s
+distance from   {\em X} along the $XY$ line is
+$x=(a^2 + c^2 - b^2)/(2c)$.
+To recurse, split the data at the median $x$ value of all instances then call WHERE on each half (stopping when
+one half has less  than $\sqrt{N}$ of the original population
+
+In the above, to computer distances, we use
+the Euclidean measure recommended for
+instance-based reasoning by Aha et al.~\cite{aha91};
+i.e. $\sqrt{\sum_i(X_i-Y_i)^2}$ where $X_i,Y_i$
+are values normalized 0..1 for the range min..max.
+\\\hline
+\end{tabular}
+\caption{Clustering data with WHERE. From~\cite{me12d}.}\label{fig:where}
+\end{figure}
+
+Having  limiting the displacement {\em distance} to no further that
+the nearest  cluster,
 there is still the issue of how to select the displacement 
 {\em direction}. 
-
-Let the training and test instances comprise pair of independent and objective values. For example:
+To determine that direction, we reflect on the objective
+scores of each cluster.
+For example:
 \bi 
@@
 \ei
-Let $X,Y$ be particular  training and test instance.
-Further, 
-let the training data be clustered and $X$
-comes from a cluster $C_i$ that is near the test instance $Y$
-and has objective scores better than those seen in $Y$.
-We call $X$  the {\em exemplar} of $C_i$ since it
+We say that each cluster can be represented by one
+{\em exemplar} that
 holds independent values that best characterize that cluster:
@@
 When designing HOW, our premises were:
-\bi
-\item
+
 This is no domain model; (b)~we have some
@@
 
+\begin{figure}
+\input{deltas1}
+\caption{Jureczko data sets, experiments with tuning.}\label{fig:jtune}
+\end{figure}
 For the  Jureczko   object-oriented data,
@@
 The remaining features remain unaltered.
-\begin{figure}[htbp!]
-\small
-\begin{tabular}{|p{.95\linewidth}|}\hline
-HERE begins by \textit{clustering} the training data into similar subsets using WHERE. WHERE works as follows:
-\begin{enumerate}
-\item Find the two most dist points in a given population; say {\em east} and {\em west}. 
-\item Draw an axis of length $c$ between the poles. 
-\item Let each point be at distance $a,b$ to the {\em east,west} poles.  Using the cosine rule, project each point onto the  axis  at $x=(a^2 + c^2 - b^2)/(2c)$.  
-\item Using the Median $x$ value, divide the population.
-\item For each half that is larger than $\sqrt{N}$ of the original population, go to step 1.
-\end{enumerate}
-
-There are couple of things to note: firstly, the above algorithm requires a distance measure between sets of decisions, for this WHERE uses case-based reasoning measure defined by Aha et al.~\cite{aha91}; secondly, in step-1 a linear time heuristic called FASTMAP~\cite{fastmap} is used to find the two most dist points, this procedure is listed below:
-\begin{itemize}
-\item Pick a point at random; 
-\item Let {\em east} be the point furthest from that point; 
-\item Then {\em west} be the point furthest from {\em east}.
-\end{itemize}
-
-The final clusters that are found by WHERE are then used by HERE as follows:
-\begin{itemize}
-\item For each cluster find its nearest neighbor.
-\item Construct a projective plane for each cluster pair. Label the cluster pairs as {\em Good} and {\em Bad}.
-\item For a test instance, project it onto the planes generated above and pick the one on which the test case has the largest projection.
-\item Mutate the attributes of the test case towards the {\em Good Cluster} in that projective plane. 
-\end{itemize}
-
-Formally, HERE can be considered as an instance based  learning scheme.
-And that's because it builds a set of recommendations based on a given test case based on the clusters for Median at the training stage.
-This is unlike a model based approach, which would have used a model to do the same~\cite{xomo}.
-\\\hline
-\end{tabular}
-\caption{Inside HERE}\label{fig:what}
-\end{figure}
 

### 2015-05-06 code.tex
Updates from ShareLaTeX

\begin{figure} 
\begin{python}[right]
def HERE(trainingData, testingData):
  training(trainingData)
  return [nearest(z).displace(z) 
          for z in testing]

def training(trainingData):
  Line.using = what2Use(trainingData)
  clusters = cluster(trainingData):
  for cluster in clusters:
    one = examplar(cluster)
    two = examplar(nearest(one, clusters))
    Line(one,two)

def what2Use(trainingData):
  second  = lambda lst: lst[1]
  weights = map(second,
                sorted(featureWeighting(trainingData)))
  use    = int(len(weights)*Line.B)
  return [i for i,_ in enumerate(weights[:use])]

def nearestLine(z):
  out,least=None,10000
  for line in Line.all:
    d = line.dist(z)
    if d < least: out,least = line,d
  return out
\end{python}
\caption{Instance-based Planning using HERE.
Testing data is {\em displaced}
towards   the $X$ point of the nearest {\tt Line} (defined in \fig{line})
The {\tt geometry} method comes from \fig{code1c}.
The {\tt featureWeighting} function comes from \fig{code1a}.
The {\tt cluster} function comes from \fig{fastmapCode}.
}\label{fig:HERE}   
\end{figure}

\begin{figure} 
\begin{python}[right]
class Line:
  "Lines connect a worse cluster Y to a better one X"
  all   = []
  using = []
  F     = 0.5
  B     = 0.5
   def __init__(i,x,y):
    if x.score < y.score:
      x,y = y,x
    i.c = dist(x,y) 
    i.obj = len(x) 
    Line.all += [i]
  def displace(i,z):
    for j,(xj,zj) in enumerate(zip(x,z)):
      if not j == i.obj and  j in Line.using:
         z[j] = zj + Line.F*( xj. - zj
    return z
  def dist(i,z):
    _,out = geometry(i.x,i.y,z)
    return out
  def exemplar(i,cluster):
    #Apply the rules at end of section II.B
\end{python}
\caption{The primary data structure of HOW
is the {\tt Line}.
Training data is converted into a set of {\tt Line}s,
each of which is defined by a $X,Y$ pair, where $X$
has better scores than $Y$. }\label{fig:line}
\end{figure}

\begin{figure} 
\begin{python}[left]
def dist(x,y):
   "See Aha et al. reference [22]. XXX"

def geometry(x, y, c, z): 
  a = dist(z,x)
  b = dist(z,y) 
  x= $(a^2 + c^2 - b^2)/(2ac)$ 
  y=  $\sqrt{a^2 - max(x,0)^2)}$
  return x,y

def nearest(x,data):
  return furthest(x,data,best=1000,better=lt)

def furthest(x,data, best= -1, better=gt):  
  out = None
  for one in data:
    d = dist(one,x)
    if gt(d,best): out, best = y, d
  return out
\end{python}
\caption{Some routines for 3 point geometry,  from \fig{where}.c.}\label{fig:code1c}
\end{figure}

\begin{figure}
\begin{python}[left]
def featureWeighting(cols):
   obj = len(cols[0])
   return sorted(weight1(col,i,obj) 
                for i,col in enumerate(cols)
                if not i == obj)

def weight1(i,obj,col):
  pairs = sorted([row[i],row[obj] for row in col])
  n     = length(col)
  return sum(v*n1/n for v,n1 in recurse(pairs,[])),i

def recurse(this,cuts):
  cut,sd = divide(this)
  if cut:
    recurse(this[:cut],cuts)
    recurse(this[cut:],cuts)
  else:
    cuts += [(sd,len(this)]
  return cuts

def divide(this,tiny=2):
  lhs, rhs = Stats(), Stats(x[1] for x in this)
  n, least, cut = rhs.n*1.0, rhs.sd(), None
  for j,x in enumerate(this):
     if lhs.n > tiny and rhs.n > tiny:
       tmp = lhs.n/n*lhs.sd() + rhs.n/n * rhs.sd()
       if tmp < least:
          cut,least = j,tmp
     rhs - x[1]
     lhs + x[1]
  return cut,least

class Stats():  
    def __init__(i,inits=[]):
      i.n = i.mu = i.m2 = 0.0
      map(i.__add__,inits)
    def sd(i) :  
      return (max(0.0,i.m2)/(i.n - 1))**0.5
    def __add__(i,x):
      i.n  += 1
      delta = x - i.mu
      i.mu += delta/(1.0*i.n)
      i.m2 += delta*(x - i.mu) 
    def __sub__(i,x):
      i.n  -= 1
      delta = x - i.mu
      i.mu -= delta/(1.0*i.n)
      i.m2 -= delta*(x - i.mu) 
\end{python}
\caption{Feature weighting, from \fig{where}.d.}\label{fig:code1a}
\end{figure}

\begin{figure} 
\begin{python}[left]
def cluster(data, n,lvl=100):
  if lvl < 1: 
     return data # stop if out of levels
  leafs = [] # Empty Set
  x,y,left,right = splitAcross2Points(data) 
  if len(left) > $\sqrt{n}$:  
     leafs += cluster(left, n, lvl - 1)  
  if len(right) > $\sqrt{n}$:  
     leafs += cluster(right,n,  lvl - 1) 
  data.has = dict(x=x,y=y,
                 l=left,r=right,
                 leafs=leafs)
  return leafs

def splitAcross2Points(data): 
  tmp = random.choose(data)
  x = furthest(tmp, data)
  y = furthest(x, data) 
  c = dist(x,y)  
  if x.scores < y.scores:
     x,y = y,x 
  for one in data.members: 
    one.pos = geometry(x,y,c,one)
  data = sorted(data) # sorted by 'pos.x'
  return x, y, split(data)

def split(data):   
  mid = len(data)/2; 
  return data[mid:], data[:mid]
\end{python}
\caption{Clustering. Lines 16,17,18 come from~\cite{fastmap}. }\label{fig:fastmapCode}   
\end{figure}

### 2015-05-06 culled.tex
Updates from ShareLaTeX

--- 2015-05-04 how.tex
@@
- \documentclass[conference]{IEEEtran}
-\usepackage{subfig}
-\usepackage{wrapfig}
- \usepackage{amsmath}
- \usepackage{url}
- \usepackage{pifont}
- \usepackage{times}
-\usepackage{rotating}
-%\usepackage{balance} 
-\usepackage{color, colortbl}
-\usepackage{graphicx}
-\usepackage{algorithmicx}
-
-\usepackage[running]{lineno}
-\usepackage{program}
-\usepackage{cite}
-\usepackage{alltt}
-\newcommand{\eq}[1]{Equation~\ref{eq:#1}}
-\newcommand{\bi}{\begin{itemize}}
-\newcommand{\ei}{\end{itemize}}
-\newcommand{\be}{\begin{enumerate}}
-\newcommand{\ee}{\end{enumerate}}
-\newcommand{\tion}[1]{\textsection\ref{sec:#1}}
-\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
-\definecolor{lightgray}{gray}{0.975}
-\usepackage{fancyvrb}
-\usepackage{stfloats}
-\usepackage{multirow}
-\usepackage{listings}
-\usepackage{amsmath} 
-\DeclareMathOperator*{\argmin}{arg\,min} 
-\DeclareMathOperator*{\argmax}{arg\,max}
-
-\definecolor{darkgreen}{rgb}{0,0.3,0}
-
-\usepackage[table]{xcolor}
-\definecolor{Gray}{rgb}{0.88,1,1}
-\definecolor{Gray}{gray}{0.85}
-\definecolor{Blue}{RGB}{0,29,193}
-\newcommand{\G}{\cellcolor{green}}
-\newcommand{\Y}{\cellcolor{yellow}}
-
-\definecolor{MyDarkBlue}{rgb}{0,0.08,0.45} 
-\newenvironment{changed}{\par\color{MyDarkBlue}}{\par}
-
-\newcommand{\ADD}[1]{\textcolor{MyDarkBlue}{{\bf #1}}}
-\newcommand{\addit}[1]{\begin{changed}\input{#1}\end{changed}}
-
-\usepackage{color}
-\usepackage{listings}
-\usepackage{setspace}
-
-\definecolor{Gray}{gray}{0.9}
-\newcommand{\kw}[1]{\textit{#1}}
-\newcommand{\quart}[4]{\begin{picture}(75,6)
-  {\color{black}\put(#3,3){\circle*{2.5}}\put(#1,3){\line(1,0){#2}}}\end{picture}}
-% New Commands
-
-\definecolor{Code}{rgb}{0,0,0}
-\definecolor{Decorators}{rgb}{0.5,0.5,0.5}
-\definecolor{Numbers}{rgb}{0.5,0,0}
-\definecolor{MatchingBrackets}{rgb}{0.25,0.5,0.5}
-\definecolor{Keywords}{rgb}{0,0,1}
-\definecolor{self}{rgb}{0,0,0}
-\definecolor{Strings}{rgb}{0,0.63,0}
-\definecolor{Comments}{rgb}{0,0.63,1}
-\definecolor{Backquotes}{rgb}{0,0,0}
-\definecolor{Classname}{rgb}{0,0,0}
-\definecolor{FunctionName}{rgb}{0,0,0}
-\definecolor{Operators}{rgb}{0,0,0}
-\definecolor{Background}{rgb}{1,1,1}
-
-\lstnewenvironment{python}[1][]{
-\lstset{
-mathescape,
-numbers=#1,
-numberstyle=\footnotesize,
-numbersep=0.5em,
-xleftmargin=0em,
-framextopmargin=2em,
-framexbottommargin=2em,
-showspaces=false,
-showtabs=false,
-showstringspaces=false,
-tabsize=2,
-% Basic
-basicstyle=\ttfamily\small\setstretch{0.8},
-backgroundcolor=\color{Background},
-language=Python,
-% Comments
-commentstyle=\color{Comments}\slshape,
-% Strings
-stringstyle=\color{Strings},
-morecomment=[s][\color{Strings}]{"""}{"""},
-morecomment=[s][\color{Strings}]{'''}{'''},
-% keywords
-morekeywords={[1]import,from,class,def,for,while,if,is,in,elif,else,not,and,or,print,break,continue,return,True,False,None,access,as,,del,except,exec,finally,global,import,lambda,pass,print,raise,try,assert, dot, norm, zip, sorted},
-keywordstyle={[1]\color{Code}\bfseries},
-% additional keywords
-morekeywords={[3]fastmap, project, furthest, split, WHERE,clusterer, getContours, envied, fWeight, nearestContour, projection, mutate, HERE, knn},
-keywordstyle={[3]\color{Keywords}\bfseries},
-morekeywords={[2]@invari},
-keywordstyle={[2]\color{Decorators}\slshape},
-emph={self},
-emphstyle={\color{self}\slshape},
-%
-}}{}
-
-\title{Learning Actionable Analytics 
- (with applications for reducing defects and reducing runtimes)}
-\author{
-% You can go ahead and credit any number of authors here,
-% e.g. one 'row of three' or two rows (consisting of one row of three
-% and a second row of one, two or three).
-%
-% The command \alignauthor (no curly braces needed) should
-% precede each author name, affiliation/snail-mail address and
-% e-mail address. Additionally, tag each line of
-% affiliation/address with \affaddr, and tag the
-% e-mail address with \email.
-%
-% 1st. author
-Rahul Krishna, Tim Menzies, Xipeng Shen\\
-       \affaddr{Computer Science, NcState, USA}\\
-       \{i.m.ralk, tim.menzies, xipengshen\}@gmail.com
-% 3rd. author
- % use '\and' if you need 'another row' of author names
-% 4th. author
-\and
- Andrian Marcus\\
-       \affaddr{Computer Science, UtDallas, USA}\\
-       {amarcus@utdallas.edu} }
-
-  \pagestyle{plain}
-\begin{document}
-  \maketitle
-
-  % make the title area
-
-  \begin{abstract}
- As business users demand more insightful
- analytics, data scientists need to change
- their tools. Instead of merely predicting 
- some result, they also need tools that generate ``policy advice'';
- i.e. suggestions on  how to change values in order to
- improve on some predicted value.
-
- This paper proposes one such policy
- generator. ``HOW'' is a near-linear-time
- tool for proposing changes to independent
- variables in order to improve on 
- the predictions of the dependent variables. Unlike other approaches
- for learning optimizations to software does not require
- an underlying of the domain (rather, HOW automatically
- learns that model as part of its operation).
-
- This paper uses  HOW to learn methods
- to reduce defects and decrease program runtime.
- For the test data of this paper, the improvements generated by HERE can reduce
- defect counts as well as runtimes by up to
- 50\% of their original values.
-  \end{abstract}
-  \begin{IEEEkeywords}
-Instance-based reasoning, defect prediction, random forest, optimization.
-  \end{IEEEkeywords}
-
-\section{Introduction}
-Business  users are now demanding that data mining tools
-be augmented with tools to support  business-level
-interpretation of that data. For example,
-at a  panel on software analytics at ICSE'12,
-industrial practitioners lamented the state of the art in data mining
-and software engineering~\cite{menzies12a}. Panelists commented that
-``prediction is all well and good, but what about decision
-making?''. That is, these panelists are more interested in the interpretations
-that follow the mining, rather than just  the mining. For example:
-\bi
-\item Instead of just accepting  {\em predictions} on how many 
- software defects
-to expect,  business users might now demand a {\em plan} to
-reduce the likelihood of those defects;
-\item Instead of just accepting {\em predictions} on the runtime
-time of their software, business users might now demand
-a {\em plan} to reduce that runtime.
-\ei
-In these two points, we say that a ``plan'' is a  set of proposed changes in order to better achieve some goal. 
-Generating {\em plans} is a  very different task the standard
-data mining tasks of {\em predicting} some discrete or numeric class.
-Predictors
-and classifiers only tell us what {\em is} while planners 
-  tell us {\em what to change}. For the kind of business user
-discussed above, planners are the preferred to mere prediction systems
-since, as one gruff user once shouted at us:
-\begin{quote}
-{\em ``Don't tell me what \underline{is};
-tell me what to \underline{change}.''}
-\end{quote}
-In order to satisfy the demands of this new kind of business user, we  study the generation of {\em plans} in the context
-of software analytics.  
-This paper presents
-HOW, a novel  {\em instance-based planner} that runs in near-linear time.
-In the experiments shown below, we see that HOW's plans can
-significantly reduce the expected
-value of:
-\bi
-\item The software defects found in  twelve object-oriented JAVA systems explored in 2010 by Jureczko et al.~\cite{jureczko10};
-\item The runtime of the six software systems whose configurations
-are explored in 2013 by Seigmund et al.~\cite{sven12};
-\ei
-In summary, this paper makes six contributions that are significantly different to
-prior work:
-\be
-\item Many software analytics papers use data to build {\em predictors} for (e.g.) defects and runtimes.
-However, aside from work by the authors of this paper,
-none of those papers then go further to use that data to build {\em planners}.
-\item This paper offers a general framework for augmenting a prediction system such that
-it becomes a planning system;
-\item This paper offers a  test that recognizes  when we should {\em not}  plan: in summary, our kind of planning is
-not recommended in domains that  generate poorly performing predictors;
-\item This paper offers a general verification rig for assessing the value of plans generated within this rig.
-\item The HOW  instance-based planner of this paper has not been presented before.
-\item The experiments of this paper show that HOW planner is useful for real-world tasks;
-e.g. reducing the
-expected values of the Jureczko software defects and the Seigmund software runtimes.
-\ee
-The rest of this paper is structured as follows.
-HOW's instance-based reasoning  makes its conclusions by
-studying the space of examples. As discussed in \tion{mm},
-this is a very different approach to
-{\em model-based planners} that use the model
-as sub-routine within a Monte Carlo simulation~\cite{me07f} or the evolutionary 
-programming methods explored by the search-based software
-engineering community~\cite{krall14,harman12dec}.
-
-\section{HOW: Motivation and Methods}\label{sec:mm}
-
- \subsection{Motivation: Why ``HOW''?}
-HOW was inspired by some recent work by Krall and Menzies and Davis on 
-the GALE optimizer~\cite{krall14}. A well-known effect in machine learning (and, in computer vision
-and compression~\cite{levina04}) is that the $n$ dimensions of a data set can be represented by a  much
-lower-dimensional approximation. GALE finds those $m << n$ dimensions then mutates examples
-towards the better end of each dimension $m_i$. Since it explores $m \ll n$ dimensions,
-GALE terminates much faster than standard optimiser (e.g. for one large model, 4 minutes versus 7 hours~\cite{krall14}).
-Better yet, GALE's rapdily generated  solutions are competitive (or better) than those found by 
-slower optimizers.
-
-A limitation with GALE is that it makes extensive use of
-an underlying domain model to asses generations of newly mutated instances.  This is an issue since
-in some domains, no such model exists or is readily accessible. For example, this whole paper
-began when, after briefing a business client on GALE, they asked:
-\begin{quote}
-{\em ``But what if I do not have a model of my business?''}
-\end{quote}
-This is a legitimate concern.
-Building and certifying a model  can  takes  long time, especially in software engineering. For  example, in previous work~\cite{me07f} we used models
-developed by Boehm's group at the University of Southern California.
-Some of those models took decades to develop and mature (from 1981~\cite{boehm81} to 2000~\cite{boehm00b}).
-This is not an isolated example.
-One of us (Menzies) teaches a graduate class in automated model-based software engineering.
-Students in that class are asked to find (or build) a non-trivial model of
-some software process (where ``non-trivial'' means something that processes
-a  model at least an order of magnitude more complex than Brooks' Law). 
-While the  number of such models has been growing in recent years\footnote{See the
-catalogue at goo.gl/nv2AVK.}, 
-the total number remains very small-- which is an observation consistent with
-SE models typically require  much effort to build and certify.
-
-Also, even when there is an existing model, instance-based reasoning can be useful.
-Models need maintenance lest they become out-dated. Elsewhere, we have described our
-extensions to the USC models to enable reasoning about agile software developments. 
-It took many months to implement and certify those extensions~\cite{me09i,me09j}.
-The problem of model maintenance is another
-motivation to look for alternate methods that can be automateically updated whenever new data arrives.
-
-Finally, sometimes  it is easier to access instances of a model's behaviour than the model
-itself. For example, in prior work with Martin  Feather from the Jet Propulsion 
-Laboratory~\cite{fea02a},  our research partner could not share a
-propriety model from within the NASA firewalls. However, they could share 
-logs of the input/output of that model.
-
-Note that this lack of access to a workable model is not just fatal for GALE, but also for every
-other model-based optimization algorithm such as simulated
-annealling or evolutuionary methods such as   
-NSGA-II, NSGA-III, SPEA2, IBEA, PSO, DE, MOEA/D, etc.~\cite{deb00a,zit02,zit04,%
-deb14,Cui2005a,storn97,zhang07:TEC}. Accordingly, this paper seeks
-an optimization methods that avoids the problem of models that are missing, slow
-to build, hard to maintain, or difficult to access.
-
-\subsection{Methods: How to Build ``HOW''?}
-HOW is a variant of GALE that does not need a underlying domain model.
-
-When designing HOW, our premises were:
-\bi
-\item
-This is no domain model; (b)~we have some
-labelled data and (b)~we seek minimal
-disrupttion
-HOW divide training into regions where the training
-data has similar properties. Each region is then examined and divided into ``west'' and ``east''
-where the region's ``west'' end has examples with worst performance stores than the east
-end (mnemoc: west starts with ``w'' and is short for ``worst' and east starts with ``e;;]which is shirt
-for excellent).so the ``e'' in
-
-\be
-\item Take  a population $P$ of examples
-\item Separate all $p \in P$ examples into their $n$ independent variables and 
-their $o$ scores;
-\item Find $m \ll n$ lower dimensional approximations for the $n$ independent variables;
-\item Look for the worst and best ends of each $m$  dimension (where the better ends
-have better objective scores);
-\item Find the $q \subseteq P$ subset of the population with ``better'' objective scores;
-\item Generate the next population $P'$ by adjust the independent variables
-of the $q$  examples
-by a random amount (in the direction of  the  better ends of each dimension).
-\item Apply some model to discover all the objective scores of $P'$
-\item Set $P=P'$ and go to step 1
-\ee
-
-PCA explores the $e$
-eigenvectors of the correlation matrix between $d$
-variables~\cite{pearson1901}.  Usually,
-only a few $e \ll d$ eigenvectors are required
-since multiple inter-related variables $i,j,k \subseteq d$ can be represented
-by a single  eigenvector.
-Also, noisy variables from $d$ are
-ignored since they  do not contribute to the signal in the data.
-Further,
-redundant  variables  become (approximately) parallel lines
-in $e$ space. For all such redundancies \mbox{$i,j \in d$}, we
-can ignore $j$
-since effects that change over $j$ also
-change in the same way over $i$.
-
-Algorithms like PDDP~\cite{boley98} use PCA to
-recursively divide data into smaller regions. Each
-step of that process requires an $O(N^2)$ analysis
-of the data to compute the components~\cite{ilin10}. Worse, it requires an evaluation of every example.
-Using WHERE, competitive results can be achieved
-using an $O(2N)$ analysis.
-WHERE uses a heuristic proposed by
-Faloutsos and Lin~\cite{Faloutsos1995}
-(which
-Platt has
-  shown computes a Nystr\"om
-  approximation to the first component of
-  PCA~\cite{platt05}).
-In step one, WHERE inputs
-$N$
-examples $N_1,N_2,..$. Secondly, WHERE
-picks any
-point $N_i$ at random. Thirdly, WHERE
-finds the point  {\em West}~$\in N$ that is
-furthest\footnote{
- For this work, we use the standard Euclidean measure recommended for
-instance-based reasoning by Aha et al.~\cite{aha91};
-i.e. $\sqrt{\sum_i(x_i-y_i)^2}$ where $x_i,y_i$
-are values normalized 0..1 for the range min..max.}
-from $N_i$.
-Finally, WHERE
-
-$m \ll n$
-dimension
-
-\be
-\item Clustering the training data 
-\item 
-(c) finding which end of the cluster has better performance scores.
-(d) find
-\ee
-
-\section{Methodological Comments:\\ from ``Prediction'' to ``Planning''}
-A major  problem with building a planning mechanism in software engineering is ``how to verify the generated
-plans?''. For example,  in the experiments shown below,  HOW comments  on how to reduce
-software defects by adjusting certain static code parameters of the code\footnote{Such parameters can be mnaually adjusted by programmers or (for large scale changes) automatically adjusted using code refactoring
-tools, as shown by Binkely et al. in 2006~\cite{Binkley2006} and more recently by Mkaouer et al. in 2015~\cite{Mkaouer15}.}. How are we to verify that HOW's recommendations actually work?
-
-Some organizations have the resources to 
-run repeated trials to assess the effect of different treatments.
-For example, in one remarkable recent study, Bente et al. report results
-were the same specification was developed into a product by four different organizations~\cite{Anda2009}. Given those kind of resources, it would be possible
-to (say) take a code base, assign it to $N$ different teams, apply
-HOW's plans the code used by  $N/2$ teams, then check in 12 months time
-if those halves of the teams have fewer defects than the other.
-
-Very few industrial or research groups have access
-to the kinds of resources using by Bente et al. (evidence: in the size years since the
-publication of that work, we know of only one of two similar studies). Hence, it
-we wish to verify HOW's plans, then some other approach is required that is less
-resource intensive.
-
-\subsection{Proposed Framework}
-
-We propose using prediction systems (built by data mining) as a verification
-tool for planners. In domains with data, from which data miners can build
-predictors of adequate performance, then those predictors can assess the value
-of the changes proposed by HOW.
-As shown in \fig{work}, 
-project data is divided into two disjoint sets {\em train} and {\em test}
-(so \mbox{{\em train} $\cup$ {\em test} $=\;\emptyset$}).
-Next, from the train set, we build both a {\em planner} as well
-as a {\em predictor}. Our general framework does not   commit to any particular  choice
-of {\em planner} or {\em predictor}. For the purposes of this discussion 
-our {\em planner}
-will be HOW (discussed below)and our
-our {\em predictors} will be the Random Forest and Random Forest
-Regressor\footnote{Decision tree learners find the attribute whose value's
-select for for sections of the data with least variation in the class
-variable. Decision tree learners then recurse on each selection~\cite{breiman84}. A random forest is a set of decision trees, each built
-from some random subset of the rows and columns. The conclusions
-of the forest are a ``vote'' generated by all the trees~\cite{Breiman2001}. 
-A standard Random Forest predicts for a discrete class variable while
-a Random Forest Regressor generates numeric predictions.} taken from the SciKit
-Learn toolkit~\cite{Pedregosa2012}.
-
-Turning now to the {\em test} data, this is passed to the {\em predictor}
-to generate a baseline {\em before} performance score.
-Note that if our {\em predictors} fail to perform adequately on the test data,
-then we cannot trust them to comment on our plans. Accordingly,
-if that performance is unsatisfactory, we abort.
-Else, we (1)~apply the {\em planner} to alter the {\em test} data;
-then (2)~apply the {\em predictor} to the altered data {\em test'};
-then (3)~return the performance delta.
-
-\begin{figure}[!t]
-\small 
-\[
-\begin{array}{r}
-\mathrm{project}\\
-\mathrm{data}
-\end{array} 
-\left\{\begin{array}{l}\mathit{train}
-        \left\{\begin{array}{l}
-                \mathrm{learn\;a\;}\mathrm{predictor\;}\mathrm{(e.g.\;via \;Random\;Forest)}\\
-                \mathrm{learn\;a\;}\mathrm{planner\;}\mathrm{(e.g.\;via \; HOW)}
-              \end{array}\right.
-       \\
-      ~\\
-\mathit{test}  
-    \left\{\begin{array}{l@{~}l}
-           \mathit{before}& =\mathrm{predictor}(\mathit{test})\\
-           \mathrm{\bf if\;}\mathit{before} & <  \mathit{satisfactory}\\
-           \mathrm{\bf then}  & \mathrm{{\bf return}\; 0}\\~\\
-           \mathrm{\bf else} &
-           \left\{
-            \begin{array}{l}
-                \mathit{test'} = \mathrm{planner}(\mathit{test})\\
-                \mathit{after} =\mathrm{predictor}(\mathit{test'})\\ 
-                \mathrm{{\bf return}\;} \mathit{after} /  \mathit{before}
-            \end{array}
-          \right.
-   \end{array}\right.
-\end{array} \right. 
-\]
-
-\caption{How to use {\em predictors} for {\em planning}.}\label{fig:work}
-\end{figure}
-
-\subsection{Are These Plans ``Causal''?}
-With one additional stipulation,   this framework can be used to check if the learned
-plans can be said to {\em cause} a change in the domain being explored.
-
-In the literature, there are two main definitions of causality: Hill's H-causality~\cite{Hill1965}
-and Granger's G-casualty~\cite{granger80}. 
-Of the two, Hill's definition is the most strict. An effect
-is H-causal if it satisfies nine criteria including
-{\em  plausibility};
-{\em strength} of the effect;
-{\em 
-specificity}, i.e. locality of the effect
-to specialized groups;
-{\em
-support} by experimental evidence;
-{\em 
-coherence} between cause-effects noted
-in the field and in laboratory samples;
-{\em
-temporally} i.e. the effect has to follow the cause;
-{\em 
-analogy}, i.e.  similar causes have similar effects;
-{\em
-biological gradient}, i.e.  more exposure to the cause leads to more of an
-effect; and
-{\em
-consistency}, i.e.  the same cause-effect pairings have been seen by different persons
-in different places.
-
-It is hard to demonstrate H-causality in software engineering.
-For example, Hill's criteria emphasises repeatability and laboratory studies-- both of which are
-hard to perform in software engineering (e.g. see the continued debate about
-the value of using undergraduate students to surrogates for industrial
-practitioners in software engineering research~\cite{Carver2003}). Also, Hill's requirement
-for consistency is far easier to achieve in studies of small closed systems (e.g. bacteria in a petri dish)
-than in large socio-technical systems (e.g. open source projects). In the latter,
-effects are more {\em probabilistic} than {\em categorical}-- by which we mean that 
-some cause tends to cause some effect at some probability $p$ less that one.
-This in turn means that at some probability $q$ (where $0 \le q < p \le 1$)
-that we will find examples of {\em inconsistency} where some cause does {\em not} lead
-to some effect (thus violating one of Hill's criteria for demonstrating causality).
-
-The  difficulties associated with Hill's criteria lead Granger~\cite{granger80}
-to propose another more practical criteria\footnote{Granger  himself comments that
-his proposal was based on earlier work by Norbert Weiner~\cite{Seth2007}.}.
-\mbox{G-causality} is based on building predictions based on {\em past} data,
-then showing that this works for {\em future} data~\cite{granger80}. 
 In should be noted  that the standard 10-way cross-validation
@@
 
-We adapt the work of Jiang,Lumpe et al.  as follows. In  \fig{work}, we demand that the {\em test}
-data is not necessarily collected before the {\em train} data:
-\bi
-\item[\#1:] For data collected from software released in multiple versions, we should hence use  versions  $i,j$ to build models that are applied to version  $k$ where $i<j<k$.
-\item[\#2:] For data collected from Monte Carlo simulations (where inputs are selected at random)
-then as long as simulation $i$ is not used to adjust simulation $j> i$, then any item in that
-data could be generated before any other. For this kind of data, we  can use the first $X\%$
-of the simulation for training, and the remaining data for testing.
-\ee
-In the two case studies of this paper, the Jureczko object-oriented defect data comes from software
-released in multiple versions while the Seigmund configuration data comes from Monte Carlo simulations.
-Hence, we use procedure \#1 for the defect data and procedure \#2 for the configuration data.
-
-With these changes,
-we can reasonably claim that the plan's generating by HOW are G-causal.
-
-\subsection{When Not to Plan: the Problem of Poor Predictors}
-
-The clear advantage of the approach of \fig{work} is that it can be readily and automatically
-applied to domains with historical data. That said, the obvious drawback with this approach
-is that our assessment of the plans is only as good as the predictor. To 
-mitigate for this {\em problem of poor predictors}, it is hence wise to demand high standards for the {\em
-satisfactory} threshold used in this \fig{work}.
-
-How prevalent is the problem of poor planners? 
-In the general case, this is hard to answer. However, as discussed in this section, for the 17 data
-sets explored in this study, only 
-%XXX 
-3 suffer from this problem.
-
-This study's data from two types of domains: the Jureczko   object-oriented data  
-and the Seigmund configuration data. 
-For the Seigmund data, the plans generated by HOW advise on how  to change the   configurations settings within a Makefile
-(in order to make resulting compiled
-code  run faster). Here, performance can be measured in terms of  difference
-between the predicted runtime $p$ of test case items and their actual runtimes $a$
-using  $s= 100*(1- \frac{abs(a - p)}{a})$.
-Using engineering judgement, we define satisfactory $s$ as anything over   70\%. 
-This paper  explores    six Seigmund configuration data sets:  Berkeley DB (Java and Windows versions), Apache, SQLite, LLVM, and
-  x264\footnote{Available from the performance prediction section of PROMISE
-  http://openscience.us/repo/performance-predict.}. 
-  After splitting that data into equal sized train:test groups, a Random Forest
-  Regressor trained on one half, then applied to the other, achieved nearly perfect scores of
-%issue 24
-\[s=\{99.9, 99.8, 99.4, 99.1, 96,1\}\]
-(Aside: if the reader doubts that such high scores are achievable, we note that these scores are 
-consistent with those achieved by predictors built by Seigmund et al.~\cite{sven12}.)
-
-For the  Jureczko   object-oriented data,
-the plans generated by HOW advise   how to change static code attributes in order to reduce defects in
-Java classes.  Here,
-performance can be measured in terms of recall (percent of faulty classes in
-the test data detected
-by the {\em predictor}). Using engineering judgement, we define satisfactory recall as anything over   70\%. 
-This paper explores 12 of the Jureczko   object-oriented static code data sets: Ant, Camel, Ivy, Jedit, JBeans, Log4, Lucene, Poi, Synapse, Velocity, Xalan, Xerces\footnote{Available from the object-oriented defects section of the PROMISE respository openscience.us/repo/defect/ck.}.
-For each of these data sets, we generated  {\em before} scores  by finding the latest
-version $k$, then training  a predictor on versions $k-2$ and $k-1$. As reported below,
-our initial recall scores from this data were unpromising (very low recall values). However,
-after applying certain data pre-processing steps (described below), a Random Forest generated
-on the $k-2,k-1$ versions achieved recalls on version $k$ of
-%issue24
-\[\mathrm{recall}=\{98,88,86,84,82,81,79,78,78,\overbrace{55,23,20}^{\mathrm{JBeans,Poi,Xalan}}\}\]
-From the above, we conclude that all the Seigmund configuration data and most of the Jureczko data
-avoids the problem of poor predictors. Hence, we can use that data for the planning
-experiments described below.
-
-\section{Experimental Methods}
-
-blah blah data. algorithms. statistics
-
-\section{Releated Work}
-
-Our prior work in generating policies relied upon a Monte Carlo
-analysis of an underlying model~\cite{me07f}. This approach had three major problems.
-Firstly, enough domain knowledge had to be collected to build that model
-and this can take a long time. For example, in our previous work we used three software process models from
-the Unviersity of Southern California that were initially
-developed and updated for nearly two decades from 1981~\cite{boehm81} to 2000~\cite{boehm00b}.
-
-Secondly, there is the computational cost of running those models.
-While
-
-~\cite{}-- which suffered from the problem of (a)~the effort required to collect the domain knowledge to build
-problem in certifying the underlying model;
- (b)~the computational problem of running that model enough
-times to learn patterns in that data; and (c)~ requrearea used large scale simulations or large
-
-While
-our case studies are defect and runtime reduction, HERE is a general
-purpose algorithm that could be applied to any table of data with at least
-one column whose values can be sorted from ``desired'' to ``undesired''.
-
-{\bf RQ1: Can Instance-based Learning techniques be used to create Planning tools that can better analyse software defect?}
-
-{\bf RQ2: Can lessons learnt from local policy generators be useful for generating solutions that can be used to mitigate defects in software systems?}
-
-{\bf RQ3: Can such instance-based planners be applied to other software engineering paradigms?}
-We check if the proposed instance-based planner is applicable to performance prediction.
-
-\section{Motivating Example}
-\section{Background}
-\section{Instance Based Learning}
-
-Assessing the quality of solutions to a real-world problem can be extremely hard~\cite{menzies2005xomo}.
-In several software engineering applications, researchers have models that can emulate the problem, for instance there is the COCOMO effort model~\cite[p29-57]{boehm2009software}, the COQUALMO defect model~\cite[p254-268]{boehm2009software}, Madachy’s schedule risk model~\cite[p284-291]{boehm2009software}, to name a few.
-Using these models it is possible to examine several scenarios in a short period of time, and this can be done in a reproducible manner.
-However, models aren't always the solution, as we shall see.
-
-There exist several problems where models are hard to obtain, or the input and output are related by complex connections that simply cannot be modeled in a reliable manner, or generation of reliable models take prohibitively long ~\cite{Ludewig2003}.
-Software defect prediction is an excellent example of such a case.
-Models that incorporate all the intricate issues that may lead defects in a product is extremely hard to come by.
-Moreover, it has been shown that models for different regions within the same data can have very different properties \cite{localvsglobal}.
-This makes it extremely hard for one to design planning systems that are capable of mitigating these defects.
-
-An alternative approach would be to make use of an instance based approach, an example of case based reasoning strategy, in place of the conventional model based approach.
-Instance based approaches have been used extensively by the effort estimation community, see~\cite{keung2008analogy, 6600685, walkerden1999empirical, shepperd1997estimating, kocaguneli2010use}.
-
-This approach has been proposed as an alternative to closed form mathematical models or other modeling methods such as regression \cite{keung2008analogy}.
-There are several other reasons for instance based approaches being a useful tool, see~\cite{6600685}.
-As pointed out by~\cite{walkerden1999empirical} it can be used with partial knowledge of the target project at an early stage which could be a very useful tool in preventing software defects.
-Instance based approaches are also rather robust in handling cases with sparse samples \cite{1438374}.
-All these features are desirable and suggest that instance-based approach is a useful adjunct to traditional model based approach.
-
-In this paper the instance based learning principle is used to first cluster the training data and then create contours in the data.
-These contours can then be used by test cases to infer meaningful information in order to improve it.
-The entire process is described in greater detail in the following sections.
-We would like to stress that the purpose of our work is not to promote instance-based planning over model based analytics, rather it is to suggest an alternative when model based approaches cannot be used.
-
-\subsection{Spectral Learning using WHERE}
-The algorithm uses WHERE to recursively cluster the input data to identify subsets in the training data that a test instance can learn from.
-WHERE is a spectral learner which uses the FastMap heuristic to estimate the first principal component.
-It then recursively partitions the data into two halves along the Median point of the projection on the first principal component, terminating when a half has less than $\sqrt{N}$ items.
-
-\subsection{Planning changes using HERE}
-We propose the HERE algorithm as a tool to plan changes in the original test data.
-Figure~\ref{fig:what} highlights the procedure by which HERE operates.
-It begins by creating clusters which are generated using the WHERE algorithm discussed above.
-Following this, a nearest neighbour scheme is applied to identify pairs of nearby clusters.
-A contour is constructed with these clusters at the vertices to characterize the cluster pairs.
-
-The mutation policy works by projecting the test instance onto the contours and identifying the the contour on which the test instance has the largest scalar projection.
-The planner then reflects over the vertices of the chosen contour, identifying the \textit{better} vertex among the two.
-Now, a new instance is generated by \textit{mutating the attributes} of the test instance towards the better vertex and away from the worse vertex.
-This process is repeated for all the test instances that are considered defective by the defect prediction scheme, discussed below.
-
-\subsection{Feature Weighting} \label{fwt}
-The algorithm also allows for a feature weighting and pruning scheme.
-We have employed a simple (and fast) attribute ranking method where the features are sorted based on their ability to find meaningful splits in the dependent class of the data, see ~\cite{hall03}.
-Features that can find splits with the \textit{lesser variance} in the dependent variable are \textit{ranked higher} than features that don't.
-
-We reason that the most informative feature must undergo a larger change as compared to other features.
-Therefore, when feature weighting is employed, the higher ranked features are mutated by a larger extent.
-Additionally, we have also included information pruning.
-Here we mutate only the top X\% of the features in each test instance.
-The remaining features remain unaltered.
-\begin{figure}[htbp!]
-\small
-\begin{tabular}{|p{.95\linewidth}|}\hline
-HERE begins by \textit{clustering} the training data into similar subsets using WHERE. WHERE works as follows:
-\begin{enumerate}
-\item Find the two most dist points in a given population; say {\em east} and {\em west}. 
-\item Draw an axis of length $c$ between the poles. 
-\item Let each point be at distance $a,b$ to the {\em east,west} poles.  Using the cosine rule, project each point onto the  axis  at $x=(a^2 + c^2 - b^2)/(2c)$.  
-\item Using the Median $x$ value, divide the population.
-\item For each half that is larger than $\sqrt{N}$ of the original population, go to step 1.
-\end{enumerate}
-
-There are couple of things to note: firstly, the above algorithm requires a distance measure between sets of decisions, for this WHERE uses case-based reasoning measure defined by Aha et al.~\cite{aha91}; secondly, in step-1 a linear time heuristic called FASTMAP~\cite{fastmap} is used to find the two most dist points, this procedure is listed below:
-\begin{itemize}
-\item Pick a point at random; 
-\item Let {\em east} be the point furthest from that point; 
-\item Then {\em west} be the point furthest from {\em east}.
-\end{itemize}
-
-The final clusters that are found by WHERE are then used by HERE as follows:
-\begin{itemize}
-\item For each cluster find its nearest neighbor.
-\item Construct a projective plane for each cluster pair. Label the cluster pairs as {\em Good} and {\em Bad}.
-\item For a test instance, project it onto the planes generated above and pick the one on which the test case has the largest projection.
-\item Mutate the attributes of the test case towards the {\em Good Cluster} in that projective plane. 
-\end{itemize}
-
-Formally, HERE can be considered as an instance based  learning scheme.
-And that's because it builds a set of recommendations based on a given test case based on the clusters for Median at the training stage.
-This is unlike a model based approach, which would have used a model to do the same~\cite{xomo}.
-\\\hline
-\end{tabular}
-\caption{Inside HERE}\label{fig:what}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{_figs/WHAT-Clusters2.pdf}
-\caption{HERE}
-\label{fig:whatflow}
-\end{figure}
-
-\begin{figure}[!b]
-\begin{python}[left]
-def fastmap(data): 
-  """Project data on a line 
-     between 2 dist points
-  """
-  z          = random.choose(data)
-  east       = furthest(z, data)
-  west       = furthest(east, data)
-  data.poles = (west,east)
-  c          = dist(west,east)     
-  for one in data.members: 
-    one.pos = project(west,east,c,one)
-  data = sorted(data) # sorted by 'pos'
-  return split(data)
-
-def project(west, east, AC, x): 
-  "Project x onto line east to west"
-  AB = dist(x,west)
-  BC = dist(x,east)
-  #cosine rule
-  return (AB$^2$ + AC$^2$ - AB$^2$)/(2*AC)
-
-def furthest(x,data): 
-  # what is furthest from x?
-  out, max = x,0
-  for y in data:
-    d = dist(x,y)
-    if d > max: out, max = y, d
-  return out
-
-def split(data): # Split at median
-   mid = len(data)/2; 
-  return data[mid:], data[:mid]
-
-def WHERE(data, scores={}, 
-          lvl=10000, prune=True):  
-  "Recursively split data."
-  if lvl < 1: 
-     return data # stop if out of levels
-  leafs      = [] # Empty Set
-  left,right = fastmap(data)
-  west, east = data.poles
-  $\omega=\sqrt{\mu}$ # enough data for recursion
-  goWest = len(left) > $\omega$  
-  goEast = len(right) > $\omega$ 
-  if prune: 
-    if goEast and better(west,east,scores): 
-       goEast = False 
-    if goWest and better(east,west,scores): 
-       goWest = False 
-  if goWest:  
-     leafs += where(left,  lvl - 1, prune)  
-  if goEast:  
-     leafs += where(right, lvl - 1, prune) 
-  return leafs
-
-\end{python}
-\caption{Clustering with WHERE}
-\label{fig:fastmapCode}   
-\end{figure}
-
-\begin{figure}[!t]
-\begin{python}[right]
-def envied(leaves):
-  """
-  Returns a single exemplary row from 
-  a cluster.
-  """
-
-def fWeight(train, prune = 0):
-  """
-  Find the feature weights & prune features
-  """
-
-def getContours(train):
-  """
-  Identify the pairs of clusters
-  that can form a contour
-  """
-  contours = []
-  # Clustering with where
-  clusters = WHERE(train) 
-  near = lambda x: knn(x, clusters)[1]
-  for c in clusters:
-    one = envied(c)
-    two = envied(near(one, clusters))
-    contours += [(one, two)]
-  return contours
-
-def project(a, b, test):
-  if score(a) > score(b):
-    good, bad = a,b 
-  else:
-    good, bad = b,a
-  AB = dist(bad,test)
-  BC = dist(good,test)
-  AC = dist(good,bad)
-  # Cosine rule
-  x = (AB$^2$ + AC$^2$ - BC$^2$)/(2*AC)
-  return $\sqrt{AB^2 - x^2}$
-
-def mutate(me, others, weights = None):
-  "Mutate 'me' towards 'others'"
-  if weights:
-    return [my + ext * f * (good - my) for 
-    f, my, good in zip(wights, me, others)]
-  else:
-    return [my + ext * (good - my) 
-    	 for my, good in zip(me, others)]
-
-def nearestContour(contours, instance):
-  "Find the nearest contour to an instance"
-  return sorted(
-        contours,
-        key=lambda F: project(
-        F[0], F[1], instance), 
-        reverse=True)[0]
-
-def HERE():
-  contours = getContours()
-  weights = fWeight(train)
-  for rows in defectiveRows:
-    vtx = nearestContour(contours, rows)
-    [good, bad] = sorted(vtx
-            , key=lambda F: score(F))
-    new += mutate(rows, good, weights)
-  return new
-\end{python}
-\caption{Instance-based Planning using HERE}
-\label{fig:HERE}   
-\end{figure}
-
-\subsection{Defect Prediction}
-
-To validate the treatments that have been suggested by our planner, we need to have defect predictors that capable of identifying if a certain module may (or may not) have a defect.
-A recent IEEE TSE paper by Lessmann et al.~\cite{lessmann} compared 21 different learners for software defect prediction:
-\bi
-\item
-{\em Statistical classifiers:}
-Linear    discrimin analysis,
-Quadratic discrimin analysis,
-Logistic regression,
-Naive Bayes,
-Bayesian networks,
-Least-angle regression,
-Relevance vector machine,
-
-\item
-{\em Nearest neighbor methods:}
-k-nearest neighbor,
-K-Star
-
-\item
-{\em Neural networks:}
-Multi-Layer Perceptron,
-Radial bias functions,
-
-\item
-{\em Support vector machine-based classifiers:}
-Support vector machine,
-Lagrangian SVM
-Least squares SVM,
-Linear programming,
-Voted perceptron,
-
-\item
-{\em Decision-tree approaches:}
-C4.5,
-CART,
-Alternating DTs
-\item
-{\em Ensemble methods:}
-\textbf{Random Forest},
-Logistic Model Tree.
-\ei
-
-They concluded that Random Forrest was the best method, CART being the worst.
-
-Random Forest is an ensemble learning scheme that constructs a number of decision trees at the training time, for a test instance it outputs the mode of the classes of individual tree.
-It's patent from how random forest operates that the prediction will suffer if there is an imbalance in classes during the training.
-Unfortunately, the data sets explored here do suffer from severe skewness, as highlighted in~\ref{fig:classimb}.
-A study conducted by Pelayo and Dick~\cite{smote2} inspected this issue.
-They showed that the SMOTE technique~\cite{smote} can be used to improve recognition of defect-prone modules.
-
-In short, SMOTE works by under-sampling the majority class and oversampling all the minority classes in the training data.
-We use a similar approach with one minor addition to the original algorithm.
-In our implementation of SMOTE we have introduced an additional step called \textit{resampling}, wherein we ensure that after we do the over/under sampling, the new training data does not have any of the original rows.
-The new training data merely resembles the original data.
-This is done as a precautionary measure, so as not to have HERE and Random Forest train on the same training data.
-%Its worth noting that both HERE and Random Forest require some data to train.
-In order to prevent the two from using the same data to train, we run SMOTE by  \textit{resampling} the classes.
-Re-sampling
-
-\begin{figure*}[htbp!]
-  \renewcommand{\baselinestretch}{0.8}\begin{center}
-    {\scriptsize
-      \begin{tabular}{c|l|p{4.7in}}
-        amc & average method complexity & e.g. number of JAVA byte codes\\\hline
-        avg\, cc & average McCabe & average McCabe's cyclomatic complexity seen
-        in class\\\hline
-        ca & afferent couplings & how many other classes use the specific
-        class. \\\hline
-class. \\\hline
-        cam & cohesion amongst classes & summation of number of different
-        types of method parameters in every method divided by a multiplication
-        of number of different method parameter types in whole class and
-        number of methods. \\\hline
-        cbm &coupling between methods &  total number of new/redefined methods
-        to which all the inherited methods are coupled\\\hline
-        cbo & coupling between objects & increased when the methods of one
-        class access services of another.\\\hline
-        ce & efferent couplings & how many other classes is used by the
-        specific class. \\\hline
-        dam & data access & ratio of the number of private (protected)
-        attributes to the total number of attributes\\\hline
-        dit & depth of inheritance tree &\\\hline
-        ic & inheritance coupling &  number of parent classes to which a given
-        class is coupled (includes counts of methods and variables inherited)
-        \\\hline
-        lcom & lack of cohesion in methods &number of pairs of methods that do
-        not share a reference to an instance variable.\\\hline
-        locm3 & another lack of cohesion measure & if $m,a$ are  the number of
-        $methods,attributes$
-        in a class number and $\mu(a)$  is the number of methods accessing an
-        attribute, 
-        then
-        $lcom3=((\frac{1}{a} \sum, j^a \mu(a, j)) - m)/ (1-m)$.
-        \\\hline
-        loc & lines of code &\\\hline
-        max\, cc & maximum McCabe & maximum McCabe's cyclomatic complexity seen
-        in class\\\hline
-        mfa & functional abstraction & number of methods inherited by a class
-        plus number of methods accessible by member methods of the
-        class\\\hline
-        moa &  aggregation &  count of the number of data declarations (class
-        fields) whose types are user defined classes\\\hline
-        noc &  number of children &\\\hline
-        npm & number of public methods & \\\hline
-        rfc & response for a class &number of  methods invoked in response to
-        a message to the object.\\\hline
-        wmc & weighted methods per class &\\\hline
-        \rowcolor{lightgray}
-        defect & defect & Boolean: where defects found in post-release bug-tracking systems.
-      \end{tabular}
-    }
-  \end{center}
-  \caption{OO measures used in our defect data sets.  Last line is
-    the dependent attribute (whether a defect is reported to  a
-    post-release bug-tracking system).}\label{fig:ck}
-\end{figure*}
-
-\begin{figure}[!tb]
-  \renewcommand{\baselinestretch}{0.8}\begin{center}
-{\scriptsize
-\begin{tabular}{l@{~~~}l@{~~~}l@{~~~}l@{~~~}l@{~~~}l@{~~~}l@{~~}}
-  \hline
-  \rowcolor{lightgray}
-  Data & Symbol & Training & Testing & Training Samples& Defective &\% Defective \\\hline
-
-Ant & ant & 1.5, 1.6  &1.7 & 644&124&19.25\\
-
-Camel & cam & 1.2, 1.4 & 1.6 & 1480&361 & 24.39\\
-
-Ivy & ivy & 1.1, 1.4 & 2.0  & 352 & 79 & 22.44\\
-
-Jedit & jed & 4.1, 4.2 & 4.3 & 679 & 127 & 18.70\\
-
-Log4j & log & 1.0, 1.1 & 1.2 & 244 & 71 & 29.09\\
-
-Lucene & luc & 2.0, 2.2 & 2.4 & 442 & 235 & 53.16\\
-
-Poi & poi & 2.0, 2.5 & 3.0 & 699 & 285 & 40.77\\
-
-Synapse & syn & 1.0, 1.1 & 1.2 & 379 & 76 & 20.05\\
-
-Velocity & vel & 1.4, 1.5 & 1.6 & 410& 289 & 70.48\\
-
-Xalan & xal &2.5, 2.6 &2.7 & 1688 & 798 & 47.27\\\hline
-\end{tabular}}
-\end{center}
-\caption{Attributes of the defect datasets}\label{fig:ck}
-\end{figure}
-
-\begin{figure}[!hbp]
-  \renewcommand{\baselinestretch}{1}\begin{center}
-{\scriptsize
-\begin{tabular}{llllll}
-  \hline
-  \rowcolor{lightgray}
-Project & Domain & Lang. & LOC & Features & Config\\\hline
-
-Berkeley DB CE & Database & C & 219,811 & 18 & 2560\\
-
-Berkeley DB JE & Database & Java & 42,596 & 32  & 400\\
-
-Apache & Web Server & C & 230,277 & 9 & 192\\
-
-SQLite & Database & C & 312,625 & 39 & 3,932,160\textsuperscript{*}\\
-
-LLVM & Compiler & C++ & 47,549 & 11 & 1024\\
-
-x264 & Video Enc. & C& 45,743 & 16 & 1152\\\hline
-\end{tabular}}\par\medskip
-
-{ \footnotesize $^*$ Dataset contains 4, 553 configurations for prediction modeling and 100 additional random configurations for prediction evaluation, see \cite{vapp}.}
-\end{center}
-
-\caption{Attributes of the Performance Prediction data sets}\label{fig:cpm}
-\end{figure}
-
-\begin{figure}[tbp!]
-% \subfloat[\label{oracle}]{\includegraphics[width=\linewidth]{{_figs//Oracle}}\\
-\includegraphics[width=\linewidth]{_figs/WHAT}
-\caption{Experimental Rig}
-\label{fig:rig}
-
-%   \subfloat[Experimental Rig for Defect Prediction]{  \includegraphics[width=\linewidth]{_figs/HERE}
-%   \label{fig:rig2}}
-
-\end{figure}
-
-%involves two key components. Firstly, there is the oracle (Random Forest with SMOTE) which is used to make predictions. Then we have the 
-\section{Data sets}
-
-The following section describes the experimental rig and the experiments used to measure the performance of HERE on 10 defect data sets and 6 performance prediction data sets.
-
-\subsection{Defect Data Set}
-The data was obtained from the PROMISE repository\footnote{Promise Repository: \url{openscience.us/repo}}.
-For the defect data we investigated 32 releases from 11 open source Java projects defined by the metrics highlighted in figure ~\ref{fig:ck}: \kw{Apache Ant} (1.5 -- 1.7), \kw{Apache Camel} (1.2 -- 1.6), \kw{Apache Ivy} (1.1 -- 2.0), \kw{JEdit} (4.1 -- 4.3), \kw{Apache Log4j} (1.0 -- 1.2), \kw{Apache Lucene} (2.0 -- 2.2), \kw{PBeans} (1.0 and 2.0), \kw{Apache POI} (2.0 -- 3.0), \kw{Apache Synapse} (1.0 -- 1.2), \kw{Apache Velocity} (1.4 -- 1.6), and \kw{Apache Xalan-Java} (2.5 -- 2.7).
-
-Given the empirical nature of the data, it is import to design an experiment such that the planning phase uses only the \kw{past} data to learn trends which can then be applied to the \kw{future} data.
-Thus for our experiment we use data sets that have at least two consecutive releases.
-\begin{itemize}
-\item To generate recommendations for a release $i$, the planner uses releases releases $(i-1)$ and $(i-2)$.
-\item The predictor also uses releases $(i-1)$ and $(i-2)$.
-However, we use SMOTE with re-sampling in order to handle the class imbalance in the data and to prevent the predictor from using the same training data as the planner.
-\end{itemize}
-
-\subsection{Performance Prediction Data Set}
-
-{\bfseries RQ3} asks if the aforementioned method can be expanded to other kinds of data.
-To answer this, we have used the performance prediction data set collected by Siegmund et al.
-for their ICSE '12 paper~\cite{sven12}.
-The data sets have been deployed as a part of the \textsc{SPLConqueror} tool\footnote{\url{fosd.de/SPLConqueror}}.
-This data set contains six examples of real world configurable systems that cover a broad spectrum of scenarios, see figure \ref{fig:cpm} for a summary.
-The systems have different characteristics (lines of code: 40 thousand to 300 thousand; Valid configurations: 192 to about 3.9 million), different implementation languages (C, C++, and Java), different mechanism (conditional compilation, configuration files, and command-line options), and different domains (Web servers, compilers, encoders, and databases).
-The data contains a measurement of all the configurations that are invoked by the benchmarking tool.
-The measurements were conducted 5 to 20 times and the mean of all measurements for each configuration was recoded.
-
-For our experiments, we randomly split the data sets into two equal halves, one for training and the other for testing.
-The planning phase learns configuration settings from the training half and plans for changes in the test half aiming to optimize the performance of the test instances.
-We repeat our measurements 20 to 25 times to overcome measurement bias.
-\section{Experimental Design}
-
-\subsection{The Rig}
-
-The experimental rig for defect prediction is shown in Figure \ref{fig:rig}. It works as follows: 
-\bi
-\item We use an {oracle} (Random Forest + SMOTE) to determine whether a certain test case is defective or not. 
-\item If the oracle suggests that an instance is defective, then we use HERE to apply the recommendations to that test instance. 
-\item The oracle is then used to predict the attributes in the modified instance.
-\item The statistical significance of the changes are verified using the cliffs delta measure described below.
-\ei
-
-For run time optimization, we use a similar rig.
-The oracle is Random Forest, and it predicts for run times of specific configuration.
-HERE is used to generate a recommended configuration to reduce the run times.
-The run time is measured by the oracle.
-The reduction of run times are expressed as fractions of the original (also referred to as baseline) run time.
-
-Note that we report the performance scores as a comparison between the oracle's prediction \textit{before} and that \textit{after}.
-We refrain from using the \textit{actual} defects in the data sets to perform the same comparison.
-This is because the oracle is limited in its ability to predict defects, there are instances that are inherently misclassified.
-These misclassifications however are not affected by the planner.
-Therefore, by comparing the defect counts before and after applying the planner and doing so with a the same oracle would give us an accurate albeit relativistic measure of performance.
-
-\subsection{Performance Assessment}
-
-In order to assess the performance of the planner for the defect data set, we use the Cliffs Delta score to measure the probability that the number of bugs in test data before applying the planner is larger than after doing so.
-In other words, we use the delta score to measure the ability of the planner to effective reduce the number of defects.
-Given the untreated test instance labeled \textit{Before} of length \textit{M} and the treated instances labeled \textit{After}, the delta score is obtained as follows:
-\begin{equation}
-\delta = \frac{\#(Before<After) - \#(Before>After)}{M^2}
-\label{eq:cliffs}
-\end{equation}
-
-In the context of our application, the $\delta$ attains a value of -1 if the number of defects after applying the treatments has reduced to zero.
-On the other hand $\delta$ will be 0 if there is no change at all.
-Thus, most of the values reported will lie between 0 and -1.
-It needs to be highlighted that although $\delta$ can lie between -1 and +1, the in our application the range is limited to -1 and 0.
-And this is because we only apply the treatments to defective cases.
-
-For the performance prediction data set on the other hand, Cliff's delta measure is not directly applicable.
-We therefore assess the performance by measuring the gain, given by $\frac{Before}{After}$.
-The gain takes a value larger than 1 if the run times have been reduced, a value of 1 if there is no change, and a value less than 1 if run times have increased after applying the recommended changes.
-
-In addition to the above, we rank the different various of the planning scheme to identify the best approach.
-We make use of the Scott-Knott procedure, recommended by Mittas \& Angelis in their 2013 IEEE TSE paper~\cite{sk}, to compute the ranks.
-It works as follows: A list of treatments \textit{l} is sorted by the Median score.
-The list \textit{l} is then split into sub-lists m, n in order to maximize the expected value of the differences in the observed performance before and after division.
-A statistical hypothesis test \textit{H} is applied on the splits \textit{m, n} to check if they are statistically different.
-If so, Skott-Knott then recurses on each division.
-
-The research conducted by Shepperd and MacDonell~\cite{shepperd12a}, Kampenes~\cite{kampenes07} and Kocaguenli et al.~\cite{}, highlighted that an ``effect size'' in lieu of a mere hypothesis test is required in order to verfiy if two populations are ``significly'' different.
-An ICSE'11 paper by Arcuri~\cite{} endorsed the use of Vargha and Delaney's A12 effect size for reporting results in software engineering.
-Thus, for hypothesis testing H in Skott-Knott, we use the A12 test and a non-parametric bootstrap sampling~\cite{}.
-
-\section{Experimental Results}
-
-\subsection{Defect Data Set}
-This sections explores \textbf{RQ2: Can lessons learnt from local policy generators be useful for generating solutions that can be used to mitigate defects in software systems?}
-
-Figure \ref{fig:bugs} compares the number of defects before and after applying "HERE".
-The graphs represent the median scores, with the inter-quartile ranges represented by the error bars.
-The results seem to show that in all data sets under consideration, the number of defects have reduced, some more so than others.
-Large differences were notice in certain data sets namely, \textit{ant}, \textit{camel}, \textit{jedit}, \textit{poi,} and \textit{xalan}, on close examination it was noticed that these data sets had comparatively large training data, which translates to more samples for the planner to learn from.
-
-In addition to this, to study the statistical significance of the changes, the results were statistically verified using the Skott-Knott procedure.
-In order to do this we computed the Cliff's Delta score.
-As highlighted previously, HERE is applied only for test instances that are considered defective by the oracle.
-Using \eq{cliffs} we can expect to see the following results:
-
-\bi
-\item $\lt$ 0 if defects have been suppressed.
-\item = 0 if no change has been made.
-\item $\gt$ 0 if new defects have been introduced.
-This is not applicable to our case because we only apply HERE to defective cases; either the defects are suppressed or they remain unaltered, introduction of new defects is not possible.
-\ei
-
-\begin{figure}[tbp]
-\centering
-\includegraphics[width=\linewidth]{_figs/histograms.pdf}
-\caption{Comparison of defects before and after planning.}
-\label{fig:bugs}
-\end{figure}
-With this in mind, it is easy to note that lower cliffs delta score translates to better the performance.
-
-The results are tabulated in figure \ref{tab:ant}. For the sake of completeness, we have introduced three basic configurations in HERE: 
-\bi
-\item \textit{Extent of Mutation:} Denotes the extent by which a test instant is \textit{mutated} towards the best cluster in the contour.
-It is a fraction that lies between 0 and 1.
-The baseline study requires no change be made, and thus extent of mutation is set to zero.
-\item \textit{Feature Weighting:} The importance of feature weighting has already been discussed in section \ref{fwt}.
-It is a fraction that lies between 0 and 1, with 0 being the least important and 1 the most important feature.
-The extent of mutation is multiplied by this fraction to determine how much a specific feature changes by.
-Generally, we would like to make the largest change to the most crucial feature.
-\item \textit{Information Pruning:} In addition to the weighting the features, we explored the possibility of mutating only the most important features.
-The feature weights are already known to us, we sort the features in descending order of their weights and mutate only the first X\%.
-\ei
-It is to be noted however that
-
-\begin{figure*}[htbp!]
-
-\noindent\begin{minipage}{0.5\textwidth}
-  {\scriptsize \textbf{Ant}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-      \arrayrulecolor{darkgray}
-      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 & 0.75 &    -0.63  &  0.08 & \quart{2}{7}{5}{144} \\
-  1 & 0.75, weighting &    -0.6  &  0.2 & \quart{0}{16}{8}{144} \\
-\hline  2 & 0.5, weighting &    -0.42  &  0.11 & \quart{17}{10}{23}{144} \\
-  2 & 0.5 &    -0.42  &  0.11 & \quart{19}{9}{23}{144} \\
-  2 & 0.75, weighting, Prune=50\% &    -0.4  &  0.11 & \quart{20}{9}{25}{144} \\
-\hline  3 & 0.25 &    -0.28  &  0.09 & \quart{31}{7}{35}{144} \\
-  3 & 0.25, weighting &    -0.28  &  0.08 & \quart{31}{7}{35}{144} \\
-\hline  4 & 0.5, weighting, Prune=50\% &    -0.25  &  0.06 & \quart{35}{5}{38}{144} \\
-\hline  5 & 0.25, weighting, Prune=50\% &    -0.19  &  0.05 & \quart{41}{4}{43}{144} \\
-\hline  6 & Baseline &    -0.11  &  0.03 & \quart{47}{2}{49}{144} \\
-\hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Camel}\\}
-{\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &  0.75, weighting, Prune=50\% &    -0.41  &  0.1 & \quart{2}{14}{9}{205} \\
-  1 &  0.75 &    -0.41  &  0.23 & \quart{1}{32}{9}{205} \\
-  1 &  0.75, weighting &    -0.39  &  0.16 & \quart{0}{22}{12}{205} \\
-\hline  2 &  0.5, weighting, Prune=50\% &    -0.27  &  0.09 & \quart{19}{12}{29}{205} \\
-  2 &  0.5 &    -0.26  &  0.12 & \quart{20}{17}{30}{205} \\
-  2 &  0.5, weighting &    -0.24  &  0.09 & \quart{24}{13}{33}{205} \\
-\hline  3 &  0.25, weighting, Prune=50\% &    -0.2  &  0.05 & \quart{36}{7}{38}{205} \\
-  3 &  0.25, weighting &    -0.19  &  0.07 & \quart{36}{9}{40}{205} \\
-  3 &  0.25 &    -0.17  &  0.06 & \quart{37}{8}{43}{205} \\
-\hline  4 &  Baseline &    -0.15  &  0.06 & \quart{41}{8}{45}{205} \\
-\hline \end{tabular}}
-\end{minipage}
-
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Ivy}\\[-0.05cm]}
-{\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &     0.75 &    -0.57  &  0.17 & \quart{0}{16}{6}{163} \\
-  1 &   0.75, weighting &    -0.55  &  0.11 & \quart{3}{11}{8}{163} \\
-\hline  2 &   0.75, weighting, Prune=50\% &    -0.38  &  0.11 & \quart{19}{11}{25}{163} \\
-  2 &    0.5, weighting &    -0.36  &  0.12 & \quart{23}{12}{27}{163} \\
-  2 &   0.5 &    -0.33  &  0.11 & \quart{25}{11}{30}{163} \\
-\hline  3 &   0.5, weighting, Prune=50\% &    -0.27  &  0.08 & \quart{30}{8}{36}{163} \\
-\hline  4 &   0.25, weighting &    -0.2  &  0.07 & \quart{41}{7}{43}{163} \\
-  4 &     0.25 &    -0.16  &  0.04 & \quart{43}{4}{47}{163} \\
-  4 &     Baseline &    -0.16  &  0.0 & \quart{47}{0}{47}{163} \\
-\hline  5 &   0.25, weighting, Prune=50\% &    -0.15  &  0.04 & \quart{45}{4}{48}{163} \\
-\hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Jedit}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &  0.75, weighting, Prune=50\% &    -0.41  &  0.18 & \quart{0}{20}{8}{172} \\
-  1 &  0.75 &    -0.35  &  0.26 & \quart{0}{30}{15}{172} \\
-\hline  2 &  0.75, weighting &    -0.25  &  0.17 & \quart{16}{20}{26}{172} \\
-  2 &  0.5, weighting, Prune=50\% &    -0.21  &  0.1 & \quart{23}{11}{31}{172} \\
-\hline  3 &   0.5 &    -0.17  &  0.08 & \quart{32}{9}{36}{172} \\
-  3 &  0.5, weighting &    -0.14  &  0.09 & \quart{31}{10}{39}{172} \\
-\hline  4 &  0.25, weighting, Prune=50\% &    -0.12  &  0.06 & \quart{39}{7}{41}{172} \\
-\hline  5 &  0.25 &    -0.08  &  0.05 & \quart{43}{5}{46}{172} \\
-  5 &  0.25, weighting &    -0.08  &  0.06 & \quart{43}{6}{46}{172} \\
-\hline  6 &  Baseline &    -0.06  &  0.01 & \quart{47}{1}{48}{172} \\
-\hline \end{tabular}}
-\end{minipage}
-
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Log4j}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &  0.75, weighting, Prune=50\% &    -0.19  &  0.13 & \quart{0}{28}{15}{273} \\
-\hline  2 &  0.75 &    -0.13  &  0.06 & \quart{23}{13}{28}{273} \\
-  2 &  0.5, weighting, Prune=50\% &    -0.13  &  0.05 & \quart{23}{11}{28}{273} \\
-  2 &  0.75, weighting &    -0.12  &  0.1 & \quart{15}{21}{30}{273} \\
-\hline  3 &  0.5, weighting &    -0.1  &  0.03 & \quart{28}{6}{34}{273} \\
-\hline  4 &   0.5 &    -0.1  &  0.07 & \quart{28}{15}{34}{273} \\
-  4 &  0.25 &    -0.09  &  0.04 & \quart{34}{9}{36}{273} \\
-  4 &  0.25, weighting, Prune=50\% &    -0.09  &  0.04 & \quart{34}{9}{36}{273} \\
-  4 &  0.25, weighting &    -0.06  &  0.04 & \quart{34}{9}{43}{273} \\
-\hline  5 &  Baseline &    -0.06  &  0.03 & \quart{43}{6}{43}{273} \\
-\hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Lucene}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &  0.75, weighting &    -0.15  &  0.09 & \quart{0}{29}{9}{393} \\
-  1 &  0.75 &    -0.13  &  0.09 & \quart{0}{29}{16}{393} \\
-  1 &  0.75, weighting, Prune=50\% &    -0.12  &  0.08 & \quart{6}{27}{19}{393} \\
-\hline  2 &  Baseline &    -0.1  &  0.03 & \quart{26}{10}{26}{393} \\
-  2 &  0.5, weighting, Prune=50\% &    -0.1  &  0.03 & \quart{23}{10}{26}{393} \\
-\hline  3 &  0.5, weighting &    -0.08  &  0.06 & \quart{23}{20}{33}{393} \\
-  3 &  0.25, weighting, Prune=50\% &    -0.07  &  0.03 & \quart{33}{10}{36}{393} \\
-  3 &  0.5 &    -0.07  &  0.05 & \quart{29}{17}{36}{393} \\
-\hline  4 &  0.25, weighting &    -0.04  &  0.04 & \quart{36}{13}{46}{393} \\
-  4 &  0.25 &    -0.04  &  0.02 & \quart{39}{7}{46}{393} \\
-\hline \end{tabular}}
-\end{minipage}
-
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Poi}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-      \arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 & 0.75, weighting &    -0.45  &  0.1 & \quart{6}{10}{11}{162} \\
-  1 &  0.75 &    -0.44  &  0.23 & \quart{0}{23}{12}{162} \\
-\hline  2 & 0.5, weighting &    -0.32  &  0.23 & \quart{12}{24}{24}{162} \\
-  2 & 0.5 &    -0.26  &  0.23 & \quart{18}{24}{31}{162} \\
-  2 & 0.75, weighting, Prune=50\% &    -0.25  &  0.19 & \quart{17}{20}{32}{162} \\
-\hline  3 & 0.5, weighting, Prune=50\% &    -0.19  &  0.09 & \quart{34}{9}{38}{162} \\
-  3 &  0.25 &    -0.19  &  0.11 & \quart{32}{11}{38}{162} \\
-  3 & 0.25, weighting &    -0.17  &  0.14 & \quart{30}{14}{40}{162} \\
-\hline  4 & 0.25, weighting, Prune=50\% &    -0.12  &  0.09 & \quart{40}{9}{45}{162} \\
-\hline  5 &  Baseline &    -0.09  &  0.03 & \quart{46}{3}{48}{162} \\
-\hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Synapse}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 & 0.75, weighting &    -0.56  &  0.2 & \quart{7}{18}{11}{148} \\
-  1 & 0.75 &    -0.48  &  0.34 & \quart{0}{29}{18}{148} \\
-\hline  2 & 0.5 &    -0.4  &  0.27 & \quart{14}{24}{25}{148} \\
-  2 & 0.5, weighting &    -0.37  &  0.17 & \quart{21}{15}{28}{148} \\
-\hline  3 & 0.25 &    -0.23  &  0.16 & \quart{31}{14}{40}{148} \\
-  3 & 0.25, weighting &    -0.23  &  0.1 & \quart{38}{9}{40}{148} \\
-  3 & 0.75, weighting, Prune=50\% &    -0.19  &  0.08 & \quart{40}{7}{43}{148} \\
-\hline  4 & 0.25, weighting, Prune=50\% &    -0.17  &  0.08 & \quart{42}{7}{45}{148} \\
-  4 & Baseline &    -0.15  &  0.0 & \quart{47}{0}{47}{148} \\
-  4 & 0.5, weighting, Prune=50\% &    -0.15  &  0.11 & \quart{40}{9}{47}{148} \\
-\hline \end{tabular}}
-\end{minipage}
-
-\noindent\begin{minipage}{0.50\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Velocity}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 & 0.75, weighting &    -0.19  &  0.22 & \quart{1}{34}{21}{207} \\
-  1 & 0.75, weighting, Prune=50\% &    -0.15  &  0.13 & \quart{14}{20}{28}{207} \\
-  1 & 0.75 &    -0.14  &  0.23 & \quart{0}{35}{29}{207} \\
-\hline  2 & 0.5 &    -0.13  &  0.11 & \quart{23}{17}{31}{207} \\
-\hline  3 & 0.5, weighting &    -0.1  &  0.08 & \quart{29}{13}{35}{207} \\
-  3 & 0.5, weighting, Prune=50\% &    -0.07  &  0.07 & \quart{32}{11}{40}{207} \\
-\hline  4 & Baseline &    -0.05  &  0.04 & \quart{43}{6}{43}{207} \\
-  4 & 0.25, weighting &    -0.05  &  0.03 & \quart{40}{5}{43}{207} \\
-  4 & 0.25 &    -0.04  &  0.02 & \quart{43}{3}{45}{207} \\
-  4 & 0.25, weighting, Prune=50\% &    -0.01  &  0.04 & \quart{43}{6}{49}{207} \\
-\hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.50\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Xalan}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 & 0.75 &    -0.36  &  0.12 & \quart{0}{16}{9}{198} \\
-  1 & 0.75, weighting &    -0.3  &  0.17 & \quart{4}{23}{18}{198} \\
-  1 &    0.5 &    -0.3  &  0.12 & \quart{9}{17}{18}{198} \\
-\hline  2 & 0.5, weighting &    -0.28  &  0.09 & \quart{16}{13}{20}{198} \\
-\hline  3 & 0.25, weighting &    -0.23  &  0.1 & \quart{20}{14}{27}{198} \\
-  3 & 0.25 &    -0.23  &  0.12 & \quart{20}{17}{27}{198} \\
-\hline  4 & 0.25, weighting, Prune=50\% &    -0.14  &  0.07 & \quart{36}{9}{40}{198} \\
-  4 & 0.75, weighting, Prune=50\% &    -0.14  &  0.07 & \quart{33}{10}{40}{198} \\
-  4 & 0.5, weighting, Prune=50\% &    -0.12  &  0.06 & \quart{37}{8}{43}{198} \\
-\hline  5 & Baseline &    -0.08  &  0.02 & \quart{47}{2}{48}{198} \\
-\hline \end{tabular}}
-\end{minipage}
-\caption{Cliffs Delta Scores for the defect data set.
-The Treatment column, has 3 possible configurations, the first (0.25, 0.50, and 0.75) represents the extent of mutation; weighting represents feature weighting; Prune represents the extent of information pruning.}
-\label{tab:ant}
-\end{figure*}
-
-\begin{figure*}[htbp!]
-\centering
-\begin{minipage}{0.30\linewidth}
-\includegraphics[width=\linewidth]{_figs/Apache.pdf}
-\end{minipage}
-\begin{minipage}{0.30\linewidth}
-\includegraphics[width=\linewidth]{_figs/BDBJ.pdf}
-\end{minipage}
-\begin{minipage}{0.30\linewidth}
-\includegraphics[width=\linewidth]{_figs/BDBC.pdf}
-\end{minipage}
-
-\begin{minipage}{0.30\linewidth}
-\includegraphics[width=\linewidth]{_figs/LLVM.pdf}
-\end{minipage}
-\begin{minipage}{0.30\linewidth}
-\includegraphics[width=\linewidth]{_figs/SQL.pdf}
-\end{minipage}
-\begin{minipage}{0.30\linewidth}
-\includegraphics[width=\linewidth]{_figs/X264.pdf}
-\end{minipage}
-\caption{Run time optimization using HERE.
-Blue curve represents a mutation probability of 0.75 with feature weighting and information pruning; Red curve represents a mutation probability of 0.25 with feature weighting, but no information pruning; Black curve represents the raw test data used as baseline for the comparison.}
-\label{fig:pp}
-\end{figure*}
-
-\subsection{Performance Prediction Data set}
-
-In this section, 
-\begin{figure*}[htbp!]
-\noindent\begin{minipage}{0.5\textwidth}
-  {\scriptsize \textbf{Apache}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-      \arrayrulecolor{darkgray}
-      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 & 75, weighting, Prune=25\% &    0.77  &  0.05 & \quart{0}{9}{3}{49} \\
-  1 &   75 &    0.79  &  0.08 & \quart{1}{16}{7}{49} \\
-\hline  2 & 75, weighting &    0.85  &  0.07 & \quart{9}{14}{19}{49} \\
-  2 & 50, weighting, Prune=25\% &    0.85  &  0.04 & \quart{15}{8}{19}{49} \\
-  2 &  50 &    0.85  &  0.05 & \quart{17}{10}{19}{49} \\
-\hline  3 & 50, weighting &    0.91  &  0.05 & \quart{25}{10}{31}{49} \\
-  3 &  25 &    0.92  &  0.04 & \quart{29}{8}{33}{49} \\
-  3 & 25, weighting, Prune=25\% &    0.93  &  0.02 & \quart{33}{4}{35}{49} \\
-\hline  4 & 25, weighting &    0.96  &  0.03 & \quart{37}{6}{41}{49} \\
-\hline  5 & baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-\hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{BDBC}\\}
-{\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &     75 &    0.22  &  0.05 & \quart{0}{3}{1}{49} \\
-  1 &  75, weighting, Prune=25\% &    0.21  &  0.04 & \quart{0}{2}{0}{49} \\
-\hline  2 &  75, weighting &    0.24  &  0.1 & \quart{0}{6}{2}{49} \\
-\hline  3 &     50 &    0.4  &  0.04 & \quart{11}{2}{12}{49} \\
-  3 &  50, weighting, Prune=25\% &    0.4  &  0.05 & \quart{10}{3}{12}{49} \\
-\hline  4 &  50, weighting &    0.47  &  0.09 & \quart{14}{5}{16}{49} \\
-\hline  5 &     25 &    0.66  &  0.03 & \quart{28}{1}{28}{49} \\
-  5 &  25, weighting, Prune=25\% &    0.67  &  0.06 & \quart{28}{3}{29}{49} \\
-\hline  6 &  25, weighting &    0.69  &  0.06 & \quart{29}{4}{30}{49} \\
-\hline  7 &  baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-\hline \end{tabular}}
-\end{minipage}
-
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{BDBJ}\\}
-{\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &     75 &    0.63  &  0.16 & \quart{0}{19}{3}{49} \\
-  1 &  75, weighting, Prune=25\% &    0.68  &  0.17 & \quart{1}{21}{9}{49} \\
-  1 &  75, weighting &    0.74  &  0.11 & \quart{8}{14}{17}{49} \\
-\hline  2 &  50, weighting, Prune=25\% &    0.75  &  0.09 & \quart{14}{12}{18}{49} \\
-  2 &     50 &    0.79  &  0.13 & \quart{16}{16}{23}{49} \\
-\hline  3 &  50, weighting &    0.82  &  0.09 & \quart{23}{11}{27}{49} \\
-\hline  4 &  25, weighting, Prune=25\% &    0.87  &  0.07 & \quart{29}{9}{33}{49} \\
-\hline  5 &     25 &    0.88  &  0.06 & \quart{33}{8}{34}{49} \\
-  5 &  25, weighting &    0.92  &  0.06 & \quart{36}{7}{39}{49} \\
-\hline  6 &  baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-\hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{LLVM}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &     75 &    0.92  &  0.01 & \quart{5}{6}{5}{49} \\
-  1 &  75, weighting, Prune=25\% &    0.92  &  0.02 & \quart{0}{11}{5}{49} \\
-  1 &  75, weighting &    0.93  &  0.02 & \quart{5}{11}{11}{49} \\
-\hline  2 &     50 &    0.94  &  0.01 & \quart{16}{6}{16}{49} \\
-  2 &  50, weighting, Prune=25\% &    0.95  &  0.0 & \quart{22}{0}{22}{49} \\
-  2 &  50, weighting &    0.96  &  0.02 & \quart{22}{11}{27}{49} \\
-\hline  3 &     25 &    0.98  &  0.01 & \quart{33}{5}{38}{49} \\
-  3 &  25, weighting, Prune=25\% &    0.98  &  0.01 & \quart{33}{5}{38}{49} \\
-  3 &  25, weighting &    0.98  &  0.0 & \quart{38}{0}{38}{49} \\
-\hline  4 &  baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-\hline \end{tabular}}
-\end{minipage}
-
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{SQL}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &      75 &    0.98  &  0.01 & \quart{0}{16}{16}{49} \\
-  1 &  75, weighting, Prune=25\% &    0.98  &  0.0 & \quart{16}{0}{16}{49} \\
-  1 &  75, weighting &    0.99  &  0.01 & \quart{16}{17}{33}{49} \\
-  1 &  50, weighting, Prune=25\% &    0.99  &  0.0 & \quart{33}{0}{33}{49} \\
-  1 &      50 &    0.99  &  0.0 & \quart{33}{0}{33}{49} \\
-  1 &  50, weighting &    0.99  &  0.01 & \quart{33}{16}{33}{49} \\
-  1 &  25, weighting, Prune=25\% &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-  1 &      25 &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-  1 &  25, weighting &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-  1 &  baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-  \hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{X264}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &  75, weighting, Prune=25\% &    0.73  &  0.05 & \quart{1}{9}{3}{49} \\
-  1 &     75 &    0.74  &  0.05 & \quart{0}{8}{5}{49} \\
-\hline  2 &  75, weighting &    0.81  &  0.04 & \quart{13}{7}{17}{49} \\
-  2 &  50, weighting, Prune=25\% &    0.82  &  0.04 & \quart{17}{7}{18}{49} \\
-  2 &     50 &    0.83  &  0.03 & \quart{17}{5}{20}{49} \\
-\hline  3 &  50, weighting &    0.88  &  0.03 & \quart{25}{6}{29}{49} \\
-\hline  4 &     25 &    0.9  &  0.03 & \quart{31}{5}{32}{49} \\
-  4 &  25, weighting, Prune=25\% &    0.91  &  0.03 & \quart{32}{5}{34}{49} \\
-\hline  5 &  25, weighting &    0.93  &  0.02 & \quart{36}{3}{37}{49} \\
-\hline  6 &  baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-\hline \end{tabular}}
-\end{minipage}
-\end{figure*}
-
-% \section{Discussion}
-\section{Threats to validity}
-\input{related}
-
-\section{Conclusion}
-% \section*{Acknowledgements}
-\newpage
-\bibliography{how}{}
-\bibliographystyle{IEEEtran}
-\end{document}
+We adapt the work of Jiang,Lumpe et al.  as follows.

### 2015-05-06 how.tex
Updates from ShareLaTeX

--- 2015-05-04 how.tex
@@
 \usepackage{amsmath} 
+\usepackage[caption=false,font=footnotesize]{subfig}
 \DeclareMathOperator*{\argmin}{arg\,min} 
@@
 mathescape,
-numbers=#1,
-numberstyle=\footnotesize,
+numbers=none,
+numberstyle=\scriptsize,
 numbersep=0.5em,
@@
  their tools. Instead of merely predicting 
- some result, they also need tools that generate ``policy advice'';
- i.e. suggestions on  how to change values in order to
+ some result, they also need tools that generate ``plans'';
+ i.e. specific suggestions on  how to change values in order to
  improve on some predicted value.
 
- This paper proposes one such policy
- generator. ``HOW'' is a near-linear-time
+ This paper proposes one such planner. ``HOW'' is a 
  tool for proposing changes to independent
@@
  the predictions of the dependent variables. Unlike other approaches
- for learning optimizations to software does not require
- an underlying of the domain (rather, HOW automatically
- learns that model as part of its operation).
+ for learning optimizations to software, HOW does not require
+ an underlying of the domain. Also, HOW's plans
+ are designed to result in {\em minimal displacement}
+ to current practice.
 
@@
   \begin{IEEEkeywords}
-Instance-based reasoning, defect prediction, random forest, optimization.
+Defect prediction, configuration, prediction, planning, instance-based reasoning.
   \end{IEEEkeywords}
@@
 \section{Introduction}
-Business  users are now demanding that data mining tools
-be augmented with tools to support  business-level
+Business  users   now demand   data mining tools
+that  support a  business-level
 interpretation of that data. For example,
@@
 making?''. That is, these panelists are more interested in the interpretations
-that follow the mining, rather than just  the mining. For example:
+and follow-up
+that occurs {\em after} the mining, rather than just  the mining itself. For example:
 \bi
@@
 \end{quote}
-In order to satisfy the demands of this new kind of business user, we  study the generation of {\em plans} in the context
-of software analytics.  
-This paper presents
-HOW, a novel  {\em instance-based planner} that runs in near-linear time.
+Generating plans is also differed to the recommender systems. 
+discussed by Robillard and Walker~\cite{rob14}.  Recommendor systems
+in software engineering
+are less {\em directive} and more    {\em collaborative} than plan generators:
+\bi
+\item
+Directive systems (such as those discussed in this paper) tell developers exactly what to do;
+e.g. ``use these settings in a Makefile''. 
+\item
+On the other hand, the collaborative systems discussed by Robillard and Walker
+are more suggestive guides that
+help (e.g.) programmers focus on very small sets
+with  very large libraries of code of documentation.
+\ei
+This paper presents HOW, a novel planner for learning actionable analytics.
 In the experiments shown below, we see that HOW's plans can
@@
 \bi
-\item The software defects found in  twelve object-oriented JAVA systems explored in 2010 by Jureczko et al.~\cite{jureczko10};
-\item The runtime of the six software systems whose configurations
+\item The software defects found in  the object-oriented JAVA systems explored in 2010 by Jureczko et al.~\cite{jureczko10};
+\item The runtime of the  software systems whose configurations
 are explored in 2013 by Seigmund et al.~\cite{sven12};
 \ei
-In summary, this paper makes six contributions that are significantly different to
+In summary, this paper makes five contributions that are significantly different to
 prior work:
 \be
-\item Many software analytics papers use data to build {\em predictors} for (e.g.) defects and runtimes.
-However, aside from work by the authors of this paper,
-none of those papers then go further to use that data to build {\em planners}.
-\item This paper offers a general framework for augmenting a prediction system such that
-it becomes a planning system;
-\item This paper offers a  test that recognizes  when we should {\em not}  plan: in summary, our kind of planning is
-not recommended in domains that  generate poorly performing predictors;
-\item This paper offers a general verification rig for assessing the value of plans generated within this rig.
 \item The HOW  instance-based planner of this paper has not been presented before.
@@
 expected values of the Jureczko software defects and the Seigmund software runtimes.
+\item Apart from HOW, we  also offers a general framework for using  predictive system to build planners;
+\item Further, we offer a  test to recognizes  when we should {\em not}  plan: specifically,
+planning is
+not recommended in domains with  poorly performing predictors;
+\item Last, we  offer a general verification rig for assessing the value of plans generated within this rig.
 \ee
@@
  \subsection{Motivation: Why ``HOW''?}
-HOW was inspired by some recent work by Krall and Menzies and Davis on 
-the GALE optimizer~\cite{krall14}. A well-known effect in machine learning (and, in computer vision
+HOW was inspired by two     business issues raised about the  GALE optimizer~\cite{krall14}. 
+A well-known effect in machine learning (and, in computer vision
 and compression~\cite{levina04}) is that the $n$ dimensions of a data set can be represented by a  much
-lower-dimensional approximation. GALE finds those $m << n$ dimensions then mutates examples
+lower-dimensional approximation. GALE finds those $m \ll n$ dimensions then mutates examples
 towards the better end of each dimension $m_i$. Since it explores $m \ll n$ dimensions,
@@
 
-A limitation with GALE is that it makes extensive use of
-an underlying domain model to asses generations of newly mutated instances.  This is an issue since
-in some domains, no such model exists or is readily accessible. For example, this whole paper
-began when, after briefing a business client on GALE, they asked:
+When GALE executes, it searches for better examples of data
+ by (a)~inputting an initial population of data; then (b)~making
+ extensive mutation to that data. In practice, GALE makes
+100s to 100,000s of mutations. Each of these mutations
+is reassessed using some domain model.
+For certain users,this approach raises some issues.  One such user commented:
 \begin{quote}
-{\em ``But what if I do not have a model of my business?''}
+ISSUE~\#1: {\em ``What if I only want the minimum useful change, not
+the maximum possible?''}
 \end{quote}
-This is a legitimate concern.
+Note here that this business user is asking for solutions  that do not require extensive 
+changes to their current  approaches.
+
+Later in that discussion, another business user asked:
+\begin{quote}
+ISSUE~\#2: {\em ``But what if I do not have a domain model of my business?''}
+\end{quote}
+This also is a legitimate issue.
 Building and certifying a model  can  takes  long time, especially in software engineering. For  example, in previous work~\cite{me07f} we used models
@@
 Some of those models took decades to develop and mature (from 1981~\cite{boehm81} to 2000~\cite{boehm00b}).
-This is not an isolated example.
-One of us (Menzies) teaches a graduate class in automated model-based software engineering.
-Students in that class are asked to find (or build) a non-trivial model of
-some software process (where ``non-trivial'' means something that processes
-a  model at least an order of magnitude more complex than Brooks' Law). 
-While the  number of such models has been growing in recent years\footnote{See the
-catalogue at goo.gl/nv2AVK.}, 
-the total number remains very small-- which is an observation consistent with
-SE models typically require  much effort to build and certify.
-
-Also, even when there is an existing model, instance-based reasoning can be useful.
-Models need maintenance lest they become out-dated. Elsewhere, we have described our
+
+Also, even when there is an existing model, they can require
+constant  maintenance lest they become out-dated. Elsewhere, we have described our
 extensions to the USC models to enable reasoning about agile software developments. 
@@
 The problem of model maintenance is another
-motivation to look for alternate methods that can be automateically updated whenever new data arrives.
-
-Finally, sometimes  it is easier to access instances of a model's behaviour than the model
+motivation to look for alternate methods that can be automatically updated whenever new data arrives.
+
+Further, sometimes  it is easier to access instances of a model's behaviour than the model
 itself. For example, in prior work with Martin  Feather from the Jet Propulsion 
@@
 
-Note that this lack of access to a workable model is not just fatal for GALE, but also for every
-other model-based optimization algorithm such as simulated
-annealling or evolutuionary methods such as   
+These two issues are not just problems for GALE, but also for every
+other model-based optimization algorithm  that makes
+extensive use of mutation  and domain models such as
 NSGA-II, NSGA-III, SPEA2, IBEA, PSO, DE, MOEA/D, etc.~\cite{deb00a,zit02,zit04,%
 deb14,Cui2005a,storn97,zhang07:TEC}. Accordingly, this paper seeks
-an optimization methods that avoids the problem of models that are missing, slow
+an optimization methods that make minimal changes to instances,
+while avoiding the problem of models that are missing, slow
 to build, hard to maintain, or difficult to access.
@@
 \subsection{Methods: How to Build ``HOW''?}
-HOW is a variant of GALE that does not need a underlying domain model.
-
-When designing HOW, our premises were:
+
+A general model for {\em predictors} is as follows. 
+During testing, each test instance gains a prediction 
+by finding which region of the data it falls into.
+During training, those regions are inferred from
+divisions that ``chunk'' together regions with instances
+with similar properties. These dividers can be categorical (as in the case of decision trees) or probabilistic (as in the
+case of Naive Bayes) or learned via some distance minimization
+process 
+(as in the case of support vector machines) or generated
+directly by some clustering algorithm.
+
+\begin{figure}[t!]
+\small
+~\hrule~
+
+{\bf \fig{where}a: top down clustering:}
+
+Data can be rapidly and recursively divided   as follows.
+Find   two   distance instances,  $X,Y$
+by picking any instance $W$ at random, then setting $X$ to its most
+distant instance, then setting $Y$ to the instance most distant from
+$X$~\cite{fastmap}
+(this requires only $O(2N)$ comparisons
+of $N$ instances).
+Next, project each instance $Z$
+onto a line that  runs between $X,Y$ using the cosine
+rule of \fig{where}b. After that,  split the data at the median $x$ value of all instances and
+recurses on each half  (stopping when
+one half has less  than $\sqrt{N}$ of the original population). See \fig{code1d} for further details.
+
+~\hrule~
+
+{\bf \fig{where}b: finding distances:}
+
+In the \fig{where}a, to compute distances, we use
+the Euclidean measure recommended for
+instance-based reasoning by Aha et al.~\cite{aha91};
+i.e. $\sqrt{\sum_iw_i(X_i-Y_i)^2}$ where $X_i,Y_i$
+where values are  normalized 0..1 for the range min..max and 
+$w_i$ is some importance weight given to attribute $i$.
+Usually, $w_i=1$ but it can be adjusted using, say,
+the feature weighting methods of \fig{where}d.
+
+ ~\hrule~
+
+{\bf \fig{where}c: 3 point geometry:}
+
+Let   $X,Y$ be two points joined by  a line  length $c$.
+A third point, $Z$, has distances  $a=dist(Z,X)$ and
+$b=dist(Z,Y)$ to $X,Y$, respectively.
+According to the cosine rule,   $Z$ projects onto  $\overline{XY}$
+at distance $x=(a^2 + c^2 - b^2)/(2c)$ from $X$.
+Further, according to Pythagoras' theorem, $Z$ stands at a distance
+$y = \sqrt{a^2 - x^2}$ from the line $\overline{XY}$. See \fig{code1c} for further details.
+
+~\hrule~
+
+{\bf \fig{where}d: feature weighting:}
+
+HERE's feature weighting algorithm
+comes from the CART regression tree learner~\cite{Breiman1984}.
+It sorts independent variables
+ according to how well they can reduce the variance
+of a  numeric objective.
+If we split some column $i$ of independent numeric data  into $N=n_1 + n_2 + ..$ splits,
+then the expected
+value of the objective value of the split  is $w_i = \sum_i v_in_i/N$
+where $v$ is the standard deviation of the objective.
+A recursive procedure can  find those divisions $n_1,n_2,...$ by (a)~sorting a numeric column,
+then split at $\argmin_i w_i$, then recursing into each half.  See \fig{code1d} for further details
+
+~\hrule~
+
+\caption{Sub-routines within HOW.}\label{fig:where}
+\end{figure}
+
+\input{code}
+
+Those same regions can be used for instance-based 
+{\em planning}-- but instead of leaving test instances in the regions
+found during training, we {\em displace} them towards regions
+with better objective scores.
+To achieve this, 
+during training, HOW clusters data using the procedure of \fig{where}a,
+then draws lines between the centroids of  clusters $X,Y$ that are nearest
+neighbors.
+By convention, we say that the cluster containing $X$ has the  better objective scores. This means we can say that the line is a useful direction for displacing
+data; i.e.  away from $Y$ and towards $X$.
+Hence,  during testing,  HOW use Pythagoras' theorem
+and \fig{where}c to find the  nearest line to every test instance. That test instance is   then displaced towards the better end
+of that line (towards  $X$).
+
+An important design decision with HOW 
+is how to determine the exact {\em direction} and {\em magnitude} of the
+displacement.  Following on from the discussion around   ISSUE~\#1,
+we note that a design goal of HOW is
+{\em minimal displacements} of project data.
+To implement minimal displacement:
 \bi
 \item
-This is no domain model; (b)~we have some
-labelled data and (b)~we seek minimal
-disrupttion
-HOW divide training into regions where the training
-data has similar properties. Each region is then examined and divided into ``west'' and ``east''
-where the region's ``west'' end has examples with worst performance stores than the east
-end (mnemoc: west starts with ``w'' and is short for ``worst' and east starts with ``e;;]which is shirt
-for excellent).so the ``e'' in
-
-\be
-\item Take  a population $P$ of examples
-\item Separate all $p \in P$ examples into their $n$ independent variables and 
-their $o$ scores;
-\item Find $m \ll n$ lower dimensional approximations for the $n$ independent variables;
-\item Look for the worst and best ends of each $m$  dimension (where the better ends
-have better objective scores);
-\item Find the $q \subseteq P$ subset of the population with ``better'' objective scores;
-\item Generate the next population $P'$ by adjust the independent variables
-of the $q$  examples
-by a random amount (in the direction of  the  better ends of each dimension).
-\item Apply some model to discover all the objective scores of $P'$
-\item Set $P=P'$ and go to step 1
-\ee
-
-PCA explores the $e$
-eigenvectors of the correlation matrix between $d$
-variables~\cite{pearson1901}.  Usually,
-only a few $e \ll d$ eigenvectors are required
-since multiple inter-related variables $i,j,k \subseteq d$ can be represented
-by a single  eigenvector.
-Also, noisy variables from $d$ are
-ignored since they  do not contribute to the signal in the data.
-Further,
-redundant  variables  become (approximately) parallel lines
-in $e$ space. For all such redundancies \mbox{$i,j \in d$}, we
-can ignore $j$
-since effects that change over $j$ also
-change in the same way over $i$.
-
-Algorithms like PDDP~\cite{boley98} use PCA to
-recursively divide data into smaller regions. Each
-step of that process requires an $O(N^2)$ analysis
-of the data to compute the components~\cite{ilin10}. Worse, it requires an evaluation of every example.
-Using WHERE, competitive results can be achieved
-using an $O(2N)$ analysis.
-WHERE uses a heuristic proposed by
-Faloutsos and Lin~\cite{Faloutsos1995}
-(which
-Platt has
-  shown computes a Nystr\"om
-  approximation to the first component of
-  PCA~\cite{platt05}).
-In step one, WHERE inputs
-$N$
-examples $N_1,N_2,..$. Secondly, WHERE
-picks any
-point $N_i$ at random. Thirdly, WHERE
-finds the point  {\em West}~$\in N$ that is
-furthest\footnote{
- For this work, we use the standard Euclidean measure recommended for
-instance-based reasoning by Aha et al.~\cite{aha91};
-i.e. $\sqrt{\sum_i(x_i-y_i)^2}$ where $x_i,y_i$
-are values normalized 0..1 for the range min..max.}
-from $N_i$.
-Finally, WHERE
-
-$m \ll n$
-dimension
-
-\be
-\item Clustering the training data 
+HOW sorts  the independent variables
+using the procedure of  \fig{where}d. It then only
+displaces the    best $B$\%  of that sort (while leaving the rest untouched).
+In  the experiments shown below,  we explore   $B \in \{25,50,100\}\%$.
 \item
-(c) finding which end of the cluster has better performance scores.
-(d) find
-\ee
-
-\section{Methodological Comments:\\ from ``Prediction'' to ``Planning''}
-A major  problem with building a planning mechanism in software engineering is ``how to verify the generated
-plans?''. For example,  in the experiments shown below,  HOW comments  on how to reduce
-software defects by adjusting certain static code parameters of the code\footnote{Such parameters can be mnaually adjusted by programmers or (for large scale changes) automatically adjusted using code refactoring
-tools, as shown by Binkely et al. in 2006~\cite{Binkley2006} and more recently by Mkaouer et al. in 2015~\cite{Mkaouer15}.}. How are we to verify that HOW's recommendations actually work?
-
-Some organizations have the resources to 
-run repeated trials to assess the effect of different treatments.
-For example, in one remarkable recent study, Bente et al. report results
-were the same specification was developed into a product by four different organizations~\cite{Anda2009}. Given those kind of resources, it would be possible
-to (say) take a code base, assign it to $N$ different teams, apply
-HOW's plans the code used by  $N/2$ teams, then check in 12 months time
-if those halves of the teams have fewer defects than the other.
-
-Very few industrial or research groups have access
-to the kinds of resources using by Bente et al. (evidence: in the size years since the
-publication of that work, we know of only one of two similar studies). Hence, it
-we wish to verify HOW's plans, then some other approach is required that is less
-resource intensive.
-
-\subsection{Proposed Framework}
-
-We propose using prediction systems (built by data mining) as a verification
-tool for planners. In domains with data, from which data miners can build
-predictors of adequate performance, then those predictors can assess the value
-of the changes proposed by HOW.
-As shown in \fig{work}, 
-project data is divided into two disjoint sets {\em train} and {\em test}
-(so \mbox{{\em train} $\cup$ {\em test} $=\;\emptyset$}).
-Next, from the train set, we build both a {\em planner} as well
-as a {\em predictor}. Our general framework does not   commit to any particular  choice
-of {\em planner} or {\em predictor}. For the purposes of this discussion 
-our {\em planner}
-will be HOW (discussed below)and our
-our {\em predictors} will be the Random Forest and Random Forest
-Regressor\footnote{Decision tree learners find the attribute whose value's
-select for for sections of the data with least variation in the class
-variable. Decision tree learners then recurse on each selection~\cite{breiman84}. A random forest is a set of decision trees, each built
-from some random subset of the rows and columns. The conclusions
-of the forest are a ``vote'' generated by all the trees~\cite{Breiman2001}. 
-A standard Random Forest predicts for a discrete class variable while
-a Random Forest Regressor generates numeric predictions.} taken from the SciKit
-Learn toolkit~\cite{Pedregosa2012}.
-
-Turning now to the {\em test} data, this is passed to the {\em predictor}
-to generate a baseline {\em before} performance score.
-Note that if our {\em predictors} fail to perform adequately on the test data,
-then we cannot trust them to comment on our plans. Accordingly,
-if that performance is unsatisfactory, we abort.
-Else, we (1)~apply the {\em planner} to alter the {\em test} data;
-then (2)~apply the {\em predictor} to the altered data {\em test'};
-then (3)~return the performance delta.
+HOW also  limits displacement
+to very small regions in the space of the training data (never more that the separation
+of the two closest clusters).  HOW's clusterer divides  data into many   small clusters containing
+$\sqrt{N}$ of the population.
+HOW   limits displacement to  \mbox{$0 \le F \le c$}, where
+$c$ is the distance between the two closest clusters. 
+In  the experiments shown below,  we explore
+\mbox{$F\in \{0.25, 0.5, 0.75\}$}.
+\ei
+Turning now to the displacement {\em direction},
+our experiments show that it useful to  carefully reflect on exactly where HOW should  push each test instance.
+HOW replaces each cluster   with one {\em exemplar} that best
+characterizes the data in that cluster. It then displaces the
+test data towards that exemplar, as follows.
+Let $Z_j$ be an independent variable within the
+test instance $Z$. If  $X$ be the exemplar found at training time,
+then we displace $Z$ as follows:
+\[Z_j =  Z_j + F*(X_j - Z_j)\]
+Here, $F$ is the  magnitude controller, discussed above.
+The experiments of this work showed that different kinds of data require
+different kinds of exemplars.
+\bi
+\item
+For the Seigmund data,
+the objective score is the runtime of the test suite of a compiled program.
+For this kind of data with numeric objectives,
+the exemplar  is the instance in a cluster
+with  best objective score.
+\item
+For the Jureczko data, the objective score
+is a boolean that is true if defects have been noted
+for that class. 
+For this kind of data with discrete objectives,
+the data, 
+has less differentiation between the objective scores
+so we set the exemplar to  
+an instance synthesized from the median values of the instances
+in that cluster.
+\ei
 
@@
 
-\subsection{Are These Plans ``Causal''?}
-With one additional stipulation,   this framework can be used to check if the learned
-plans can be said to {\em cause} a change in the domain being explored.
-
-In the literature, there are two main definitions of causality: Hill's H-causality~\cite{Hill1965}
-and Granger's G-casualty~\cite{granger80}. 
-Of the two, Hill's definition is the most strict. An effect
-is H-causal if it satisfies nine criteria including
-{\em  plausibility};
-{\em strength} of the effect;
-{\em 
-specificity}, i.e. locality of the effect
-to specialized groups;
-{\em
-support} by experimental evidence;
-{\em 
-coherence} between cause-effects noted
-in the field and in laboratory samples;
-{\em
-temporally} i.e. the effect has to follow the cause;
-{\em 
-analogy}, i.e.  similar causes have similar effects;
-{\em
-biological gradient}, i.e.  more exposure to the cause leads to more of an
-effect; and
-{\em
-consistency}, i.e.  the same cause-effect pairings have been seen by different persons
-in different places.
-
-It is hard to demonstrate H-causality in software engineering.
-For example, Hill's criteria emphasises repeatability and laboratory studies-- both of which are
-hard to perform in software engineering (e.g. see the continued debate about
-the value of using undergraduate students to surrogates for industrial
-practitioners in software engineering research~\cite{Carver2003}). Also, Hill's requirement
-for consistency is far easier to achieve in studies of small closed systems (e.g. bacteria in a petri dish)
-than in large socio-technical systems (e.g. open source projects). In the latter,
-effects are more {\em probabilistic} than {\em categorical}-- by which we mean that 
-some cause tends to cause some effect at some probability $p$ less that one.
-This in turn means that at some probability $q$ (where $0 \le q < p \le 1$)
-that we will find examples of {\em inconsistency} where some cause does {\em not} lead
-to some effect (thus violating one of Hill's criteria for demonstrating causality).
-
-The  difficulties associated with Hill's criteria lead Granger~\cite{granger80}
-to propose another more practical criteria\footnote{Granger  himself comments that
-his proposal was based on earlier work by Norbert Weiner~\cite{Seth2007}.}.
-\mbox{G-causality} is based on building predictions based on {\em past} data,
-then showing that this works for {\em future} data~\cite{granger80}. 
-In should be noted  that the standard 10-way cross-validation
-procedure used  in data mining does not necessarily demonstrate G-causality.  In a N-way cross-val experiments, the data is divided into $N$ bins.  
-$N-1$ bins are used for learning and the results are tested
-on the  remaining bin.
-This is repeated $N$ times, each time using a different bin for the test set.
-This approach can not be used to demonstrate causality since, if the initial data is collected
-over (say) $N$ months, then it is possible that the test set contains observations collected
-{\em before}   items seen in the training set.
-
-Jiang et al.~\cite{me11f} and Lumpe et al.~\cite{me11f} propose a modification to cross-validation.
-which lets a researcher
-demonstrate G-causal defect effects in software engineering.
-In this modification, we  divide project data  into $N$ bins, each of with contain data collected at similar times.
-They then sort those bins (on the collection date) and use bins $i,j$ to build models that
-are applied to bin  $k$ where 
-$i<j<k$. Note that this procedure ensures that we are building theories on data seen
-before the test data.
-
-We adapt the work of Jiang,Lumpe et al.  as follows. In  \fig{work}, we demand that the {\em test}
-data is not necessarily collected before the {\em train} data:
-\bi
-\item[\#1:] For data collected from software released in multiple versions, we should hence use  versions  $i,j$ to build models that are applied to version  $k$ where $i<j<k$.
-\item[\#2:] For data collected from Monte Carlo simulations (where inputs are selected at random)
-then as long as simulation $i$ is not used to adjust simulation $j> i$, then any item in that
-data could be generated before any other. For this kind of data, we  can use the first $X\%$
-of the simulation for training, and the remaining data for testing.
-\ee
-In the two case studies of this paper, the Jureczko object-oriented defect data comes from software
-released in multiple versions while the Seigmund configuration data comes from Monte Carlo simulations.
-Hence, we use procedure \#1 for the defect data and procedure \#2 for the configuration data.
-
-With these changes,
-we can reasonably claim that the plan's generating by HOW are G-causal.
-
-\subsection{When Not to Plan: the Problem of Poor Predictors}
+\subsection{How to Assess ``HOW''}
+In the experiments shown below,  HOW comments  on how to reduce
+software defects by adjusting certain static code parameters of the code\footnote{Such parameters can be manually adjusted by programmers or (for large scale changes) automatically adjusted using code refactoring
+tools, as shown by Binkely et al. in 2006~\cite{Binkley2006} and more recently by Mkaouer et al. in 2015~\cite{Mkaouer15}.}. How are we to verify that HOW's recommendations actually work?
+
+Some organizations have the resources to 
+run repeated trials to assess the effect of different treatments.
+For example, in one remarkable recent study, Bente et al. report results
+were the same specification was developed into a product by four different organizations~\cite{Anda2009}. Given those kind of resources, it would be possible
+to (say) take a code base, assign it to $N$ different teams, apply
+HOW's plans the code used by  $N/2$ teams, then check in 12 months time
+if those halves of the teams have fewer defects than the other.
+
+Very few industrial or research groups have access
+to the kinds of resources using by Bente et al. (evidence: in the size years since the
+publication of that work, we know of only one of two similar studies). Hence, it
+we wish to verify HOW's plans, then some other framework is required that is less
+resource intensive.
+
+We propose using prediction systems (built by data mining) as a verification
+tool for planners. In domains with data, from which data miners can build
+predictors of adequate performance, then those predictors can assess the value
+of the changes proposed by HOW.
+
+As shown in \fig{work}, our proposal divides
+project data  into two disjoint sets {\em train} and {\em test}
+(so \mbox{{\em train} $\cup$ {\em test} $=\;\emptyset$}).
+Next, from the train set, we build both a {\em planner} as well
+as a {  predictor}. Our general framework does not   commit to any particular  choice
+of { planner} or { predictor} but, for the purposes of this paper, 
+our { planner}
+will be HOW  and our
+our { predictors} will be the Random Forest and Random Forest
+Regressor taken from the SciKit
+Learn toolkit~\cite{Pedregosa2012}. The Random Forests procedure is explained in \fig{rr}.
+
+\begin{figure}[t!]
+\small
+\begin{tabular}{|p{.95\linewidth}|}\hline
+ Decision tree learners find the attribute whose value's
+select for for sections of the data with least variation in the class
+variable. Decision tree learners then recurse on each selection~\cite{breiman84}.
+
+A random forest is a set of decision trees, each built
+from some random subset of the rows and columns. The conclusions
+of the forest are a ``vote'' generated by all the trees~\cite{Breiman2001}.
+
+A standard Random Forest predicts for a discrete class variable while
+a Random Forest Regressor generates numeric predictions.\\\hline
+\end{tabular}
+\caption{Random Forests and Random Forest Regressors.}\label{fig:rr}
+\end{figure}
+
+Turning now to the {\em test} data, this is passed to the { predictor}
+to generate a baseline {\em before} performance score.
+Note that if our { predictors} fail to perform adequately on the test data,
+then we cannot trust them to comment on our plans. Accordingly,
+if that performance is unsatisfactory, we abort.
+Else, we (1)~apply the { planner} to alter the {\em test} data;
+then (2)~apply the { predictor} to the altered data {\em test'};
+then (3)~return the performance delta.
+
+\begin{figure*}[!t]
+\scriptsize
+   \begin{center}
+   \begin{minipage}{.46\linewidth}
+    \begin{tabular}{r@{~}|l@{~}|r@{~}|l@{~}|r@{~}|r@{~}|} \cline{2-6}
+   & \multicolumn{5}{c|}{ }\\
+
+   & \multicolumn{5}{c|}{ Data set  properties}\\ 
+   & \multicolumn{5}{c|}{  }\\ 
+           & \multicolumn{2}{c|}{training}   & \multicolumn{3}{c|}{testing}      \\ \cline{2-6}
+   data set      & versions           & instances & versions     & instances    & \% defective             \\ \hline
+        jedit    & 3.2, 4.0, 4.1, 4.2 & 1257      & 4.3          & 492          & 2 \\
+        ivy      & 1.1, 1.4           & 352       & 2.0          & 352          & 11 \\
+        camel    & 1.0, 1.2, 1.4      & 1819      & 1.6          & 965          & 19 \\
+        ant      & 1.3, 1.4, 1.5, 1.6 & 947       & 1.7          & 745          & 22 \\
+        synapse  & 1.0, 1.1           & 379       & 1.2          & 256          & 34 \\
+        velocity & 1.4, 1.5           & 410       & 1.6          & 229          & 34 \\
+        lucene   & 2.0, 2.2           & 442       & 2.4          & 340          & 59 \\
+        poi      & 1.5, 2, 2.5        & 936       & 3.0          & 442          & 64 \\
+        xerces   & 1.0, 1.2, 1.3      & 1055      & 1.4          & 588          & 74  \\ 
+        log4j    & 1.0, 1.1           & 244       & 1.2          & 205          & 92   \\
+        xalan    & 2.4, 2.5, 2.6      & 2411      & 2.7          & 909          & 99  \\\hline
+        \multicolumn{6}{c}{~}\\
+        \multicolumn{6}{c}{~}\\
+        \multicolumn{6}{c}{~}\\
+
+    \end{tabular}\end{minipage}\begin{minipage}{.4\linewidth}
+    \begin{tabular}{|rrr|rrr|rr|l} \cline{1-8}
+      \multicolumn{8}{|c|}{  }\\
+      \multicolumn{8}{|c|}{  Results from learning}\\
+       \multicolumn{8}{|c|}{   }\\
+   \multicolumn{3}{|c|}{untuned} & \multicolumn{3}{c|}{tuned} & \multicolumn{2}{c|}{change}\\
+  \cline{1-8}
+
+  pd & pf & good? & pd & pf & good? & pd & pf\\\cline{1-8}
+  50 & 27 &   & 64 & 28 & y & 14 & 1&$\star$\\
+  65 & 35 & y & 65 & 25 & y & 0 & -10&$\star$\\
+  50 & 30 &   & 62 & 41 &   & 12 & 11\\
+  66 & 21 & y & 63 & 18 & y & -3 & -3\\
+  45 & 18 &   & 47 & 15 &   & 2 & -3\\
+  79 & 61 &   & 77 & 61 &   & -2 & 0\\
+  55 & 25 &   & 60 & 27 & y & 5 & 2\\
+  51 & 32 &   & 61 & 12 & y & 10 & -20&$\star$\\
+ 30 & 28 &   & 39 & 33 &   & 9 & 5&$\times$\\
+  32 & 6 &   & 30 & 9 &   & -2 & 3&$\times$\\
+  41 & 5 &   & 48 & 0 &   & 7 & -5&\times\\
+\hline
+  \multicolumn{5}{c}{~}    &  & -1 & -4& 25th\\
+\multicolumn{6}{r|}{the percentiles of the changes:}    &   5 & 0 & 50th\\
+ \multicolumn{5}{c}{~}             & & 10 & 3 & 75th\\
+\end{tabular}
+
+\end{minipage}
+\end{center}
+
+    \caption{Training and test {\em data set properties} for the Jureczko data sets,
+    sorted in ascending order of \% defective examples.
+    On the right-hand-side, we show the {\em results from learning}.
+    Data is ``good'' if it has   recalls over 60\% and false alarms under 40\%
+(and note that, after tuning, there are more ``good'' than before).
+Data   marked with ``$\star$'' show large improvements in performance, after tuning.
+Data   marked with ``$\times$'' are not ``good'' since their test suites  have so few undefective examples (less than 5\% of the total sample) that it becomes harder to find better data towards which we can displace test data.
+}\label{fig:j}
+\end{figure*}
+
+\section{When Not to Plan: \\the Problem of Poor Predictors}
 
@@
 is that our assessment of the plans is only as good as the predictor. To 
-mitigate for this {\em problem of poor predictors}, it is hence wise to demand high standards for the {\em
+mitigate for this {\em problem of poor predictors}, it is hence wise to demand certain standards for the {\em
 satisfactory} threshold used in this \fig{work}.
 
-How prevalent is the problem of poor planners? 
-In the general case, this is hard to answer. However, as discussed in this section, for the 17 data
-sets explored in this study, only 
-%XXX 
-3 suffer from this problem.
-
-This study's data from two types of domains: the Jureczko   object-oriented data  
+For example, this study's data from two types of domains: the Jureczko   object-oriented data  
 and the Seigmund configuration data. 
@@
 using  $s= 100*(1- \frac{abs(a - p)}{a})$.
-Using engineering judgement, we define satisfactory $s$ as anything over   70\%. 
 This paper  explores    six Seigmund configuration data sets:  Berkeley DB (Java and Windows versions), Apache, SQLite, LLVM, and
@@
 \[s=\{99.9, 99.8, 99.4, 99.1, 96,1\}\]
+That is, we can be very confident that the predictors from the Seigmund data can assess
+HOW's plans.
 (Aside: if the reader doubts that such high scores are achievable, we note that these scores are 
@@
 
-For the  Jureczko   object-oriented data,
+Turning now to the Jureczko   OO data sets, we found:
+\bi
+\item
+Most   predictors in this domain were far from      perfect;
+\item 
+But several of these predictors could
+be salvaged using some sampling and optimization methods (see the notes on SMOTE and differential evolution, below).
+\ei
+As shown in \fig{j}, we   explore numerous examples of the Jureczko   object-oriented static code data sets: Ant, Camel, Ivy, Jedit,   Log4, Lucene, Poi, Synapse, Velocity, Xalan, Xerces\footnote{Available from the object-oriented defects section of the PROMISE respository openscience.us/repo/defect/ck.}.
+Given access to $V$ released
+versions, we test on version $V$ and train on the available data from earlier releases (as
+shown in \fig{j}, this means that we are training on hundreds to thousands
+of classes and testing on smaller test suites).
+Note the three bottom rows marked with $\times$: these contain predominately
+defective classes (two-thirds, or more) and in such data sets, it is hard to distinguish
+good from bad (since there are so many bad examples).
+
+For the  Jureczko   data,
 the plans generated by HOW advise   how to change static code attributes in order to reduce defects in
 Java classes.  Here,
-performance can be measured in terms of recall (percent of faulty classes in
+performance can be measured in terms of:
+\bi
+\item Probability of detection (a.k.a. ``pd'' or recall) which is the percent of faulty classes in
 the test data detected
-by the {\em predictor}). Using engineering judgement, we define satisfactory recall as anything over   70\%. 
-This paper explores 12 of the Jureczko   object-oriented static code data sets: Ant, Camel, Ivy, Jedit, JBeans, Log4, Lucene, Poi, Synapse, Velocity, Xalan, Xerces\footnote{Available from the object-oriented defects section of the PROMISE respository openscience.us/repo/defect/ck.}.
-For each of these data sets, we generated  {\em before} scores  by finding the latest
-version $k$, then training  a predictor on versions $k-2$ and $k-1$. As reported below,
-our initial recall scores from this data were unpromising (very low recall values). However,
-after applying certain data pre-processing steps (described below), a Random Forest generated
-on the $k-2,k-1$ versions achieved recalls on version $k$ of
-%issue24
-\[\mathrm{recall}=\{98,88,86,84,82,81,79,78,78,\overbrace{55,23,20}^{\mathrm{JBeans,Poi,Xalan}}\}\]
-From the above, we conclude that all the Seigmund configuration data and most of the Jureczko data
-avoids the problem of poor predictors. Hence, we can use that data for the planning
-experiments described below.
+by the {\em predictor}.
+\item Probability of false alarm (a.k.a. ``pf'') which is the percent of non-fault
+classes that are predicted to be defective.
+\ei 
+The ``untuned'' columns of \fig{j} shows RandomForest's learned {\em pd,pf}
+values generated after learning from the training data, then being applied to the test data.
+If we define ``good'' to mean $\mathit{pd}>60 \wedge \mathit{pf} < 40$\%,
+then only two of our data sets ({\em ivy,ant}) are ``good'' enough.
+
+The ``tuned'' columns of \fig{j} show that we can salvage some of the data sets
+using two techniques.
+ Pelayo and Dick~\cite{pelayo07} report that defect prediction can be improved via SMOTE~\cite{Chawla2002}; i.e. an over-sampling of minority-class examples.
+ Also, Fu et al.~\cite{fu:ase15} report that an optimization method called differential evolution~\cite{storn97}
+applied to defect predictors can quickly explore the tuning
+options of Random Forest to find better settings for the size of the forest, the termination criteria
+for tree generation, etc.
+The rows marked with $\star$ in \fig{j} show data sets whose performance was improved remarkably by these
+techniques. For example, in {\em poi}, the recall increased by 10\% while the false alarm rate dropped by 20\%).
+However,  as might be expected
+the the three bottom rows remain
+unsalvageable.
+
+In summary, while we cannot trust predictors from some of our data sets,
+we can plan ways to reduce defects in {\em jedit, ivy, ant, lucene} and {\em poi}.
+(Aside: note that this tuning used optimization and sub-sampling   on   {\em only} the
+training instances of \fig{j}
+i.e.
+no clues from the test set were ever used in this tuning process.)
 
@@
 \label{fig:whatflow}
-\end{figure}
-
-\begin{figure}[!b]
-\begin{python}[left]
-def fastmap(data): 
-  """Project data on a line 
-     between 2 dist points
-  """
-  z          = random.choose(data)
-  east       = furthest(z, data)
-  west       = furthest(east, data)
-  data.poles = (west,east)
-  c          = dist(west,east)     
-  for one in data.members: 
-    one.pos = project(west,east,c,one)
-  data = sorted(data) # sorted by 'pos'
-  return split(data)
-
-def project(west, east, AC, x): 
-  "Project x onto line east to west"
-  AB = dist(x,west)
-  BC = dist(x,east)
-  #cosine rule
-  return (AB$^2$ + AC$^2$ - AB$^2$)/(2*AC)
-
-def furthest(x,data): 
-  # what is furthest from x?
-  out, max = x,0
-  for y in data:
-    d = dist(x,y)
-    if d > max: out, max = y, d
-  return out
-
-def split(data): # Split at median
-   mid = len(data)/2; 
-  return data[mid:], data[:mid]
-
-def WHERE(data, scores={}, 
-          lvl=10000, prune=True):  
-  "Recursively split data."
-  if lvl < 1: 
-     return data # stop if out of levels
-  leafs      = [] # Empty Set
-  left,right = fastmap(data)
-  west, east = data.poles
-  $\omega=\sqrt{\mu}$ # enough data for recursion
-  goWest = len(left) > $\omega$  
-  goEast = len(right) > $\omega$ 
-  if prune: 
-    if goEast and better(west,east,scores): 
-       goEast = False 
-    if goWest and better(east,west,scores): 
-       goWest = False 
-  if goWest:  
-     leafs += where(left,  lvl - 1, prune)  
-  if goEast:  
-     leafs += where(right, lvl - 1, prune) 
-  return leafs
-
-\end{python}
-\caption{Clustering with WHERE}
-\label{fig:fastmapCode}   
-\end{figure}
-
-\begin{figure}[!t]
-\begin{python}[right]
-def envied(leaves):
-  """
-  Returns a single exemplary row from 
-  a cluster.
-  """
-
-def fWeight(train, prune = 0):
-  """
-  Find the feature weights & prune features
-  """
-
-def getContours(train):
-  """
-  Identify the pairs of clusters
-  that can form a contour
-  """
-  contours = []
-  # Clustering with where
-  clusters = WHERE(train) 
-  near = lambda x: knn(x, clusters)[1]
-  for c in clusters:
-    one = envied(c)
-    two = envied(near(one, clusters))
-    contours += [(one, two)]
-  return contours
-
-def project(a, b, test):
-  if score(a) > score(b):
-    good, bad = a,b 
-  else:
-    good, bad = b,a
-  AB = dist(bad,test)
-  BC = dist(good,test)
-  AC = dist(good,bad)
-  # Cosine rule
-  x = (AB$^2$ + AC$^2$ - BC$^2$)/(2*AC)
-  return $\sqrt{AB^2 - x^2}$
-
-def mutate(me, others, weights = None):
-  "Mutate 'me' towards 'others'"
-  if weights:
-    return [my + ext * f * (good - my) for 
-    f, my, good in zip(wights, me, others)]
-  else:
-    return [my + ext * (good - my) 
-    	 for my, good in zip(me, others)]
-
-def nearestContour(contours, instance):
-  "Find the nearest contour to an instance"
-  return sorted(
-        contours,
-        key=lambda F: project(
-        F[0], F[1], instance), 
-        reverse=True)[0]
-
-def HERE():
-  contours = getContours()
-  weights = fWeight(train)
-  for rows in defectiveRows:
-    vtx = nearestContour(contours, rows)
-    [good, bad] = sorted(vtx
-            , key=lambda F: score(F))
-    new += mutate(rows, good, weights)
-  return new
-\end{python}
-\caption{Instance-based Planning using HERE}
-\label{fig:HERE}   
 \end{figure}
@@
 % \section*{Acknowledgements}
-\newpage
+
+\clearpage
 \bibliography{how}{}

### 2015-05-06 related.tex
Updates from ShareLaTeX

@@
 \section{Related Work}
-The connection of HOW to model-based evolutionary programming was discussed above.
-In summary,   model-based tools such as NSGA-III~\cite{deb14} or MOEA/D~\cite{zhang07:TEC}
-use some domain model as part of extensive Monte Carlo studies (augmented with some
-evolution of selected best instances).
-The premise of HOW is that we have access to domain data, but not a domain model.
-Also, the results shown above were obtained without evolving/updating some current population
-multiple times.
-
-Planning with HERE is somewhat different to the recommendor systems.
-As described by Robillard and Walker~\cite{rob14}, recommendor systems
-in software engineering
-are less {\em directive} and more    {\em collaborative} than policy
-generators:
-\bi
-\item
-Directive systems such as HERE tell developers exactly what to do
-(e.g. ``use these settings in a Makefile'') 
-\item
-The collaborative systems discussed by Robillard and Walker
-are more suggestive guides that
-help (e.g.) programmers focus on very small sets
-with  very large libraries of code of documentation.
-\ei
-One difference between directive and collaborative systems is that
-the latter may not presume to suggest exactly what to do next.
-However, planning systems like HOW are much more ardent: then make precise recommendations
-of how to change all items in the test suite.
 
@@
 using the evolutionary methods that make extensive demands on an underlying domain model.
+
+ \subsubsection{Aside: Can We Call These Plans ``Causal''?}
+With one additional stipulation,   this framework can be used to check if the learned
+plans can be said to {\em cause} a change in the domain being explored.
+
+In the literature, there are two main definitions of causality: Hill's H-causality~\cite{Hill1965}
+and Granger's G-casualty~\cite{granger80}. 
+An effect
+is H-causal if it satisfies nine criteria\footnote{Hill's criteria for
+demonstrating causality:
+{\em  plausibility};
+{\em strength} of the effect;
+{\em 
+specificity}, i.e. locality of the effect
+to specialized groups;
+{\em
+support} by experimental evidence;
+{\em 
+coherence} between cause-effects noted
+in the field and in laboratory samples;
+{\em
+temporally} i.e. the effect has to follow the cause;
+{\em 
+analogy}, i.e.  similar causes have similar effects;
+{\em
+biological gradient}, i.e.  more exposure to the cause leads to more of an
+effect; and
+{\em
+consistency}, i.e.  the same cause-effect pairings have been seen by different persons
+in different places.}
+It is hard to demonstrate H-causality in software engineering.
+For example, Hill's criteria emphasises repeatability and laboratory studies-- both of which are
+hard to perform in software engineering (e.g. see the continued debate about
+the value of using undergraduate students to surrogates for industrial
+practitioners in software engineering research~\cite{Carver2003}). Also, Hill's requirement
+for consistent results is far easier to achieve in studies of small closed systems (e.g. bacteria in a petri dish)
+than in large socio-technical systems (e.g. open source projects). In the latter,
+effects are more {\em probabilistic} than {\em categorical}-- by which we mean that 
+some cause tends to cause some effect at some probability $p$ less that one.
+This in turn means that at some probability $q$ (where $0 \le q < p \le 1$)
+that we will find examples of {\em inconsistency} where some cause does {\em not} lead
+to some effect (thus violating one of Hill's criteria for demonstrating causality).
+
+The  difficulties associated with Hill's criteria lead Granger~\cite{granger80}
+to propose another more practical criteria\footnote{Granger  himself comments that
+his proposal was based on earlier work by Norbert Weiner~\cite{Seth2007}.}.
+\mbox{G-causality} is based on building predictions based on {\em past} data,
+then showing that this works for {\em future} data~\cite{granger80}. 
+ In  \fig{work}, we demand that the {\em test}
+data is not necessarily collected before the {\em train} data:
+\bi
+\item[\#1:] For data collected from software released in multiple versions, we should hence use  versions  $i,j$ to build models that are applied to version  $k$ where $i<j<k$.
+\item[\#2:] For data collected from Monte Carlo simulations (where inputs are selected at random)
+then as long as simulation $i$ is not used to adjust simulation $j> i$, then any item in that
+data could be generated before any other. For this kind of data, we  can use the first $X\%$
+of the simulation for training, and the remaining data for testing.
+\ee
+In the two case studies of this paper, the Jureczko object-oriented defect data comes from software
+released in multiple versions while the Seigmund configuration data comes from Monte Carlo simulations.
+Hence, we use procedure \#1 for the defect data and procedure \#2 for the configuration data.
+
+With these changes,
+we can reasonably claim that the plan's generating by HOW are G-causal.

### 2015-05-07 code.tex
Updates from ShareLaTeX

@@
-\begin{figure} 
-\begin{python}[right]
-def HERE(trainingData, testingData):
-  training(trainingData)
-  return [nearest(z).displace(z) 
-          for z in testing]
+\begin{figure*} 
+~\hrule~
+\begin{minipage}{.45\linewidth}
+\small
 
-def training(trainingData):
-  Line.using = what2Use(trainingData)
-  clusters = cluster(trainingData):
+~\\
+
+{\bf The Line class (as described in \tion{mm}:}
+Note that this is the primary data structure of HOW.
+Training data is converted into a set of {\tt Line}s,
+each of which is defined by a $X,Y$ pair, where $X$
+has better scores than $Y$.
+
+\begin{python}[left]
+class Line:
+  "Lines connect a worse cluster Y to a better one X"
+  all   = []    # where to store all the lines
+  using = []    # what columns to use
+  F     = 0.5   # magnitude control parameter
+  B     = 50    # ratio of how many columns to displace
+
+ def __init__(i,x,y):
+    if x.score < y.score:
+      x,y = y,x      # x must have best score
+    i.c = dist(x,y) 
+    i.obj = len(x) 
+    Line.all += [i]  # remember this line
+
+  def displace(i,z):
+    for j,(xj,zj) in enumerate(zip(x,z)):
+      if j in Line.using and not j == i.obj:  
+        z[j] = zj + Line.F*( xj - zj)
+    return z
+
+  def dist(i,z):
+    _,out = geometry(i.x,i.y,z)
+    return out
+\end{python}
+
+~\colorrule{gray}~
+
+{\bf Main loop, of the  HOW  instance-based planner:}
+Testing data is {\em displaced}
+towards   the $X$ point of the nearest {\tt Line}.
+\begin{python}[left]
+def HOW(training, testing):
+  def train(data):
+    Line.using = bPruning(data)
+    clusters   = cluster(data,len(data)):
     for cluster in clusters:
-    one = examplar(cluster)
-    two = examplar(nearest(one, clusters))
+      one = exemplar(cluster)
+      two = exemplar(nearest(one, clusters))
       Line(one,two)
 
-def what2Use(trainingData):
-  second  = lambda lst: lst[1]
-  weights = map(second,
-                sorted(featureWeighting(trainingData)))
-  use    = int(len(weights)*Line.B)
-  return [i for i,_ in enumerate(weights[:use])]
+   def exemplar(cluster):
+    "Apply the rules at end of section II.B"
+
+   def bPruning(data,  b = Line.B):
+    "Return the indexes of the 'b' best columns" 
+    enough  = int(len(weights)*b/100)
+    return featureWeighting(data)[:enough]
 
@@
     return out
+
+  #---------------------------------
+  # begin main code for  'HOW'
+  train(training)
+  return [nearestLine(z).displace(z) for z in testing]
 \end{python}
-\caption{Instance-based Planning using HERE.
-Testing data is {\em displaced}
-towards   the $X$ point of the nearest {\tt Line} (defined in \fig{line})
-The {\tt geometry} method comes from \fig{code1c}.
-The {\tt featureWeighting} function comes from \fig{code1a}.
-The {\tt cluster} function comes from \fig{fastmapCode}.
-}\label{fig:HERE}   
-\end{figure}
 
-\begin{figure} 
-\begin{python}[right]
-class Line:
-  "Lines connect a worse cluster Y to a better one X"
-  all   = []
-  using = []
-  F     = 0.5
-  B     = 0.5
-   def __init__(i,x,y):
-    if x.score < y.score:
-      x,y = y,x
-    i.c = dist(x,y) 
-    i.obj = len(x) 
-    Line.all += [i]
-  def displace(i,z):
-    for j,(xj,zj) in enumerate(zip(x,z)):
-      if not j == i.obj and  j in Line.using:
-         z[j] = zj + Line.F*( xj. - zj
-    return z
-  def dist(i,z):
-    _,out = geometry(i.x,i.y,z)
-    return out
-  def exemplar(i,cluster):
-    #Apply the rules at end of section II.B
-\end{python}
-\caption{The primary data structure of HOW
-is the {\tt Line}.
-Training data is converted into a set of {\tt Line}s,
-each of which is defined by a $X,Y$ pair, where $X$
-has better scores than $Y$. }\label{fig:line}
-\end{figure}
+~\colorrule{gray}~
 
-\begin{figure} 
+{\bf Code for geometry (as described in \fig{where}c):}
+
 \begin{python}[left]
@@
   b = dist(z,y) 
-  x= $(a^2 + c^2 - b^2)/(2ac)$ 
-  y=  $\sqrt{a^2 - max(x,0)^2)}$
+  x= $(a^2 + c^2 - b^2)/(2c)$ 
+  y=  $\sqrt{(a^2 - max(x,0))^2}$
   return x,y
@@
 def nearest(x,data):
-  return furthest(x,data,best=1000,better=lt)
+  return furthest(x,data,best=1000,
+                    better=lambda j,k:j < k)
 
-def furthest(x,data, best= -1, better=gt):  
+def furthest(x,data, best= -1, 
+                     better=lambda j,k:j > k):  
   out = None
@@
 \end{python}
-\caption{Some routines for 3 point geometry,  from \fig{where}.c.}\label{fig:code1c}
-\end{figure}
+ \end{minipage}~~~~~~~~~\begin{minipage}{.45\linewidth} 
+\small
 
-\begin{figure}
-\begin{python}[left]
-def featureWeighting(cols):
-   obj = len(cols[0])
-   return sorted(weight1(col,i,obj) 
-                for i,col in enumerate(cols)
-                if not i == obj)
+~\\
 
-def weight1(i,obj,col):
-  pairs = sorted([row[i],row[obj] for row in col])
-  n     = length(col)
-  return sum(v*n1/n for v,n1 in recurse(pairs,[])),i
-
-def recurse(this,cuts):
-  cut,sd = divide(this)
-  if cut:
-    recurse(this[:cut],cuts)
-    recurse(this[cut:],cuts)
-  else:
-    cuts += [(sd,len(this)]
-  return cuts
-
-def divide(this,tiny=2):
-  lhs, rhs = Stats(), Stats(x[1] for x in this)
-  n, least, cut = rhs.n*1.0, rhs.sd(), None
-  for j,x in enumerate(this):
-     if lhs.n > tiny and rhs.n > tiny:
-       tmp = lhs.n/n*lhs.sd() + rhs.n/n * rhs.sd()
-       if tmp < least:
-          cut,least = j,tmp
-     rhs - x[1]
-     lhs + x[1]
-  return cut,least
-
-class Stats():  
-    def __init__(i,inits=[]):
-      i.n = i.mu = i.m2 = 0.0
-      map(i.__add__,inits)
-    def sd(i) :  
-      return (max(0.0,i.m2)/(i.n - 1))**0.5
-    def __add__(i,x):
-      i.n  += 1
-      delta = x - i.mu
-      i.mu += delta/(1.0*i.n)
-      i.m2 += delta*(x - i.mu) 
-    def __sub__(i,x):
-      i.n  -= 1
-      delta = x - i.mu
-      i.mu -= delta/(1.0*i.n)
-      i.m2 -= delta*(x - i.mu) 
-\end{python}
-\caption{Feature weighting, from \fig{where}.d.}\label{fig:code1a}
-\end{figure}
-
-\begin{figure} 
-\begin{python}[left]
+{\bf Clustering (as described in \fig{where}a):}
+\begin{python}[right]
 def cluster(data, n,lvl=100):
-  if lvl < 1: 
-     return data # stop if out of levels
-  leafs = [] # Empty Set
-  x,y,left,right = splitAcross2Points(data) 
-  if len(left) > $\sqrt{n}$:  
-     leafs += cluster(left, n, lvl - 1)  
-  if len(right) > $\sqrt{n}$:  
-     leafs += cluster(right,n,  lvl - 1) 
-  data.has = dict(x=x,y=y,
-                 l=left,r=right,
-                 leafs=leafs)
-  return leafs
-
   def splitAcross2Points(data): 
@@
     return data[mid:], data[:mid]
+
+  # --------------------------------------
+  # begin main code for  'cluster'
+  if lvl < 1: 
+     return data # stop if out of levels
+  leafs = [] # Empty Set
+  x,y,left,right = splitAcross2Points(data) 
+  if len(left) > $\sqrt{n}$:  
+     leafs += cluster(left, n, lvl - 1)  
+  if len(right) > $\sqrt{n}$:  
+     leafs += cluster(right,n,  lvl - 1) 
+  data.has = dict(x=x,y=y,
+                 l=left,r=right,
+                 leafs=leafs)
+  return leafs
+
 \end{python}
-\caption{Clustering. Lines 16,17,18 come from~\cite{fastmap}. }\label{fig:fastmapCode}   
-\end{figure}
+
+~\colorrule{gray}~
+
+{\bf Feature weighting  (as described in \fig{where}d):}
+
+\begin{python}[right]
+def featureWeighting(cols):
+  "Returns col indexes, sorted by their weight."
+  class Stats():  
+    """Utility class. Handles incremental update of
+       n, mean, standard dev."""
+    def __init__(i,inits=[]):
+      i.n = i.mu = i.m2 = 0.0
+      map(i.__add__,inits)
+    def sd(i) :  return (max(0.0,i.m2)/(i.n - 1))**0.5
+    def __add__(i,x):
+      i.n  += 1
+      delta = x - i.mu
+      i.mu += delta/(1.0*i.n)
+      i.m2 += delta*(x - i.mu) 
+    def __sub__(i,x):
+      i.n  -= 1
+      delta = x - i.mu
+      i.mu -= delta/(1.0*i.n)
+      i.m2 -= delta*(x - i.mu)
+
+  def divide(this,tiny=2):
+    "Find the split that most reduces std dev."
+    lhs, rhs = Stats(), Stats(x[1] for x in this)
+    n, least, cut = rhs.n*1.0, rhs.sd(), None
+    for j,x in enumerate(this):
+      if lhs.n > tiny and rhs.n > tiny:
+        tmp = lhs.n/n*lhs.sd() + rhs.n/n * rhs.sd()
+        if tmp < least:
+           cut,least = j,tmp
+      rhs - x[1]
+      lhs + x[1]
+    return cut,least
+
+  def recurse(this,cuts):
+    cut,sd = divide(this)
+    if cut:
+      recurse(this[:cut],cuts)
+      recurse(this[cut:],cuts)
+    else:
+      cuts += [(sd,len(this)]
+    return cuts
+
+  def weight1(i,obj,col):
+    "Returns weight of column 'i'."
+    pairs = sorted([row[i],row[obj] for row in col])
+    n     = length(col)
+    w     = sum(v*n1/n for v,n1 in recurse(pairs,[]))
+    return w,i
+
+  #---------------------------------
+  # begin main code for  'featureWeighting'
+  obj = len(cols[0]) - 1 
+  return map(lambda k:k[1],
+             sorted(weight1(col,i,obj) 
+                    for i,col in enumerate(cols)
+                    if not i == obj))
+\end{python}
+\end{minipage}
+~\hrule~
+\caption{HOW (Python-style psuedo-code).
+For brevity's sake, this code skips certain low-level details.
+For a full working implementation, see https://github.com/ai-se/HOW1/src.
+Functions shown in \textcolor{blue}{{\bf blue}} are defined somewhere in this figure.}\label{fig:howcode}   
+\end{figure*}

### 2015-05-07 culled.tex
Updates from ShareLaTeX

@@
+\subsection{Performance Prediction Data Set}
+
+{\bfseries RQ3} asks if the aforementioned method can be expanded to other kinds of data.
+To answer this, we have used the performance prediction data set collected by Siegmund et al.
+for their ICSE '12 paper~\cite{sven12}.
+The data sets have been deployed as a part of the \textsc{SPLConqueror} tool\footnote{\url{fosd.de/SPLConqueror}}.
+This data set contains six examples of real world configurable systems that cover a broad spectrum of scenarios, see figure \ref{fig:cpm} for a summary.
+The systems have different characteristics (lines of code: 40 thousand to 300 thousand; Valid configurations: 192 to about 3.9 million), different implementation languages (C, C++, and Java), different mechanism (conditional compilation, configuration files, and command-line options), and different domains (Web servers, compilers, encoders, and databases).
+The data contains a measurement of all the configurations that are invoked by the benchmarking tool.
+The measurements were conducted 5 to 20 times and the mean of all measurements for each configuration was recoded.
+
+For our experiments, we randomly split the data sets into two equal halves, one for training and the other for testing.
+The planning phase learns configuration settings from the training half and plans for changes in the test half aiming to optimize the performance of the test instances.
+We repeat our measurements 20 to 25 times to overcome measurement bias.
+\section{Experimental Design}
+
+\subsection{The Rig}
+
+The experimental rig for defect prediction is shown in Figure \ref{fig:rig}. It works as follows: 
+\bi
+\item We use an {oracle} (Random Forest + SMOTE) to determine whether a certain test case is defective or not. 
+\item If the oracle suggests that an instance is defective, then we use HERE to apply the recommendations to that test instance. 
+\item The oracle is then used to predict the attributes in the modified instance.
+\item The statistical significance of the changes are verified using the cliffs delta measure described below.
+\ei
+
+For run time optimization, we use a similar rig.
+The oracle is Random Forest, and it predicts for run times of specific configuration.
+HERE is used to generate a recommended configuration to reduce the run times.
+The run time is measured by the oracle.
+The reduction of run times are expressed as fractions of the original (also referred to as baseline) run time.
+
+Note that we report the performance scores as a comparison between the oracle's prediction \textit{before} and that \textit{after}.
+We refrain from using the \textit{actual} defects in the data sets to perform the same comparison.
+This is because the oracle is limited in its ability to predict defects, there are instances that are inherently misclassified.
+These misclassifications however are not affected by the planner.
+Therefore, by comparing the defect counts before and after applying the planner and doing so with a the same oracle would give us an accurate albeit relativistic measure of performance.
+
 In should be noted  that the standard 10-way cross-validation
@@
 demonstrate G-causal defect effects in software engineering.
-In this modification, we  divide project data  into $N$ bins, each of with contain data collected at similar times.
+In this modification, we  divide project data  into $N$ bins, each of with contain data collected at similar t
+
+imes.
 They then sort those bins (on the collection date) and use bins $i,j$ to build models that
@@
 We adapt the work of Jiang,Lumpe et al.  as follows.
+
+blah blah data. algorithms. statistics
+
+\section{Releated Work}
+
+Our prior work in generating policies relied upon a Monte Carlo
+analysis of an underlying model~\cite{me07f}. This approach had three major problems.
+Firstly, enough domain knowledge had to be collected to build that model
+and this can take a long time. For example, in our previous work we used three software process models from
+the Unviersity of Southern California that were initially
+developed and updated for nearly two decades from 1981~\cite{boehm81} to 2000~\cite{boehm00b}.
+
+Secondly, there is the computational cost of running those models.
+While
+
+~\cite{}-- which suffered from the problem of (a)~the effort required to collect the domain knowledge to build
+problem in certifying the underlying model;
+ (b)~the computational problem of running that model enough
+times to learn patterns in that data; and (c)~ requrearea used large scale simulations or large
+
+While
+our case studies are defect and runtime reduction, HERE is a general
+purpose algorithm that could be applied to any table of data with at least
+one column whose values can be sorted from ``desired'' to ``undesired''.
+
+{\bf RQ1: Can Instance-based Learning techniques be used to create Planning tools that can better analyse software defect?}
+
+{\bf RQ2: Can lessons learnt from local policy generators be useful for generating solutions that can be used to mitigate defects in software systems?}
+
+{\bf RQ3: Can such instance-based planners be applied to other software engineering paradigms?}
+We check if the proposed instance-based planner is applicable to performance prediction.
+
+\section{Motivating Example}
+\section{Background}
+\section{Instance Based Learning}
+
+Assessing the quality of solutions to a real-world problem can be extremely hard~\cite{menzies2005xomo}.
+In several software engineering applications, researchers have models that can emulate the problem, for instance there is the COCOMO effort model~\cite[p29-57]{boehm2009software}, the COQUALMO defect model~\cite[p254-268]{boehm2009software}, Madachy’s schedule risk model~\cite[p284-291]{boehm2009software}, to name a few.
+Using these models it is possible to examine several scenarios in a short period of time, and this can be done in a reproducible manner.
+However, models aren't always the solution, as we shall see.
+
+There exist several problems where models are hard to obtain, or the input and output are related by complex connections that simply cannot be modeled in a reliable manner, or generation of reliable models take prohibitively long ~\cite{Ludewig2003}.
+Software defect prediction is an excellent example of such a case.
+Models that incorporate all the intricate issues that may lead defects in a product is extremely hard to come by.
+Moreover, it has been shown that models for different regions within the same data can have very different properties \cite{localvsglobal}.
+This makes it extremely hard for one to design planning systems that are capable of mitigating these defects.
+
+An alternative approach would be to make use of an instance based approach, an example of case based reasoning strategy, in place of the conventional model based approach.
+Instance based approaches have been used extensively by the effort estimation community, see~\cite{keung2008analogy, 6600685, walkerden1999empirical, shepperd1997estimating, kocaguneli2010use}.
+
+This approach has been proposed as an alternative to closed form mathematical models or other modeling methods such as regression \cite{keung2008analogy}.
+There are several other reasons for instance based approaches being a useful tool, see~\cite{6600685}.
+As pointed out by~\cite{walkerden1999empirical} it can be used with partial knowledge of the target project at an early stage which could be a very useful tool in preventing software defects.
+Instance based approaches are also rather robust in handling cases with sparse samples \cite{1438374}.
+All these features are desirable and suggest that instance-based approach is a useful adjunct to traditional model based approach.
+
+In this paper the instance based learning principle is used to first cluster the training data and then create contours in the data.
+These contours can then be used by test cases to infer meaningful information in order to improve it.
+The entire process is described in greater detail in the following sections.
+We would like to stress that the purpose of our work is not to promote instance-based planning over model based analytics, rather it is to suggest an alternative when model based approaches cannot be used.
+
+\subsection{Spectral Learning using WHERE}
+The algorithm uses WHERE to recursively cluster the input data to identify subsets in the training data that a test instance can learn from.
+WHERE is a spectral learner which uses the FastMap heuristic to estimate the first principal component.
+It then recursively partitions the data into two halves along the Median point of the projection on the first principal component, terminating when a half has less than $\sqrt{N}$ items.
+
+\subsection{Planning changes using HERE}
+We propose the HERE algorithm as a tool to plan changes in the original test data.
+Figure~\ref{fig:what} highlights the procedure by which HERE operates.
+It begins by creating clusters which are generated using the WHERE algorithm discussed above.
+Following this, a nearest neighbour scheme is applied to identify pairs of nearby clusters.
+A contour is constructed with these clusters at the vertices to characterize the cluster pairs.
+
+The mutation policy works by projecting the test instance onto the contours and identifying the the contour on which the test instance has the largest scalar projection.
+The planner then reflects over the vertices of the chosen contour, identifying the \textit{better} vertex among the two.
+Now, a new instance is generated by \textit{mutating the attributes} of the test instance towards the better vertex and away from the worse vertex.
+This process is repeated for all the test instances that are considered defective by the defect prediction scheme, discussed below.
+
+\subsection{Feature Weighting} \label{fwt}
+The algorithm also allows for a feature weighting and pruning scheme.
+We have employed a simple (and fast) attribute ranking method where the features are sorted based on their ability to find meaningful splits in the dependent class of the data, see ~\cite{hall03}.
+Features that can find splits with the \textit{lesser variance} in the dependent variable are \textit{ranked higher} than features that don't.
+
+We reason that the most informative feature must undergo a larger change as compared to other features.
+Therefore, when feature weighting is employed, the higher ranked features are mutated by a larger extent.
+Additionally, we have also included information pruning.
+Here we mutate only the top X\% of the features in each test instance.
+The remaining features remain unaltered.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{_figs/WHAT-Clusters2.pdf}
+\caption{HERE}
+\label{fig:whatflow}
+\end{figure}
+
+\subsection{Defect Prediction}
+
+To validate the treatments that have been suggested by our planner, we need to have defect predictors that capable of identifying if a certain module may (or may not) have a defect.
+A recent IEEE TSE paper by Lessmann et al.~\cite{lessmann} compared 21 different learners for software defect prediction:
+\bi
+\item
+{\em Statistical classifiers:}
+Linear    discrimin analysis,
+Quadratic discrimin analysis,
+Logistic regression,
+Naive Bayes,
+Bayesian networks,
+Least-angle regression,
+Relevance vector machine,
+
+\item
+{\em Nearest neighbor methods:}
+k-nearest neighbor,
+K-Star
+
+\item
+{\em Neural networks:}
+Multi-Layer Perceptron,
+Radial bias functions,
+
+\item
+{\em Support vector machine-based classifiers:}
+Support vector machine,
+Lagrangian SVM
+Least squares SVM,
+Linear programming,
+Voted perceptron,
+
+\item
+{\em Decision-tree approaches:}
+C4.5,
+CART,
+Alternating DTs
+\item
+{\em Ensemble methods:}
+\textbf{Random Forest},
+Logistic Model Tree.
+\ei
+
+They concluded that Random Forrest was the best method, CART being the worst.
+
+Random Forest is an ensemble learning scheme that constructs a number of decision trees at the training time, for a test instance it outputs the mode of the classes of individual tree.
+It's patent from how random forest operates that the prediction will suffer if there is an imbalance in classes during the training.
+Unfortunately, the data sets explored here do suffer from severe skewness, as highlighted in~\ref{fig:classimb}.
+A study conducted by Pelayo and Dick~\cite{smote2} inspected this issue.
+They showed that the SMOTE technique~\cite{smote} can be used to improve recognition of defect-prone modules.
+
+In short, SMOTE works by under-sampling the majority class and oversampling all the minority classes in the training data.
+We use a similar approach with one minor addition to the original algorithm.
+In our implementation of SMOTE we have introduced an additional step called \textit{resampling}, wherein we ensure that after we do the over/under sampling, the new training data does not have any of the original rows.
+The new training data merely resembles the original data.
+This is done as a precautionary measure, so as not to have HERE and Random Forest train on the same training data.
+%Its worth noting that both HERE and Random Forest require some data to train.
+In order to prevent the two from using the same data to train, we run SMOTE by  \textit{resampling} the classes.
+Re-sampling
+
+\section{Data sets}
+
+The following section describes the experimental rig and the experiments used to measure the performance of HERE on 10 defect data sets and 6 performance prediction data sets.
+
+\subsection{Defect Data Set}
+The data was obtained from the PROMISE repository\footnote{Promise Repository: \url{openscience.us/repo}}.
+For the defect data we investigated 32 releases from 11 open source Java projects defined by the metrics highlighted in figure ~\ref{fig:ck}: \kw{Apache Ant} (1.5 -- 1.7), \kw{Apache Camel} (1.2 -- 1.6), \kw{Apache Ivy} (1.1 -- 2.0), \kw{JEdit} (4.1 -- 4.3), \kw{Apache Log4j} (1.0 -- 1.2), \kw{Apache Lucene} (2.0 -- 2.2), \kw{PBeans} (1.0 and 2.0), \kw{Apache POI} (2.0 -- 3.0), \kw{Apache Synapse} (1.0 -- 1.2), \kw{Apache Velocity} (1.4 -- 1.6), and \kw{Apache Xalan-Java} (2.5 -- 2.7).
+
+Given the empirical nature of the data, it is import to design an experiment such that the planning phase uses only the \kw{past} data to learn trends which can then be applied to the \kw{future} data.
+Thus for our experiment we use data sets that have at least two consecutive releases.
+\begin{itemize}
+\item To generate recommendations for a release $i$, the planner uses releases releases $(i-1)$ and $(i-2)$.
+\item The predictor also uses releases $(i-1)$ and $(i-2)$.
+However, we use SMOTE with re-sampling in order to handle the class imbalance in the data and to prevent the predictor from using the same training data as the planner.
+\end{itemize}

### 2015-05-07 how.tex
Updates from ShareLaTeX

@@
 \usepackage{algorithmicx}
-
 \usepackage[running]{lineno}
@@
 \usepackage{amsmath}  
-\usepackage[caption=false,font=footnotesize]{subfig}
 \DeclareMathOperator*{\argmin}{arg\,min} 
 \DeclareMathOperator*{\argmax}{arg\,max}
+
+\usepackage{color}
+\newcommand{\colorrule}[1]{\begingroup\color{#1}\hrule\endgroup}
 
@@
 mathescape,
-numbers=none,
+numbers=right,
 numberstyle=\scriptsize,
+stepnumber=1,
 numbersep=0.5em,
@@
 % additional keywords
-morekeywords={[3]fastmap, project, furthest, split, WHERE,clusterer, getContours, envied, fWeight, nearestContour, projection, mutate, HERE, knn},
+morekeywords={[3]fastmap, Line,bPruning,clister,train, exemplar,nearestLine,dist,displace,geometry,splitAcross2Points,How,nearest,bPruning,Stats,divide,recurse,weight1,project, furthest, split, WHERE,clusterer, getContours, envied, fWeight, nearestContour, projection, mutate, HERE, knn},
 keywordstyle={[3]\color{Keywords}\bfseries},
@@
 emphstyle={\color{self}\slshape},
+firstnumber=last
 %
@@
 recurses on each half  (stopping when
-one half has less  than $\sqrt{N}$ of the original population). See \fig{code1d} for further details.
+one half has less  than $\sqrt{N}$ of the original population). For more details. \fig{howcode}, line~76,
 
@@
 Further, according to Pythagoras' theorem, $Z$ stands at a distance
-$y = \sqrt{a^2 - x^2}$ from the line $\overline{XY}$. See \fig{code1c} for further details.
+$y = \sqrt{a^2 - x^2}$ from the line $\overline{XY}$. For more details, see  \fig{howcode}, line~59.
 
@@
 A recursive procedure can  find those divisions $n_1,n_2,...$ by (a)~sorting a numeric column,
-then split at $\argmin_i w_i$, then recursing into each half.  See \fig{code1d} for further details
+then split at $\argmin_i w_i$, then recursing into each half.  For more details, see  \fig{howcode}, line~109.
 
@@
 during training, HOW clusters data using the procedure of \fig{where}a,
-then draws lines between the centroids of  clusters $X,Y$ that are nearest
+then draws {\tt Line}s between the centroids of  clusters $X,Y$ that are nearest
 neighbors.
-By convention, we say that the cluster containing $X$ has the  better objective scores. This means we can say that the line is a useful direction for displacing
-data; i.e.  away from $Y$ and towards $X$.
-Hence,  during testing,  HOW use Pythagoras' theorem
-and \fig{where}c to find the  nearest line to every test instance. That test instance is   then displaced towards the better end
-of that line (towards  $X$).
+By convention, we say that the cluster containing $X$ has the  better objective scores. This means we can say that the {\tt Line} is a useful direction for displacing
+data; i.e.  away from $Y$ and towards $X$ (for an implementation of such a {\tt Line} class, see \fig{howcode}, line~1).
+ During testing,  HOW   finds the  nearest {\tt Line} to every test instance. That  test instance is   then displaced towards the better end
+of that line; i.e. towards  $X$ (see \fig{howcode}, line 53).
 
@@
 using the procedure of  \fig{where}d. It then only
-displaces the    best $B$\%  of that sort (while leaving the rest untouched).
+displaces the    best $B$\%  of that sort, while leaving the rest untouched
+(see \fig{howcode}, line 38).
 In  the experiments shown below,  we explore   $B \in \{25,50,100\}\%$.
@@
 of the two closest clusters).  HOW's clusterer divides  data into many   small clusters containing
-$\sqrt{N}$ of the population.
+$\sqrt{N}$ of the population (using the {\tt cluster} function, \fig{howcode}, line 76).
 HOW   limits displacement to  \mbox{$0 \le F \le c$}, where
@@
 characterizes the data in that cluster. It then displaces the
-test data towards that exemplar, as follows.
-Let $Z_j$ be an independent variable within the
-test instance $Z$. If  $X$ be the exemplar found at training time,
+test data towards that exemplar, as shown in \fig{howcode}, line 19. In summary, 
+If  $Z_j$ is an independent variable within the
+test instance $Z$ and  $X$ is the exemplar found at training time,
 then we displace $Z$ as follows:
@@
                 \mathit{after} =\mathrm{predictor}(\mathit{test'})\\ 
-                \mathrm{{\bf return}\;} \mathit{after} /  \mathit{before}
+                \mathrm{{\bf return}\;} \mathit{before} /  \mathit{after}
             \end{array}
@@
   32 & 6 &   & 30 & 9 &   & -2 & 3&$\times$\\
-  41 & 5 &   & 48 & 0 &   & 7 & -5&\times\\
+  41 & 5 &   & 48 & 0 &   & 7 & -5&$\times$\\
 \hline
@@
 
-\section{When Not to Plan: \\the Problem of Poor Predictors}
+\section{When Not to Plan: the Problem of Poor Predictors}
 
@@
 consistent with those achieved by predictors built by Seigmund et al.~\cite{sven12}.)
-
-Turning now to the Jureczko   OO data sets, we found:
-\bi
-\item
-Most   predictors in this domain were far from      perfect;
-\item 
-But several of these predictors could
-be salvaged using some sampling and optimization methods (see the notes on SMOTE and differential evolution, below).
-\ei
-As shown in \fig{j}, we   explore numerous examples of the Jureczko   object-oriented static code data sets: Ant, Camel, Ivy, Jedit,   Log4, Lucene, Poi, Synapse, Velocity, Xalan, Xerces\footnote{Available from the object-oriented defects section of the PROMISE respository openscience.us/repo/defect/ck.}.
-Given access to $V$ released
-versions, we test on version $V$ and train on the available data from earlier releases (as
-shown in \fig{j}, this means that we are training on hundreds to thousands
-of classes and testing on smaller test suites).
-Note the three bottom rows marked with $\times$: these contain predominately
-defective classes (two-thirds, or more) and in such data sets, it is hard to distinguish
-good from bad (since there are so many bad examples).
-
-For the  Jureczko   data,
-the plans generated by HOW advise   how to change static code attributes in order to reduce defects in
-Java classes.  Here,
-performance can be measured in terms of:
-\bi
-\item Probability of detection (a.k.a. ``pd'' or recall) which is the percent of faulty classes in
-the test data detected
-by the {\em predictor}.
-\item Probability of false alarm (a.k.a. ``pf'') which is the percent of non-fault
-classes that are predicted to be defective.
-\ei 
-The ``untuned'' columns of \fig{j} shows RandomForest's learned {\em pd,pf}
-values generated after learning from the training data, then being applied to the test data.
-If we define ``good'' to mean $\mathit{pd}>60 \wedge \mathit{pf} < 40$\%,
-then only two of our data sets ({\em ivy,ant}) are ``good'' enough.
-
-The ``tuned'' columns of \fig{j} show that we can salvage some of the data sets
-using two techniques.
- Pelayo and Dick~\cite{pelayo07} report that defect prediction can be improved via SMOTE~\cite{Chawla2002}; i.e. an over-sampling of minority-class examples.
- Also, Fu et al.~\cite{fu:ase15} report that an optimization method called differential evolution~\cite{storn97}
-applied to defect predictors can quickly explore the tuning
-options of Random Forest to find better settings for the size of the forest, the termination criteria
-for tree generation, etc.
-The rows marked with $\star$ in \fig{j} show data sets whose performance was improved remarkably by these
-techniques. For example, in {\em poi}, the recall increased by 10\% while the false alarm rate dropped by 20\%).
-However,  as might be expected
-the the three bottom rows remain
-unsalvageable.
-
-In summary, while we cannot trust predictors from some of our data sets,
-we can plan ways to reduce defects in {\em jedit, ivy, ant, lucene} and {\em poi}.
-(Aside: note that this tuning used optimization and sub-sampling   on   {\em only} the
-training instances of \fig{j}
-i.e.
-no clues from the test set were ever used in this tuning process.)
-
-\section{Experimental Methods}
-
-blah blah data. algorithms. statistics
-
-\section{Releated Work}
-
-Our prior work in generating policies relied upon a Monte Carlo
-analysis of an underlying model~\cite{me07f}. This approach had three major problems.
-Firstly, enough domain knowledge had to be collected to build that model
-and this can take a long time. For example, in our previous work we used three software process models from
-the Unviersity of Southern California that were initially
-developed and updated for nearly two decades from 1981~\cite{boehm81} to 2000~\cite{boehm00b}.
-
-Secondly, there is the computational cost of running those models.
-While
-
-~\cite{}-- which suffered from the problem of (a)~the effort required to collect the domain knowledge to build
-problem in certifying the underlying model;
- (b)~the computational problem of running that model enough
-times to learn patterns in that data; and (c)~ requrearea used large scale simulations or large
-
-While
-our case studies are defect and runtime reduction, HERE is a general
-purpose algorithm that could be applied to any table of data with at least
-one column whose values can be sorted from ``desired'' to ``undesired''.
-
-{\bf RQ1: Can Instance-based Learning techniques be used to create Planning tools that can better analyse software defect?}
-
-{\bf RQ2: Can lessons learnt from local policy generators be useful for generating solutions that can be used to mitigate defects in software systems?}
-
-{\bf RQ3: Can such instance-based planners be applied to other software engineering paradigms?}
-We check if the proposed instance-based planner is applicable to performance prediction.
-
-\section{Motivating Example}
-\section{Background}
-\section{Instance Based Learning}
-
-Assessing the quality of solutions to a real-world problem can be extremely hard~\cite{menzies2005xomo}.
-In several software engineering applications, researchers have models that can emulate the problem, for instance there is the COCOMO effort model~\cite[p29-57]{boehm2009software}, the COQUALMO defect model~\cite[p254-268]{boehm2009software}, Madachy’s schedule risk model~\cite[p284-291]{boehm2009software}, to name a few.
-Using these models it is possible to examine several scenarios in a short period of time, and this can be done in a reproducible manner.
-However, models aren't always the solution, as we shall see.
-
-There exist several problems where models are hard to obtain, or the input and output are related by complex connections that simply cannot be modeled in a reliable manner, or generation of reliable models take prohibitively long ~\cite{Ludewig2003}.
-Software defect prediction is an excellent example of such a case.
-Models that incorporate all the intricate issues that may lead defects in a product is extremely hard to come by.
-Moreover, it has been shown that models for different regions within the same data can have very different properties \cite{localvsglobal}.
-This makes it extremely hard for one to design planning systems that are capable of mitigating these defects.
-
-An alternative approach would be to make use of an instance based approach, an example of case based reasoning strategy, in place of the conventional model based approach.
-Instance based approaches have been used extensively by the effort estimation community, see~\cite{keung2008analogy, 6600685, walkerden1999empirical, shepperd1997estimating, kocaguneli2010use}.
-
-This approach has been proposed as an alternative to closed form mathematical models or other modeling methods such as regression \cite{keung2008analogy}.
-There are several other reasons for instance based approaches being a useful tool, see~\cite{6600685}.
-As pointed out by~\cite{walkerden1999empirical} it can be used with partial knowledge of the target project at an early stage which could be a very useful tool in preventing software defects.
-Instance based approaches are also rather robust in handling cases with sparse samples \cite{1438374}.
-All these features are desirable and suggest that instance-based approach is a useful adjunct to traditional model based approach.
-
-In this paper the instance based learning principle is used to first cluster the training data and then create contours in the data.
-These contours can then be used by test cases to infer meaningful information in order to improve it.
-The entire process is described in greater detail in the following sections.
-We would like to stress that the purpose of our work is not to promote instance-based planning over model based analytics, rather it is to suggest an alternative when model based approaches cannot be used.
-
-\subsection{Spectral Learning using WHERE}
-The algorithm uses WHERE to recursively cluster the input data to identify subsets in the training data that a test instance can learn from.
-WHERE is a spectral learner which uses the FastMap heuristic to estimate the first principal component.
-It then recursively partitions the data into two halves along the Median point of the projection on the first principal component, terminating when a half has less than $\sqrt{N}$ items.
-
-\subsection{Planning changes using HERE}
-We propose the HERE algorithm as a tool to plan changes in the original test data.
-Figure~\ref{fig:what} highlights the procedure by which HERE operates.
-It begins by creating clusters which are generated using the WHERE algorithm discussed above.
-Following this, a nearest neighbour scheme is applied to identify pairs of nearby clusters.
-A contour is constructed with these clusters at the vertices to characterize the cluster pairs.
-
-The mutation policy works by projecting the test instance onto the contours and identifying the the contour on which the test instance has the largest scalar projection.
-The planner then reflects over the vertices of the chosen contour, identifying the \textit{better} vertex among the two.
-Now, a new instance is generated by \textit{mutating the attributes} of the test instance towards the better vertex and away from the worse vertex.
-This process is repeated for all the test instances that are considered defective by the defect prediction scheme, discussed below.
-
-\subsection{Feature Weighting} \label{fwt}
-The algorithm also allows for a feature weighting and pruning scheme.
-We have employed a simple (and fast) attribute ranking method where the features are sorted based on their ability to find meaningful splits in the dependent class of the data, see ~\cite{hall03}.
-Features that can find splits with the \textit{lesser variance} in the dependent variable are \textit{ranked higher} than features that don't.
-
-We reason that the most informative feature must undergo a larger change as compared to other features.
-Therefore, when feature weighting is employed, the higher ranked features are mutated by a larger extent.
-Additionally, we have also included information pruning.
-Here we mutate only the top X\% of the features in each test instance.
-The remaining features remain unaltered.
-
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{_figs/WHAT-Clusters2.pdf}
-\caption{HERE}
-\label{fig:whatflow}
-\end{figure}
-
-\subsection{Defect Prediction}
-
-To validate the treatments that have been suggested by our planner, we need to have defect predictors that capable of identifying if a certain module may (or may not) have a defect.
-A recent IEEE TSE paper by Lessmann et al.~\cite{lessmann} compared 21 different learners for software defect prediction:
-\bi
-\item
-{\em Statistical classifiers:}
-Linear    discrimin analysis,
-Quadratic discrimin analysis,
-Logistic regression,
-Naive Bayes,
-Bayesian networks,
-Least-angle regression,
-Relevance vector machine,
-
-\item
-{\em Nearest neighbor methods:}
-k-nearest neighbor,
-K-Star
-
-\item
-{\em Neural networks:}
-Multi-Layer Perceptron,
-Radial bias functions,
-
-\item
-{\em Support vector machine-based classifiers:}
-Support vector machine,
-Lagrangian SVM
-Least squares SVM,
-Linear programming,
-Voted perceptron,
-
-\item
-{\em Decision-tree approaches:}
-C4.5,
-CART,
-Alternating DTs
-\item
-{\em Ensemble methods:}
-\textbf{Random Forest},
-Logistic Model Tree.
-\ei
-
-They concluded that Random Forrest was the best method, CART being the worst.
-
-Random Forest is an ensemble learning scheme that constructs a number of decision trees at the training time, for a test instance it outputs the mode of the classes of individual tree.
-It's patent from how random forest operates that the prediction will suffer if there is an imbalance in classes during the training.
-Unfortunately, the data sets explored here do suffer from severe skewness, as highlighted in~\ref{fig:classimb}.
-A study conducted by Pelayo and Dick~\cite{smote2} inspected this issue.
-They showed that the SMOTE technique~\cite{smote} can be used to improve recognition of defect-prone modules.
-
-In short, SMOTE works by under-sampling the majority class and oversampling all the minority classes in the training data.
-We use a similar approach with one minor addition to the original algorithm.
-In our implementation of SMOTE we have introduced an additional step called \textit{resampling}, wherein we ensure that after we do the over/under sampling, the new training data does not have any of the original rows.
-The new training data merely resembles the original data.
-This is done as a precautionary measure, so as not to have HERE and Random Forest train on the same training data.
-%Its worth noting that both HERE and Random Forest require some data to train.
-In order to prevent the two from using the same data to train, we run SMOTE by  \textit{resampling} the classes.
-Re-sampling
 
@@
 
-\begin{figure}[!tb]
-  \renewcommand{\baselinestretch}{0.8}\begin{center}
-{\scriptsize
-\begin{tabular}{l@{~~~}l@{~~~}l@{~~~}l@{~~~}l@{~~~}l@{~~~}l@{~~}}
-  \hline
-  \rowcolor{lightgray}
-  Data & Symbol & Training & Testing & Training Samples& Defective &\% Defective \\\hline
-
-Ant & ant & 1.5, 1.6  &1.7 & 644&124&19.25\\
-
-Camel & cam & 1.2, 1.4 & 1.6 & 1480&361 & 24.39\\
-
-Ivy & ivy & 1.1, 1.4 & 2.0  & 352 & 79 & 22.44\\
-
-Jedit & jed & 4.1, 4.2 & 4.3 & 679 & 127 & 18.70\\
-
-Log4j & log & 1.0, 1.1 & 1.2 & 244 & 71 & 29.09\\
-
-Lucene & luc & 2.0, 2.2 & 2.4 & 442 & 235 & 53.16\\
-
-Poi & poi & 2.0, 2.5 & 3.0 & 699 & 285 & 40.77\\
-
-Synapse & syn & 1.0, 1.1 & 1.2 & 379 & 76 & 20.05\\
-
-Velocity & vel & 1.4, 1.5 & 1.6 & 410& 289 & 70.48\\
-
-Xalan & xal &2.5, 2.6 &2.7 & 1688 & 798 & 47.27\\\hline
-\end{tabular}}
-\end{center}
-\caption{Attributes of the defect datasets}\label{fig:ck}
-\end{figure}
+Turning now to the Jureczko   OO data sets, we found:
+\bi
+\item
+Most   predictors in this domain were far from      perfect;
+\item 
+But several of these predictors could
+be salvaged using some sampling and optimization methods (see the notes on SMOTE and differential evolution, below).
+\ei
+As shown in \fig{j}, we   explore numerous examples of the Jureczko   object-oriented static code data sets: Ant, Camel, Ivy, Jedit,   Log4, Lucene, Poi, Synapse, Velocity, Xalan, Xerces\footnote{Available from the object-oriented defects section of the PROMISE respository openscience.us/repo/defect/ck.}.
+Given access to $V$ released
+versions, we test on version $V$ and train on the available data from earlier releases (as
+shown in \fig{j}, this means that we are training on hundreds to thousands
+of classes and testing on smaller test suites).
+Note the three bottom rows marked with $\times$: these contain predominately
+defective classes (two-thirds, or more) and in such data sets, it is hard to distinguish
+good from bad (since there are so many bad examples).
+
+For the  Jureczko   data,
+the plans generated by HOW advise   how to change static code attributes in order to reduce defects in
+Java classes.  Here,
+performance can be measured using:
+\bi
+\item Probability of detection (a.k.a. ``pd'' or recall):  the percent of faulty classes in
+the test data detected
+by the {\em predictor}.
+\item Probability of false alarm (a.k.a. ``pf''): the percent of non-fault
+classes that are predicted to be defective.
+\ei 
+The ``untuned'' columns of \fig{j} shows RandomForest's learned {\em pd,pf}
+values generated after learning from the training data, then being applied to the test data.
+If we define ``good'' to mean $\mathit{pd}>60 \wedge \mathit{pf} < 40$\%,
+then only two of our data sets ({\em ivy,ant}) are ``good'' enough.
+
+The ``tuned'' columns of \fig{j} show that we can salvage some of the data sets
+using two techniques.
+ Pelayo and Dick~\cite{pelayo07} report that defect prediction can be improved via SMOTE~\cite{Chawla2002}; i.e. an over-sampling of minority-class examples.
+ Also, Fu et al.~\cite{fu:ase15} report that an optimization method called differential evolution~\cite{storn97}
+applied to defect predictors can quickly explore the tuning
+options of Random Forest to find better settings for the size of the forest, the termination criteria
+for tree generation, etc.
+The rows marked with $\star$ in \fig{j} show data sets whose performance was improved remarkably by these
+techniques. For example, in {\em poi}, the recall increased by 10\% while the false alarm rate dropped by 20\%.
+However,  as might be expected
+the data sets in the  three bottom rows remain
+unsalvageable.
+
+In summary, while we cannot trust predictors from some of our defect data sets,
+we can plan ways to reduce defects in {\em jedit, ivy, ant, lucene} and {\em poi}.
+(Aside: note that this tuning used optimization and sub-sampling   on   {\em only} the
+training instances of \fig{j}
+i.e.
+no clues from the test set were ever used in this tuning process.)
+
+\section{Experimental Methods}
+
+To assess HOW, we applied its plans to all the Seigmund data, and the five ``good''
+  Jureczko   data sets.
+  The training and tests used for Jurecko were display in \fig{j}. For Siegmind,
+  25 times, 
+  we randomized the order of the data, trained on the first half, then tested on the second half.
+
+  \fig{ck} shows the attributes in the Jureczko data.
+  The Seigmund data sets are far more varied (every configuration option in the Makefiles
+  for BerkeleyDB-- the Java  and  Windows  versions,  Apache,  SQLite,  LLVM,and x264).
+  \fig{cpm} lists the size of Seigmund attribute sets.
 
@@
 
-\begin{figure}[tbp!]
+%\begin{figure}[tbp!]
 % \subfloat[\label{oracle}]{\includegraphics[width=\linewidth]{{_figs//Oracle}}\\
-\includegraphics[width=\linewidth]{_figs/WHAT}
-\caption{Experimental Rig}
-\label{fig:rig}
+%\includegraphics[width=\linewidth]{_figs/WHAT}
+%\caption{Experimental Rig}
+%\label{fig:rig}
 
@@
 
-\end{figure}
+%\end{figure}
 
 %involves two key components. Firstly, there is the oracle (Random Forest with SMOTE) which is used to make predictions. Then we have the
-\section{Data sets}
-
-The following section describes the experimental rig and the experiments used to measure the performance of HERE on 10 defect data sets and 6 performance prediction data sets.
-
-\subsection{Defect Data Set}
-The data was obtained from the PROMISE repository\footnote{Promise Repository: \url{openscience.us/repo}}.
-For the defect data we investigated 32 releases from 11 open source Java projects defined by the metrics highlighted in figure ~\ref{fig:ck}: \kw{Apache Ant} (1.5 -- 1.7), \kw{Apache Camel} (1.2 -- 1.6), \kw{Apache Ivy} (1.1 -- 2.0), \kw{JEdit} (4.1 -- 4.3), \kw{Apache Log4j} (1.0 -- 1.2), \kw{Apache Lucene} (2.0 -- 2.2), \kw{PBeans} (1.0 and 2.0), \kw{Apache POI} (2.0 -- 3.0), \kw{Apache Synapse} (1.0 -- 1.2), \kw{Apache Velocity} (1.4 -- 1.6), and \kw{Apache Xalan-Java} (2.5 -- 2.7).
-
-Given the empirical nature of the data, it is import to design an experiment such that the planning phase uses only the \kw{past} data to learn trends which can then be applied to the \kw{future} data.
-Thus for our experiment we use data sets that have at least two consecutive releases.
-\begin{itemize}
-\item To generate recommendations for a release $i$, the planner uses releases releases $(i-1)$ and $(i-2)$.
-\item The predictor also uses releases $(i-1)$ and $(i-2)$.
-However, we use SMOTE with re-sampling in order to handle the class imbalance in the data and to prevent the predictor from using the same training data as the planner.
-\end{itemize}
-
-\subsection{Performance Prediction Data Set}
-
-{\bfseries RQ3} asks if the aforementioned method can be expanded to other kinds of data.
-To answer this, we have used the performance prediction data set collected by Siegmund et al.
-for their ICSE '12 paper~\cite{sven12}.
-The data sets have been deployed as a part of the \textsc{SPLConqueror} tool\footnote{\url{fosd.de/SPLConqueror}}.
-This data set contains six examples of real world configurable systems that cover a broad spectrum of scenarios, see figure \ref{fig:cpm} for a summary.
-The systems have different characteristics (lines of code: 40 thousand to 300 thousand; Valid configurations: 192 to about 3.9 million), different implementation languages (C, C++, and Java), different mechanism (conditional compilation, configuration files, and command-line options), and different domains (Web servers, compilers, encoders, and databases).
-The data contains a measurement of all the configurations that are invoked by the benchmarking tool.
-The measurements were conducted 5 to 20 times and the mean of all measurements for each configuration was recoded.
-
-For our experiments, we randomly split the data sets into two equal halves, one for training and the other for testing.
-The planning phase learns configuration settings from the training half and plans for changes in the test half aiming to optimize the performance of the test instances.
-We repeat our measurements 20 to 25 times to overcome measurement bias.
-\section{Experimental Design}
-
-\subsection{The Rig}
-
-The experimental rig for defect prediction is shown in Figure \ref{fig:rig}. It works as follows: 
-\bi
-\item We use an {oracle} (Random Forest + SMOTE) to determine whether a certain test case is defective or not. 
-\item If the oracle suggests that an instance is defective, then we use HERE to apply the recommendations to that test instance. 
-\item The oracle is then used to predict the attributes in the modified instance.
-\item The statistical significance of the changes are verified using the cliffs delta measure described below.
-\ei
-
-For run time optimization, we use a similar rig.
-The oracle is Random Forest, and it predicts for run times of specific configuration.
-HERE is used to generate a recommended configuration to reduce the run times.
-The run time is measured by the oracle.
-The reduction of run times are expressed as fractions of the original (also referred to as baseline) run time.
-
-Note that we report the performance scores as a comparison between the oracle's prediction \textit{before} and that \textit{after}.
-We refrain from using the \textit{actual} defects in the data sets to perform the same comparison.
-This is because the oracle is limited in its ability to predict defects, there are instances that are inherently misclassified.
-These misclassifications however are not affected by the planner.
-Therefore, by comparing the defect counts before and after applying the planner and doing so with a the same oracle would give us an accurate albeit relativistic measure of performance.
-
-\subsection{Performance Assessment}
-
-In order to assess the performance of the planner for the defect data set, we use the Cliffs Delta score to measure the probability that the number of bugs in test data before applying the planner is larger than after doing so.
+
+We  assess the performance of HOW  by measuring the gain, given by $\frac{Before}{After}$. Since
+our goal is to reduce all our objective scores (defects and runtimes of the compiled systems).
+the gain takes a value larger than 1 if the run times have been reduced, a value of 1 if there is no change, and a value less than 1 if run times have increased after applying the recommended changes.
+
+Second, we summarizes all our runs using some visualizations and some statistical tests.
+In those statistical tests, in  order to avoid any parametric bias,
+we use the Cliffs Delta score to measure the probability that the number of bugs in test data before applying the planner is larger than after doing so.
 In other words, we use the delta score to measure the ability of the planner to effective reduce the number of defects.
@@
 
-In the context of our application, the $\delta$ attains a value of -1 if the number of defects after applying the treatments has reduced to zero.
-On the other hand $\delta$ will be 0 if there is no change at all.
-Thus, most of the values reported will lie between 0 and -1.
-It needs to be highlighted that although $\delta$ can lie between -1 and +1, the in our application the range is limited to -1 and 0.
-And this is because we only apply the treatments to defective cases.
+A $\delta$ of  0 implies no change at all.
 
 For the performance prediction data set on the other hand, Cliff's delta measure is not directly applicable.
-We therefore assess the performance by measuring the gain, given by $\frac{Before}{After}$.
-The gain takes a value larger than 1 if the run times have been reduced, a value of 1 if there is no change, and a value less than 1 if run times have increased after applying the recommended changes.
 
@@
 We make use of the Scott-Knott procedure, recommended by Mittas \& Angelis in their 2013 IEEE TSE paper~\cite{sk}, to compute the ranks.
-It works as follows: A list of treatments \textit{l} is sorted by the Median score.
-The list \textit{l} is then split into sub-lists m, n in order to maximize the expected value of the differences in the observed performance before and after division.
+It works as follows.
+A list of treatments \textit{l} is sorted by their median score.
+The list \textit{l} is then split into sub-lists $m, n$ in order to maximize the expected value of the differences in the observed performance before and after division.
 A statistical hypothesis test \textit{H} is applied on the splits \textit{m, n} to check if they are statistically different.

### 2015-05-07 related.tex
Updates from ShareLaTeX

@@
 of the simulation for training, and the remaining data for testing.
-\ee
+\ei
 In the two case studies of this paper, the Jureczko object-oriented defect data comes from software

### 2015-05-07 how.tex
Updates from ShareLaTeX

@@
                 \mathit{after} =\mathrm{predictor}(\mathit{test'})\\ 
-                \mathrm{{\bf return}\;} \mathit{before} /  \mathit{after}
+                \mathrm{{\bf return}\;} \mathit{before},\mathit{after}
             \end{array}
@@
 
-\subsection{How to Assess ``HOW''}
+\subsection{How to Assess ``HOW''}\label{sect:assess}
 In the experiments shown below,  HOW comments  on how to reduce
@@
 then (2)~apply the { predictor} to the altered data {\em test'};
-then (3)~return the performance delta.
+then (3)~return data on the {\em before,after} predictions.
 
@@
         xalan    & 2.4, 2.5, 2.6      & 2411      & 2.7          & 909          & 99  \\\hline
-        \multicolumn{6}{c}{~}\\
-        \multicolumn{6}{c}{~}\\
-        \multicolumn{6}{c}{~}\\
 
@@
 \hline 
-  \multicolumn{5}{c}{~}    &  & -1 & -4& 25th\\
-\multicolumn{6}{r|}{the percentiles of the changes:}    &   5 & 0 & 50th\\
- \multicolumn{5}{c}{~}             & & 10 & 3 & 75th\\
 \end{tabular}
@@
 
-\section{Experimental Methods}
-
+\section{Results}
+
+\subsection{Data}
 To assess HOW, we applied its plans to all the Seigmund data, and the five ``good''
-  Jureczko   data sets.
-  The training and tests used for Jurecko were display in \fig{j}. For Siegmind,
+  Jureczko   data sets {\em jedit, ivy, ant, lucene} and {\em poi}.
+  The training and tests used for Jurecko were display in \fig{j}. For these data
+  sets, training was managed by a Random Forest (tuned in the SMOTED training data using differential
+  evolution). \fig{ck} shows the attributes in the Jureczko data.
+
+  The Seigmund data sets are far more varied than the Jurecko data (since they contain every configuration option in the Makefiles
+  for BerkeleyDB-- the Java  and  Windows  versions,  Apache,  SQLite,  LLVM,and x264).
+  \fig{cpm} lists the size of Seigmund attribute sets. For the Siegmind data, 
   25 times, 
-  we randomized the order of the data, trained on the first half, then tested on the second half.
-
-  \fig{ck} shows the attributes in the Jureczko data.
-  The Seigmund data sets are far more varied (every configuration option in the Makefiles
-  for BerkeleyDB-- the Java  and  Windows  versions,  Apache,  SQLite,  LLVM,and x264).
-  \fig{cpm} lists the size of Seigmund attribute sets.
+  we randomized the order of the data, trained on the first half (using
+  Random Forest Regressor), then tested on the second half.
 
@@
 
-\caption{Attributes of the Performance Prediction data sets}\label{fig:cpm}
+\caption{Seigmund data sets: details on the data sets}\label{fig:cpm}
 \end{figure}
@@
 
-We  assess the performance of HOW  by measuring the gain, given by $\frac{Before}{After}$. Since
-our goal is to reduce all our objective scores (defects and runtimes of the compiled systems).
-the gain takes a value larger than 1 if the run times have been reduced, a value of 1 if there is no change, and a value less than 1 if run times have increased after applying the recommended changes.
-
-Second, we summarizes all our runs using some visualizations and some statistical tests.
-In those statistical tests, in  order to avoid any parametric bias,
-we use the Cliffs Delta score to measure the probability that the number of bugs in test data before applying the planner is larger than after doing so.
-In other words, we use the delta score to measure the ability of the planner to effective reduce the number of defects.
-Given the untreated test instance labeled \textit{Before} of length \textit{M} and the treated instances labeled \textit{After}, the delta score is obtained as follows:
+\begin{figure}[tbp]
+\centering
+\includegraphics[width=\linewidth]{_figs/histograms.pdf}
+\caption{Jureczko object-oriented defect data sets. 
+Comparisons of predictions of defects in the Jureczko data sets before and after planning.}
+\label{fig:bugs}
+\end{figure}
+
+\subsection{Visualisations of Changes}
+
+In this section, we show some sample results. In the next section, we conduct a statistical
+analysis of all   results.
+
+\fig{bugs} shows the effects of planning on the five good Jureczko data sets. Note that:
+\bi
+\item
+The number of defects predicted in the ``after'' set is always less than ``before'';
+\item
+The reduction can be quite large: e.g. see the over 50\% reduction in the {\em ant} data set.
+\ei
+
+ \begin{figure*}[htbp!]
+\centering
+\begin{minipage}{0.30\linewidth}
+\includegraphics[width=\linewidth]{_figs/Apache.pdf}
+\end{minipage}
+\begin{minipage}{0.30\linewidth}
+\includegraphics[width=\linewidth]{_figs/BDBJ.pdf}
+\end{minipage}
+\begin{minipage}{0.30\linewidth}
+\includegraphics[width=\linewidth]{_figs/BDBC.pdf}
+\end{minipage}
+
+\begin{minipage}{0.30\linewidth}
+\includegraphics[width=\linewidth]{_figs/LLVM.pdf}
+\end{minipage}
+\begin{minipage}{0.30\linewidth}
+\includegraphics[width=\linewidth]{_figs/SQL.pdf}
+\end{minipage}
+\begin{minipage}{0.30\linewidth}
+\includegraphics[width=\linewidth]{_figs/X264.pdf}
+\end{minipage}
+\caption{Run time optimization using HERE .
+Blue curve represents a mutation probability of 0.75 with feature weighting and information pruning; Red curve represents a mutation probability of 0.25 with feature weighting, but no information pruning; Black curve represents the raw test data used as baseline for the comparison.}
+\label{fig:pp}
+\end{figure*}
+
+\fig{pp} shows the effects of planning on the Seigmund data sets. The black, red %XXX
+curves show the
+runtimes as predicted in the test sets before/after our planning.  While some of the differences
+are small (eg. LLVM and SQL), some of the others are very large indeed (e.g. the Apache and   BD*).
+
+This visual samples of HOW's planning results look promising-- but they need to be confirmed by a
+ more rigorous statistical analysis.
+
+\subsection{Statistical Analysis}
+
+HOW's performance can be adjusted in numerous ways:
+\bi
+\item The $F$ variable controls the size of the displacement;
+\item The $B$ variable controls how many of the attributes are displaced;
+\item The $w_i$ weight inside our distance calcylation controls how important are each variable in computing
+     the space between instances. A standard default is $w_i=1$ but this can be adjusted via
+     the {\tt featureWeighting} procedure of \fig{howcode}.
+\ei
+
+To understand how much (if at all) these variables change the planning results, 
+this study ranks methods using the Scott-Knott
+procedure recommended by Mittas \& Angelis in their 2013
+IEEE TSE paper~\cite{mittas13}.  This method
+sorts a list of $l$ treatments with $ls$ measurements by their median
+score. It then
+splits $l$ into sub-lists $m,n$ in order to maximize the expected value of
+ differences  in the observed performances
+before and after divisions. E.g. for lists $l,m,n$ of size $ls,ms,ns$ where $l=m\cup n$:
+ $E(\Delta)=\frac{ms}{ls}abs(m.\mu - l.\mu)^2 + \frac{ns}{ls}abs(n.\mu - l.\mu)^2$.
+Scott-Knott then applies some statistical hypothesis test $H$ to check
+if $m,n$ are significantly different. If so, Scott-Knott then recurses on each division.
+
+For this study, our hypothesis test $H$ was a
+conjunction of the A12 effect size test of  a
+non-parametric bootstrap sampling; i.e. our
+Scott-Knott divided the data if {\em both}
+bootstrapping and an effect size test agreed that
+the division was statistically significant (99\%
+confidence) and not a ``small'' effect ($A12 \ge
+0.6$).
+For a justification of the use of non-parametric
+bootstrapping, see Efron \&
+Tibshirani~\cite[p220-223]{efron93}.
+For a justification of the use of effect size tests
+see Shepperd\&MacDonell~\cite{shepperd12a}; Kampenes~\cite{kampenes07}; and
+Kocaguenli et al.~\cite{kocharm13}. These researchers
+warn that even if an
+hypothesis test declares two populations to be
+``significantly'' different, then that result is
+misleading if the ``effect size'' is very small.
+Hence, to assess 
+the performance differences 
+we first must rule out small effects.
+This test was recently 
+endorsed by Arcuri and Briand
+at ICSE'11~\cite{arcuri11}.
+
+To get an overall count of the   in  order to avoid any parametric bias,
+we use the Cliffs Delta score to measure the probability that performance has been changed
+by the planner.   Given the untreated test data labeled \textit{Before} of length \textit{M} and the treated instances labeled \textit{After}, the delta score is obtained as follows:
 \begin{equation}
@@
 
-A $\delta$ of  0 implies no change at all.
-
-For the performance prediction data set on the other hand, Cliff's delta measure is not directly applicable.
-
-In addition to the above, we rank the different various of the planning scheme to identify the best approach.
-We make use of the Scott-Knott procedure, recommended by Mittas \& Angelis in their 2013 IEEE TSE paper~\cite{sk}, to compute the ranks.
-It works as follows.
-A list of treatments \textit{l} is sorted by their median score.
-The list \textit{l} is then split into sub-lists $m, n$ in order to maximize the expected value of the differences in the observed performance before and after division.
-A statistical hypothesis test \textit{H} is applied on the splits \textit{m, n} to check if they are statistically different.
-If so, Skott-Knott then recurses on each division.
-
-The research conducted by Shepperd and MacDonell~\cite{shepperd12a}, Kampenes~\cite{kampenes07} and Kocaguenli et al.~\cite{}, highlighted that an ``effect size'' in lieu of a mere hypothesis test is required in order to verfiy if two populations are ``significly'' different.
-An ICSE'11 paper by Arcuri~\cite{} endorsed the use of Vargha and Delaney's A12 effect size for reporting results in software engineering.
-Thus, for hypothesis testing H in Skott-Knott, we use the A12 test and a non-parametric bootstrap sampling~\cite{}.
-
-\section{Experimental Results}
-
-\subsection{Defect Data Set}
-This sections explores \textbf{RQ2: Can lessons learnt from local policy generators be useful for generating solutions that can be used to mitigate defects in software systems?}
-
-Figure \ref{fig:bugs} compares the number of defects before and after applying "HERE".
-The graphs represent the median scores, with the inter-quartile ranges represented by the error bars.
-The results seem to show that in all data sets under consideration, the number of defects have reduced, some more so than others.
-Large differences were notice in certain data sets namely, \textit{ant}, \textit{camel}, \textit{jedit}, \textit{poi,} and \textit{xalan}, on close examination it was noticed that these data sets had comparatively large training data, which translates to more samples for the planner to learn from.
-
-In addition to this, to study the statistical significance of the changes, the results were statistically verified using the Skott-Knott procedure.
-In order to do this we computed the Cliff's Delta score.
-As highlighted previously, HERE is applied only for test instances that are considered defective by the oracle.
-Using \eq{cliffs} we can expect to see the following results:
-
-\bi
-\item $\lt$ 0 if defects have been suppressed.
-\item = 0 if no change has been made.
-\item $\gt$ 0 if new defects have been introduced.
-This is not applicable to our case because we only apply HERE to defective cases; either the defects are suppressed or they remain unaltered, introduction of new defects is not possible.
-\ei
-
-\begin{figure}[tbp]
-\centering
-\includegraphics[width=\linewidth]{_figs/histograms.pdf}
-\caption{Comparison of defects before and after planning.}
-\label{fig:bugs}
-\end{figure}
-With this in mind, it is easy to note that lower cliffs delta score translates to better the performance.
-
-The results are tabulated in figure \ref{tab:ant}. For the sake of completeness, we have introduced three basic configurations in HERE: 
-\bi
-\item \textit{Extent of Mutation:} Denotes the extent by which a test instant is \textit{mutated} towards the best cluster in the contour.
-It is a fraction that lies between 0 and 1.
-The baseline study requires no change be made, and thus extent of mutation is set to zero.
-\item \textit{Feature Weighting:} The importance of feature weighting has already been discussed in section \ref{fwt}.
-It is a fraction that lies between 0 and 1, with 0 being the least important and 1 the most important feature.
-The extent of mutation is multiplied by this fraction to determine how much a specific feature changes by.
-Generally, we would like to make the largest change to the most crucial feature.
-\item \textit{Information Pruning:} In addition to the weighting the features, we explored the possibility of mutating only the most important features.
-The feature weights are already known to us, we sort the features in descending order of their weights and mutate only the first X\%.
-\ei
-It is to be noted however that
+A $\delta$ of  0 implies no change at all and, according to Romano et al.~\cite{romano06}, a value less
+that 14]7\% is a ``small'' (i.e. negliable) effect.
 
@@
 
-\begin{figure*}[htbp!]
-\centering
-\begin{minipage}{0.30\linewidth}
-\includegraphics[width=\linewidth]{_figs/Apache.pdf}
-\end{minipage}
-\begin{minipage}{0.30\linewidth}
-\includegraphics[width=\linewidth]{_figs/BDBJ.pdf}
-\end{minipage}
-\begin{minipage}{0.30\linewidth}
-\includegraphics[width=\linewidth]{_figs/BDBC.pdf}
-\end{minipage}
-
-\begin{minipage}{0.30\linewidth}
-\includegraphics[width=\linewidth]{_figs/LLVM.pdf}
-\end{minipage}
-\begin{minipage}{0.30\linewidth}
-\includegraphics[width=\linewidth]{_figs/SQL.pdf}
-\end{minipage}
-\begin{minipage}{0.30\linewidth}
-\includegraphics[width=\linewidth]{_figs/X264.pdf}
-\end{minipage}
-\caption{Run time optimization using HERE.
-Blue curve represents a mutation probability of 0.75 with feature weighting and information pruning; Red curve represents a mutation probability of 0.25 with feature weighting, but no information pruning; Black curve represents the raw test data used as baseline for the comparison.}
-\label{fig:pp}
-\end{figure*}
-
 \subsection{Performance Prediction Data set}
@@
 \section{Threats to validity}
-\input{related}
+
+As with any empirical study, biases can affect the final results. Therefore, any
+conclusions made from this work must be considered with the following issues in
+mind.
+
+{\em 1. Sampling bias} threatens any data mining experiment; i.e., what matters
+there may not be true here. For example, the data sets used here comes from two sources
+(Seigmund et al. and Jureczko et al.) and any biases in their selection procedures
+threaten the validity of these results. 
+That said,
+the best we can do is define our methods and publicize our data and code so that other researchers can
+try to repeat our results and, perhaps, point out a previously unknown bias
+in our analysis. Hopefully, other researchers will emulate our methods in
+order to repeat, refute, or improve our results.
+
+{\em 2. Learner bias: } For building the defect predictors in this study, we elected
+to use  Random Forest  .
+We chose Random Forest based on its reputation for having the better  performance of 
+21 other learners for defect prediction~\cite{lessmann}.
+Data mining is a
+large and active field and any single study can only use a small
+subset of the known classification algorithms.
+
+{\em 3. Evaluation bias:} The issue was discussed above in \tion{assess} where
+we asserted that plans can be assessed via predictors-- with the all important
+priviso that the predictors are not performing poorly.
+
+%%\footnote{LL: It seems to me that $privacy$ in LACE approach could be compromised in the case of extremes if I had some knowledge of the parties.
+Consider a case where you know that a bunch of startups and Microsoft contributed to a private cache.
+Even with the random perturbation in MORPH, it will be REALLY obvious which defect data came from Windows vs.
+all of the others because Windows will have LOC orders of magnitude greater than anyone else, right?}
+
+%XXXX everytime it says LACE, do you mean LACE2
+
+%{\em 4. Comparison bias:}
+%There are many privacy algorithms~\cite{Fung2010survey} and it would be difficult to 
+%compare their performances (especially with various ways to measure privacy).
+%In this work, we use LACE.
+
+%{\em 5. Other Evaluation Bias:}
+%The utility of  obfuscated data can be measured
+%semantically (where the workload is unknown) or empirically (known workload
+%e.g., classification or aggregate query answering). In this work we measure
+%utility empirically for defect prediction only.
+
+%\input{related}
 

### 2015-05-07 code.tex
Updates from ShareLaTeX

@@
       x,y = y,x      # x must have best score
-    i.c = dist(x,y) 
+    i.x, i.y, i.c = x, y, dist(x,y) 
     i.obj = len(x) 

### 2015-05-08 code.tex
Updates from ShareLaTeX

--- 2015-05-07 code.tex
@@
 ~\hrule~
-\begin{minipage}{.45\linewidth}
-\small
-
-~\\
-
-{\bf The Line class (as described in \tion{mm}:}
-Note that this is the primary data structure of HOW.
-Training data is converted into a set of {\tt Line}s,
-each of which is defined by a $X,Y$ pair, where $X$
-has better scores than $Y$.
+\begin{minipage}[t]{.45\linewidth}
+\scriptsize\vspace{1mm}
+{\bf The Line class (as described in \tion{mm}):}
 
@@
 class Line:
-  "Lines connect a worse cluster Y to a better one X"
+  """The central data structure of HOW. Training data 
+  is converted into a set of Lines, each of which is 
+  defined by a 'X,Y' pair, where 'X'
+  has better scores than 'Y'."""
   all   = []    # where to store all the lines
+  weights=[]    # (weight,feature) pairs, sorted
   using = []    # what columns to use
@@
       x,y = y,x      # x must have best score
-    i.c = dist(x,y) 
-    i.obj = len(x) 
+    i.x, i.y, i.c = x, y, dist(x,y) 
     Line.all += [i]  # remember this line
@@
   def displace(i,z):
-    for j,(xj,zj) in enumerate(zip(x,z)):
-      if j in Line.using and not j == i.obj:  
-        z[j] = zj + Line.F*( xj - zj)
+    for j in Line.using:
+      z[j] = z[j] + Line.F*(x[j] - z[j])
     return z
@@
 {\bf Main loop, of the  HOW  instance-based planner:}
-Testing data is {\em displaced}
-towards   the $X$ point of the nearest {\tt Line}.
+
 \begin{python}[left]
-def HOW(training, testing):
+def HOW(training, testing, b = Line.b):
+  """ Testing data is displaced towards
+  the X point of the nearest Line."""
   def train(data):
-    Line.using = bPruning(data)
-    clusters   = cluster(data,len(data)):
+    Line.weights= weightedFeatures(data)
+    b           = int(len(Line.weights)*B/100)
+    Lines.using = Line.weights[:b])
+    clusters    = [k for k in 
+                   leafs(cluster(data,len(data)))]
     for cluster in clusters:
@@
 
-   def bPruning(data,  b = Line.B):
-    "Return the indexes of the 'b' best columns" 
-    enough  = int(len(weights)*b/100)
-    return featureWeighting(data)[:enough]
-
   def nearestLine(z):
@@
     return out
-
-  #---------------------------------
-  # begin main code for  'HOW'
+  # ---- begin main code for  'HOW' ---------------
   train(training)
@@
 
-{\bf Code for geometry (as described in \fig{where}c):}
+{\bf Misc utilities; e.g. code for geometry (as described in \fig{where}c):}
 
 \begin{python}[left]
-def dist(x,y):
-   "See Aha et al. reference [22]. XXX"
-
 def geometry(x, y, c, z): 
@@
   return x,y
+
+def dist(x,y):
+   tmp = sum(w*(x[j] - y[j])**2 for w,j in Line.using) 
+   return tmp**0.5 / len(Line.using)**2
 
@@
   return out
+
+def leafs(data):
+  leaf = True
+  for more in data.leafs:
+    if more:
+       leaf = False
+       for one in leafs(more):
+         yield one
+  if leaf: 
+    yield data
 \end{python}
- \end{minipage}~~~~~~~~~\begin{minipage}{.45\linewidth} 
-\small
-
-~\\
-
+ \end{minipage}~~~~~~~~~\begin{minipage}[t]{.45\linewidth} 
+\scriptsize\vspace{1mm}
 {\bf Clustering (as described in \fig{where}a):}
@@
 def cluster(data, n,lvl=100):
+
   def splitAcross2Points(data): 
@@
 
-  # --------------------------------------
-  # begin main code for  'cluster'
+  # --- begin main code for  'cluster' --------
   if lvl < 1: 
@@
      leafs += cluster(right,n,  lvl - 1) 
-  data.has = dict(x=x,y=y,
-                 l=left,r=right,
-                 leafs=leafs)
+  date.leafs = leafs
   return leafs
-
 \end{python}
@@
 \begin{python}[right]
-def featureWeighting(cols):
+def weightedFeatures(cols):
   "Returns col indexes, sorted by their weight."
+
   class Stats():  
@@
       map(i.__add__,inits)
-    def sd(i) :  return (max(0.0,i.m2)/(i.n - 1))**0.5
+
+    def sd(i) :  
+      return (max(0.0,i.m2)/(i.n - 1))**0.5
+
     def __add__(i,x):
@@
       i.m2 += delta*(x - i.mu)
+
     def __sub__(i,x):
@@
 
-  #---------------------------------
-  # begin main code for  'featureWeighting'
+  # ---- begin main code for 'featureWeighting' -----
   obj = len(cols[0]) - 1 
-  return map(lambda k:k[1],
-             sorted(weight1(col,i,obj) 
+  return sorted(weight1(col,i,obj) 
                     for i,col in enumerate(cols)

### 2015-05-08 how.tex
Updates from ShareLaTeX

@@
 % additional keywords
-morekeywords={[3]fastmap, Line,bPruning,clister,train, exemplar,nearestLine,dist,displace,geometry,splitAcross2Points,How,nearest,bPruning,Stats,divide,recurse,weight1,project, furthest, split, WHERE,clusterer, getContours, envied, fWeight, nearestContour, projection, mutate, HERE, knn},
+morekeywords={[3]fastmap, Line,bPruning,clister,train,leafs,weightedFeatures, exemplar,nearestLine,dist,displace,geometry,splitAcross2Points,leaves,How,nearest,bPruning,Stats,divide,recurse,weight1,project, furthest, split, WHERE,clusterer, getContours, envied, fWeight, nearestContour, projection, mutate, HERE, knn},
 keywordstyle={[3]\color{Keywords}\bfseries},
@@
 It sorts independent variables
- according to how well they can reduce the variance
+ according to how well they can reduce the variability
 of a  numeric objective.
@@
 \includegraphics[width=\linewidth]{_figs/BDBC.pdf}
-\end{minipage}
+\end{minipage}\\[0.25cm]
 
@@
 we asserted that plans can be assessed via predictors-- with the all important
-priviso that the predictors are not performing poorly.
+proviso that the planning should {\em not} be attempted if the predictors
+are performing poorly.
 

### 2015-05-10 how.tex
Updates from ShareLaTeX

@@
 \bi
-\item Instead of just accepting  {\em predictions} on how many 
+\item 
+Instead of just accepting  {\em predictions} on how many 
  software defects
@@
 \ei
-In these two points, we say that a ``plan'' is a  set of proposed changes in order to better achieve some goal. 
-Generating {\em plans} is a  very different task the standard
-data mining tasks of {\em predicting} some discrete or numeric class.
-Predictors
-and classifiers only tell us what {\em is} while planners 
-  tell us {\em what to change}. For the kind of business user
-discussed above, planners are the preferred to mere prediction systems
-since, as one gruff user once shouted at us:
+In this paper, we say   a ``plan'' is a  set of changes
+proposed  in order to better achieve some goal. 
+Specifically, for every $Z$  that requests a plan $\delta$, we want
+to adjust the attributes $Z_j$ as follows:
+\begin{equation}\label{eq:one}
+Z_j = Z_j + \delta_j
+\end{equation}
+The usual way such plans are generated in the SE literature
+is via some search-based method. Recently, we have made  some progress
+in this area with the  GALE optimizer~\cite{krall14}. 
+Like other search-based algorithms,
+ GALE executes by proposing multiple $\delta$s
+ (one for each generation in an evolutionary program).
+ In practice, GALE makes
+ extensive changes to initial sample of project data
+ (perhaps 
+100s to 100,000s of mutations). Each of these mutations
+is reassessed using some domain model.
+GALE runs faster than standard search-based SE tools~\cite{deb00a,zit02} since
+it explores  the principle components
+ of the project data (rather than   the raw data). Since it explores
+ a smaller space, it also
+ terminates much faster than standard optimiser; e.g. for one large model, 4 minutes versus 7 hours~\cite{krall14}.
+
+When presented to some  users, the GALE approach was challenged by
+two business users.   Note that the following issues
+challenge not just GALE, but also  any  optimization algorithm  that makes
+extensive use of mutation  and domain models such as
+NSGA-II, NSGA-III, SPEA2, IBEA, particle swarm optimization, MOEA/D, etc.~\cite{deb00a,zit02,zit04,%
+deb14,Cui2005a,zhang07:TEC}.
+
+One  user asked:
 \begin{quote}
-{\em ``Don't tell me what \underline{is};
-tell me what to \underline{change}.''}
+ISSUE~\#1: {\em ``What if I only want the minimum useful change, not
+the maximum possible?''}
 \end{quote}
-Generating plans is also differed to the recommender systems. 
-discussed by Robillard and Walker~\cite{rob14}.  Recommendor systems
-in software engineering
-are less {\em directive} and more    {\em collaborative} than plan generators:
-\bi
-\item
-Directive systems (such as those discussed in this paper) tell developers exactly what to do;
-e.g. ``use these settings in a Makefile''. 
-\item
-On the other hand, the collaborative systems discussed by Robillard and Walker
-are more suggestive guides that
-help (e.g.) programmers focus on very small sets
-with  very large libraries of code of documentation.
-\ei
-This paper presents HOW, a novel planner for learning actionable analytics.
-In the experiments shown below, we see that HOW's plans can
-significantly reduce the expected
+Note here that this business user is asking for solutions  that do not require extensive 
+changes to their current  approaches.
+
+Later in that discussion, another business user asked:
+\begin{quote}
+ISSUE~\#2: {\em ``But what if I do not have a domain model of my business?''}
+\end{quote}
+This also is a legitimate issue.
+Building and certifying a model  can  takes  long time, especially in software engineering. For  example, in previous work~\cite{me07f} we used models
+developed by Boehm's group at the University of Southern California.
+Some of those models took decades to develop and mature (from 1981~\cite{boehm81} to 2000~\cite{boehm00b}). 
+Also, even when there is an existing model, they can require
+constant  maintenance lest they become out-dated. Elsewhere, we have described our
+extensions to the USC models to enable reasoning about agile software developments. 
+It took many months to implement and certify those extensions~\cite{me09i,me09j}.
+The problem of model maintenance is another
+motivation to look for alternate methods that can be automatically updated whenever new data arrives.
+Further, sometimes  it is easier to access instances of a model's behaviour than the model
+itself. For example, in prior work with Martin  Feather from the Jet Propulsion 
+Laboratory~\cite{fea02a},  our research partner could not share a
+propriety model from within the NASA firewalls. However, they could share 
+logs of the input/output of that model.
+
+Every challenge is an opportunity to explore  a new approach.
+If we  restrict $\delta$ to very small changes, then any 
+predictive data miner applied to the original data could also be used
+to assessed the mutated data (proviso: we have to guarantee that
+the mutations do not leave the space of examples present in the original data).
+Note that this approach addresses ISSUE~\#1 since it only uses minimal changes.
+It also addresses  ISSUE~\#2 since, when lack a domain model, we automatically
+create one (via data mining).
+
+This paper presents HOW, a novel planner for learning actionable analytics via
+minimal changes. 
+In the experiments shown below, we see that HOW's plans  can significantly
+reduce the  expected
 value of:
@@
 \ei
-In summary, this paper makes five contributions that are significantly different to
-prior work:
+This paper makes five contributions:
 \be
-\item The HOW  instance-based planner of this paper has not been presented before.
+\item The HOW  instance-based planner (which has not been presented before).
 \item The experiments of this paper show that HOW planner is useful for real-world tasks;
@@
 \ee
-The rest of this paper is structured as follows.
-HOW's instance-based reasoning  makes its conclusions by
-studying the space of examples. As discussed in \tion{mm},
-this is a very different approach to
-{\em model-based planners} that use the model
-as sub-routine within a Monte Carlo simulation~\cite{me07f} or the evolutionary 
-programming methods explored by the search-based software
-engineering community~\cite{krall14,harman12dec}.
-
-\section{HOW: Motivation and Methods}\label{sec:mm}
-
- \subsection{Motivation: Why ``HOW''?}
-HOW was inspired by two     business issues raised about the  GALE optimizer~\cite{krall14}. 
-A well-known effect in machine learning (and, in computer vision
-and compression~\cite{levina04}) is that the $n$ dimensions of a data set can be represented by a  much
-lower-dimensional approximation. GALE finds those $m \ll n$ dimensions then mutates examples
-towards the better end of each dimension $m_i$. Since it explores $m \ll n$ dimensions,
-GALE terminates much faster than standard optimiser (e.g. for one large model, 4 minutes versus 7 hours~\cite{krall14}).
-Better yet, GALE's rapdily generated  solutions are competitive (or better) than those found by 
-slower optimizers.
-
-When GALE executes, it searches for better examples of data
- by (a)~inputting an initial population of data; then (b)~making
- extensive mutation to that data. In practice, GALE makes
-100s to 100,000s of mutations. Each of these mutations
-is reassessed using some domain model.
-For certain users,this approach raises some issues.  One such user commented:
-\begin{quote}
-ISSUE~\#1: {\em ``What if I only want the minimum useful change, not
-the maximum possible?''}
-\end{quote}
-Note here that this business user is asking for solutions  that do not require extensive 
-changes to their current  approaches.
-
-Later in that discussion, another business user asked:
-\begin{quote}
-ISSUE~\#2: {\em ``But what if I do not have a domain model of my business?''}
-\end{quote}
-This also is a legitimate issue.
-Building and certifying a model  can  takes  long time, especially in software engineering. For  example, in previous work~\cite{me07f} we used models
-developed by Boehm's group at the University of Southern California.
-Some of those models took decades to develop and mature (from 1981~\cite{boehm81} to 2000~\cite{boehm00b}).
-
-Also, even when there is an existing model, they can require
-constant  maintenance lest they become out-dated. Elsewhere, we have described our
-extensions to the USC models to enable reasoning about agile software developments. 
-It took many months to implement and certify those extensions~\cite{me09i,me09j}.
-The problem of model maintenance is another
-motivation to look for alternate methods that can be automatically updated whenever new data arrives.
-
-Further, sometimes  it is easier to access instances of a model's behaviour than the model
-itself. For example, in prior work with Martin  Feather from the Jet Propulsion 
-Laboratory~\cite{fea02a},  our research partner could not share a
-propriety model from within the NASA firewalls. However, they could share 
-logs of the input/output of that model.
-
-These two issues are not just problems for GALE, but also for every
-other model-based optimization algorithm  that makes
-extensive use of mutation  and domain models such as
-NSGA-II, NSGA-III, SPEA2, IBEA, PSO, DE, MOEA/D, etc.~\cite{deb00a,zit02,zit04,%
-deb14,Cui2005a,storn97,zhang07:TEC}. Accordingly, this paper seeks
-an optimization methods that make minimal changes to instances,
-while avoiding the problem of models that are missing, slow
-to build, hard to maintain, or difficult to access.
-
-\subsection{Methods: How to Build ``HOW''?}
-
+
+\section{How to Build ``HOW''?}\label{sec:mm}
+
+\subsection{Design}
 A general model for {\em predictors} is as follows. 
@@
 \[Z_j =  Z_j + F*(X_j - Z_j)\]
-Here, $F$ is the  magnitude controller, discussed above.
+Here, $F$ is the  magnitude controller, discussed above. Note that this
+this equations satisfies our definition of a ``plan'' as offered in
+\eq{one} in the {\em Introduction}
+
 The experiments of this work showed that different kinds of data require
@@
 \bi
+\item
+For the Jureczko data, the objective score
+is a boolean that is true if defects have been noted
+for that class. 
+For this kind of data with discrete objectives,
+the data, 
+has very little to  differentiate between the objective scores
+so we just set the exemplar to  
+an instance synthesized from the median values of the instances
+in that cluster.
 \item
@@
 with  best objective score.
-\item
-For the Jureczko data, the objective score
-is a boolean that is true if defects have been noted
-for that class. 
-For this kind of data with discrete objectives,
-the data, 
-has less differentiation between the objective scores
-so we set the exemplar to  
-an instance synthesized from the median values of the instances
-in that cluster.
 \ei
@@
 
-\subsection{How to Assess ``HOW''}\label{sect:assess}
+\subsection{Assessment}\label{sect:assess}
 In the experiments shown below,  HOW comments  on how to reduce
@@
 
-\section{When Not to Plan: the Problem of Poor Predictors}
+\subsection{When Not to Plan: the Problem of Poor Predictors}
 
@@
 
-\section{Results}
+\section{Experiments}
 
@@
 
-\begin{figure*}[htbp!]
+\begin{figure}[htbp!]
 
 \noindent\begin{minipage}{0.5\textwidth}
-  {\scriptsize \textbf{Ant}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
+  {\scriptsize \textbf{Ant}\\[0.1cm]}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~~}c@{}r}}
       \arrayrulecolor{darkgray}
-      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 & 0.75 &    -0.63  &  0.08 & \quart{2}{7}{5}{144} \\
-  1 & 0.75, weighting &    -0.6  &  0.2 & \quart{0}{16}{8}{144} \\
-\hline  2 & 0.5, weighting &    -0.42  &  0.11 & \quart{17}{10}{23}{144} \\
-  2 & 0.5 &    -0.42  &  0.11 & \quart{19}{9}{23}{144} \\
-  2 & 0.75, weighting, Prune=50\% &    -0.4  &  0.11 & \quart{20}{9}{25}{144} \\
-\hline  3 & 0.25 &    -0.28  &  0.09 & \quart{31}{7}{35}{144} \\
-  3 & 0.25, weighting &    -0.28  &  0.08 & \quart{31}{7}{35}{144} \\
-\hline  4 & 0.5, weighting, Prune=50\% &    -0.25  &  0.06 & \quart{35}{5}{38}{144} \\
-\hline  5 & 0.25, weighting, Prune=50\% &    -0.19  &  0.05 & \quart{41}{4}{43}{144} \\
-\hline  6 & Baseline &    -0.11  &  0.03 & \quart{47}{2}{49}{144} \\
+      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} && \textbf{Bugs}\\
+  1 &  0.75-weight &    0.71  &  0.19 & \quart{0}{25}{10}{49} & 62\\
+  1 &         0.75 &    0.72  &  0.14 & \quart{6}{19}{12}{49} & 64\\
+\hline  2 &          0.5 &    0.86  &  0.08 & \quart{25}{11}{31}{49} & 77 \\
+  2 &   0.5-weight &    0.88  &  0.14 & \quart{20}{19}{33}{49} & 77\\
+\hline  3 & 0.5-weight-B=50\% &    0.91  &  0.08 & \quart{32}{11}{37}{49} & 80\\
+  3 & 0.75-weight-B=50\% &    0.92  &  0.09 & \quart{31}{12}{39}{49} & 82\\
+  3 &  0.25-weight &    0.92  &  0.04 & \quart{36}{5}{39}{49} & 81\\
+\hline  4 &         0.25 &    0.93  &  0.05 & \quart{37}{7}{40}{49} & 83\\
+  4 & 0.75-weight-B=25\% &    0.94  &  0.09 & \quart{36}{12}{41}{49} & 82\\
+\hline  5 & 0.25-weight-B=50\% &    0.97  &  0.03 & \quart{44}{4}{45}{49} & 86\\
+  5 & 0.5-weight-B=25\% &    0.98  &  0.06 & \quart{40}{8}{47}{49} & 86 \\
+\hline  6 & 0.25-weight-B=25\% &    0.99  &  0.01 & \quart{48}{1}{48}{49} & 87\\
+\hline  7 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 90\\
 \hline \end{tabular}}
-\end{minipage}
+\end{minipage}\\[0.1cm]
+
 \noindent\begin{minipage}{0.5\textwidth}
   \flushleft
-  {\scriptsize \textbf{Camel}\\}
-{\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
+  {\scriptsize \textbf{Ivy}\\[0.1cm]}
+{\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c@{}r}}
 \arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &  0.75, weighting, Prune=50\% &    -0.41  &  0.1 & \quart{2}{14}{9}{205} \\
-  1 &  0.75 &    -0.41  &  0.23 & \quart{1}{32}{9}{205} \\
-  1 &  0.75, weighting &    -0.39  &  0.16 & \quart{0}{22}{12}{205} \\
-\hline  2 &  0.5, weighting, Prune=50\% &    -0.27  &  0.09 & \quart{19}{12}{29}{205} \\
-  2 &  0.5 &    -0.26  &  0.12 & \quart{20}{17}{30}{205} \\
-  2 &  0.5, weighting &    -0.24  &  0.09 & \quart{24}{13}{33}{205} \\
-\hline  3 &  0.25, weighting, Prune=50\% &    -0.2  &  0.05 & \quart{36}{7}{38}{205} \\
-  3 &  0.25, weighting &    -0.19  &  0.07 & \quart{36}{9}{40}{205} \\
-  3 &  0.25 &    -0.17  &  0.06 & \quart{37}{8}{43}{205} \\
-\hline  4 &  Baseline &    -0.15  &  0.06 & \quart{41}{8}{45}{205} \\
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & & \textbf{Bugs}\\
+  1 &  0.75-weight &    0.75  &  0.18 & \quart{0}{29}{8}{49} & 50\\
+  1 &         0.75 &    0.79  &  0.12 & \quart{8}{20}{14}{49} & 53\\
+\hline  2 &          0.5 &    0.84  &  0.1 & \quart{18}{16}{23}{49} & 56\\
+  2 &   0.5-weight &    0.84  &  0.08 & \quart{14}{14}{23}{49} & 56\\
+  2 & 0.75-weight-B=50\% &    0.84  &  0.09 & \quart{18}{15}{23}{49} & 56 \\
+\hline  3 & 0.5-weight-B=50\% &    0.91  &  0.05 & \quart{29}{9}{34}{49} & 61\\
+\hline  4 & 0.25-weight-B=50\% &    0.96  &  0.01 & \quart{43}{1}{43}{49} & 64\\
+  4 & 0.75-weight-B=25\% &    0.96  &  0.05 & \quart{39}{9}{43}{49} & 65\\
+  4 &         0.25 &    0.97  &  0.01 & \quart{43}{1}{44}{49} & 65\\
+  4 &  0.25-weight &    0.97  &  0.05 & \quart{39}{9}{44}{49} & 65 \\
+  4 & 0.5-weight-B=25\% &    0.97  &  0.03 & \quart{43}{5}{44}{49} & 65 \\
+\hline  5 & 0.25-weight-B=25\% &    0.99  &  0.01 & \quart{48}{1}{48}{49} & 66\\
+\hline  
+6 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 67\\
 \hline \end{tabular}}
-\end{minipage}
+\end{minipage}\\[0.1cm]
 
@@
   \flushleft
-  {\scriptsize \textbf{Ivy}\\[-0.05cm]}
-{\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
+  {\scriptsize \textbf{Jedit}\\[0.1cm]}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c@{}r}}
 \arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &     0.75 &    -0.57  &  0.17 & \quart{0}{16}{6}{163} \\
-  1 &   0.75, weighting &    -0.55  &  0.11 & \quart{3}{11}{8}{163} \\
-\hline  2 &   0.75, weighting, Prune=50\% &    -0.38  &  0.11 & \quart{19}{11}{25}{163} \\
-  2 &    0.5, weighting &    -0.36  &  0.12 & \quart{23}{12}{27}{163} \\
-  2 &   0.5 &    -0.33  &  0.11 & \quart{25}{11}{30}{163} \\
-\hline  3 &   0.5, weighting, Prune=50\% &    -0.27  &  0.08 & \quart{30}{8}{36}{163} \\
-\hline  4 &   0.25, weighting &    -0.2  &  0.07 & \quart{41}{7}{43}{163} \\
-  4 &     0.25 &    -0.16  &  0.04 & \quart{43}{4}{47}{163} \\
-  4 &     Baseline &    -0.16  &  0.0 & \quart{47}{0}{47}{163} \\
-\hline  5 &   0.25, weighting, Prune=50\% &    -0.15  &  0.04 & \quart{45}{4}{48}{163} \\
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & & \textbf{Bugs}\\\hline
+  1 &         0.75 &    0.64  &  0.28 & \quart{0}{27}{14}{49} & 110\\
+\hline  2 &  0.75-weight &    0.76  &  0.21 & \quart{13}{21}{26}{49}& 131 \\
+  2 &   0.5-weight &    0.76  &  0.16 & \quart{20}{16}{26}{49} & 130\\
+  2 &          0.5 &    0.79  &  0.17 & \quart{19}{17}{29}{49} & 137\\
+\hline  3 & 0.75-weight-B=50\% &    0.85  &  0.12 & \quart{30}{12}{35}{49} & 146\\
+  3 &  0.25-weight &    0.87  &  0.07 & \quart{34}{7}{37}{49} & 152\\
+\hline  4 &         0.25 &    0.93  &  0.09 & \quart{37}{9}{43}{49} & 161\\
+  4 & 0.5-weight-B=50\% &    0.93  &  0.05 & \quart{41}{5}{43}{49} & 162\\
+\hline  5 & 0.25-weight-B=50\% &    0.97  &  0.03 & \quart{45}{3}{47}{49} & 167\\
+  5 & 0.75-weight-B=25\% &    0.97  &  0.02 & \quart{46}{2}{47}{49} & 168\\
+\hline  6 & 0.5-weight-B=25\% &    0.98  &  0.02 & \quart{47}{2}{48}{49} & 170\\
+  6 & 0.25-weight-B=25\% &    0.98  &  0.01 & \quart{48}{1}{48}{49} & 171\\
+\hline  7 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 175\\
 \hline \end{tabular}}
-\end{minipage}
+\end{minipage}\\[0.1cm]
+
 \noindent\begin{minipage}{0.5\textwidth}
   \flushleft
-  {\scriptsize \textbf{Jedit}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
+  {\scriptsize \textbf{Lucene}\\[0.1cm]}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c@{}r}}
 \arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &  0.75, weighting, Prune=50\% &    -0.41  &  0.18 & \quart{0}{20}{8}{172} \\
-  1 &  0.75 &    -0.35  &  0.26 & \quart{0}{30}{15}{172} \\
-\hline  2 &  0.75, weighting &    -0.25  &  0.17 & \quart{16}{20}{26}{172} \\
-  2 &  0.5, weighting, Prune=50\% &    -0.21  &  0.1 & \quart{23}{11}{31}{172} \\
-\hline  3 &   0.5 &    -0.17  &  0.08 & \quart{32}{9}{36}{172} \\
-  3 &  0.5, weighting &    -0.14  &  0.09 & \quart{31}{10}{39}{172} \\
-\hline  4 &  0.25, weighting, Prune=50\% &    -0.12  &  0.06 & \quart{39}{7}{41}{172} \\
-\hline  5 &  0.25 &    -0.08  &  0.05 & \quart{43}{5}{46}{172} \\
-  5 &  0.25, weighting &    -0.08  &  0.06 & \quart{43}{6}{46}{172} \\
-\hline  6 &  Baseline &    -0.06  &  0.01 & \quart{47}{1}{48}{172} \\
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & & \textbf{Bugs}\\
+  1 &  0.75-weight &    0.66  &  0.2 & \quart{0}{21}{13}{49} & 97 \\
+\hline  2 & 0.75-weight-B=50\% &    0.7  &  0.1 & \quart{14}{10}{17}{49} & 103 \\
+\hline  3 &         0.75 &    0.77  &  0.3 & \quart{9}{33}{24}{49} & 113\\
+  3 & 0.75-weight-B=25\% &    0.8  &  0.09 & \quart{21}{10}{28}{49} & 117\\
+  3 &   0.5-weight &    0.81  &  0.09 & \quart{26}{9}{29}{49} & 119\\
+  3 &          0.5 &    0.84  &  0.1 & \quart{26}{10}{32}{49} & 123\\
+\hline  4 & 0.5-weight-B=50\% &    0.88  &  0.07 & \quart{34}{8}{36}{49} & 128\\
+  4 & 0.25-weight-B=25\% &    0.89  &  0.07 & \quart{36}{8}{38}{49} & 130 \\
+  4 &  0.25-weight &    0.92  &  0.04 & \quart{39}{4}{41}{49} & 133 \\
+  4 &         0.25 &    0.93  &  0.07 & \quart{36}{8}{42}{49} & 136 \\
+\hline  5 & 0.25-weight-B=50\% &    0.95  &  0.04 & \quart{42}{4}{44}{49} & 139 \\
+  5 & 0.5-weight-B=25\% &    0.96  &  0.03 & \quart{43}{3}{45}{49} &141 \\
+\hline  6 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 146\\
 \hline \end{tabular}}
-\end{minipage}
+\end{minipage}\\[0.1cm]
 
@@
   \flushleft
-  {\scriptsize \textbf{Log4j}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
+  {\scriptsize \textbf{Poi}\\[0.1cm]}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c@{}r}}
       \arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &  0.75, weighting, Prune=50\% &    -0.19  &  0.13 & \quart{0}{28}{15}{273} \\
-\hline  2 &  0.75 &    -0.13  &  0.06 & \quart{23}{13}{28}{273} \\
-  2 &  0.5, weighting, Prune=50\% &    -0.13  &  0.05 & \quart{23}{11}{28}{273} \\
-  2 &  0.75, weighting &    -0.12  &  0.1 & \quart{15}{21}{30}{273} \\
-\hline  3 &  0.5, weighting &    -0.1  &  0.03 & \quart{28}{6}{34}{273} \\
-\hline  4 &   0.5 &    -0.1  &  0.07 & \quart{28}{15}{34}{273} \\
-  4 &  0.25 &    -0.09  &  0.04 & \quart{34}{9}{36}{273} \\
-  4 &  0.25, weighting, Prune=50\% &    -0.09  &  0.04 & \quart{34}{9}{36}{273} \\
-  4 &  0.25, weighting &    -0.06  &  0.04 & \quart{34}{9}{43}{273} \\
-\hline  5 &  Baseline &    -0.06  &  0.03 & \quart{43}{6}{43}{273} \\
-\hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Lucene}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &  0.75, weighting &    -0.15  &  0.09 & \quart{0}{29}{9}{393} \\
-  1 &  0.75 &    -0.13  &  0.09 & \quart{0}{29}{16}{393} \\
-  1 &  0.75, weighting, Prune=50\% &    -0.12  &  0.08 & \quart{6}{27}{19}{393} \\
-\hline  2 &  Baseline &    -0.1  &  0.03 & \quart{26}{10}{26}{393} \\
-  2 &  0.5, weighting, Prune=50\% &    -0.1  &  0.03 & \quart{23}{10}{26}{393} \\
-\hline  3 &  0.5, weighting &    -0.08  &  0.06 & \quart{23}{20}{33}{393} \\
-  3 &  0.25, weighting, Prune=50\% &    -0.07  &  0.03 & \quart{33}{10}{36}{393} \\
-  3 &  0.5 &    -0.07  &  0.05 & \quart{29}{17}{36}{393} \\
-\hline  4 &  0.25, weighting &    -0.04  &  0.04 & \quart{36}{13}{46}{393} \\
-  4 &  0.25 &    -0.04  &  0.02 & \quart{39}{7}{46}{393} \\
-\hline \end{tabular}}
-\end{minipage}
-
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Poi}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-      \arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 & 0.75, weighting &    -0.45  &  0.1 & \quart{6}{10}{11}{162} \\
-  1 &  0.75 &    -0.44  &  0.23 & \quart{0}{23}{12}{162} \\
-\hline  2 & 0.5, weighting &    -0.32  &  0.23 & \quart{12}{24}{24}{162} \\
-  2 & 0.5 &    -0.26  &  0.23 & \quart{18}{24}{31}{162} \\
-  2 & 0.75, weighting, Prune=50\% &    -0.25  &  0.19 & \quart{17}{20}{32}{162} \\
-\hline  3 & 0.5, weighting, Prune=50\% &    -0.19  &  0.09 & \quart{34}{9}{38}{162} \\
-  3 &  0.25 &    -0.19  &  0.11 & \quart{32}{11}{38}{162} \\
-  3 & 0.25, weighting &    -0.17  &  0.14 & \quart{30}{14}{40}{162} \\
-\hline  4 & 0.25, weighting, Prune=50\% &    -0.12  &  0.09 & \quart{40}{9}{45}{162} \\
-\hline  5 &  Baseline &    -0.09  &  0.03 & \quart{46}{3}{48}{162} \\
-\hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Synapse}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 & 0.75, weighting &    -0.56  &  0.2 & \quart{7}{18}{11}{148} \\
-  1 & 0.75 &    -0.48  &  0.34 & \quart{0}{29}{18}{148} \\
-\hline  2 & 0.5 &    -0.4  &  0.27 & \quart{14}{24}{25}{148} \\
-  2 & 0.5, weighting &    -0.37  &  0.17 & \quart{21}{15}{28}{148} \\
-\hline  3 & 0.25 &    -0.23  &  0.16 & \quart{31}{14}{40}{148} \\
-  3 & 0.25, weighting &    -0.23  &  0.1 & \quart{38}{9}{40}{148} \\
-  3 & 0.75, weighting, Prune=50\% &    -0.19  &  0.08 & \quart{40}{7}{43}{148} \\
-\hline  4 & 0.25, weighting, Prune=50\% &    -0.17  &  0.08 & \quart{42}{7}{45}{148} \\
-  4 & Baseline &    -0.15  &  0.0 & \quart{47}{0}{47}{148} \\
-  4 & 0.5, weighting, Prune=50\% &    -0.15  &  0.11 & \quart{40}{9}{47}{148} \\
-\hline \end{tabular}}
-\end{minipage}
-
-\noindent\begin{minipage}{0.50\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Velocity}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 & 0.75, weighting &    -0.19  &  0.22 & \quart{1}{34}{21}{207} \\
-  1 & 0.75, weighting, Prune=50\% &    -0.15  &  0.13 & \quart{14}{20}{28}{207} \\
-  1 & 0.75 &    -0.14  &  0.23 & \quart{0}{35}{29}{207} \\
-\hline  2 & 0.5 &    -0.13  &  0.11 & \quart{23}{17}{31}{207} \\
-\hline  3 & 0.5, weighting &    -0.1  &  0.08 & \quart{29}{13}{35}{207} \\
-  3 & 0.5, weighting, Prune=50\% &    -0.07  &  0.07 & \quart{32}{11}{40}{207} \\
-\hline  4 & Baseline &    -0.05  &  0.04 & \quart{43}{6}{43}{207} \\
-  4 & 0.25, weighting &    -0.05  &  0.03 & \quart{40}{5}{43}{207} \\
-  4 & 0.25 &    -0.04  &  0.02 & \quart{43}{3}{45}{207} \\
-  4 & 0.25, weighting, Prune=50\% &    -0.01  &  0.04 & \quart{43}{6}{49}{207} \\
-\hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.50\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Xalan}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 & 0.75 &    -0.36  &  0.12 & \quart{0}{16}{9}{198} \\
-  1 & 0.75, weighting &    -0.3  &  0.17 & \quart{4}{23}{18}{198} \\
-  1 &    0.5 &    -0.3  &  0.12 & \quart{9}{17}{18}{198} \\
-\hline  2 & 0.5, weighting &    -0.28  &  0.09 & \quart{16}{13}{20}{198} \\
-\hline  3 & 0.25, weighting &    -0.23  &  0.1 & \quart{20}{14}{27}{198} \\
-  3 & 0.25 &    -0.23  &  0.12 & \quart{20}{17}{27}{198} \\
-\hline  4 & 0.25, weighting, Prune=50\% &    -0.14  &  0.07 & \quart{36}{9}{40}{198} \\
-  4 & 0.75, weighting, Prune=50\% &    -0.14  &  0.07 & \quart{33}{10}{40}{198} \\
-  4 & 0.5, weighting, Prune=50\% &    -0.12  &  0.06 & \quart{37}{8}{43}{198} \\
-\hline  5 & Baseline &    -0.08  &  0.02 & \quart{47}{2}{48}{198} \\
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & & \textbf{Bugs}\\
+  1 &  0.75-weight &    0.72  &  0.26 & \quart{0}{29}{18}{49} & 173\\
+  1 &         0.75 &    0.74  &  0.18 & \quart{12}{20}{20}{49} & 178\\
+\hline  2 & 0.75-weight-B=50\% &    0.79  &  0.15 & \quart{14}{17}{26}{49} & 190\\
+  2 &          0.5 &    0.81  &  0.15 & \quart{22}{17}{28}{49} & 195\\
+  2 &   0.5-weight &    0.81  &  0.14 & \quart{21}{16}{28}{49} & 195\\
+\hline  3 & 0.5-weight-B=50\% &    0.9  &  0.11 & \quart{30}{13}{38}{49} & 217\\
+  3 &         0.25 &    0.91  &  0.07 & \quart{35}{8}{39}{49} & 219\\
+  3 &  0.25-weight &    0.91  &  0.05 & \quart{36}{6}{39}{49} & 219\\
+\hline  4 & 0.75-weight-B=25\% &    0.94  &  0.05 & \quart{39}{6}{43}{49} & 226\\
+  4 & 0.25-weight-B=50\% &    0.94  &  0.06 & \quart{39}{7}{43}{49} & 226\\
+\hline  5 & 0.25-weight-B=25\% &    0.96  &  0.03 & \quart{44}{3}{45}{49} & 231\\
+  5 & 0.5-weight-B=25\% &    0.96  &  0.03 & \quart{44}{3}{45}{49} & 231\\
+\hline  6 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 240 \\
 \hline \end{tabular}}
@@
 \label{tab:ant}
-\end{figure*}
+\end{figure}
 
@@
       \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 & 75, weighting, Prune=25\% &    0.77  &  0.05 & \quart{0}{9}{3}{49} \\
-  1 &   75 &    0.79  &  0.08 & \quart{1}{16}{7}{49} \\
-\hline  2 & 75, weighting &    0.85  &  0.07 & \quart{9}{14}{19}{49} \\
-  2 & 50, weighting, Prune=25\% &    0.85  &  0.04 & \quart{15}{8}{19}{49} \\
-  2 &  50 &    0.85  &  0.05 & \quart{17}{10}{19}{49} \\
-\hline  3 & 50, weighting &    0.91  &  0.05 & \quart{25}{10}{31}{49} \\
-  3 &  25 &    0.92  &  0.04 & \quart{29}{8}{33}{49} \\
-  3 & 25, weighting, Prune=25\% &    0.93  &  0.02 & \quart{33}{4}{35}{49} \\
-\hline  4 & 25, weighting &    0.96  &  0.03 & \quart{37}{6}{41}{49} \\
-\hline  5 & baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-\hline \end{tabular}}
+  1 & 0.75-weight-B=25\% &    0.77  &  0.05 & \quart{0}{14}{5}{74}\\
+  1 &  0.75 &    0.79  &  0.08 & \quart{2}{24}{11}{74}\\
+\hline  2 & 0.75-weight &    0.85  &  0.07 & \quart{14}{21}{29}{74}\\
+  2 & Apache\_50\_w\_iP(25) &    0.85  &  0.04 & \quart{23}{12}{29}{74}\\
+  2 &  Apache\_50 &    0.85  &  0.05 & \quart{26}{15}{29}{74}\\
+\hline  3 & Apache\_50\_w &    0.91  &  0.05 & \quart{38}{15}{47}{74}\\
+\hline  4 &  Apache\_25 &    0.92  &  0.04 & \quart{44}{12}{50}{74}\\
+  4 & Apache\_25\_w\_iP(25) &    0.93  &  0.02 & \quart{50}{6}{53}{74}\\
+\hline  5 & Apache\_25\_w &    0.96  &  0.03 & \quart{56}{9}{62}{74}\\
+\hline  6 & Apache\_baseline &    1.0  &  0.0 & \quart{74}{0}{74}{74}\\\hline \end{tabular}}
 \end{minipage}

### 2015-05-10 old/culled.tex
Updates from ShareLaTeX

--- 2015-05-01 manuscript.tex
@@
- \documentclass[conference]{IEEEtran}
-\usepackage{subfig}
-\usepackage{wrapfig}
- \usepackage{amsmath}
- \usepackage{url}
- \usepackage{pifont}
- \usepackage{times}
-\usepackage{rotating}
-%\usepackage{balance} 
-\usepackage{color, colortbl}
-\usepackage{graphicx}
-\usepackage{algorithmicx}
-\usepackage{program}
-\usepackage{cite}
-\usepackage{alltt}
-\newcommand{\eq}[1]{Equation~\ref{eq:#1}}
-\newcommand{\bi}{\begin{itemize}}
-\newcommand{\ei}{\end{itemize}}
-\newcommand{\be}{\begin{enumerate}}
-\newcommand{\ee}{\end{enumerate}}
-\newcommand{\tion}[1]{\textsection\ref{sec:#1}}
-\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
-\definecolor{lightgray}{gray}{0.975}
-\usepackage{fancyvrb}
-\usepackage{stfloats}
-\usepackage{multirow}
-\usepackage{listings}
-\usepackage{amsmath} 
-\DeclareMathOperator*{\argmin}{arg\,min} 
-\DeclareMathOperator*{\argmax}{arg\,max}
+\subsection{Performance Prediction Data Set}
 
-\definecolor{darkgreen}{rgb}{0,0.3,0}
+{\bfseries RQ3} asks if the aforementioned method can be expanded to other kinds of data.
+To answer this, we have used the performance prediction data set collected by Siegmund et al.
+for their ICSE '12 paper~\cite{sven12}.
+The data sets have been deployed as a part of the \textsc{SPLConqueror} tool\footnote{\url{fosd.de/SPLConqueror}}.
+This data set contains six examples of real world configurable systems that cover a broad spectrum of scenarios, see figure \ref{fig:cpm} for a summary.
+The systems have different characteristics (lines of code: 40 thousand to 300 thousand; Valid configurations: 192 to about 3.9 million), different implementation languages (C, C++, and Java), different mechanism (conditional compilation, configuration files, and command-line options), and different domains (Web servers, compilers, encoders, and databases).
+The data contains a measurement of all the configurations that are invoked by the benchmarking tool.
+The measurements were conducted 5 to 20 times and the mean of all measurements for each configuration was recoded.
 
-\usepackage[table]{xcolor}
-\definecolor{Gray}{rgb}{0.88,1,1}
-\definecolor{Gray}{gray}{0.85}
-\definecolor{Blue}{RGB}{0,29,193}
-\newcommand{\G}{\cellcolor{green}}
-\newcommand{\Y}{\cellcolor{yellow}}
+For our experiments, we randomly split the data sets into two equal halves, one for training and the other for testing.
+The planning phase learns configuration settings from the training half and plans for changes in the test half aiming to optimize the performance of the test instances.
+We repeat our measurements 20 to 25 times to overcome measurement bias.
+\section{Experimental Design}
 
-\definecolor{MyDarkBlue}{rgb}{0,0.08,0.45} 
-\newenvironment{changed}{\par\color{MyDarkBlue}}{\par}
+\subsection{The Rig}
 
-\newcommand{\ADD}[1]{\textcolor{MyDarkBlue}{{\bf #1}}}
-\newcommand{\addit}[1]{\begin{changed}\input{#1}\end{changed}}
+The experimental rig for defect prediction is shown in Figure \ref{fig:rig}. It works as follows: 
+\bi
+\item We use an {oracle} (Random Forest + SMOTE) to determine whether a certain test case is defective or not. 
+\item If the oracle suggests that an instance is defective, then we use HERE to apply the recommendations to that test instance. 
+\item The oracle is then used to predict the attributes in the modified instance.
+\item The statistical significance of the changes are verified using the cliffs delta measure described below.
+\ei
 
-\usepackage{color}
-\usepackage{listings}
-\usepackage{setspace}
+For run time optimization, we use a similar rig.
+The oracle is Random Forest, and it predicts for run times of specific configuration.
+HERE is used to generate a recommended configuration to reduce the run times.
+The run time is measured by the oracle.
+The reduction of run times are expressed as fractions of the original (also referred to as baseline) run time.
 
-\definecolor{Gray}{gray}{0.9}
-\newcommand{\kw}[1]{\textit{#1}}
-\newcommand{\quart}[4]{\begin{picture}(75,6)
-  {\color{black}\put(#3,3){\circle*{2.5}}\put(#1,3){\line(1,0){#2}}}\end{picture}}
-% New Commands
+Note that we report the performance scores as a comparison between the oracle's prediction \textit{before} and that \textit{after}.
+We refrain from using the \textit{actual} defects in the data sets to perform the same comparison.
+This is because the oracle is limited in its ability to predict defects, there are instances that are inherently misclassified.
+These misclassifications however are not affected by the planner.
+Therefore, by comparing the defect counts before and after applying the planner and doing so with a the same oracle would give us an accurate albeit relativistic measure of performance.
 
-\definecolor{Code}{rgb}{0,0,0}
-\definecolor{Decorators}{rgb}{0.5,0.5,0.5}
-\definecolor{Numbers}{rgb}{0.5,0,0}
-\definecolor{MatchingBrackets}{rgb}{0.25,0.5,0.5}
-\definecolor{Keywords}{rgb}{0,0,1}
-\definecolor{self}{rgb}{0,0,0}
-\definecolor{Strings}{rgb}{0,0.63,0}
-\definecolor{Comments}{rgb}{0,0.63,1}
-\definecolor{Backquotes}{rgb}{0,0,0}
-\definecolor{Classname}{rgb}{0,0,0}
-\definecolor{FunctionName}{rgb}{0,0,0}
-\definecolor{Operators}{rgb}{0,0,0}
-\definecolor{Background}{rgb}{1,1,1}
+In should be noted  that the standard 10-way cross-validation
+procedure used  in data mining does not necessarily demonstrate G-causality.  In a N-way cross-val experiments, the data is divided into $N$ bins.  
+$N-1$ bins are used for learning and the results are tested
+on the  remaining bin.
+This is repeated $N$ times, each time using a different bin for the test set.
+This approach can not be used to demonstrate causality since, if the initial data is collected
+over (say) $N$ months, then it is possible that the test set contains observations collected
+{\em before}   items seen in the training set.
 
-\lstnewenvironment{python}[1][]{
-\lstset{
-mathescape,
-numbers=#1,
-numberstyle=\footnotesize,
-numbersep=0.5em,
-xleftmargin=0em,
-framextopmargin=2em,
-framexbottommargin=2em,
-showspaces=false,
-showtabs=false,
-showstringspaces=false,
-tabsize=2,
-% Basic
-basicstyle=\ttfamily\small\setstretch{0.8},
-backgroundcolor=\color{Background},
-language=Python,
-% Comments
-commentstyle=\color{Comments}\slshape,
-% Strings
-stringstyle=\color{Strings},
-morecomment=[s][\color{Strings}]{"""}{"""},
-morecomment=[s][\color{Strings}]{'''}{'''},
-% keywords
-morekeywords={[1]import,from,class,def,for,while,if,is,in,elif,else,not,and,or,print,break,continue,return,True,False,None,access,as,,del,except,exec,finally,global,import,lambda,pass,print,raise,try,assert, dot, norm, zip, sorted},
-keywordstyle={[1]\color{Code}\bfseries},
-% additional keywords
-morekeywords={[3]fastmap, project, furthest, split, WHERE,clusterer, getContours, envied, fWeight, nearestContour, projection, mutate, HERE, knn},
-keywordstyle={[3]\color{Keywords}\bfseries},
-morekeywords={[2]@invari},
-keywordstyle={[2]\color{Decorators}\slshape},
-emph={self},
-emphstyle={\color{self}\slshape},
-%
-}}{}
+Jiang et al.~\cite{me11f} and Lumpe et al.~\cite{me11f} propose a modification to cross-validation.
+which lets a researcher
+demonstrate G-causal defect effects in software engineering.
+In this modification, we  divide project data  into $N$ bins, each of with contain data collected at similar t
 
-\author{
-% You can go ahead and credit any number of authors here,
-% e.g. one 'row of three' or two rows (consisting of one row of three
-% and a second row of one, two or three).
-%
-% The command \alignauthor (no curly braces needed) should
-% precede each author name, affiliation/snail-mail address and
-% e-mail address. Additionally, tag each line of
-% affiliation/address with \affaddr, and tag the
-% e-mail address with \email.
-%
-% 1st. author
-Rahul Krishna, Tim Menzies, Xipeng Shen\\
-       \affaddr{Computer Science, NcState, USA}\\
-       \{i.m.ralk, tim.menzies, xipengshen\}@gmail.com
-% 3rd. author
- % use '\and' if you need 'another row' of author names
-% 4th. author
-\and
- Andrian Marcus\\
-       \affaddr{Computer Science, UtDallas, USA}\\
-       {amarcus@utdallas.edu} }
+imes.
+They then sort those bins (on the collection date) and use bins $i,j$ to build models that
+are applied to bin  $k$ where 
+$i<j<k$. Note that this procedure ensures that we are building theories on data seen
+before the test data.
 
-\begin{document}
-  \title{Learning Actionable Analytics 
- (with Applications for Reducing Defects and Reducing Runtimes)}
+We adapt the work of Jiang,Lumpe et al.  as follows.
 
-  % make the title area
-  \maketitle
-  \pagestyle{plain}
-
-  \begin{abstract}
- As business users demand more insightful
- analytics, data scientists need to change
- their tools. Instead of merely predicting 
- some result, they also need tools that generate ``policy advice'';
- i.e. suggestions on  how to change values in order to
- improve on some predicted value.
-
- This paper proposes one such policy
- generator. ``HOW'' is a near-linear-time
- tool for proposing changes to independent
- variables in order to improve on 
- the predictions of the dependent variables. Unlike other approaches
- for learning optimizations to software does not require
- an underlying of the domain (rather, HOW automatically
- learns that model as part of its operation).
-
- This paper uses  HOW to learn methods
- to reduce defects and decrease program runtime.
- For the test data used in this paper,
- we have observed that the improvements generated by HERE can reduce
- defect prediction and runtimes by up to
- 50\% of their original values.
-  \end{abstract}
-  \begin{IEEEkeywords}
-Instance-based reasoning, defect prediction, random forest, optimization.
-  \end{IEEEkeywords}
-
-\section{Introduction}
-In the $21^{st}$ century, it is now impossible to manually browse all
-the available software defect data.  For example, as of April 2015,
-Mozilla Firefox has over a million bug reports on software projects.  While it is
-now possible to automatically analyze such data with data miners, at
-some stage a group of business users will have to convene to {\em
-  interpret the results} (e.g., to decide if it is wise to deploy the
-results as a defect reduction method within an organization).
-
-These business  users are now demanding that data mining tools
-be augmented with tools to support  business-level
-interpretation of that data. For example,
-at a  panel on software analytics at ICSE'12,
-industrial practitioners lamented the state of the art in data mining
-and software engineering~\cite{menzies12a}. Panelists commented that
-``prediction is all well and good, but what about decision
-making?''. That is, these panelists are more interested in the interpretations
-that follow the mining, rather than just  the mining. For example:
-\bi
-\item Instead of just accepting  {\em predictions} on how many 
- software defects
-to expect,  business users now demand {\em policies} that
-reduce the likelihood of those defects;
-\item Instead of just accepting {\em predictions} on the runtime
-time of their software, business users might now demand
-{\em policies} that reduce that runtime.
-\ei
-In order to satisfy the demands of this new kind of business user, we  explore the generation of {\em policies} in the context
-of software analytics. Such {\em policies} are recommendations of what
-to change in order to better achieve some goal. 
-Note that such {\em policy generation} is very different to the standard
-data mining tasks of prediction some discrete or numeric class.
-Predictors
-and classifiers only tell us what {\em is} while policy 
-generators tell us {\em what to change}. For the kind of business user
-discussed above, policy generators are the prefeered tool since,
-as one gruff user once shouted at us ``don't tell me what \underline{is};
-tell me what to \underline{change}''.
-
-This paper presents the following general framework for extending  predictor systems
-such that they become 
-policy generators:
-\begin{small}
-\[
-project\;data \rightarrow \left\{\begin{array}{l}\mathit{train}
-\rightarrow \left\{\begin{array}{l}\mathit{predictor\;(e.g.\;CART\;or\; RF)}\\
-\mathit{policy\; generator\; (e.g.\; HOW)}\end{array}\right.
-\\
-~\\
-\mathit{test}  \rightarrow  \left\{\begin{array}{r@{~}l}
-\mathit{before}& =\mathit{predictor}(\mathit{test})\\
-\mathit{after}& =\mathit{predictor}(\; \mathit{policy}(\mathit{test})\;)\\
-\Delta& =\mathit{after} / \mathit{before}
-\end{array}\right.
-\end{array} \right.
-\]
-\end{small}
-In the above:
-\bi
-\item
-Project data is divided into a train and test set.
-\item
-From the train set, we learn {\em both} a policy generator as well
-as a predictor using (e.g.)
-CART (for making numeric predictions~\cite{Breiman1984}) or Random Forests (for making predictions
-about symbolic classes~\cite{Breiman2001}). 
-\item
-The test data is then studied to generate two predictions:
-a {\em before} prediction (on the raw test data); then an {\em after}
-prediction (after applying the policies learned from the training data).
-\item
-The improvement delta $\Delta$ is then computed by dividing {\em after} and {\em before}.
-\ei
-This paper presents a novel policy generator called ``HOW''.
-HOW is a near-linear time  instance-based
-local search algorithm that looks for improvement trends in the data,
-then adjusting examples to nudge them along that trend.
-The experiments of this paper apply HOW to learning policies for 
-software defect reduction and for compiling software that runs faster.
-At least for the data explored here, HOW's reductions in defects and runtimes
-are very large-- up to 50\% fewer defects and up to 50\% faster runtimes.
-
-The rest of this paper is structured as follows.
+blah blah data. algorithms. statistics
 
@@
 
-\begin{figure*}[htbp!]
-  \renewcommand{\baselinestretch}{0.8}\begin{center}
-    {\scriptsize
-      \begin{tabular}{c|l|p{4.7in}}
-        amc & average method complexity & e.g. number of JAVA byte codes\\\hline
-        avg\, cc & average McCabe & average McCabe's cyclomatic complexity seen
-        in class\\\hline
-        ca & afferent couplings & how many other classes use the specific
-        class. \\\hline
-class. \\\hline
-        cam & cohesion amongst classes & summation of number of different
-        types of method parameters in every method divided by a multiplication
-        of number of different method parameter types in whole class and
-        number of methods. \\\hline
-        cbm &coupling between methods &  total number of new/redefined methods
-        to which all the inherited methods are coupled\\\hline
-        cbo & coupling between objects & increased when the methods of one
-        class access services of another.\\\hline
-        ce & efferent couplings & how many other classes is used by the
-        specific class. \\\hline
-        dam & data access & ratio of the number of private (protected)
-        attributes to the total number of attributes\\\hline
-        dit & depth of inheritance tree &\\\hline
-        ic & inheritance coupling &  number of parent classes to which a given
-        class is coupled (includes counts of methods and variables inherited)
-        \\\hline
-        lcom & lack of cohesion in methods &number of pairs of methods that do
-        not share a reference to an instance variable.\\\hline
-        locm3 & another lack of cohesion measure & if $m,a$ are  the number of
-        $methods,attributes$
-        in a class number and $\mu(a)$  is the number of methods accessing an
-        attribute, 
-        then
-        $lcom3=((\frac{1}{a} \sum, j^a \mu(a, j)) - m)/ (1-m)$.
-        \\\hline
-        loc & lines of code &\\\hline
-        max\, cc & maximum McCabe & maximum McCabe's cyclomatic complexity seen
-        in class\\\hline
-        mfa & functional abstraction & number of methods inherited by a class
-        plus number of methods accessible by member methods of the
-        class\\\hline
-        moa &  aggregation &  count of the number of data declarations (class
-        fields) whose types are user defined classes\\\hline
-        noc &  number of children &\\\hline
-        npm & number of public methods & \\\hline
-        rfc & response for a class &number of  methods invoked in response to
-        a message to the object.\\\hline
-        wmc & weighted methods per class &\\\hline
-        \rowcolor{lightgray}
-        defect & defect & Boolean: where defects found in post-release bug-tracking systems.
-      \end{tabular}
-    }
-  \end{center}
-  \caption{OO measures used in our defect data sets.  Last line is
-    the dependent attribute (whether a defect is reported to  a
-    post-release bug-tracking system).}\label{fig:ck}
-\end{figure*}
-
-\begin{figure}[!tb]
-  \renewcommand{\baselinestretch}{0.8}\begin{center}
-{\scriptsize
-\begin{tabular}{l@{~~~}l@{~~~}l@{~~~}l@{~~~}l@{~~~}l@{~~~}l@{~~}}
-  \hline
-  \rowcolor{lightgray}
-  Data & Symbol & Training & Testing & Training Samples& Defective &\% Defective \\\hline
-
-Ant & ant & 1.5, 1.6  &1.7 & 644&124&19.25\\
-
-Camel & cam & 1.2, 1.4 & 1.6 & 1480&361 & 24.39\\
-
-Ivy & ivy & 1.1, 1.4 & 2.0  & 352 & 79 & 22.44\\
-
-Jedit & jed & 4.1, 4.2 & 4.3 & 679 & 127 & 18.70\\
-
-Log4j & log & 1.0, 1.1 & 1.2 & 244 & 71 & 29.09\\
-
-Lucene & luc & 2.0, 2.2 & 2.4 & 442 & 235 & 53.16\\
-
-Poi & poi & 2.0, 2.5 & 3.0 & 699 & 285 & 40.77\\
-
-Synapse & syn & 1.0, 1.1 & 1.2 & 379 & 76 & 20.05\\
-
-Velocity & vel & 1.4, 1.5 & 1.6 & 410& 289 & 70.48\\
-
-Xalan & xal &2.5, 2.6 &2.7 & 1688 & 798 & 47.27\\\hline
-\end{tabular}}
-\end{center}
-\caption{Attributes of the defect datasets}\label{fig:ck}
-\end{figure}
-
-\begin{figure}[!hbp]
-  \renewcommand{\baselinestretch}{1}\begin{center}
-{\scriptsize
-\begin{tabular}{llllll}
-  \hline
-  \rowcolor{lightgray}
-Project & Domain & Lang. & LOC & Features & Config\\\hline
-
-Berkeley DB CE & Database & C & 219,811 & 18 & 2560\\
-
-Berkeley DB JE & Database & Java & 42,596 & 32  & 400\\
-
-Apache & Web Server & C & 230,277 & 9 & 192\\
-
-SQLite & Database & C & 312,625 & 39 & 3,932,160\textsuperscript{*}\\
-
-LLVM & Compiler & C++ & 47,549 & 11 & 1024\\
-
-x264 & Video Enc. & C& 45,743 & 16 & 1152\\\hline
-\end{tabular}}\par\medskip
-
-{ \footnotesize $^*$ Dataset contains 4, 553 configurations for prediction modeling and 100 additional random configurations for prediction evaluation, see \cite{vapp}.}
-\end{center}
-
-\caption{Attributes of the Performance Prediction data sets}\label{fig:cpm}
-\end{figure}
-
-\begin{figure}[tbp!]
-% \subfloat[\label{oracle}]{\includegraphics[width=\linewidth]{{_figs//Oracle}}\\
-\includegraphics[width=\linewidth]{_figs/WHAT}
-\caption{Experimental Rig}
-\label{fig:rig}
-
-%   \subfloat[Experimental Rig for Defect Prediction]{  \includegraphics[width=\linewidth]{_figs/HERE}
-%   \label{fig:rig2}}
-
-\end{figure}
-
-%involves two key components. Firstly, there is the oracle (Random Forest with SMOTE) which is used to make predictions. Then we have the 
 \section{Data sets}
@@
 
-\subsection{Performance Prediction Data Set}
-
-{\bfseries RQ3} asks if the aforementioned method can be expanded to other kinds of data.
-To answer this, we have used the performance prediction data set collected by Siegmund et al.
-for their ICSE '12 paper~\cite{sven12}.
-The data sets have been deployed as a part of the \textsc{SPLConqueror} tool\footnote{\url{http://fosd.de/SPLConqueror}}.
-This data set contains six examples of real world configurable systems that cover a broad spectrum of scenarios, see figure \ref{fig:cpm} for a summary.
-The systems have different characteristics (lines of code: 40 thousand to 300 thousand; Valid configurations: 192 to about 3.9 million), different implementation languages (C, C++, and Java), different mechanism (conditional compilation, configuration files, and command-line options), and different domains (Web servers, compilers, encoders, and databases).
-The data contains a measurement of all the configurations that are invoked by the benchmarking tool.
-The measurements were conducted 5 to 20 times and the mean of all measurements for each configuration was recoded.
-
-For our experiments, we randomly split the data sets into two equal halves, one for training and the other for testing.
-The planning phase learns configuration settings from the training half and plans for changes in the test half aiming to optimize the performance of the test instances.
-We repeat our measurements 20 to 25 times to overcome measurement bias.
-\section{Experimental Design}
-
-\subsection{The Rig}
-
-The experimental rig for defect prediction is shown in Figure \ref{fig:rig}. It works as follows: 
-\bi
-\item We use an {oracle} (Random Forest + SMOTE) to determine whether a certain test case is defective or not. 
-\item If the oracle suggests that an instance is defective, then we use HERE to apply the recommendations to that test instance. 
-\item The oracle is then used to predict the attributes in the modified instance.
-\item The statistical significance of the changes are verified using the cliffs delta measure described below.
-\ei
-
-For run time optimization, we use a similar rig.
-The oracle is Random Forest, and it predicts for run times of specific configuration.
-HERE is used to generate a recommended configuration to reduce the run times.
-The run time is measured by the oracle.
-The reduction of run times are expressed as fractions of the original (also referred to as baseline) run time.
-
-Note that we report the performance scores as a comparison between the oracle's prediction \textit{before} and that \textit{after}.
-We refrain from using the \textit{actual} defects in the data sets to perform the same comparison.
-This is because the oracle is limited in its ability to predict defects, there are instances that are inherently misclassified.
-These misclassifications however are not affected by the planner.
-Therefore, by comparing the defect counts before and after applying the planner and doing so with a the same oracle would give us an accurate albeit relativistic measure of performance.
-
-\subsection{Performance Assessment}
-
-In order to assess the performance of the planner for the defect data set, we use the Cliffs Delta score to measure the probability that the number of bugs in test data before applying the planner is larger than after doing so.
-In other words, we use the delta score to measure the ability of the planner to effective reduce the number of defects.
-Given the untreated test instance labeled \textit{Before} of length \textit{M} and the treated instances labeled \textit{After}, the delta score is obtained as follows:
-\begin{equation}
-\delta = \frac{\#(Before<After) - \#(Before>After)}{M^2}
-\label{eq:cliffs}
-\end{equation}
-
-In the context of our application, the $\delta$ attains a value of -1 if the number of defects after applying the treatments has reduced to zero.
-On the other hand $\delta$ will be 0 if there is no change at all.
-Thus, most of the values reported will lie between 0 and -1.
-It needs to be highlighted that although $\delta$ can lie between -1 and +1, the in our application the range is limited to -1 and 0.
-And this is because we only apply the treatments to defective cases.
-
-For the performance prediction data set on the other hand, Cliff's delta measure is not directly applicable.
-We therefore assess the performance by measuring the gain, given by $\frac{Before}{After}$.
-The gain takes a value larger than 1 if the run times have been reduced, a value of 1 if there is no change, and a value less than 1 if run times have increased after applying the recommended changes.
-
-In addition to the above, we rank the different various of the planning scheme to identify the best approach.
-We make use of the Scott-Knott procedure, recommended by Mittas \& Angelis in their 2013 IEEE TSE paper~\cite{sk}, to compute the ranks.
-It works as follows: A list of treatments \textit{l} is sorted by the Median score.
-The list \textit{l} is then split into sub-lists m, n in order to maximize the expected value of the differences in the observed performance before and after division.
-A statistical hypothesis test \textit{H} is applied on the splits \textit{m, n} to check if they are statistically different.
-If so, Skott-Knott then recurses on each division.
-
-The research conducted by Shepperd and MacDonell~\cite{shepperd12a}, Kampenes~\cite{kampenes07} and Kocaguenli et al.~\cite{}, highlighted that an ``effect size'' in lieu of a mere hypothesis test is required in order to verfiy if two populations are ``significly'' different.
-An ICSE'11 paper by Arcuri~\cite{} endorsed the use of Vargha and Delaney's A12 effect size for reporting results in software engineering.
-Thus, for hypothesis testing H in Skott-Knott, we use the A12 test and a non-parametric bootstrap sampling~\cite{}.
-
-\section{Experimental Results}
+section{Experimental Results}
 
@@
 
-\begin{figure}[tbp]
-\centering
-\includegraphics[width=\linewidth]{_figs/histograms.pdf}
-\caption{Comparison of defects before and after planning.}
-\label{fig:bugs}
-\end{figure}
 With this in mind, it is easy to note that lower cliffs delta score translates to better the performance.
@@
 It is to be noted however that
-
-\begin{figure*}[htbp!]
-
-\noindent\begin{minipage}{0.5\textwidth}
-  {\scriptsize \textbf{Ant}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-      \arrayrulecolor{darkgray}
-      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 & 0.75 &    -0.63  &  0.08 & \quart{2}{7}{5}{144} \\
-  1 & 0.75, weighting &    -0.6  &  0.2 & \quart{0}{16}{8}{144} \\
-\hline  2 & 0.5, weighting &    -0.42  &  0.11 & \quart{17}{10}{23}{144} \\
-  2 & 0.5 &    -0.42  &  0.11 & \quart{19}{9}{23}{144} \\
-  2 & 0.75, weighting, Prune=50\% &    -0.4  &  0.11 & \quart{20}{9}{25}{144} \\
-\hline  3 & 0.25 &    -0.28  &  0.09 & \quart{31}{7}{35}{144} \\
-  3 & 0.25, weighting &    -0.28  &  0.08 & \quart{31}{7}{35}{144} \\
-\hline  4 & 0.5, weighting, Prune=50\% &    -0.25  &  0.06 & \quart{35}{5}{38}{144} \\
-\hline  5 & 0.25, weighting, Prune=50\% &    -0.19  &  0.05 & \quart{41}{4}{43}{144} \\
-\hline  6 & Baseline &    -0.11  &  0.03 & \quart{47}{2}{49}{144} \\
-\hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Camel}\\}
-{\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &  0.75, weighting, Prune=50\% &    -0.41  &  0.1 & \quart{2}{14}{9}{205} \\
-  1 &  0.75 &    -0.41  &  0.23 & \quart{1}{32}{9}{205} \\
-  1 &  0.75, weighting &    -0.39  &  0.16 & \quart{0}{22}{12}{205} \\
-\hline  2 &  0.5, weighting, Prune=50\% &    -0.27  &  0.09 & \quart{19}{12}{29}{205} \\
-  2 &  0.5 &    -0.26  &  0.12 & \quart{20}{17}{30}{205} \\
-  2 &  0.5, weighting &    -0.24  &  0.09 & \quart{24}{13}{33}{205} \\
-\hline  3 &  0.25, weighting, Prune=50\% &    -0.2  &  0.05 & \quart{36}{7}{38}{205} \\
-  3 &  0.25, weighting &    -0.19  &  0.07 & \quart{36}{9}{40}{205} \\
-  3 &  0.25 &    -0.17  &  0.06 & \quart{37}{8}{43}{205} \\
-\hline  4 &  Baseline &    -0.15  &  0.06 & \quart{41}{8}{45}{205} \\
-\hline \end{tabular}}
-\end{minipage}
-
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Ivy}\\[-0.05cm]}
-{\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &     0.75 &    -0.57  &  0.17 & \quart{0}{16}{6}{163} \\
-  1 &   0.75, weighting &    -0.55  &  0.11 & \quart{3}{11}{8}{163} \\
-\hline  2 &   0.75, weighting, Prune=50\% &    -0.38  &  0.11 & \quart{19}{11}{25}{163} \\
-  2 &    0.5, weighting &    -0.36  &  0.12 & \quart{23}{12}{27}{163} \\
-  2 &   0.5 &    -0.33  &  0.11 & \quart{25}{11}{30}{163} \\
-\hline  3 &   0.5, weighting, Prune=50\% &    -0.27  &  0.08 & \quart{30}{8}{36}{163} \\
-\hline  4 &   0.25, weighting &    -0.2  &  0.07 & \quart{41}{7}{43}{163} \\
-  4 &     0.25 &    -0.16  &  0.04 & \quart{43}{4}{47}{163} \\
-  4 &     Baseline &    -0.16  &  0.0 & \quart{47}{0}{47}{163} \\
-\hline  5 &   0.25, weighting, Prune=50\% &    -0.15  &  0.04 & \quart{45}{4}{48}{163} \\
-\hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Jedit}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &  0.75, weighting, Prune=50\% &    -0.41  &  0.18 & \quart{0}{20}{8}{172} \\
-  1 &  0.75 &    -0.35  &  0.26 & \quart{0}{30}{15}{172} \\
-\hline  2 &  0.75, weighting &    -0.25  &  0.17 & \quart{16}{20}{26}{172} \\
-  2 &  0.5, weighting, Prune=50\% &    -0.21  &  0.1 & \quart{23}{11}{31}{172} \\
-\hline  3 &   0.5 &    -0.17  &  0.08 & \quart{32}{9}{36}{172} \\
-  3 &  0.5, weighting &    -0.14  &  0.09 & \quart{31}{10}{39}{172} \\
-\hline  4 &  0.25, weighting, Prune=50\% &    -0.12  &  0.06 & \quart{39}{7}{41}{172} \\
-\hline  5 &  0.25 &    -0.08  &  0.05 & \quart{43}{5}{46}{172} \\
-  5 &  0.25, weighting &    -0.08  &  0.06 & \quart{43}{6}{46}{172} \\
-\hline  6 &  Baseline &    -0.06  &  0.01 & \quart{47}{1}{48}{172} \\
-\hline \end{tabular}}
-\end{minipage}
-
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Log4j}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &  0.75, weighting, Prune=50\% &    -0.19  &  0.13 & \quart{0}{28}{15}{273} \\
-\hline  2 &  0.75 &    -0.13  &  0.06 & \quart{23}{13}{28}{273} \\
-  2 &  0.5, weighting, Prune=50\% &    -0.13  &  0.05 & \quart{23}{11}{28}{273} \\
-  2 &  0.75, weighting &    -0.12  &  0.1 & \quart{15}{21}{30}{273} \\
-\hline  3 &  0.5, weighting &    -0.1  &  0.03 & \quart{28}{6}{34}{273} \\
-\hline  4 &   0.5 &    -0.1  &  0.07 & \quart{28}{15}{34}{273} \\
-  4 &  0.25 &    -0.09  &  0.04 & \quart{34}{9}{36}{273} \\
-  4 &  0.25, weighting, Prune=50\% &    -0.09  &  0.04 & \quart{34}{9}{36}{273} \\
-  4 &  0.25, weighting &    -0.06  &  0.04 & \quart{34}{9}{43}{273} \\
-\hline  5 &  Baseline &    -0.06  &  0.03 & \quart{43}{6}{43}{273} \\
-\hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Lucene}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &  0.75, weighting &    -0.15  &  0.09 & \quart{0}{29}{9}{393} \\
-  1 &  0.75 &    -0.13  &  0.09 & \quart{0}{29}{16}{393} \\
-  1 &  0.75, weighting, Prune=50\% &    -0.12  &  0.08 & \quart{6}{27}{19}{393} \\
-\hline  2 &  Baseline &    -0.1  &  0.03 & \quart{26}{10}{26}{393} \\
-  2 &  0.5, weighting, Prune=50\% &    -0.1  &  0.03 & \quart{23}{10}{26}{393} \\
-\hline  3 &  0.5, weighting &    -0.08  &  0.06 & \quart{23}{20}{33}{393} \\
-  3 &  0.25, weighting, Prune=50\% &    -0.07  &  0.03 & \quart{33}{10}{36}{393} \\
-  3 &  0.5 &    -0.07  &  0.05 & \quart{29}{17}{36}{393} \\
-\hline  4 &  0.25, weighting &    -0.04  &  0.04 & \quart{36}{13}{46}{393} \\
-  4 &  0.25 &    -0.04  &  0.02 & \quart{39}{7}{46}{393} \\
-\hline \end{tabular}}
-\end{minipage}
-
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Poi}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-      \arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 & 0.75, weighting &    -0.45  &  0.1 & \quart{6}{10}{11}{162} \\
-  1 &  0.75 &    -0.44  &  0.23 & \quart{0}{23}{12}{162} \\
-\hline  2 & 0.5, weighting &    -0.32  &  0.23 & \quart{12}{24}{24}{162} \\
-  2 & 0.5 &    -0.26  &  0.23 & \quart{18}{24}{31}{162} \\
-  2 & 0.75, weighting, Prune=50\% &    -0.25  &  0.19 & \quart{17}{20}{32}{162} \\
-\hline  3 & 0.5, weighting, Prune=50\% &    -0.19  &  0.09 & \quart{34}{9}{38}{162} \\
-  3 &  0.25 &    -0.19  &  0.11 & \quart{32}{11}{38}{162} \\
-  3 & 0.25, weighting &    -0.17  &  0.14 & \quart{30}{14}{40}{162} \\
-\hline  4 & 0.25, weighting, Prune=50\% &    -0.12  &  0.09 & \quart{40}{9}{45}{162} \\
-\hline  5 &  Baseline &    -0.09  &  0.03 & \quart{46}{3}{48}{162} \\
-\hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Synapse}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 & 0.75, weighting &    -0.56  &  0.2 & \quart{7}{18}{11}{148} \\
-  1 & 0.75 &    -0.48  &  0.34 & \quart{0}{29}{18}{148} \\
-\hline  2 & 0.5 &    -0.4  &  0.27 & \quart{14}{24}{25}{148} \\
-  2 & 0.5, weighting &    -0.37  &  0.17 & \quart{21}{15}{28}{148} \\
-\hline  3 & 0.25 &    -0.23  &  0.16 & \quart{31}{14}{40}{148} \\
-  3 & 0.25, weighting &    -0.23  &  0.1 & \quart{38}{9}{40}{148} \\
-  3 & 0.75, weighting, Prune=50\% &    -0.19  &  0.08 & \quart{40}{7}{43}{148} \\
-\hline  4 & 0.25, weighting, Prune=50\% &    -0.17  &  0.08 & \quart{42}{7}{45}{148} \\
-  4 & Baseline &    -0.15  &  0.0 & \quart{47}{0}{47}{148} \\
-  4 & 0.5, weighting, Prune=50\% &    -0.15  &  0.11 & \quart{40}{9}{47}{148} \\
-\hline \end{tabular}}
-\end{minipage}
-
-\noindent\begin{minipage}{0.50\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Velocity}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 & 0.75, weighting &    -0.19  &  0.22 & \quart{1}{34}{21}{207} \\
-  1 & 0.75, weighting, Prune=50\% &    -0.15  &  0.13 & \quart{14}{20}{28}{207} \\
-  1 & 0.75 &    -0.14  &  0.23 & \quart{0}{35}{29}{207} \\
-\hline  2 & 0.5 &    -0.13  &  0.11 & \quart{23}{17}{31}{207} \\
-\hline  3 & 0.5, weighting &    -0.1  &  0.08 & \quart{29}{13}{35}{207} \\
-  3 & 0.5, weighting, Prune=50\% &    -0.07  &  0.07 & \quart{32}{11}{40}{207} \\
-\hline  4 & Baseline &    -0.05  &  0.04 & \quart{43}{6}{43}{207} \\
-  4 & 0.25, weighting &    -0.05  &  0.03 & \quart{40}{5}{43}{207} \\
-  4 & 0.25 &    -0.04  &  0.02 & \quart{43}{3}{45}{207} \\
-  4 & 0.25, weighting, Prune=50\% &    -0.01  &  0.04 & \quart{43}{6}{49}{207} \\
-\hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.50\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Xalan}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 & 0.75 &    -0.36  &  0.12 & \quart{0}{16}{9}{198} \\
-  1 & 0.75, weighting &    -0.3  &  0.17 & \quart{4}{23}{18}{198} \\
-  1 &    0.5 &    -0.3  &  0.12 & \quart{9}{17}{18}{198} \\
-\hline  2 & 0.5, weighting &    -0.28  &  0.09 & \quart{16}{13}{20}{198} \\
-\hline  3 & 0.25, weighting &    -0.23  &  0.1 & \quart{20}{14}{27}{198} \\
-  3 & 0.25 &    -0.23  &  0.12 & \quart{20}{17}{27}{198} \\
-\hline  4 & 0.25, weighting, Prune=50\% &    -0.14  &  0.07 & \quart{36}{9}{40}{198} \\
-  4 & 0.75, weighting, Prune=50\% &    -0.14  &  0.07 & \quart{33}{10}{40}{198} \\
-  4 & 0.5, weighting, Prune=50\% &    -0.12  &  0.06 & \quart{37}{8}{43}{198} \\
-\hline  5 & Baseline &    -0.08  &  0.02 & \quart{47}{2}{48}{198} \\
-\hline \end{tabular}}
-\end{minipage}
-\caption{Cliffs Delta Scores for the defect data set.
-The Treatment column, has 3 possible configurations, the first (0.25, 0.50, and 0.75) represents the extent of mutation; weighting represents feature weighting; Prune represents the extent of information pruning.}
-\label{tab:ant}
-\end{figure*}
-
-\begin{figure*}[htbp!]
-\centering
-\begin{minipage}{0.30\linewidth}
-\includegraphics[width=\linewidth]{_figs/Apache.pdf}
-\end{minipage}
-\begin{minipage}{0.30\linewidth}
-\includegraphics[width=\linewidth]{_figs/BDBJ.pdf}
-\end{minipage}
-\begin{minipage}{0.30\linewidth}
-\includegraphics[width=\linewidth]{_figs/BDBC.pdf}
-\end{minipage}
-
-\begin{minipage}{0.30\linewidth}
-\includegraphics[width=\linewidth]{_figs/LLVM.pdf}
-\end{minipage}
-\begin{minipage}{0.30\linewidth}
-\includegraphics[width=\linewidth]{_figs/SQL.pdf}
-\end{minipage}
-\begin{minipage}{0.30\linewidth}
-\includegraphics[width=\linewidth]{_figs/X264.pdf}
-\end{minipage}
-\caption{Run time optimization using HERE.
-Blue curve represents a mutation probability of 0.75 with feature weighting and information pruning; Red curve represents a mutation probability of 0.25 with feature weighting, but no information pruning; Black curve represents the raw test data used as baseline for the comparison.}
-\label{fig:pp}
-\end{figure*}
-
-\subsection{Performance Prediction Data set}
-
-In this section, 
-\begin{figure*}[htbp!]
-\noindent\begin{minipage}{0.5\textwidth}
-  {\scriptsize \textbf{Apache}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-      \arrayrulecolor{darkgray}
-      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 & 75, weighting, Prune=25\% &    0.77  &  0.05 & \quart{0}{9}{3}{49} \\
-  1 &   75 &    0.79  &  0.08 & \quart{1}{16}{7}{49} \\
-\hline  2 & 75, weighting &    0.85  &  0.07 & \quart{9}{14}{19}{49} \\
-  2 & 50, weighting, Prune=25\% &    0.85  &  0.04 & \quart{15}{8}{19}{49} \\
-  2 &  50 &    0.85  &  0.05 & \quart{17}{10}{19}{49} \\
-\hline  3 & 50, weighting &    0.91  &  0.05 & \quart{25}{10}{31}{49} \\
-  3 &  25 &    0.92  &  0.04 & \quart{29}{8}{33}{49} \\
-  3 & 25, weighting, Prune=25\% &    0.93  &  0.02 & \quart{33}{4}{35}{49} \\
-\hline  4 & 25, weighting &    0.96  &  0.03 & \quart{37}{6}{41}{49} \\
-\hline  5 & baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-\hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{BDBC}\\}
-{\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &     75 &    0.22  &  0.05 & \quart{0}{3}{1}{49} \\
-  1 &  75, weighting, Prune=25\% &    0.21  &  0.04 & \quart{0}{2}{0}{49} \\
-\hline  2 &  75, weighting &    0.24  &  0.1 & \quart{0}{6}{2}{49} \\
-\hline  3 &     50 &    0.4  &  0.04 & \quart{11}{2}{12}{49} \\
-  3 &  50, weighting, Prune=25\% &    0.4  &  0.05 & \quart{10}{3}{12}{49} \\
-\hline  4 &  50, weighting &    0.47  &  0.09 & \quart{14}{5}{16}{49} \\
-\hline  5 &     25 &    0.66  &  0.03 & \quart{28}{1}{28}{49} \\
-  5 &  25, weighting, Prune=25\% &    0.67  &  0.06 & \quart{28}{3}{29}{49} \\
-\hline  6 &  25, weighting &    0.69  &  0.06 & \quart{29}{4}{30}{49} \\
-\hline  7 &  baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-\hline \end{tabular}}
-\end{minipage}
-
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{BDBJ}\\}
-{\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &     75 &    0.63  &  0.16 & \quart{0}{19}{3}{49} \\
-  1 &  75, weighting, Prune=25\% &    0.68  &  0.17 & \quart{1}{21}{9}{49} \\
-  1 &  75, weighting &    0.74  &  0.11 & \quart{8}{14}{17}{49} \\
-\hline  2 &  50, weighting, Prune=25\% &    0.75  &  0.09 & \quart{14}{12}{18}{49} \\
-  2 &     50 &    0.79  &  0.13 & \quart{16}{16}{23}{49} \\
-\hline  3 &  50, weighting &    0.82  &  0.09 & \quart{23}{11}{27}{49} \\
-\hline  4 &  25, weighting, Prune=25\% &    0.87  &  0.07 & \quart{29}{9}{33}{49} \\
-\hline  5 &     25 &    0.88  &  0.06 & \quart{33}{8}{34}{49} \\
-  5 &  25, weighting &    0.92  &  0.06 & \quart{36}{7}{39}{49} \\
-\hline  6 &  baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-\hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{LLVM}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &     75 &    0.92  &  0.01 & \quart{5}{6}{5}{49} \\
-  1 &  75, weighting, Prune=25\% &    0.92  &  0.02 & \quart{0}{11}{5}{49} \\
-  1 &  75, weighting &    0.93  &  0.02 & \quart{5}{11}{11}{49} \\
-\hline  2 &     50 &    0.94  &  0.01 & \quart{16}{6}{16}{49} \\
-  2 &  50, weighting, Prune=25\% &    0.95  &  0.0 & \quart{22}{0}{22}{49} \\
-  2 &  50, weighting &    0.96  &  0.02 & \quart{22}{11}{27}{49} \\
-\hline  3 &     25 &    0.98  &  0.01 & \quart{33}{5}{38}{49} \\
-  3 &  25, weighting, Prune=25\% &    0.98  &  0.01 & \quart{33}{5}{38}{49} \\
-  3 &  25, weighting &    0.98  &  0.0 & \quart{38}{0}{38}{49} \\
-\hline  4 &  baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-\hline \end{tabular}}
-\end{minipage}
-
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{SQL}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &      75 &    0.98  &  0.01 & \quart{0}{16}{16}{49} \\
-  1 &  75, weighting, Prune=25\% &    0.98  &  0.0 & \quart{16}{0}{16}{49} \\
-  1 &  75, weighting &    0.99  &  0.01 & \quart{16}{17}{33}{49} \\
-  1 &  50, weighting, Prune=25\% &    0.99  &  0.0 & \quart{33}{0}{33}{49} \\
-  1 &      50 &    0.99  &  0.0 & \quart{33}{0}{33}{49} \\
-  1 &  50, weighting &    0.99  &  0.01 & \quart{33}{16}{33}{49} \\
-  1 &  25, weighting, Prune=25\% &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-  1 &      25 &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-  1 &  25, weighting &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-  1 &  baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-  \hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{X264}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &  75, weighting, Prune=25\% &    0.73  &  0.05 & \quart{1}{9}{3}{49} \\
-  1 &     75 &    0.74  &  0.05 & \quart{0}{8}{5}{49} \\
-\hline  2 &  75, weighting &    0.81  &  0.04 & \quart{13}{7}{17}{49} \\
-  2 &  50, weighting, Prune=25\% &    0.82  &  0.04 & \quart{17}{7}{18}{49} \\
-  2 &     50 &    0.83  &  0.03 & \quart{17}{5}{20}{49} \\
-\hline  3 &  50, weighting &    0.88  &  0.03 & \quart{25}{6}{29}{49} \\
-\hline  4 &     25 &    0.9  &  0.03 & \quart{31}{5}{32}{49} \\
-  4 &  25, weighting, Prune=25\% &    0.91  &  0.03 & \quart{32}{5}{34}{49} \\
-\hline  5 &  25, weighting &    0.93  &  0.02 & \quart{36}{3}{37}{49} \\
-\hline  6 &  baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-\hline \end{tabular}}
-\end{minipage}
-\end{figure*}
-
-% \section{Discussion}
-% \section{Threats to validity}
-% \section{Conclusion}
-% \section*{Acknowledgements}
-\newpage
-\bibliography{References}{}
-\bibliographystyle{IEEEtran}
-\end{document}

### 2015-05-10 how.tex
Updates from ShareLaTeX

@@
 \documentclass[conference]{IEEEtran}
+%related work (gentling them in)
+%future work: local patch operator
+%complexity
+% planning in ai
+
 \usepackage{subfig}
@@
 Rahul Krishna, Tim Menzies, Xipeng Shen\\
-       \affaddr{Computer Science, NcState, USA}\\
-       \{i.m.ralk, tim.menzies, xipengshen\}@gmail.com
+        Computer Science, NcState, USA\\
+       \{i.m.ralk, tim.menzies, xipengshen\}\@gmail.com
 % 3rd. author
@@
  Andrian Marcus\\
-       \affaddr{Computer Science, UtDallas, USA}\\
-       {amarcus@utdallas.edu} }
+       Computer Science, UtDallas, USA \\
+       amarcus\@utdallas.edu }
 
@@
 This also is a legitimate issue.
-Building and certifying a model  can  takes  long time, especially in software engineering. For  example, in previous work~\cite{me07f} we used models
-developed by Boehm's group at the University of Southern California.
-Some of those models took decades to develop and mature (from 1981~\cite{boehm81} to 2000~\cite{boehm00b}). 
-Also, even when there is an existing model, they can require
-constant  maintenance lest they become out-dated. Elsewhere, we have described our
-extensions to the USC models to enable reasoning about agile software developments. 
-It took many months to implement and certify those extensions~\cite{me09i,me09j}.
-The problem of model maintenance is another
-motivation to look for alternate methods that can be automatically updated whenever new data arrives.
-Further, sometimes  it is easier to access instances of a model's behaviour than the model
-itself. For example, in prior work with Martin  Feather from the Jet Propulsion 
-Laboratory~\cite{fea02a},  our research partner could not share a
-propriety model from within the NASA firewalls. However, they could share 
-logs of the input/output of that model.
+As discussed below,
+building (or accessing) and certifying and maintaining a 
+trust-worthy model  can  takes  long time, especially in software engineering.
 
@@
 
+\section{Related Work}
+\subsection{Accessing a Trustworthy model}
+The premise of this work is that we do {\em not} have
+a ready-to-use
+
+In some domains, there is ready access to 
+trustworthy domain model that can offer an assessment
+of newly generated examples. For example, in other work
+we have used executing source code as the ``model'' to check
+if our mutations to test suites
+  minimize
+test suite size while maximizing the number of statements covered~\cite{}
+
+For  example, in previous work~\cite{me07f} we used models
+developed by Boehm's group at the University of Southern California.
+Some of those models took decades to develop and mature (from 1981~\cite{boehm81} to 2000~\cite{boehm00b}). 
+Also, even when there is an existing model, they can require
+constant  maintenance lest they become out-dated. Elsewhere, we have described our
+extensions to the USC models to enable reasoning about agile software developments. 
+It took many months to implement and certify those extensions~\cite{me09i,me09j}.
+The problem of model maintenance is another
+motivation to look for alternate methods that can be automatically updated whenever new data arrives.
+Further, sometimes  it is easier to access instances of a model's behaviour than the model
+itself. For example, in prior work with Martin  Feather from the Jet Propulsion 
+Laboratory~\cite{fea02a},  our research partner could not share a
+propriety model from within the NASA firewalls. However, they could share 
+logs of the input/output of that model.
+
 \section{How to Build ``HOW''?}\label{sec:mm}
@@
 
-\input{code}
+\input{_tex/code}
 
 Those same regions can be used for instance-based 
-{\em planning}-- but instead of leaving test instances in the regions
+{\em planning}. However,  instead of leaving test instances in the regions
 found during training, we {\em displace} them towards regions

### 2015-05-10 how.tex
Updates from ShareLaTeX

@@
 
-\section{Related Work}
-\subsection{Accessing a Trustworthy model}
-The premise of this work is that we do {\em not} have
-a ready-to-use
+\section{Background and Related Work}
+\subsection{Accessing Trustworthy Models}
 
@@
   minimize
-test suite size while maximizing the number of statements covered~\cite{}
-
+test suite size while maximizing the number of statements covered~\cite{me09m,andrews07,andrews10}.
+
+However, not all domains come with ready-to-use models.
+In fact, our experience has been that accessing and/or commissioning
+a model can be a labor-intensive process.
 For  example, in previous work~\cite{me07f} we used models
@@
 Some of those models took decades to develop and mature (from 1981~\cite{boehm81} to 2000~\cite{boehm00b}).
+
 Also, even when there is an existing model, they can require
@@
 motivation to look for alternate methods that can be automatically updated whenever new data arrives.
+
 Further, sometimes  it is easier to access instances of a model's behaviour than the model
@@
 logs of the input/output of that model.
+
+In summary, for domains with readily accessible models, we recommend
+the kinds of tools that are widely used in the search-based
+software engineering community such as NSGA-II, NSGA-III, SPEA2, IBEA, particle swarm optimization, MOEA/D, etc.~\cite{deb00a,zit02,zit04,%
+deb14,Cui2005a,zhang07:TEC} or our own GALE tool~\cite{krall14}. However,
+when those models are not available, we recommend tools like HOW.
+
+\subsection{Planning and AI}
+Planning, in the classical AI sense, is a logical procedure
+that seeks an ordering on {\em operators} to take some domain
+{\em state} from a {\em start} state to a {\em goal} state.
+This classical logical approach is known to suffer from
+computational bottlenecks~\cite{Bylander1994}. Hence,
+like this paper,
+many researchers take a probabilistic approach.
+That said, the commitment to minimal displacement and the fully-automated
+modeling approach of this paper makes it stand apart from, say,
+  the Bayesian/Markov chain approach to planning of Dean et al.~\cite{dean1995planning}.
+
+\subsection{Instance-based Reasoning}
+Another  connection to AI is case-based reasoning, or CBR
+(a.k.a. reasoning via anology or instance-based reasoning).
+CBR seeks to emulate human recollection and adaptation
+of past experiences in order to find solutions to current
+problems. According to 
+Kolodner~\cite{Kolodner1992} and Shank~\cite{Schank1977},
+humans do not base their decisions
+on complex reductive analysis, but on an instantaneous survey of past experiences.
+To put that claim another way, according to CBR theory, 
+{\em humans  don’t
+think,  they remember.}
+
+CBR is purely based on this direct
+adaptation of previous cases based on the similarity of
+those cases with the current situation. That is, 
+CBR based system have no explicit world model such as the Markov
+chains used by, say, Dean et al.~\cite{dean1995planning}).
+farming.
+Rather, that model is implicit within  the available past
+cases in the case cache.
+
+One  advantage of CBR is that
+when this  cache is  updated and appended with additional cases, then a CBR system is instantly updated
+to the latest findings.
 

### 2015-05-11 how.tex
Updates from ShareLaTeX

--- 2015-05-10 how.tex
@@
 \DeclareMathOperator*{\argmax}{arg\,max} 
+%\usepackage[usenames]{xcolor}
 
@@
 % additional keywords
-morekeywords={[3]fastmap, Line,bPruning,clister,train,leafs,weightedFeatures, exemplar,nearestLine,dist,displace,geometry,splitAcross2Points,leaves,How,nearest,bPruning,Stats,divide,recurse,weight1,project, furthest, split, WHERE,clusterer, getContours, envied, fWeight, nearestContour, projection, mutate, HERE, knn},
+morekeywords={[3]fastmap,Slope,bPruning,clister,train,leafs,weightedFeatures,HOW, exemplar,nearestSlope,dist,displace,geometry,splitAcross2Points,leaves,How,nearest,bPruning,Stats,divide,recurse,weight1,project, furthest, split,WHERE,clusterer, getContours,envied, fWeight, nearestContour, projection, mutate, HERE, knn},
 keywordstyle={[3]\color{Keywords}\bfseries},
@@
 % precede each author name, affiliation/snail-mail address and
-% e-mail address. Additionally, tag each line of
+% e-mail address. Additionally, tag each Slope of
 % affiliation/address with \affaddr, and tag the
@@
  to reduce defects and decrease program runtime.
- For the test data of this paper, the improvements generated by HERE can reduce
- defect counts as well as runtimes by up to
- 50\% of their original values.
+ For the test data of this paper, those improvements   reduce
+ defect counts and  runtimes by   
+ (25,33)\% (median)   to (37,78)\% (max) of
+ their original values.
   \end{abstract}
   \begin{IEEEkeywords}
-Defect prediction, configuration, prediction, planning, instance-based reasoning.
+Defect prediction, configuration, prediction, planning, case-based reasoning.
   \end{IEEEkeywords}
@@
 proposed  in order to better achieve some goal. 
-Specifically, for every $Z$  that requests a plan $\delta$, we want
-to adjust the attributes $Z_j$ as follows:
+Specifically, for every $Z$  that requests a plan $\delta$ to
+  adjust   attributes $Z_j$:
 \begin{equation}\label{eq:one}
@@
 is reassessed using some domain model.
-GALE runs faster than standard search-based SE tools~\cite{deb00a,zit02} since
-it explores  the principle components
- of the project data (rather than   the raw data). Since it explores
- a smaller space, it also
- terminates much faster than standard optimiser; e.g. for one large model, 4 minutes versus 7 hours~\cite{krall14}.
-
-When presented to some  users, the GALE approach was challenged by
-two business users.   Note that the following issues
-challenge not just GALE, but also  any  optimization algorithm  that makes
-extensive use of mutation  and domain models such as
-NSGA-II, NSGA-III, SPEA2, IBEA, particle swarm optimization, MOEA/D, etc.~\cite{deb00a,zit02,zit04,%
-deb14,Cui2005a,zhang07:TEC}.
-
+GALE uses an eigenvector technique to find better mutants faster than standard search-based SE tools~\cite{deb00a,zit02}.
+
+When presented to some  software project managers, the GALE approach was challenged by
+two business users. Note that the   issues they raise are
+challenges not just  about GALE, but also  about any     optimization algorithm  that  
+ make extensive use of mutation  and domain models.
 One  user asked:
@@
 \end{quote}
-Note here that this business user is asking for solutions  that do not require extensive 
+Here, the business user is asking for solutions  that do not require extensive 
 changes to their current  approaches.
@@
 
-Every challenge is an opportunity to explore  a new approach.
-If we  restrict $\delta$ to very small changes, then any 
-predictive data miner applied to the original data could also be used
-to assessed the mutated data (proviso: we have to guarantee that
-the mutations do not leave the space of examples present in the original data).
-Note that this approach addresses ISSUE~\#1 since it only uses minimal changes.
-It also addresses  ISSUE~\#2 since, when lack a domain model, we automatically
-create one (via data mining).
-
-This paper presents HOW, a novel planner for learning actionable analytics via
-minimal changes. 
-In the experiments shown below, we see that HOW's plans  can significantly
-reduce the  expected
+This paper addresses  ISSUE~\#1 and ISSUE~\#2 using case-based reasoning.
+CBR  is purely based on the direct
+adaptation of previous cases based on the similarity of
+those cases with the current situation. That is, 
+CBR based system have no explicit world model.
+Rather, that model is implicit within  the available past
+cases in the case cache.
+
+This paper presents a novel CBR tool called ``HOW''. This tool  restricts test data $\delta$s to {\em minimal
+displacements} (very small changes to a subset of the attributes)
+thereby addressing ISSUE \#1. 
+HOW ensures that the   $\delta$ displaces test data towards some region in the training data.
+This is important since we address ISSUES~\#2 via some data mining
+tool that train  a predictor from the training  data. Since we are pushing test data
+into regions of the training data,  we can use the predictor to assess
+the effectiveness of the $\delta$.
+This paper shows that  that HOW's plans can be very effective indeed.
+In the experiments shown below, HOW's plans
+reduced the  expected
 value of:
 \bi
-\item The software defects found in  the object-oriented JAVA systems explored in 2010 by Jureczko et al.~\cite{jureczko10};
-\item The runtime of the  software systems whose configurations
-are explored in 2013 by Seigmund et al.~\cite{sven12};
+\item The  defects found  in Jureczko et al.'s    object-oriented JAVA systems~\cite{jureczko10}.
+\item The runtime of the  software systems   configured by  Seigmund et al.~\cite{sven12}.
 \ei 
-This paper makes five contributions:
+In summary, this paper makes five contributions:
 \be
-\item The HOW  instance-based planner (which has not been presented before).
-\item The experiments of this paper show that HOW planner is useful for real-world tasks;
+\item The HOW  case-based planner (which has not been presented before).
+\item The experiments of this paper showing that HOW planner is useful for real-world tasks;
 e.g. reducing the
@@
 
-\section{Related Work}
-\subsection{Accessing a Trustworthy model}
-The premise of this work is that we do {\em not} have
-a ready-to-use
+\section{Background and Related Work}
+\subsection{Search-based Software Engineering (SBSE)} CPUs are becoming
+faster and cloud computing enables access to more CPUs. Hence, it is now pratical
+to solve large problems in SBSE via 
+genetic algorithms  that build multiple generations by  mutating  an existing population,  
+the combine the best mutants to fond the next population~\cite{Harman2009,Harman2011}.
+Examples of these algorithms include GALE, NSGA-II, NSGA-III, SPEA2, IBEA, particle swarm optimization, MOEA/D, etc.~\cite{krall14,deb00a,zit02,zit04,%
+deb14,Cui2005a,zhang07:TEC}.
+
+SBSE methods can make extensive mutations to the data they are exploring. Hence, these methods
+require some domain model that can assess new and highly novel examples.
+
+\subsection{Accessing Trustworthy Models}
 
@@
   minimize
-test suite size while maximizing the number of statements covered~\cite{}
-
+test suite size while maximizing the number of statements covered~\cite{me09m,andrews07,andrews10}.
+
+However, not all domains come with ready-to-use models.
+For   several problems where models are hard to obtain, or the input and output are related by complex connections that simply cannot be modeled in a reliable manner~\cite{Ludewig2003}. For example, 
+consider software defect prediction and all the intricate issues that may lead defects in a product. A odel that includes {\em all} those
+potential issues would be very large and unweliding. Further,
+the empirical data required to validate any/all parts
+of that model can be hard to find.
+
+In fact, our experience has been that accessing and/or commissioning
+a model can be a labor-intensive process.
 For  example, in previous work~\cite{me07f} we used models
@@
 motivation to look for alternate methods that can be automatically updated whenever new data arrives.
-Further, sometimes  it is easier to access instances of a model's behaviour than the model
+
+Further, sometimes  it is easier to access cases of a model's behaviour than the model
 itself. For example, in prior work with Martin  Feather from the Jet Propulsion
@@
 
+In summary, for domains with readily accessible models, we recommend
+the kinds of tools that are widely used in the search-based
+software engineering community such as GALE,NSGA-II, NSGA-III, SPEA2, IBEA, particle swarm optimization, MOEA/D, etc.~\cite{krall14,deb00a,zit02,zit04,%
+deb14,Cui2005a,zhang07:TEC}. Otherwise, we recommend tools like HOW.
+
+\subsection{Planning and AI}
+HOW is a {\em probablistic} planner, which is a different approach to that taken by
+classical AI. 
+That kind of planning is a logical procedure~\cite{Fikes1971}
+that seeks an ordering on {\em operators} to take some domain
+{\em state} from a {\em start} state to a {\em goal} state.
+This classical logical approach is known to suffer from
+computational bottlenecks~\cite{Bylander1994}. Hence,
+like this paper,
+many researchers take a probabilistic approach.
+HOW's commitment to minimal displacement (and the fully-automated
+modeling approach) of this paper makes it stand apart from, say,
+  the Bayesian/Markov chain approach to planning of Dean et al.~\cite{dean1995planning}.
+
+\subsection{Case-based Reasoning}
+Case-based reasoning (CBR) has been extensively
+explored in the AI literature
+(where it has also bee called
+ reasoning via anology or instance-based reasoning).
+CBR seeks to emulate human recollection and adaptation
+of past experiences in order to find solutions to current
+problems.
+
+CBR was first motivated by appeals to human cognition. According to 
+Kolodner~\cite{Kolodner1992} and Shank~\cite{Schank1977},
+humans do not base their decisions
+on complex reductive analysis, but on an instantaneous survey of past experiences.
+To say that   another way, according  to  CBR, 
+{\em humans  don’t
+think,  they remember.}
+
+CBR has several advantages.
+Firstly,
+when the  cache of past cases is  updated and appended with additional cases, then a CBR system is instantly updated
+to the latest findings.
+
+Secondly, the output of a CBR is made on a ``case-by-case'' basis. 
+That is, CBR does not offer some trite generalization over multiple
+exmaples. Rather, the advice it gives is specialized to the particular
+case being considered at the current time.  This is particularly attractive
+since much of our recent work has focused on issues
+of locality (where the best solutions for some part of the data
+are very different some average case solution obtained from all the data~\cite{localvsglobal}).
+
+\subsection{CBR in Software Engineering}
+Due to the advantages of CBR, numerous papers in SE
+have applied this technique.
+CBR  has been used extensively by the effort estimation community, see~\cite{keung2008analogy, 6600685, walkerden1999empirical, shepperd1997estimating, kocaguneli2010use}.
+Researchers have found that, in some domains, they are competitive with  closed form mathematical models or other modeling methods such as regression \cite{keung2008analogy}. 
+CBR is also useful when dealing with spare data sets~\cite{1438374} of with 
+partial knowledge  at, for example,  an early stage of a project)~\cite{walkerden1999empirical}.
+
+ HOW    is very different
+to the above CBR systems.
+Firstly, HOW is a {\em planner} while the above
+CBR methods are all {\em prediction} algorithms\footnote{The disctiniction being that
+predictions systems tell you ``what is'', while planners tell you ``what to do''.}.
+Secondly, all the above CBR tools explore the nearest ``k'' neighors,
+HOW, on the other hand,  explores the {\em gradient between the scores of pairs of nearest neighbors}. 
+To put that
+another way,   the above CBR methods explore {\em points} while
+HOW explores the slope {\em between} points.
+
+\subsection{Prior Work}
+HOW is the third
+generation of our experiments with planning and CBR.
+Generation one of that work resulted in
+ W2, a CBR planner that reflected over the delta of raw  attributes~\cite{6600685}.
+It suffered from all-too-frequent {\em optimization failure}; i.e.
+when its plans were applied the resulting observed
+performances {\em increased} in up to $\frac{1}{3}$rd of test cases.
+
+Generation two of that work resulted in  IDEA~\cite{me12c}.
+IDEA and HOW use the    same recursive clustering
+method but IDEA made the mistake of  summarize those
+recursive divisions into a tree structure. Initial results with IDEA were weak, but somewhat
+positive~\cite{me12c}. We tried unsuccessfully for  months to extend and improve
+the IDEA prototype. The results were most discouraging: those tree-based summaries often suffered
+from the same optimization failure problem seen with W2.
+
+As part of the IDEA work, we built HOW as a ``straw-man'' ; i.e. a  simpler
+approach that was  to provide a baseline result,  above which IDEA was meant
+to do better.   However, HOW's results were so good that we  threw away months
+of work on tree-based planning with IDEA. Now, we strongly recommend HOW
+over IDEA (and W2) since, as shown by the following results, HOW's plans {\em never} lead to performance getting worse. Also, when HOW did improve the expected values of the performance,
+those performance improvements were an order of magnitude larger than those seen
+with IDEA.
+
 \section{How to Build ``HOW''?}\label{sec:mm}
@@
 A general model for {\em predictors} is as follows. 
-During testing, each test instance gains a prediction 
+During testing, each test case gains a prediction 
 by finding which region of the data it falls into.
 During training, those regions are inferred from
-divisions that ``chunk'' together regions with instances
+divisions that ``chunk'' together regions with cases
 with similar properties. These dividers can be categorical (as in the case of decision trees) or probabilistic (as in the
@@
 Data can be rapidly and recursively divided   as follows.
-Find   two   distance instances,  $X,Y$
-by picking any instance $W$ at random, then setting $X$ to its most
-distant instance, then setting $Y$ to the instance most distant from
+Find   two   distance cases,  $X,Y$
+by picking any case $W$ at random, then setting $X$ to its most
+distant case, then setting $Y$ to the case most distant from
 $X$~\cite{fastmap}
 (this requires only $O(2N)$ comparisons
-of $N$ instances).
-Next, project each instance $Z$
-onto a line that  runs between $X,Y$ using the cosine
-rule of \fig{where}b. After that,  split the data at the median $x$ value of all instances and
+of $N$ cases).
+Next, HOW projects each case $Z$
+onto a {\tt Slope} that  runs between $X,Y$ using the cosine
+rule of \fig{where}b. After that,  split the data at the median $x$ value of all cases and
 recurses on each half  (stopping when
-one half has less  than $\sqrt{N}$ of the original population). For more details. \fig{howcode}, line~76,
+one half has less  than $\sqrt{N}$ of the original population). For more details. \fig{howcode}, line~84,
 
@@
 the Euclidean measure recommended for
-instance-based reasoning by Aha et al.~\cite{aha91};
+case-based reasoning by Aha et al.~\cite{aha91};
 i.e. $\sqrt{\sum_iw_i(X_i-Y_i)^2}$ where $X_i,Y_i$
@@
 
-Let   $X,Y$ be two points joined by  a line  length $c$.
+Let   $X,Y$ be two points joined by  a {\em Slope} of  length $c$.
 A third point, $Z$, has distances  $a=dist(Z,X)$ and
@@
 Further, according to Pythagoras' theorem, $Z$ stands at a distance
-$y = \sqrt{a^2 - x^2}$ from the line $\overline{XY}$. For more details, see  \fig{howcode}, line~59.
+$y = \sqrt{a^2 - x^2}$ from the line $\overline{XY}$. For more details, see  \fig{howcode}, line~52.
 
@@
 A recursive procedure can  find those divisions $n_1,n_2,...$ by (a)~sorting a numeric column,
-then split at $\argmin_i w_i$, then recursing into each half.  For more details, see  \fig{howcode}, line~109.
+then split at $\argmin_i w_i$, then recursing into each half.  For more details, see  \fig{howcode}, line~113.
 
@@
 
-\input{_tex/code}
-
-Those same regions can be used for instance-based 
-{\em planning}. However,  instead of leaving test instances in the regions
+\input{tex/code}
+
+Those same regions can be used for case-based 
+{\em planning}. However,  instead of leaving test cases in the regions
 found during training, we {\em displace} them towards regions
@@
 during training, HOW clusters data using the procedure of \fig{where}a,
-then draws {\tt Line}s between the centroids of  clusters $X,Y$ that are nearest
+then draws {\tt Slope}s between the centroids of  clusters $X,Y$ that are nearest
 neighbors.
-By convention, we say that the cluster containing $X$ has the  better objective scores. This means we can say that the {\tt Line} is a useful direction for displacing
-data; i.e.  away from $Y$ and towards $X$ (for an implementation of such a {\tt Line} class, see \fig{howcode}, line~1).
- During testing,  HOW   finds the  nearest {\tt Line} to every test instance. That  test instance is   then displaced towards the better end
-of that line; i.e. towards  $X$ (see \fig{howcode}, line 53).
-
-An important design decision with HOW 
-is how to determine the exact {\em direction} and {\em magnitude} of the
-displacement.  Following on from the discussion around   ISSUE~\#1,
-we note that a design goal of HOW is
-{\em minimal displacements} of project data.
-To implement minimal displacement:
-\bi
-\item
+By convention, we say that the cluster containing $X$ has the  better objective scores. This means we can say that the {\tt Slope} is a useful direction for displacing
+data; i.e.  away from $Y$ and towards $X$ (for an implementation of such a {\tt Slope} class, see \fig{howcode}, line~1).
+ During testing,  HOW   finds the  nearest {\tt Slope} to every test case. That  test case is   then displaced towards the better end
+of that {\tt Slope}; i.e. towards  $X$ (see \fig{howcode}, line 51).
+
+ HOW needs to  determine the  exact {\em direction} and {\em magnitude} of 
+displacement.  To address  ISSUE~\#1,
+HOW uses two techniques to result in 
+{\em minimal displacements} of project data. Firstly,
 HOW sorts  the independent variables
@@
 (see \fig{howcode}, line 38).
-In  the experiments shown below,  we explore   $B \in \{25,50,100\}\%$.
-\item
-HOW also  limits displacement
+In  the experiments shown below,  we explore   \mbox{$B \in \{25,50,100\}\%$}.
+
+Secondly, HOW   limits displacement
 to very small regions in the space of the training data (never more that the separation
@@
 \mbox{$F\in \{0.25, 0.5, 0.75\}$}.
-\ei
+
 Turning now to the displacement {\em direction},
-our experiments show that it useful to  carefully reflect on exactly where HOW should  push each test instance.
+our experiments show that it useful to  carefully reflect on exactly where HOW should  push each test case.
 HOW replaces each cluster   with one {\em exemplar} that best
 characterizes the data in that cluster. It then displaces the
-test data towards that exemplar, as shown in \fig{howcode}, line 19. In summary, 
+test data towards that exemplar, as shown in \fig{howcode}, line 20. In summary, 
 If  $Z_j$ is an independent variable within the
-test instance $Z$ and  $X$ is the exemplar found at training time,
+test case $Z$ and  $X$ is the exemplar found at training time,
 then we displace $Z$ as follows:
@@
 this equations satisfies our definition of a ``plan'' as offered in
-\eq{one} in the {\em Introduction}
-
-The experiments of this work showed that different kinds of data require
-different kinds of exemplars.
+\eq{one} in the  Introduction.
+
+Different kinds of data require
+different policies for exemplar generation.
+For the Jureczko data, the objective score
+is a boolean variable is true if defects have been noted
+for that class.  For this kind of data (with discrete objectives),
+we found nothing better than  making the exemplar of a cluster be the mean
+value of all attributes of all cases in that cluster.
+
+However, for the Seigmund data, we found a better exemplar generation policy.
+\fig{pp} shows the effects of selecting different kinds of exemplars for 
+Berkeley DB, one of the Seigmund data sets.
+The \textcolor{black}{\bf black baseline} curve  shows the runtimes for 600 random configurations
+of the Makefiles used in Berkely DB. The other two curves shows the predictions of the runtimes if test cases are displaced towards exemplars
+  built from:
 \bi
-\item
-For the Jureczko data, the objective score
-is a boolean that is true if defects have been noted
-for that class. 
-For this kind of data with discrete objectives,
-the data, 
-has very little to  differentiate between the objective scores
-so we just set the exemplar to  
-an instance synthesized from the median values of the instances
-in that cluster.
-\item
-For the Seigmund data,
-the objective score is the runtime of the test suite of a compiled program.
-For this kind of data with numeric objectives,
-the exemplar  is the instance in a cluster
-with  best objective score.
+\item The \textcolor{red}{\bf   mean}    value of all cases in the  cluster.
+\item The  case with the \textcolor{green}{\bf  best}  objective score. 
 \ei
+Note that using the best as the exemplar does better than useing the mean.
+The pattern shown in \fig{pp} has been seen in all the Seigmund data sets;
+i.e. for data sets with continuous classes,
+best results come from using exemplars formed from the best instance (and not the mean).
 
@@
 
+ \begin{figure}[!t]
+\centering
+%\begin{minipage}{0.30\linewidth}
+%\includegraphics[width=\linewidth]{figs/Apache.pdf}
+%\end{minipage}
+%\begin{minipage}{0.30\linewidth}
+%\includegraphics[width=\linewidth]{figs/BDBJ.pdf}
+%\end{minipage}
+%\begin{minipage}{0.30\linewidth}
+%\includegraphics[width=\linewidth]{figs/BDBC.pdf}
+%\end{minipage}\\[0.25cm]
+%
+%\begin{minipage}{0.30\linewidth}
+%\includegraphics[width=\linewidth]{figs/LLVM.pdf}
+%\end{minipage}
+%\begin{minipage}{0.30\linewidth}
+%includegraphics[width=\linewidth]{figs/SQL.pdf}
+%\end{minipage}
+%\begin{minipage}{0.30\linewidth}
+\includegraphics[width=2.5inches]{figs/BDBC.pdf}
+%\end{minipage}
+\caption{Effects of selecting different kinds of exemplars:
+the   \textcolor{black}{\bf  baseline} curve; the
+\textcolor{red}{\bf    ``mean''}; and the  
+\textcolor{green}{\bf    ``best''} curve.}\label{fig:pp}
+\end{figure}
+
 \subsection{Assessment}\label{sect:assess}
@@
 will be HOW  and our
-our { predictors} will be the Random Forest and Random Forest
+our { predictors} will be the Random Forest~\cite{Breiman2001} and Random Forest
 Regressor taken from the SciKit
-Learn toolkit~\cite{Pedregosa2012}. The Random Forests procedure is explained in \fig{rr}.
-
-\begin{figure}[t!]
-\small
-\begin{tabular}{|p{.95\linewidth}|}\hline
- Decision tree learners find the attribute whose value's
-select for for sections of the data with least variation in the class
-variable. Decision tree learners then recurse on each selection~\cite{breiman84}.
-
-A random forest is a set of decision trees, each built
-from some random subset of the rows and columns. The conclusions
-of the forest are a ``vote'' generated by all the trees~\cite{Breiman2001}.
-
-A standard Random Forest predicts for a discrete class variable while
-a Random Forest Regressor generates numeric predictions.\\\hline
-\end{tabular}
-\caption{Random Forests and Random Forest Regressors.}\label{fig:rr}
-\end{figure}
+Learn toolkit~\cite{Pedregosa2012}.  
+%\begin{figure}[t!]
+%\small
+%\begin{tabular}{|p{.95\linewidth}|}\hline
+% Decision tree learners find the attribute whose value's
+%select for for sections of the data with least variation in the class
+%variable. Decision tree learners then recurse on each selection~\cite{breiman84}. 
+%
+%A random forest is a set of decision trees, each built
+%from some random subset of the rows and columns. The conclusions
+%of the forest are a ``vote'' generated by all the trees~\cite{Breiman2001}. 
+%
+%A standard Random Forest predicts for a discrete class variable while
+%a Random Forest Regressor generates numeric predictions.\\\hline
+%\end{tabular}
+%\caption{Random Forests and Random Forest Regressors.}\label{fig:rr}
+%\end{figure}
 
@@
            & \multicolumn{2}{c|}{training}   & \multicolumn{3}{c|}{testing}      \\ \cline{2-6}
-   data set      & versions           & instances & versions     & instances    & \% defective             \\ \hline
+   data set      & versions           & cases & versions     & cases    & \% defective             \\ \hline
         jedit    & 3.2, 4.0, 4.1, 4.2 & 1257      & 4.3          & 492          & 2 \\
@@
         lcom & lack of cohesion in methods &number of pairs of methods that do
-        not share a reference to an instance variable.\\\hline
+        not share a reference to an case variable.\\\hline
         locm3 & another lack of cohesion measure & if $m,a$ are  the number of
@@
 \item Probability of false alarm (a.k.a. ``pf''): the percent of non-fault
-classes that are predicted to be defective.
+classes that are {\e, predicted} to be defective.
 \ei 
@@
 
-The ``tuned'' columns of \fig{j} show that we can salvage some of the data sets
-using two techniques.
+The ``tuned'' columns of \fig{j} show that we can salvage some of the data sets.
  Pelayo and Dick~\cite{pelayo07} report that defect prediction can be improved via SMOTE~\cite{Chawla2002}; i.e. an over-sampling of minority-class examples.
- Also, Fu et al.~\cite{fu:ase15} report that an optimization method called differential evolution~\cite{storn97}
+ Also, Fu et al.~\cite{fu:ase15} report that parameter tuning with differential evolution~\cite{storn97}
 applied to defect predictors can quickly explore the tuning
@@
 we can plan ways to reduce defects in {\em jedit, ivy, ant, lucene} and {\em poi}.
-(Aside: note that this tuning used optimization and sub-sampling   on   {\em only} the
-training instances of \fig{j}
+One important detail to be stressed here is that, when we applied    SMOTE-ing and
+parameter tunings, those techniques should be applied the training data and {\em not}
+the test data;  
 i.e.
-no clues from the test set were ever used in this tuning process.)
+we took care that no clues from the test set were ever used in this tuning process.
 
@@
 
-  The Seigmund data sets are far more varied than the Jurecko data (since they contain every configuration option in the Makefiles
-  for BerkeleyDB-- the Java  and  Windows  versions,  Apache,  SQLite,  LLVM,and x264).
-  \fig{cpm} lists the size of Seigmund attribute sets. For the Siegmind data, 
-  25 times, 
-  we randomized the order of the data, trained on the first half (using
-  Random Forest Regressor), then tested on the second half.
-
-\begin{figure}[!hbp]
-  \renewcommand{\baselinestretch}{1}\begin{center}
-{\scriptsize
+  The Seigmund data sets are far more varied than the Jurecko data.
+  These contain the results of applying a large number of mutators
+  to the configuration options of the Makefiles of  BerkeleyDB (the Java  and  Windows  versions),  Apache,  SQLite,  LLVM, and x264. For details on those datasets, see \fig{cpm}.
+
+\begin{figure}[!t]
+\scriptsize
 \begin{tabular}{llllll}
@@
 Project & Domain & Lang. & LOC & Features & Config\\\hline
-
 Berkeley DB CE & Database & C & 219,811 & 18 & 2560\\
-
 Berkeley DB JE & Database & Java & 42,596 & 32  & 400\\
-
 Apache & Web Server & C & 230,277 & 9 & 192\\
-
-SQLite & Database & C & 312,625 & 39 & 3,932,160\textsuperscript{*}\\
-
+SQLite & Database & C & 312,625 & 39 & 3,932,160\\
 LLVM & Compiler & C++ & 47,549 & 11 & 1024\\
-
 x264 & Video Enc. & C& 45,743 & 16 & 1152\\\hline
-\end{tabular}}\par\medskip
-
-{ \footnotesize $^*$ Dataset contains 4, 553 configurations for prediction modeling and 100 additional random configurations for prediction evaluation, see \cite{vapp}.}
-\end{center}
-
-\caption{Seigmund data sets: details on the data sets}\label{fig:cpm}
+\end{tabular}
+
+\caption{Seigmund data sets: details on the data sets.
+For SQLite, the data  contains 4,553 configurations for prediction modeling and 100 additional random configurations for prediction evaluation, see \cite{vapp}.}\label{fig:cpm}
 \end{figure}
@@
 %\begin{figure}[tbp!]
-% \subfloat[\label{oracle}]{\includegraphics[width=\linewidth]{{_figs//Oracle}}\\
-%\includegraphics[width=\linewidth]{_figs/WHAT}
+% \subfloat[\label{oracle}]{\includegraphics[width=\linewidth]{{figs//Oracle}}\\
+%\includegraphics[width=\linewidth]{figs/WHAT}
 %\caption{Experimental Rig}
@@
 
-%   \subfloat[Experimental Rig for Defect Prediction]{  \includegraphics[width=\linewidth]{_figs/HERE}
+%   \subfloat[Experimental Rig for Defect Prediction]{  \includegraphics[width=\linewidth]{figs/HERE}
 %   \label{fig:rig2}}
@@
 
-\begin{figure}[tbp]
-\centering
-\includegraphics[width=\linewidth]{_figs/histograms.pdf}
-\caption{Jureczko object-oriented defect data sets. 
-Comparisons of predictions of defects in the Jureczko data sets before and after planning.}
-\label{fig:bugs}
+%\begin{figure}[tbp]
+%\centering
+%\includegraphics[width=\linewidth]{figs/histograms.pdf}
+%\caption{Jureczko object-oriented defect data sets. 
+%Comparisons of predictions of defects in the Jureczko data sets before and after planning.}
+%\label{fig:bugs}
+%\end{figure}
+
+%\subsection{Visualisations of Changes}%
+
+%In this section, we show some sample results. In the next section, we conduct a statistical
+%analysis of all   results.
+
+%\fig{bugs} shows the effects of planning on the five good Jureczko data sets. Note that:
+%\bi
+%\item
+%The number of defects predicted in the ``after'' set is always less than ``before'';
+%\item
+%The reduction can be quite large: e.g. see the over 50\% reduction in the {\em ant} data set.
+%\ei
+%
+%\fig{pp} shows the effects of planning on the Seigmund data sets. The black, red %XXX
+%curves show the
+%runtimes as predicted in the test sets before/after our planning.  While some of the differences
+%are small (eg. LLVM and SQL), some of the others are very large indeed (e.g. the Apache and   BD*).
+
+%This visual samples of HOW's planning results look promising-- but they need to be confirmed by a
+% more rigorous statistical analysis.
+
+\begin{figure}[!t] 
+  {\scriptsize \textbf{Ant}\\[0.1cm]}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~~}c@{}r}}
+      \arrayrulecolor{darkgray}
+      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} && \textbf{Bugs}\\
+  1 &  0.75-weight &    0.71  &  0.19 & \quart{0}{25}{10}{49} & 62\\
+  1 &         0.75 &    0.72  &  0.14 & \quart{6}{19}{12}{49} & 64\\
+\hline  2 &          0.5 &    0.86  &  0.08 & \quart{25}{11}{31}{49} & 77 \\
+  2 &   0.5-weight &    0.88  &  0.14 & \quart{20}{19}{33}{49} & 77\\
+\hline  3 & 0.5-weight-B=50\% &    0.91  &  0.08 & \quart{32}{11}{37}{49} & 80\\
+  3 & 0.75-weight-B=50\% &    0.92  &  0.09 & \quart{31}{12}{39}{49} & 82\\
+  3 &  0.25-weight &    0.92  &  0.04 & \quart{36}{5}{39}{49} & 81\\
+\hline  4 &         0.25 &    0.93  &  0.05 & \quart{37}{7}{40}{49} & 83\\
+  4 & 0.75-weight-B=25\% &    0.94  &  0.09 & \quart{36}{12}{41}{49} & 82\\
+\hline  5 & 0.25-weight-B=50\% &    0.97  &  0.03 & \quart{44}{4}{45}{49} & 86\\
+  5 & 0.5-weight-B=25\% &    0.98  &  0.06 & \quart{40}{8}{47}{49} & 86 \\
+\hline  6 & 0.25-weight-B=25\% &    0.99  &  0.01 & \quart{48}{1}{48}{49} & 87\\
+\hline  7 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 90\\
+\hline \end{tabular}}
+%\end{minipage}\\[0.1cm]
+
+%\noindent\begin{minipage}{0.5\textwidth}
+ % \flushleft
+ \vspace{2mm}
+ \noindent {\scriptsize \textbf{Ivy}\\[0.1cm]}
+{\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c@{}r}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & & \textbf{Bugs}\\
+  1 &  0.75-weight &    0.75  &  0.18 & \quart{0}{29}{8}{49} & 50\\
+  1 &         0.75 &    0.79  &  0.12 & \quart{8}{20}{14}{49} & 53\\
+\hline  2 &          0.5 &    0.84  &  0.1 & \quart{18}{16}{23}{49} & 56\\
+  2 &   0.5-weight &    0.84  &  0.08 & \quart{14}{14}{23}{49} & 56\\
+  2 & 0.75-weight-B=50\% &    0.84  &  0.09 & \quart{18}{15}{23}{49} & 56 \\
+\hline  3 & 0.5-weight-B=50\% &    0.91  &  0.05 & \quart{29}{9}{34}{49} & 61\\
+\hline  4 & 0.25-weight-B=50\% &    0.96  &  0.01 & \quart{43}{1}{43}{49} & 64\\
+  4 & 0.75-weight-B=25\% &    0.96  &  0.05 & \quart{39}{9}{43}{49} & 65\\
+  4 &         0.25 &    0.97  &  0.01 & \quart{43}{1}{44}{49} & 65\\
+  4 &  0.25-weight &    0.97  &  0.05 & \quart{39}{9}{44}{49} & 65 \\
+  4 & 0.5-weight-B=25\% &    0.97  &  0.03 & \quart{43}{5}{44}{49} & 65 \\
+\hline  5 & 0.25-weight-B=25\% &    0.99  &  0.01 & \quart{48}{1}{48}{49} & 66\\
+\hline  
+6 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 67\\
+\hline \end{tabular}}
+%\end{minipage}\\[0.1cm]
+
+%\noindent\begin{minipage}{0.5\textwidth}
+ % \flushleft
+\vspace{2mm}\noindent{\scriptsize \textbf{Jedit}\\[0.1cm]}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c@{}r}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & & \textbf{Bugs}\\\hline
+  1 &         0.75 &    0.64  &  0.28 & \quart{0}{27}{14}{49} & 110\\
+\hline  2 &  0.75-weight &    0.76  &  0.21 & \quart{13}{21}{26}{49}& 131 \\
+  2 &   0.5-weight &    0.76  &  0.16 & \quart{20}{16}{26}{49} & 130\\
+  2 &          0.5 &    0.79  &  0.17 & \quart{19}{17}{29}{49} & 137\\
+\hline  3 & 0.75-weight-B=50\% &    0.85  &  0.12 & \quart{30}{12}{35}{49} & 146\\
+  3 &  0.25-weight &    0.87  &  0.07 & \quart{34}{7}{37}{49} & 152\\
+\hline  4 &         0.25 &    0.93  &  0.09 & \quart{37}{9}{43}{49} & 161\\
+  4 & 0.5-weight-B=50\% &    0.93  &  0.05 & \quart{41}{5}{43}{49} & 162\\
+\hline  5 & 0.25-weight-B=50\% &    0.97  &  0.03 & \quart{45}{3}{47}{49} & 167\\
+  5 & 0.75-weight-B=25\% &    0.97  &  0.02 & \quart{46}{2}{47}{49} & 168\\
+\hline  6 & 0.5-weight-B=25\% &    0.98  &  0.02 & \quart{47}{2}{48}{49} & 170\\
+  6 & 0.25-weight-B=25\% &    0.98  &  0.01 & \quart{48}{1}{48}{49} & 171\\
+\hline  7 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 175\\
+\hline \end{tabular}}
+%\end{minipage}\\[0.1cm]
+
+%\noindent\begin{minipage}{0.5\textwidth}
+%  \flushleft
+\vspace{2mm}\noindent{\scriptsize \textbf{Lucene}\\[0.1cm]}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c@{}r}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & & \textbf{Bugs}\\
+  1 &  0.75-weight &    0.66  &  0.2 & \quart{0}{21}{13}{49} & 97 \\
+\hline  2 & 0.75-weight-B=50\% &    0.7  &  0.1 & \quart{14}{10}{17}{49} & 103 \\
+\hline  3 &         0.75 &    0.77  &  0.3 & \quart{9}{33}{24}{49} & 113\\
+  3 & 0.75-weight-B=25\% &    0.8  &  0.09 & \quart{21}{10}{28}{49} & 117\\
+  3 &   0.5-weight &    0.81  &  0.09 & \quart{26}{9}{29}{49} & 119\\
+  3 &          0.5 &    0.84  &  0.1 & \quart{26}{10}{32}{49} & 123\\
+\hline  4 & 0.5-weight-B=50\% &    0.88  &  0.07 & \quart{34}{8}{36}{49} & 128\\
+  4 & 0.25-weight-B=25\% &    0.89  &  0.07 & \quart{36}{8}{38}{49} & 130 \\
+  4 &  0.25-weight &    0.92  &  0.04 & \quart{39}{4}{41}{49} & 133 \\
+  4 &         0.25 &    0.93  &  0.07 & \quart{36}{8}{42}{49} & 136 \\
+\hline  5 & 0.25-weight-B=50\% &    0.95  &  0.04 & \quart{42}{4}{44}{49} & 139 \\
+  5 & 0.5-weight-B=25\% &    0.96  &  0.03 & \quart{43}{3}{45}{49} &141 \\
+\hline  6 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 146\\
+\hline \end{tabular}}
+%\end{minipage}\\[0.1cm]
+
+%\noindent\begin{minipage}{0.5\textwidth}
+%  \flushleft
+\vspace{2mm}\noindent{\scriptsize \textbf{Poi}\\[0.1cm]}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c@{}r}}
+      \arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & & \textbf{Bugs}\\
+  1 &  0.75-weight &    0.72  &  0.26 & \quart{0}{29}{18}{49} & 173\\
+  1 &         0.75 &    0.74  &  0.18 & \quart{12}{20}{20}{49} & 178\\
+\hline  2 & 0.75-weight-B=50\% &    0.79  &  0.15 & \quart{14}{17}{26}{49} & 190\\
+  2 &          0.5 &    0.81  &  0.15 & \quart{22}{17}{28}{49} & 195\\
+  2 &   0.5-weight &    0.81  &  0.14 & \quart{21}{16}{28}{49} & 195\\
+\hline  3 & 0.5-weight-B=50\% &    0.9  &  0.11 & \quart{30}{13}{38}{49} & 217\\
+  3 &         0.25 &    0.91  &  0.07 & \quart{35}{8}{39}{49} & 219\\
+  3 &  0.25-weight &    0.91  &  0.05 & \quart{36}{6}{39}{49} & 219\\
+\hline  4 & 0.75-weight-B=25\% &    0.94  &  0.05 & \quart{39}{6}{43}{49} & 226\\
+  4 & 0.25-weight-B=50\% &    0.94  &  0.06 & \quart{39}{7}{43}{49} & 226\\
+\hline  5 & 0.25-weight-B=25\% &    0.96  &  0.03 & \quart{44}{3}{45}{49} & 231\\
+  5 & 0.5-weight-B=25\% &    0.96  &  0.03 & \quart{44}{3}{45}{49} & 231\\
+\hline  6 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 240 \\
+\hline \end{tabular}}
+%\end{minipage}
+\caption{Results on  Jureczko   data sets. Baseline values shown at bottom. All other values
+are ratios of baselines.}
+\label{tab:ant}
 \end{figure}
 
-\subsection{Visualisations of Changes}
-
-In this section, we show some sample results. In the next section, we conduct a statistical
-analysis of all   results.
-
-\fig{bugs} shows the effects of planning on the five good Jureczko data sets. Note that:
+   \subsection{Procedures}
+   The procedure used to build and test HOW's plans was shown above in \fig{work}.
+The    Seigmund and Jureczko data sets have continuous and discrete classes (respectively).
+Hence, when building a predictor, we used (1)~Random Forest Regressors for the Seigmund data and (2)~Random Forests
+for the Jureczko data.
+
+   For both the Siegmind and Jureczko, we designed a procedure such we had at least
+   20 samples from the \fig{work} procedure for  each data set (the value of 20 was choosen as the minimum use sample size via the central limit theorem):
    \bi
    \item
-The number of defects predicted in the ``after'' set is always less than ``before'';
+  For the Siegmind data set of \fig{cpm}, 
+  25 times, 
+  we randomized the order of the data, trained on the first half (using
+  Random Forest Regressor), then tested on the second half.
   \item
-The reduction can be quite large: e.g. see the over 50\% reduction in the {\em ant} data set.
+  For the Jureczko, if we just  used the training and test sets of  \fig{j}, that would only
+  give us sample per data set. Such a singleton sample could hide important details since the methods
+  used for parameter tuning (SMOTE and differential evolution) use some stochastic sub-routines.
+  Hence, for each  of the training sets of \fig{j}, we ran SMOTE+differential evolution 25 times to learn
+  parameters for Random Forests.
   \ei
-
- \begin{figure*}[htbp!]
-\centering
-\begin{minipage}{0.30\linewidth}
-\includegraphics[width=\linewidth]{_figs/Apache.pdf}
-\end{minipage}
-\begin{minipage}{0.30\linewidth}
-\includegraphics[width=\linewidth]{_figs/BDBJ.pdf}
-\end{minipage}
-\begin{minipage}{0.30\linewidth}
-\includegraphics[width=\linewidth]{_figs/BDBC.pdf}
-\end{minipage}\\[0.25cm]
-
-\begin{minipage}{0.30\linewidth}
-\includegraphics[width=\linewidth]{_figs/LLVM.pdf}
-\end{minipage}
-\begin{minipage}{0.30\linewidth}
-\includegraphics[width=\linewidth]{_figs/SQL.pdf}
-\end{minipage}
-\begin{minipage}{0.30\linewidth}
-\includegraphics[width=\linewidth]{_figs/X264.pdf}
-\end{minipage}
-\caption{Run time optimization using HERE .
-Blue curve represents a mutation probability of 0.75 with feature weighting and information pruning; Red curve represents a mutation probability of 0.25 with feature weighting, but no information pruning; Black curve represents the raw test data used as baseline for the comparison.}
-\label{fig:pp}
-\end{figure*}
-
-\fig{pp} shows the effects of planning on the Seigmund data sets. The black, red %XXX
-curves show the
-runtimes as predicted in the test sets before/after our planning.  While some of the differences
-are small (eg. LLVM and SQL), some of the others are very large indeed (e.g. the Apache and   BD*).
-
-This visual samples of HOW's planning results look promising-- but they need to be confirmed by a
- more rigorous statistical analysis.
-
-\subsection{Statistical Analysis}
-
-HOW's performance can be adjusted in numerous ways:
+\fig{where} defined two control parameters for HOW:
 \bi
@@
 \item The $B$ variable controls how many of the attributes are displaced;
-\item The $w_i$ weight inside our distance calcylation controls how important are each variable in computing
-     the space between instances. A standard default is $w_i=1$ but this can be adjusted via
-     the {\tt featureWeighting} procedure of \fig{howcode}.
 \ei
-
-To understand how much (if at all) these variables change the planning results, 
-this study ranks methods using the Scott-Knott
+The   25 repeats defined above were executed for various values of $F,B$ and for each data set.
+Those results, summarized below, are presented as horizontal quartile charts. For example,
+the following horizontal quartile chart   shows one result for ``some treatment'' where  the median performance was 20\% and
+the interquartile range (25th to 70th percentile) as 30\%:
+ \begin{center}
+ some treatment 0\%:\quart{0}{29}{18}{49}:100\%
+ \end{center}
+We take all the quartile charts for one data set, sort them on their median value,
+then apply a Scott-Knott procedure to rank each one. 
+The Scott-Knott
 procedure recommended by Mittas \& Angelis in their 2013
@@
 
-To get an overall count of the   in  order to avoid any parametric bias,
-we use the Cliffs Delta score to measure the probability that performance has been changed
-by the planner.   Given the untreated test data labeled \textit{Before} of length \textit{M} and the treated instances labeled \textit{After}, the delta score is obtained as follows:
-\begin{equation}
-\delta = \frac{\#(Before<After) - \#(Before>After)}{M^2}
-\label{eq:cliffs}
-\end{equation}
-
-A $\delta$ of  0 implies no change at all and, according to Romano et al.~\cite{romano06}, a value less
-that 14]7\% is a ``small'' (i.e. negliable) effect.
-
-\begin{figure}[htbp!]
-
-\noindent\begin{minipage}{0.5\textwidth}
-  {\scriptsize \textbf{Ant}\\[0.1cm]}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~~}c@{}r}}
-      \arrayrulecolor{darkgray}
-      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} && \textbf{Bugs}\\
-  1 &  0.75-weight &    0.71  &  0.19 & \quart{0}{25}{10}{49} & 62\\
-  1 &         0.75 &    0.72  &  0.14 & \quart{6}{19}{12}{49} & 64\\
-\hline  2 &          0.5 &    0.86  &  0.08 & \quart{25}{11}{31}{49} & 77 \\
-  2 &   0.5-weight &    0.88  &  0.14 & \quart{20}{19}{33}{49} & 77\\
-\hline  3 & 0.5-weight-B=50\% &    0.91  &  0.08 & \quart{32}{11}{37}{49} & 80\\
-  3 & 0.75-weight-B=50\% &    0.92  &  0.09 & \quart{31}{12}{39}{49} & 82\\
-  3 &  0.25-weight &    0.92  &  0.04 & \quart{36}{5}{39}{49} & 81\\
-\hline  4 &         0.25 &    0.93  &  0.05 & \quart{37}{7}{40}{49} & 83\\
-  4 & 0.75-weight-B=25\% &    0.94  &  0.09 & \quart{36}{12}{41}{49} & 82\\
-\hline  5 & 0.25-weight-B=50\% &    0.97  &  0.03 & \quart{44}{4}{45}{49} & 86\\
-  5 & 0.5-weight-B=25\% &    0.98  &  0.06 & \quart{40}{8}{47}{49} & 86 \\
-\hline  6 & 0.25-weight-B=25\% &    0.99  &  0.01 & \quart{48}{1}{48}{49} & 87\\
-\hline  7 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 90\\
-\hline \end{tabular}}
-\end{minipage}\\[0.1cm]
-
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Ivy}\\[0.1cm]}
-{\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c@{}r}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & & \textbf{Bugs}\\
-  1 &  0.75-weight &    0.75  &  0.18 & \quart{0}{29}{8}{49} & 50\\
-  1 &         0.75 &    0.79  &  0.12 & \quart{8}{20}{14}{49} & 53\\
-\hline  2 &          0.5 &    0.84  &  0.1 & \quart{18}{16}{23}{49} & 56\\
-  2 &   0.5-weight &    0.84  &  0.08 & \quart{14}{14}{23}{49} & 56\\
-  2 & 0.75-weight-B=50\% &    0.84  &  0.09 & \quart{18}{15}{23}{49} & 56 \\
-\hline  3 & 0.5-weight-B=50\% &    0.91  &  0.05 & \quart{29}{9}{34}{49} & 61\\
-\hline  4 & 0.25-weight-B=50\% &    0.96  &  0.01 & \quart{43}{1}{43}{49} & 64\\
-  4 & 0.75-weight-B=25\% &    0.96  &  0.05 & \quart{39}{9}{43}{49} & 65\\
-  4 &         0.25 &    0.97  &  0.01 & \quart{43}{1}{44}{49} & 65\\
-  4 &  0.25-weight &    0.97  &  0.05 & \quart{39}{9}{44}{49} & 65 \\
-  4 & 0.5-weight-B=25\% &    0.97  &  0.03 & \quart{43}{5}{44}{49} & 65 \\
-\hline  5 & 0.25-weight-B=25\% &    0.99  &  0.01 & \quart{48}{1}{48}{49} & 66\\
-\hline  
-6 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 67\\
-\hline \end{tabular}}
-\end{minipage}\\[0.1cm]
-
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Jedit}\\[0.1cm]}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c@{}r}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & & \textbf{Bugs}\\\hline
-  1 &         0.75 &    0.64  &  0.28 & \quart{0}{27}{14}{49} & 110\\
-\hline  2 &  0.75-weight &    0.76  &  0.21 & \quart{13}{21}{26}{49}& 131 \\
-  2 &   0.5-weight &    0.76  &  0.16 & \quart{20}{16}{26}{49} & 130\\
-  2 &          0.5 &    0.79  &  0.17 & \quart{19}{17}{29}{49} & 137\\
-\hline  3 & 0.75-weight-B=50\% &    0.85  &  0.12 & \quart{30}{12}{35}{49} & 146\\
-  3 &  0.25-weight &    0.87  &  0.07 & \quart{34}{7}{37}{49} & 152\\
-\hline  4 &         0.25 &    0.93  &  0.09 & \quart{37}{9}{43}{49} & 161\\
-  4 & 0.5-weight-B=50\% &    0.93  &  0.05 & \quart{41}{5}{43}{49} & 162\\
-\hline  5 & 0.25-weight-B=50\% &    0.97  &  0.03 & \quart{45}{3}{47}{49} & 167\\
-  5 & 0.75-weight-B=25\% &    0.97  &  0.02 & \quart{46}{2}{47}{49} & 168\\
-\hline  6 & 0.5-weight-B=25\% &    0.98  &  0.02 & \quart{47}{2}{48}{49} & 170\\
-  6 & 0.25-weight-B=25\% &    0.98  &  0.01 & \quart{48}{1}{48}{49} & 171\\
-\hline  7 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 175\\
-\hline \end{tabular}}
-\end{minipage}\\[0.1cm]
-
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Lucene}\\[0.1cm]}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c@{}r}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & & \textbf{Bugs}\\
-  1 &  0.75-weight &    0.66  &  0.2 & \quart{0}{21}{13}{49} & 97 \\
-\hline  2 & 0.75-weight-B=50\% &    0.7  &  0.1 & \quart{14}{10}{17}{49} & 103 \\
-\hline  3 &         0.75 &    0.77  &  0.3 & \quart{9}{33}{24}{49} & 113\\
-  3 & 0.75-weight-B=25\% &    0.8  &  0.09 & \quart{21}{10}{28}{49} & 117\\
-  3 &   0.5-weight &    0.81  &  0.09 & \quart{26}{9}{29}{49} & 119\\
-  3 &          0.5 &    0.84  &  0.1 & \quart{26}{10}{32}{49} & 123\\
-\hline  4 & 0.5-weight-B=50\% &    0.88  &  0.07 & \quart{34}{8}{36}{49} & 128\\
-  4 & 0.25-weight-B=25\% &    0.89  &  0.07 & \quart{36}{8}{38}{49} & 130 \\
-  4 &  0.25-weight &    0.92  &  0.04 & \quart{39}{4}{41}{49} & 133 \\
-  4 &         0.25 &    0.93  &  0.07 & \quart{36}{8}{42}{49} & 136 \\
-\hline  5 & 0.25-weight-B=50\% &    0.95  &  0.04 & \quart{42}{4}{44}{49} & 139 \\
-  5 & 0.5-weight-B=25\% &    0.96  &  0.03 & \quart{43}{3}{45}{49} &141 \\
-\hline  6 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 146\\
-\hline \end{tabular}}
-\end{minipage}\\[0.1cm]
-
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{Poi}\\[0.1cm]}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~}c@{}r}}
-      \arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & & \textbf{Bugs}\\
-  1 &  0.75-weight &    0.72  &  0.26 & \quart{0}{29}{18}{49} & 173\\
-  1 &         0.75 &    0.74  &  0.18 & \quart{12}{20}{20}{49} & 178\\
-\hline  2 & 0.75-weight-B=50\% &    0.79  &  0.15 & \quart{14}{17}{26}{49} & 190\\
-  2 &          0.5 &    0.81  &  0.15 & \quart{22}{17}{28}{49} & 195\\
-  2 &   0.5-weight &    0.81  &  0.14 & \quart{21}{16}{28}{49} & 195\\
-\hline  3 & 0.5-weight-B=50\% &    0.9  &  0.11 & \quart{30}{13}{38}{49} & 217\\
-  3 &         0.25 &    0.91  &  0.07 & \quart{35}{8}{39}{49} & 219\\
-  3 &  0.25-weight &    0.91  &  0.05 & \quart{36}{6}{39}{49} & 219\\
-\hline  4 & 0.75-weight-B=25\% &    0.94  &  0.05 & \quart{39}{6}{43}{49} & 226\\
-  4 & 0.25-weight-B=50\% &    0.94  &  0.06 & \quart{39}{7}{43}{49} & 226\\
-\hline  5 & 0.25-weight-B=25\% &    0.96  &  0.03 & \quart{44}{3}{45}{49} & 231\\
-  5 & 0.5-weight-B=25\% &    0.96  &  0.03 & \quart{44}{3}{45}{49} & 231\\
-\hline  6 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 240 \\
-\hline \end{tabular}}
-\end{minipage}
-\caption{Cliffs Delta Scores for the defect data set.
-The Treatment column, has 3 possible configurations, the first (0.25, 0.50, and 0.75) represents the extent of mutation; weighting represents feature weighting; Prune represents the extent of information pruning.}
-\label{tab:ant}
-\end{figure}
-
-\subsection{Performance Prediction Data set}
-
-In this section, 
-\begin{figure*}[htbp!]
-\noindent\begin{minipage}{0.5\textwidth}
-  {\scriptsize \textbf{Apache}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-      \arrayrulecolor{darkgray}
-      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 & 0.75-weight-B=25\% &    0.77  &  0.05 & \quart{0}{14}{5}{74}\\
-  1 &  0.75 &    0.79  &  0.08 & \quart{2}{24}{11}{74}\\
-\hline  2 & 0.75-weight &    0.85  &  0.07 & \quart{14}{21}{29}{74}\\
-  2 & Apache\_50\_w\_iP(25) &    0.85  &  0.04 & \quart{23}{12}{29}{74}\\
-  2 &  Apache\_50 &    0.85  &  0.05 & \quart{26}{15}{29}{74}\\
-\hline  3 & Apache\_50\_w &    0.91  &  0.05 & \quart{38}{15}{47}{74}\\
-\hline  4 &  Apache\_25 &    0.92  &  0.04 & \quart{44}{12}{50}{74}\\
-  4 & Apache\_25\_w\_iP(25) &    0.93  &  0.02 & \quart{50}{6}{53}{74}\\
-\hline  5 & Apache\_25\_w &    0.96  &  0.03 & \quart{56}{9}{62}{74}\\
-\hline  6 & Apache\_baseline &    1.0  &  0.0 & \quart{74}{0}{74}{74}\\\hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{BDBC}\\}
-{\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &     75 &    0.22  &  0.05 & \quart{0}{3}{1}{49} \\
-  1 &  75, weighting, Prune=25\% &    0.21  &  0.04 & \quart{0}{2}{0}{49} \\
-\hline  2 &  75, weighting &    0.24  &  0.1 & \quart{0}{6}{2}{49} \\
-\hline  3 &     50 &    0.4  &  0.04 & \quart{11}{2}{12}{49} \\
-  3 &  50, weighting, Prune=25\% &    0.4  &  0.05 & \quart{10}{3}{12}{49} \\
-\hline  4 &  50, weighting &    0.47  &  0.09 & \quart{14}{5}{16}{49} \\
-\hline  5 &     25 &    0.66  &  0.03 & \quart{28}{1}{28}{49} \\
-  5 &  25, weighting, Prune=25\% &    0.67  &  0.06 & \quart{28}{3}{29}{49} \\
-\hline  6 &  25, weighting &    0.69  &  0.06 & \quart{29}{4}{30}{49} \\
-\hline  7 &  baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-\hline \end{tabular}}
-\end{minipage}
-
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{BDBJ}\\}
-{\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &     75 &    0.63  &  0.16 & \quart{0}{19}{3}{49} \\
-  1 &  75, weighting, Prune=25\% &    0.68  &  0.17 & \quart{1}{21}{9}{49} \\
-  1 &  75, weighting &    0.74  &  0.11 & \quart{8}{14}{17}{49} \\
-\hline  2 &  50, weighting, Prune=25\% &    0.75  &  0.09 & \quart{14}{12}{18}{49} \\
-  2 &     50 &    0.79  &  0.13 & \quart{16}{16}{23}{49} \\
-\hline  3 &  50, weighting &    0.82  &  0.09 & \quart{23}{11}{27}{49} \\
-\hline  4 &  25, weighting, Prune=25\% &    0.87  &  0.07 & \quart{29}{9}{33}{49} \\
-\hline  5 &     25 &    0.88  &  0.06 & \quart{33}{8}{34}{49} \\
-  5 &  25, weighting &    0.92  &  0.06 & \quart{36}{7}{39}{49} \\
-\hline  6 &  baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-\hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{LLVM}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &     75 &    0.92  &  0.01 & \quart{5}{6}{5}{49} \\
-  1 &  75, weighting, Prune=25\% &    0.92  &  0.02 & \quart{0}{11}{5}{49} \\
-  1 &  75, weighting &    0.93  &  0.02 & \quart{5}{11}{11}{49} \\
-\hline  2 &     50 &    0.94  &  0.01 & \quart{16}{6}{16}{49} \\
-  2 &  50, weighting, Prune=25\% &    0.95  &  0.0 & \quart{22}{0}{22}{49} \\
-  2 &  50, weighting &    0.96  &  0.02 & \quart{22}{11}{27}{49} \\
-\hline  3 &     25 &    0.98  &  0.01 & \quart{33}{5}{38}{49} \\
-  3 &  25, weighting, Prune=25\% &    0.98  &  0.01 & \quart{33}{5}{38}{49} \\
-  3 &  25, weighting &    0.98  &  0.0 & \quart{38}{0}{38}{49} \\
-\hline  4 &  baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-\hline \end{tabular}}
-\end{minipage}
-
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{SQL}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &      75 &    0.98  &  0.01 & \quart{0}{16}{16}{49} \\
-  1 &  75, weighting, Prune=25\% &    0.98  &  0.0 & \quart{16}{0}{16}{49} \\
-  1 &  75, weighting &    0.99  &  0.01 & \quart{16}{17}{33}{49} \\
-  1 &  50, weighting, Prune=25\% &    0.99  &  0.0 & \quart{33}{0}{33}{49} \\
-  1 &      50 &    0.99  &  0.0 & \quart{33}{0}{33}{49} \\
-  1 &  50, weighting &    0.99  &  0.01 & \quart{33}{16}{33}{49} \\
-  1 &  25, weighting, Prune=25\% &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-  1 &      25 &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-  1 &  25, weighting &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-  1 &  baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-  \hline \end{tabular}}
-\end{minipage}
-\noindent\begin{minipage}{0.5\textwidth}
-  \flushleft
-  {\scriptsize \textbf{X264}\\}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{~~~~}r@{~~~~}r@{~~~~}c}}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 &  75, weighting, Prune=25\% &    0.73  &  0.05 & \quart{1}{9}{3}{49} \\
-  1 &     75 &    0.74  &  0.05 & \quart{0}{8}{5}{49} \\
-\hline  2 &  75, weighting &    0.81  &  0.04 & \quart{13}{7}{17}{49} \\
-  2 &  50, weighting, Prune=25\% &    0.82  &  0.04 & \quart{17}{7}{18}{49} \\
-  2 &     50 &    0.83  &  0.03 & \quart{17}{5}{20}{49} \\
-\hline  3 &  50, weighting &    0.88  &  0.03 & \quart{25}{6}{29}{49} \\
-\hline  4 &     25 &    0.9  &  0.03 & \quart{31}{5}{32}{49} \\
-  4 &  25, weighting, Prune=25\% &    0.91  &  0.03 & \quart{32}{5}{34}{49} \\
-\hline  5 &  25, weighting &    0.93  &  0.02 & \quart{36}{3}{37}{49} \\
-\hline  6 &  baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-\hline \end{tabular}}
-\end{minipage}
-\end{figure*}
+\subsection{Results}
+The results for each data set, for different ranges of $(F,B)$ are shown in \fig{ant} and \fig{xxx}.
+Also included are a {\em baseline} figure which is taken from the cases in the test data
+and  Since we wish to demonstrate
+improving defects
+(for Jureczko data) and runtimes (for the Seigmund data), all our results are presented as ratios of the baseline (so numbers less than 1.0 indicate improvements).
 
@@
 
-\clearpage
 \bibliography{how}{}

### 2015-05-12 how.tex
Updates from ShareLaTeX

@@
 \documentclass[conference]{IEEEtran}
-%related work (gentling them in)
 %future work: local patch operator
 %complexity
-% planning in ai
 
@@
  For the test data of this paper, those improvements   reduce
- defect counts and  runtimes by   
- (25,33)\% (median)   to (37,78)\% (max) of
- their original values.
+ the expected values of defect counts and  runtimes to    
+ 72\%,75\%  (median) and 66\%,20\% (best case) of the initial values.
   \end{abstract}
@@
 \section{Introduction}
+Suppose someone suggests a change to your project. How might you assess the effectiveness of that change?
+
+This is an open and pressing issue.
 Business  users   now demand   data mining tools
@@
 and follow-up
-that occurs {\em after} the mining, rather than just  the mining itself. For example:
+that occurs {\em after} the mining, rather than just  the mining itself; e.g.
 \bi
@@
 \ei
-In this paper, we say   a ``plan'' is a  set of changes
+How to assess such {\em plans}?
+Some organizations have the resources to 
+run repeated trials to assess  different treatments.
+For example, in one remarkable recent study, Bente et al. report results
+were the same specification was developed into a product by four different organizations~\cite{Anda2009}. Given those kind of resources, it would be possible
+to (say) take a code base, assign it to $N$ different teams, apply
+HOW's plans the code used by  $N/2$ teams, then check in 12 months time
+if those halves of the teams have fewer defects than the other.
+
+Very few industrial or research groups have access
+to the kinds of resources using by Bente et al. (evidence: in the size years since the
+publication of that work, we know of only one of two similar studies). Also, given the
+diversity of modern software projects, it might be unreasonable to demand that all
+proposed changes for all projects are always evaluated by something like the Bente et al. study.
+
+This paper proposes another, less resource intensive,  method for assessing the effectiveness of proposed
+changes to a project.  
+We propose using prediction systems (built by data mining) as a verification
+tool for planners. In domains where  data miners can build
+predictors of adequate performance, then those predictors can assess the value
+of proposed changes.
+
+The planner explored in this paper is the ``HOW'' case-based planner.
+HOW's  ``plans'' are  set of changes
 proposed  in order to better achieve some goal. 
-Specifically, for every $Z$  that requests a plan $\delta$ to
+Specifically, for every test case $Z$, HOW proposes a  plan $\delta$ to
   adjust   attributes $Z_j$:
@@
 \end{equation}
-The usual way such plans are generated in the SE literature
-is via some search-based method. Recently, we have made  some progress
-in this area with the  GALE optimizer~\cite{krall14}. 
-Like other search-based algorithms,
- GALE executes by proposing multiple $\delta$s
- (one for each generation in an evolutionary program).
- In practice, GALE makes
- extensive changes to initial sample of project data
- (perhaps 
-100s to 100,000s of mutations). Each of these mutations
-is reassessed using some domain model.
-GALE uses an eigenvector technique to find better mutants faster than standard search-based SE tools~\cite{deb00a,zit02}.
-
-When presented to some  software project managers, the GALE approach was challenged by
-two business users. Note that the   issues they raise are
-challenges not just  about GALE, but also  about any     optimization algorithm  that  
- make extensive use of mutation  and domain models.
-One  user asked:
-\begin{quote}
-ISSUE~\#1: {\em ``What if I only want the minimum useful change, not
-the maximum possible?''}
+For example, to simplify a  large bug-prone  method, HOW might suggest
+to a developer to reduce its size (i.e.  refactor that code by, say, splitting it across
+two simpler functions).
+
+HOW's  plans displace the test case into some region
+of the training data. This is important since we will use that training data
+to build a predictor to assess the impact of that plan.
+To put that another way, when a novel test case is presented,
+HOW says 
+\begin{quote}{\em ``I may not know too much about that, but once you change into something like
+what I've already seen, then I can suggest how to change it''.}
 \end{quote}
-Here, the business user is asking for solutions  that do not require extensive 
-changes to their current  approaches.
-
-Later in that discussion, another business user asked:
-\begin{quote}
-ISSUE~\#2: {\em ``But what if I do not have a domain model of my business?''}
-\end{quote}
-This also is a legitimate issue.
-As discussed below,
-building (or accessing) and certifying and maintaining a 
-trust-worthy model  can  takes  long time, especially in software engineering.
-
-This paper addresses  ISSUE~\#1 and ISSUE~\#2 using case-based reasoning.
-CBR  is purely based on the direct
-adaptation of previous cases based on the similarity of
-those cases with the current situation. That is, 
-CBR based system have no explicit world model.
-Rather, that model is implicit within  the available past
-cases in the case cache.
-
-This paper presents a novel CBR tool called ``HOW''. This tool  restricts test data $\delta$s to {\em minimal
-displacements} (very small changes to a subset of the attributes)
-thereby addressing ISSUE \#1. 
-HOW ensures that the   $\delta$ displaces test data towards some region in the training data.
-This is important since we address ISSUES~\#2 via some data mining
-tool that train  a predictor from the training  data. Since we are pushing test data
-into regions of the training data,  we can use the predictor to assess
-the effectiveness of the $\delta$.
-This paper shows that  that HOW's plans can be very effective indeed.
-In the experiments shown below, HOW's plans
-reduced the  expected
+This paper shows experimentally  that   HOW's plans can be quite effective and 
+ significantly reduce the  predicted
 value of:
@@
 \ei 
-In summary, this paper makes five contributions:
-\be
-\item The HOW  case-based planner (which has not been presented before).
-\item The experiments of this paper showing that HOW planner is useful for real-world tasks;
-e.g. reducing the
-expected values of the Jureczko software defects and the Seigmund software runtimes.
-\item Apart from HOW, we  also offers a general framework for using  predictive system to build planners;
-\item Further, we offer a  test to recognizes  when we should {\em not}  plan: specifically,
-planning is
-not recommended in domains with  poorly performing predictors;
-\item Last, we  offer a general verification rig for assessing the value of plans generated within this rig.
-\ee
-
-\section{Background and Related Work}
-\subsection{Search-based Software Engineering (SBSE)} CPUs are becoming
-faster and cloud computing enables access to more CPUs. Hence, it is now pratical
-to solve large problems in SBSE via 
-genetic algorithms  that build multiple generations by  mutating  an existing population,  
-the combine the best mutants to fond the next population~\cite{Harman2009,Harman2011}.
+The rest of this paper presents the background to this work in Section~2; the design of HOW in Section~3;
+then our experimental results  in Section~4. Those experiments show that HOW can   reduce the expected
+value of defects in Jureczko   data sets by 72\% to 66\%  (median,best).
+Also, in the Seigmund data sets, HOW can   reduce the expected value of the runtimes by  75\% to 20\% (median,best).
+
+\section{Background}
+\subsection{Search-based Software Engineering (SBSE)}
+One way to propose changes to software artifacts
+is   via some search-based method~\cite{Harman2009,Harman2011}. Such SBSE methods are   evolutionary programs that 
+make
+ extensive changes to  some initial sample of project data
+ (perhaps 
+100s to 100,000s of mutations). Each of these mutations
+is reassessed using some domain model.
 Examples of these algorithms include GALE, NSGA-II, NSGA-III, SPEA2, IBEA, particle swarm optimization, MOEA/D, etc.~\cite{krall14,deb00a,zit02,zit04,%
@@
 
-SBSE methods can make extensive mutations to the data they are exploring. Hence, these methods
+These SBSE methods can make extensive mutations to the data they are exploring. Hence, these methods
 require some domain model that can assess new and highly novel examples.
@@
 
- HOW    is very different
-to the above CBR systems.
-Firstly, HOW is a {\em planner} while the above
-CBR methods are all {\em prediction} algorithms\footnote{The disctiniction being that
-predictions systems tell you ``what is'', while planners tell you ``what to do''.}.
-Secondly, all the above CBR tools explore the nearest ``k'' neighors,
-HOW, on the other hand,  explores the {\em gradient between the scores of pairs of nearest neighbors}. 
-To put that
-another way,   the above CBR methods explore {\em points} while
-HOW explores the slope {\em between} points.
-
 \subsection{Prior Work}
+
 HOW is the third
-generation of our experiments with planning and CBR.
-Generation one of that work resulted in
+generation of our exploration of  planning and CBR and software engineering.
+Generation one  resulted in
  W2, a CBR planner that reflected over the delta of raw  attributes~\cite{6600685}.
@@
 \section{How to Build ``HOW''?}\label{sec:mm}
+
+HOW is very different to other CBR systems. Firstly, HOW is a {\em planner} while many
+CBR methods in software engineering explore  {\em prediction} algorithms\footnote{The distinction being that
+predictions systems tell you ``what is'', while planners tell you ``what to do''.}.
+Secondly, all the above CBR tools explore the nearest ``k'' neighors,
+HOW, on the other hand, explores the {\em gradient between the scores of pairs of nearest neighbors}. 
+To put that another way, the above CBR methods explore {\em points} while
+HOW explores the slope {\em between} points.
+
+\fig{howcode}, line~1, shows  an implementation of such a {\tt Slope} class and
+the rest
+of this section  details   {\tt Slope}'s role within the HOW system.
 
@@
 
-\begin{figure}[t!]
+\begin{figure}[b!]
 \small
@@
 By convention, we say that the cluster containing $X$ has the  better objective scores. This means we can say that the {\tt Slope} is a useful direction for displacing
-data; i.e.  away from $Y$ and towards $X$ (for an implementation of such a {\tt Slope} class, see \fig{howcode}, line~1).
+data; i.e.  away from $Y$ and towards $X$. 
  During testing,  HOW   finds the  nearest {\tt Slope} to every test case. That  test case is   then displaced towards the better end
@@
  HOW needs to  determine the  exact {\em direction} and {\em magnitude} of 
-displacement.  To address  ISSUE~\#1,
+displacement.   
 HOW uses two techniques to result in 
-{\em minimal displacements} of project data. Firstly,
+{\em minimal displacements} of project data. Those techniques are described below. Note
+ that the net result of these techniques is to drive the test case into some region of the training 
+ set (this is important since we will use a predictor learned from that training data to assess
+ the effectiveness of HOW's plans).
+
+ Firstly,
 HOW sorts  the independent variables
@@
 test case $Z$ and  $X$ is the exemplar found at training time,
-then we displace $Z$ as follows:
+then we displace $Z_j$ as follows:
 \[Z_j =  Z_j + F*(X_j - Z_j)\]
-Here, $F$ is the  magnitude controller, discussed above. Note that this
-this equations satisfies our definition of a ``plan'' as offered in
-\eq{one} in the  Introduction.
+Here, $F$ is the  magnitude controller, discussed above.
 
@@
 Note that using the best as the exemplar does better than useing the mean.
-The pattern shown in \fig{pp} has been seen in all the Seigmund data sets;
+The general pattern shown of \fig{pp} has been seen in all the Seigmund data sets;
 i.e. for data sets with continuous classes,
@@
 
+\begin{figure*}[!t]
+\scriptsize
+   \begin{center}
+   \begin{minipage}{.46\linewidth}
+    \begin{tabular}{r@{~}|l@{~}|r@{~}|l@{~}|r@{~}|r@{~}|} \cline{2-6}
+   & \multicolumn{5}{c|}{ }\\
+
+   & \multicolumn{5}{c|}{ Data set  properties}\\ 
+   & \multicolumn{5}{c|}{  }\\ 
+           & \multicolumn{2}{c|}{training}   & \multicolumn{3}{c|}{testing}      \\ \cline{2-6}
+   data set      & versions           & cases & versions     & cases    & \% defective             \\ \hline
+        jedit    & 3.2, 4.0, 4.1, 4.2 & 1257      & 4.3          & 492          & 2 \\
+        ivy      & 1.1, 1.4           & 352       & 2.0          & 352          & 11 \\
+        camel    & 1.0, 1.2, 1.4      & 1819      & 1.6          & 965          & 19 \\
+        ant      & 1.3, 1.4, 1.5, 1.6 & 947       & 1.7          & 745          & 22 \\
+        synapse  & 1.0, 1.1           & 379       & 1.2          & 256          & 34 \\
+        velocity & 1.4, 1.5           & 410       & 1.6          & 229          & 34 \\
+        lucene   & 2.0, 2.2           & 442       & 2.4          & 340          & 59 \\
+        poi      & 1.5, 2, 2.5        & 936       & 3.0          & 442          & 64 \\
+        xerces   & 1.0, 1.2, 1.3      & 1055      & 1.4          & 588          & 74  \\ 
+        log4j    & 1.0, 1.1           & 244       & 1.2          & 205          & 92   \\
+        xalan    & 2.4, 2.5, 2.6      & 2411      & 2.7          & 909          & 99  \\\hline
+
+    \end{tabular}\end{minipage}\begin{minipage}{.4\linewidth}
+    \begin{tabular}{|rrr|rrr|rr|l} \cline{1-8}
+      \multicolumn{8}{|c|}{  }\\
+      \multicolumn{8}{|c|}{  Results from learning}\\
+       \multicolumn{8}{|c|}{   }\\
+   \multicolumn{3}{|c|}{untuned} & \multicolumn{3}{c|}{tuned} & \multicolumn{2}{c|}{change}\\
+  \cline{1-8}
+
+  pd & pf & good? & pd & pf & good? & pd & pf\\\cline{1-8}
+  50 & 27 &   & 64 & 28 & y & 14 & 1&$\star$\\
+  65 & 35 & y & 65 & 25 & y & 0 & -10&$\star$\\
+  50 & 30 &   & 62 & 41 &   & 12 & 11\\
+  66 & 21 & y & 63 & 18 & y & -3 & -3\\
+  45 & 18 &   & 47 & 15 &   & 2 & -3\\
+  79 & 61 &   & 77 & 61 &   & -2 & 0\\
+  55 & 25 &   & 60 & 27 & y & 5 & 2\\
+  51 & 32 &   & 61 & 12 & y & 10 & -20&$\star$\\
+ 30 & 28 &   & 39 & 33 &   & 9 & 5&$\times$\\
+  32 & 6 &   & 30 & 9 &   & -2 & 3&$\times$\\
+  41 & 5 &   & 48 & 0 &   & 7 & -5&$\times$\\
+\hline 
+\end{tabular}
+
+\end{minipage}
+\end{center}
+
+    \caption{Training and test {\em data set properties} for the Jureczko data sets,
+    sorted in ascending order of \% defective examples.
+    On the right-hand-side, we show the {\em results from learning}.
+    Data is ``good'' if it has   recalls over 60\% and false alarms under 40\%
+(and note that, after tuning, there are more ``good'' than before).
+Data   marked with ``$\star$'' show large improvements in performance, after tuning.
+Data   marked with ``$\times$'' are not ``good'' since their test suites  have so few undefective examples (less than 5\% of the total sample) that it becomes harder to find better data towards which we can displace test data.
+}\label{fig:j}
+\end{figure*}
+
 \subsection{Assessment}\label{sect:assess}
@@
 tools, as shown by Binkely et al. in 2006~\cite{Binkley2006} and more recently by Mkaouer et al. in 2015~\cite{Mkaouer15}.}. How are we to verify that HOW's recommendations actually work?
-
-Some organizations have the resources to 
-run repeated trials to assess the effect of different treatments.
-For example, in one remarkable recent study, Bente et al. report results
-were the same specification was developed into a product by four different organizations~\cite{Anda2009}. Given those kind of resources, it would be possible
-to (say) take a code base, assign it to $N$ different teams, apply
-HOW's plans the code used by  $N/2$ teams, then check in 12 months time
-if those halves of the teams have fewer defects than the other.
-
-Very few industrial or research groups have access
-to the kinds of resources using by Bente et al. (evidence: in the size years since the
-publication of that work, we know of only one of two similar studies). Hence, it
-we wish to verify HOW's plans, then some other framework is required that is less
-resource intensive.
-
-We propose using prediction systems (built by data mining) as a verification
-tool for planners. In domains with data, from which data miners can build
-predictors of adequate performance, then those predictors can assess the value
-of the changes proposed by HOW.
 
@@
 Turning now to the {\em test} data, this is passed to the { predictor}
-to generate a baseline {\em before} performance score.
-Note that if our { predictors} fail to perform adequately on the test data,
+to generate a baseline {\em before}  score.
+If our { predictors} fail to perform adequately on the test data,
 then we cannot trust them to comment on our plans. Accordingly,
@@
 
-\begin{figure*}[!t]
-\scriptsize
-   \begin{center}
-   \begin{minipage}{.46\linewidth}
-    \begin{tabular}{r@{~}|l@{~}|r@{~}|l@{~}|r@{~}|r@{~}|} \cline{2-6}
-   & \multicolumn{5}{c|}{ }\\
-
-   & \multicolumn{5}{c|}{ Data set  properties}\\ 
-   & \multicolumn{5}{c|}{  }\\ 
-           & \multicolumn{2}{c|}{training}   & \multicolumn{3}{c|}{testing}      \\ \cline{2-6}
-   data set      & versions           & cases & versions     & cases    & \% defective             \\ \hline
-        jedit    & 3.2, 4.0, 4.1, 4.2 & 1257      & 4.3          & 492          & 2 \\
-        ivy      & 1.1, 1.4           & 352       & 2.0          & 352          & 11 \\
-        camel    & 1.0, 1.2, 1.4      & 1819      & 1.6          & 965          & 19 \\
-        ant      & 1.3, 1.4, 1.5, 1.6 & 947       & 1.7          & 745          & 22 \\
-        synapse  & 1.0, 1.1           & 379       & 1.2          & 256          & 34 \\
-        velocity & 1.4, 1.5           & 410       & 1.6          & 229          & 34 \\
-        lucene   & 2.0, 2.2           & 442       & 2.4          & 340          & 59 \\
-        poi      & 1.5, 2, 2.5        & 936       & 3.0          & 442          & 64 \\
-        xerces   & 1.0, 1.2, 1.3      & 1055      & 1.4          & 588          & 74  \\ 
-        log4j    & 1.0, 1.1           & 244       & 1.2          & 205          & 92   \\
-        xalan    & 2.4, 2.5, 2.6      & 2411      & 2.7          & 909          & 99  \\\hline
-
-    \end{tabular}\end{minipage}\begin{minipage}{.4\linewidth}
-    \begin{tabular}{|rrr|rrr|rr|l} \cline{1-8}
-      \multicolumn{8}{|c|}{  }\\
-      \multicolumn{8}{|c|}{  Results from learning}\\
-       \multicolumn{8}{|c|}{   }\\
-   \multicolumn{3}{|c|}{untuned} & \multicolumn{3}{c|}{tuned} & \multicolumn{2}{c|}{change}\\
-  \cline{1-8}
-
-  pd & pf & good? & pd & pf & good? & pd & pf\\\cline{1-8}
-  50 & 27 &   & 64 & 28 & y & 14 & 1&$\star$\\
-  65 & 35 & y & 65 & 25 & y & 0 & -10&$\star$\\
-  50 & 30 &   & 62 & 41 &   & 12 & 11\\
-  66 & 21 & y & 63 & 18 & y & -3 & -3\\
-  45 & 18 &   & 47 & 15 &   & 2 & -3\\
-  79 & 61 &   & 77 & 61 &   & -2 & 0\\
-  55 & 25 &   & 60 & 27 & y & 5 & 2\\
-  51 & 32 &   & 61 & 12 & y & 10 & -20&$\star$\\
- 30 & 28 &   & 39 & 33 &   & 9 & 5&$\times$\\
-  32 & 6 &   & 30 & 9 &   & -2 & 3&$\times$\\
-  41 & 5 &   & 48 & 0 &   & 7 & -5&$\times$\\
-\hline 
-\end{tabular}
-
-\end{minipage}
-\end{center}
-
-    \caption{Training and test {\em data set properties} for the Jureczko data sets,
-    sorted in ascending order of \% defective examples.
-    On the right-hand-side, we show the {\em results from learning}.
-    Data is ``good'' if it has   recalls over 60\% and false alarms under 40\%
-(and note that, after tuning, there are more ``good'' than before).
-Data   marked with ``$\star$'' show large improvements in performance, after tuning.
-Data   marked with ``$\times$'' are not ``good'' since their test suites  have so few undefective examples (less than 5\% of the total sample) that it becomes harder to find better data towards which we can displace test data.
-}\label{fig:j}
-\end{figure*}
-
-\subsection{When Not to Plan: the Problem of Poor Predictors}
+\subsection{When Not to Plan: the Problem of Poor Predictors}\label{sec:notplan}
 
@@
 The ``tuned'' columns of \fig{j} show that we can salvage some of the data sets.
- Pelayo and Dick~\cite{pelayo07} report that defect prediction can be improved via SMOTE~\cite{Chawla2002}; i.e. an over-sampling of minority-class examples.
+ Pelayo and Dick~\cite{pelayo07} report that defect prediction is improved by SMOTE~\cite{Chawla2002}; i.e. an over-sampling of minority-class examples.
  Also, Fu et al.~\cite{fu:ase15} report that parameter tuning with differential evolution~\cite{storn97}
-applied to defect predictors can quickly explore the tuning
-options of Random Forest to find better settings for the size of the forest, the termination criteria
+can quickly explore the tuning
+options of Random Forest to find better settings for the (e.g.) size of the forest, the termination criteria
 for tree generation, etc.
@@
 techniques. For example, in {\em poi}, the recall increased by 10\% while the false alarm rate dropped by 20\%.
-However,  as might be expected
-the data sets in the  three bottom rows remain
-unsalvageable.
+However,  as might have been  expected
+we could not salvage the data sets in the  three bottom rows.
 
@@
 \subsection{Data}
-To assess HOW, we applied its plans to all the Seigmund data, and the five ``good''
+We applied HOW's plans to all  Seigmund data, and the five ``good''
   Jureczko   data sets {\em jedit, ivy, ant, lucene} and {\em poi}.
@@
   sets, training was managed by a Random Forest (tuned in the SMOTED training data using differential
-  evolution). \fig{ck} shows the attributes in the Jureczko data.
-
-  The Seigmund data sets are far more varied than the Jurecko data.
-  These contain the results of applying a large number of mutators
-  to the configuration options of the Makefiles of  BerkeleyDB (the Java  and  Windows  versions),  Apache,  SQLite,  LLVM, and x264. For details on those datasets, see \fig{cpm}.
+  evolution). \fig{ck} shows Jureczko data attributes.
+
+   \fig{cpm} shows the  Seigmund data attributes.
+   There were more diverse than the 
+    Jurecko data since they
+   contain the results of applying many  mutators
+  to the configuration options of the Makefiles of  BerkeleyDB (the Java  and  Windows  versions),  Apache,  SQLite,  LLVM, and x264.
 
@@
 
+   \subsection{Procedures}
+  \fig{work} showed how to   build and test HOW's plans.
+The    Seigmund and Jureczko data sets have continuous and discrete classes (respectively).
+Hence, when building a predictor, we used (1)~Random Forest Regressors for the Seigmund data and (2)~Random Forests
+for the Jureczko data.
+
+   For both the Siegmind and Jureczko, we designed a procedure such we had at least
+   20 samples from the \fig{work} procedure for  each data set (the value of 20 was choosen as the minimum use sample size via the central limit theorem):
+   \bi
+   \item
+  For the Siegmind data, 
+  25 times, 
+  we randomized the order of the data, trained on one half (via
+  Random Forest Regressor), then tested on the other.
+  \item
+  For the Jureczko, if we just  used the training and test sets of  \fig{j}, that would only
+  give us sample per data set. Such a singleton sample could hide important details since the methods
+  used for parameter tuning (SMOTE and differential evolution) use some stochastic sub-routines.
+  Hence, for each  of the training sets of \fig{j}, we ran SMOTE+differential evolution 25 times to learn
+  parameters for Random Forests.
+  \ei
+\fig{where} defined two control parameters for HOW:
+\bi
+\item  $F$   controls the size of the displacement;
+\item   $B$   controls how many  attributes are displaced.
+\ei
+The   25 repeats defined above were executed for various values of $F,B$.
+A Scott-Knott procedure was used to test for statistically significant differences in the results.
+The Scott-Knott
+procedure recommended by Mittas \& Angelis in their 2013
+IEEE TSE paper~\cite{mittas13}.  This method
+sorts a list of $l$ treatments with $ls$ measurements by their median
+score. It then
+splits $l$ into sub-lists $m,n$ in order to maximize the expected value of
+ differences  in the observed performances
+before and after divisions. E.g. for lists $l,m,n$ of size $ls,ms,ns$ where $l=m\cup n$:
+ $E(\Delta)=\frac{ms}{ls}abs(m.\mu - l.\mu)^2 + \frac{ns}{ls}abs(n.\mu - l.\mu)^2$.
+Scott-Knott  applies an  hypothesis test $H$ to check
+if $m,n$ are significantly different. If so, Scott-Knott  recurses on the splits.
+
 %\begin{figure}[tbp!]
@@
 
+\begin{figure*}[!t]
+\begin{center}
+\begin{minipage}{.44\linewidth}
+%\noindent\begin{minipage}{0.5\textwidth}
+  {\scriptsize \textbf{Apache}\\[0.1cm]}
+  {\scriptsize  \begin{tabular}{{llrrc}}
+      \arrayrulecolor{darkgray}
+      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
+  1 & F=0.75, B=25 &    0.79  &  0.06 & \quart{0}{11}{7}{49} \\
+\hline  2 & F=0.75, B=50 &    0.82  &  0.07 & \quart{7}{14}{13}{49} \\
+\hline  3 &  F=0.75, B=100  &    0.85  &  0.06 & \quart{11}{12}{19}{49} \\
+  3 & F=0.5, B=25 &    0.87  &  0.03 & \quart{19}{6}{23}{49} \\
+  3 & F=0.5, B=50 &    0.87  &  0.07 & \quart{17}{14}{23}{49} \\
+\hline  4 &   F=0.5, B=100  &    0.91  &  0.07 & \quart{21}{14}{31}{49} \\
+\hline  5 & F=0.25, B=25 &    0.92  &  0.05 & \quart{29}{10}{33}{49} \\
+  5 & F=0.25, B=50 &    0.94  &  0.04 & \quart{35}{8}{37}{49} \\
+  5 &  F=0.25,B=100   &    0.95  &  0.04 & \quart{35}{8}{39}{49} \\
+\hline  6 &     Baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
+\hline \end{tabular}}
+
+\vspace{2mm}\noindent {\scriptsize \textbf{BDBC}\\[0.1cm]}
+{\scriptsize  \begin{tabular}{{llrrc}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
+  1 & F=0.75, B=50 &    0.2  &  0.03 & \quart{0}{1}{1}{49} \\
+  1 & F=0.75, B=25 &    0.2  &  0.05 & \quart{0}{3}{1}{49} \\
+\hline  2 &  F=0.75, B=100  &    0.22  &  0.07 & \quart{1}{5}{2}{49} \\
+\hline  3 & F=0.5, B=25 &    0.39  &  0.06 & \quart{11}{4}{12}{49} \\
+  3 & F=0.5, B=50 &    0.4  &  0.05 & \quart{12}{3}{13}{49} \\
+\hline  4 &   F=0.5,B=100   &    0.45  &  0.08 & \quart{14}{4}{16}{49} \\
+\hline  5 & F=0.25, B=25 &    0.65  &  0.05 & \quart{27}{3}{28}{49} \\
+  5 & F=0.25, B=50 &    0.66  &  0.05 & \quart{27}{3}{29}{49} \\
+\hline  6 &  F=0.25,B=100   &    0.69  &  0.05 & \quart{29}{3}{31}{49} \\
+\hline  7 &     Baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
+\hline \end{tabular}}
+%\end{minipage}
+
+\vspace{2mm}\noindent{\scriptsize \textbf{BDBJ}\\[0.1cm]}
+{\scriptsize  \begin{tabular}{{llrrc}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
+  1 & F=0.75, B=25 &    0.64  &  0.1 & \quart{1}{12}{6}{49} \\
+  1 & F=0.75, B=50 &    0.68  &  0.14 & \quart{0}{17}{10}{49} \\
+\hline  2 &  F=0.75, B=100   &    0.74  &  0.1 & \quart{12}{12}{18}{49} \\
+  2 & F=0.5, B=25 &    0.76  &  0.09 & \quart{15}{11}{20}{49} \\
+  2 & F=0.5, B=50 &    0.78  &  0.17 & \quart{15}{21}{23}{49} \\
+  2 &   F=0.5,B=100   &    0.8  &  0.07 & \quart{20}{9}{25}{49} \\
+\hline  3 & F=0.25, B=25 &    0.85  &  0.05 & \quart{30}{6}{31}{49} \\
+\hline  4 & F=0.25, B=50 &    0.89  &  0.09 & \quart{30}{11}{36}{49} \\
+  4 &  F=0.25, B=100  &    0.9  &  0.06 & \quart{35}{7}{37}{49} \\
+\hline  5 &     Baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
+\hline \end{tabular}}
+%\end{minipage}
+%\noindent\begin{minipage}{0.5\textwidth}
+%  \flushleft
+\end{minipage}~~~~~\begin{minipage}{.44\linewidth}
+\noindent
+{\scriptsize \textbf{LLVM}\\[0.1cm]}
+  {\scriptsize  \begin{tabular}{{llrrc}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
+  1 & F=0.75, B=25 &    0.92  &  0.02 & \quart{0}{11}{5}{49} \\
+  1 & F=0.75, B=50 &    0.93  &  0.02 & \quart{5}{11}{11}{49} \\
+  1 &  F=0.75, B=100   &    0.93  &  0.02 & \quart{11}{11}{11}{49} \\
+\hline  2 & F=0.5, B=25 &    0.95  &  0.01 & \quart{16}{6}{22}{49} \\
+  2 & F=0.5, B=50 &    0.95  &  0.01 & \quart{16}{6}{22}{49} \\
+  2 &   F=0.5, B=100   &    0.96  &  0.01 & \quart{22}{5}{27}{49} \\
+\hline  3 & F=0.25, B=25 &    0.97  &  0.01 & \quart{33}{5}{33}{49} \\
+  3 & F=0.25, B=50 &    0.98  &  0.0 & \quart{38}{0}{38}{49} \\
+  3 &  F=0.25, B=100  &    0.98  &  0.01 & \quart{38}{6}{38}{49} \\
+\hline  4 &     Baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
+\hline \end{tabular}}
+%\end{minipage}
+
+\vspace{2mm}\noindent {\scriptsize \textbf{SQL}\\[0.1cm]}
+  {\scriptsize  \begin{tabular}{{llrrc}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
+  1 & F=0.75, B=25 &    0.98  &  0.0 & \quart{0}{0}{0}{49} \\
+  1 & F=0.75, B=50 &    0.98  &  0.0 & \quart{0}{0}{0}{49} \\
+  1 & F=0.75, B=100 &   0.99  &  0.01 & \quart{0}{24}{24}{49} \\
+  1 & F=0.5, B=25 &    0.99  &  0.0 & \quart{24}{0}{24}{49} \\
+  1 & F=0.5, B=50 &    0.99  &  0.0 & \quart{24}{0}{24}{49} \\
+  1 & F=0.5, B=100 &    0.99  &  0.01 & \quart{24}{25}{24}{49} \\
+  1 & F=0.25, B=50 &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
+  1 & F=0.25-weight-B=25 &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
+  1 & F=0.25, B=100 &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
+  1 &     Baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
+  \hline \end{tabular}}
+%\end{minipage}
+%\noindent\begin{minipage}{0.5\textwidth}
+%  \flushleft
+
+\vspace{2mm}\noindent {\scriptsize \textbf{X264}\\[0.1cm]}
+  {\scriptsize  \begin{tabular}{{llrrc}}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
+  1 & F=0.75, B=25 &    0.72  &  0.04 & \quart{0}{6}{3}{49} \\
+  1 & F=0.75, B=50 &    0.74  &  0.04 & \quart{3}{6}{6}{49} \\
+\hline  2 & F=0.5, B=50 &    0.82  &  0.04 & \quart{16}{7}{19}{49} \\
+  2 &  F=0.75, B=100  &    0.82  &  0.06 & \quart{13}{10}{19}{49} \\
+  2 & F=0.5, B=25 &    0.82  &  0.03 & \quart{19}{5}{19}{49} \\
+\hline  3 &   F=0.5, B=100   &    0.88  &  0.03 & \quart{26}{5}{29}{49} \\
+\hline  4 & F=0.25, B=50 &    0.91  &  0.02 & \quart{33}{3}{34}{49} \\
+  4 & F=0.25, B=25 &    0.91  &  0.02 & \quart{34}{4}{34}{49} \\
+\hline  5 &  F=0.25, B=100 &    0.93  &  0.02 & \quart{36}{3}{38}{49} \\
+\hline  6 &     Baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
+\hline \end{tabular}}
+\end{minipage}
+
+\end{center}
+\caption{Results on  Seigmund   data sets. Baseline values shown at bottom. All other values
+are ratios of baselines.
+Recall that $B$ denotes how what {\em percent} of the attributes are displaced
+and $F$ denotes how {\em far} the test cases are mutated (so at $F=0.75,B=100$, all
+attributes are displaced 75\% of the distance to the exemplar).
+For each of the  tables in this figure, better methods appear higher up.
+In these tables, median and IQR are the 50th and the (75-25)th percentiles.
+The IQR ranges are shown in the right column with black dot at the median.
+Horizontal lines divide the “ranks” found by Scott-Knott (shown in left column).
+}\label{fig:jur}
+\end{figure*}
+
 \begin{figure}[!t] 
@@
       \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} && \textbf{Bugs}\\
-  1 &  0.75-weight &    0.71  &  0.19 & \quart{0}{25}{10}{49} & 62\\
-  1 &         0.75 &    0.72  &  0.14 & \quart{6}{19}{12}{49} & 64\\
-\hline  2 &          0.5 &    0.86  &  0.08 & \quart{25}{11}{31}{49} & 77 \\
-  2 &   0.5-weight &    0.88  &  0.14 & \quart{20}{19}{33}{49} & 77\\
-\hline  3 & 0.5-weight-B=50\% &    0.91  &  0.08 & \quart{32}{11}{37}{49} & 80\\
-  3 & 0.75-weight-B=50\% &    0.92  &  0.09 & \quart{31}{12}{39}{49} & 82\\
-  3 &  0.25-weight &    0.92  &  0.04 & \quart{36}{5}{39}{49} & 81\\
-\hline  4 &         0.25 &    0.93  &  0.05 & \quart{37}{7}{40}{49} & 83\\
-  4 & 0.75-weight-B=25\% &    0.94  &  0.09 & \quart{36}{12}{41}{49} & 82\\
-\hline  5 & 0.25-weight-B=50\% &    0.97  &  0.03 & \quart{44}{4}{45}{49} & 86\\
-  5 & 0.5-weight-B=25\% &    0.98  &  0.06 & \quart{40}{8}{47}{49} & 86 \\
-\hline  6 & 0.25-weight-B=25\% &    0.99  &  0.01 & \quart{48}{1}{48}{49} & 87\\
-\hline  7 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 90\\
+   1 &  F=0.75, B=100 &    0.71  &  0.19 & \quart{0}{25}{10}{49} & 62 \\
+\hline  2 &   F=0.5, B=100  &    0.88  &  0.14 & \quart{20}{19}{33}{49} & 77\\
+\hline  3 & F=0.5, B=50\% &    0.91  &  0.08 & \quart{32}{11}{37}{49} & 80\\
+  3 & F=0.75, B=50\% &    0.92  &  0.09 & \quart{31}{12}{39}{49} & 82\\
+  3 &  F=0.25, B=100  &    0.92  &  0.04 & \quart{36}{5}{39}{49} & 81\\
+  3 & F=0.75, B=25\% &    0.94  &  0.09 & \quart{36}{12}{41}{49} & 82\\
+\hline  4 & F=0.25, B=50\% &    0.97  &  0.03 & \quart{44}{4}{45}{49} & 86\\
+  4 & F=0.5, B=25\% &    0.98  &  0.06 & \quart{40}{8}{47}{49} & 86\\
+\hline  5 &F= 0.25, B=25\% &    0.99  &  0.01 & \quart{48}{1}{48}{49} & 87\\
+\hline  6 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 90\\
 \hline \end{tabular}}
@@
 \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & & \textbf{Bugs}\\
-  1 &  0.75-weight &    0.75  &  0.18 & \quart{0}{29}{8}{49} & 50\\
-  1 &         0.75 &    0.79  &  0.12 & \quart{8}{20}{14}{49} & 53\\
-\hline  2 &          0.5 &    0.84  &  0.1 & \quart{18}{16}{23}{49} & 56\\
-  2 &   0.5-weight &    0.84  &  0.08 & \quart{14}{14}{23}{49} & 56\\
-  2 & 0.75-weight-B=50\% &    0.84  &  0.09 & \quart{18}{15}{23}{49} & 56 \\
-\hline  3 & 0.5-weight-B=50\% &    0.91  &  0.05 & \quart{29}{9}{34}{49} & 61\\
-\hline  4 & 0.25-weight-B=50\% &    0.96  &  0.01 & \quart{43}{1}{43}{49} & 64\\
-  4 & 0.75-weight-B=25\% &    0.96  &  0.05 & \quart{39}{9}{43}{49} & 65\\
-  4 &         0.25 &    0.97  &  0.01 & \quart{43}{1}{44}{49} & 65\\
-  4 &  0.25-weight &    0.97  &  0.05 & \quart{39}{9}{44}{49} & 65 \\
-  4 & 0.5-weight-B=25\% &    0.97  &  0.03 & \quart{43}{5}{44}{49} & 65 \\
-\hline  5 & 0.25-weight-B=25\% &    0.99  &  0.01 & \quart{48}{1}{48}{49} & 66\\
-\hline  
-6 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 67\\
+  1 &  F=0.75,  B=100 &    0.75  &  0.18 & \quart{0}{29}{8}{49} & 50\\
+\hline  2 &   F=0.5,B=100   &    0.84  &  0.08 & \quart{14}{14}{23}{49} & 56\\
+  2 & F=0.75, B=50 &    0.84  &  0.09 & \quart{18}{15}{23}{49} & 56\\
+\hline  3 & F=0.5, B=50 &    0.91  &  0.05 & \quart{29}{9}{34}{49} & 61\\
+\hline  4 & F=0.25, B=50 &    0.96  &  0.01 & \quart{43}{1}{43}{49} & 64\\
+  4 & F=0.75, B=25 &    0.96  &  0.05 & \quart{39}{9}{43}{49} & 65\\
+  4 &  F=0.25, B=100  &    0.97  &  0.05 & \quart{39}{9}{44}{49} & 65\\
+  4 & F=0.5, B=25 &    0.97  &  0.03 & \quart{43}{5}{44}{49} & 65\\
+\hline  5 & F=0.25, B=25 &    0.99  &  0.01 & \quart{48}{1}{48}{49} & 66\\
+\hline  6 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 67\\
 \hline \end{tabular}}
@@
 \arrayrulecolor{darkgray}
-\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & & \textbf{Bugs}\\\hline
-  1 &         0.75 &    0.64  &  0.28 & \quart{0}{27}{14}{49} & 110\\
-\hline  2 &  0.75-weight &    0.76  &  0.21 & \quart{13}{21}{26}{49}& 131 \\
-  2 &   0.5-weight &    0.76  &  0.16 & \quart{20}{16}{26}{49} & 130\\
-  2 &          0.5 &    0.79  &  0.17 & \quart{19}{17}{29}{49} & 137\\
-\hline  3 & 0.75-weight-B=50\% &    0.85  &  0.12 & \quart{30}{12}{35}{49} & 146\\
-  3 &  0.25-weight &    0.87  &  0.07 & \quart{34}{7}{37}{49} & 152\\
-\hline  4 &         0.25 &    0.93  &  0.09 & \quart{37}{9}{43}{49} & 161\\
-  4 & 0.5-weight-B=50\% &    0.93  &  0.05 & \quart{41}{5}{43}{49} & 162\\
-\hline  5 & 0.25-weight-B=50\% &    0.97  &  0.03 & \quart{45}{3}{47}{49} & 167\\
-  5 & 0.75-weight-B=25\% &    0.97  &  0.02 & \quart{46}{2}{47}{49} & 168\\
-\hline  6 & 0.5-weight-B=25\% &    0.98  &  0.02 & \quart{47}{2}{48}{49} & 170\\
-  6 & 0.25-weight-B=25\% &    0.98  &  0.01 & \quart{48}{1}{48}{49} & 171\\
+\rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & & \textbf{Bugs}\\
+  1 &  F=0.75,  &    0.76  &  0.21 & \quart{0}{28}{17}{49} & 130\\
+  1 &   0.5,  &    0.76  &  0.16 & \quart{9}{22}{17}{49} & 131\\
+\hline  2 & 0.75, B=50\% &    0.85  &  0.12 & \quart{22}{17}{29}{49} & 146\\
+\hline  3 &  0.25,  &    0.87  &  0.07 & \quart{28}{9}{32}{49} & 152\\
+\hline  4 & 0.5, B=50\% &    0.93  &  0.05 & \quart{37}{7}{40}{49} & 162\\
+\hline  5 & 0.25, B=50\% &    0.97  &  0.03 & \quart{43}{4}{45}{49} & 167\\
+  5 & 0.75, B=25\% &    0.97  &  0.02 & \quart{44}{3}{45}{49} & 168\\
+\hline  6 & 0.5, B=25\% &    0.98  &  0.02 & \quart{45}{3}{47}{49} & 170\\
+  6 & 0.25, B=25\% &    0.98  &  0.01 & \quart{47}{1}{47}{49} & 171\\
 \hline  7 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 175\\
@@
 \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & & \textbf{Bugs}\\
-  1 &  0.75-weight &    0.66  &  0.2 & \quart{0}{21}{13}{49} & 97 \\
-\hline  2 & 0.75-weight-B=50\% &    0.7  &  0.1 & \quart{14}{10}{17}{49} & 103 \\
-\hline  3 &         0.75 &    0.77  &  0.3 & \quart{9}{33}{24}{49} & 113\\
-  3 & 0.75-weight-B=25\% &    0.8  &  0.09 & \quart{21}{10}{28}{49} & 117\\
-  3 &   0.5-weight &    0.81  &  0.09 & \quart{26}{9}{29}{49} & 119\\
-  3 &          0.5 &    0.84  &  0.1 & \quart{26}{10}{32}{49} & 123\\
-\hline  4 & 0.5-weight-B=50\% &    0.88  &  0.07 & \quart{34}{8}{36}{49} & 128\\
-  4 & 0.25-weight-B=25\% &    0.89  &  0.07 & \quart{36}{8}{38}{49} & 130 \\
-  4 &  0.25-weight &    0.92  &  0.04 & \quart{39}{4}{41}{49} & 133 \\
-  4 &         0.25 &    0.93  &  0.07 & \quart{36}{8}{42}{49} & 136 \\
-\hline  5 & 0.25-weight-B=50\% &    0.95  &  0.04 & \quart{42}{4}{44}{49} & 139 \\
-  5 & 0.5-weight-B=25\% &    0.96  &  0.03 & \quart{43}{3}{45}{49} &141 \\
+  1 &  0.75,  &    0.66  &  0.2 & \quart{0}{21}{13}{49} & 97\\
+\hline  2 & 0.75, B=50\% &    0.7  &  0.1 & \quart{14}{10}{17}{49} & 103\\
+\hline  3 & 0.75, B=25\% &    0.8  &  0.09 & \quart{21}{10}{28}{49} & 117\\
+  3 &   0.5,  &    0.81  &  0.09 & \quart{26}{9}{29}{49} & 119\\
+\hline  4 & 0.5, B=50\% &    0.88  &  0.07 & \quart{34}{8}{36}{49} & 128\\
+  4 & 0.25, B=25\% &    0.89  &  0.07 & \quart{36}{8}{38}{49} & 130\\
+  4 &  0.25,  &    0.92  &  0.04 & \quart{39}{4}{41}{49} & 133\\
+\hline  5 & 0.25, B=50\% &    0.95  &  0.04 & \quart{42}{4}{44}{49} & 139\\
+  5 & 0.5, B=25\% &    0.96  &  0.03 & \quart{43}{3}{45}{49} & 141\\
 \hline  6 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 146\\
@@
 \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & & \textbf{Bugs}\\
-  1 &  0.75-weight &    0.72  &  0.26 & \quart{0}{29}{18}{49} & 173\\
-  1 &         0.75 &    0.74  &  0.18 & \quart{12}{20}{20}{49} & 178\\
-\hline  2 & 0.75-weight-B=50\% &    0.79  &  0.15 & \quart{14}{17}{26}{49} & 190\\
-  2 &          0.5 &    0.81  &  0.15 & \quart{22}{17}{28}{49} & 195\\
-  2 &   0.5-weight &    0.81  &  0.14 & \quart{21}{16}{28}{49} & 195\\
-\hline  3 & 0.5-weight-B=50\% &    0.9  &  0.11 & \quart{30}{13}{38}{49} & 217\\
-  3 &         0.25 &    0.91  &  0.07 & \quart{35}{8}{39}{49} & 219\\
-  3 &  0.25-weight &    0.91  &  0.05 & \quart{36}{6}{39}{49} & 219\\
-\hline  4 & 0.75-weight-B=25\% &    0.94  &  0.05 & \quart{39}{6}{43}{49} & 226\\
-  4 & 0.25-weight-B=50\% &    0.94  &  0.06 & \quart{39}{7}{43}{49} & 226\\
-\hline  5 & 0.25-weight-B=25\% &    0.96  &  0.03 & \quart{44}{3}{45}{49} & 231\\
-  5 & 0.5-weight-B=25\% &    0.96  &  0.03 & \quart{44}{3}{45}{49} & 231\\
-\hline  6 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 240 \\
+  1 &  0.75,  &    0.72  &  0.26 & \quart{0}{29}{18}{49} & 173\\
+\hline  2 & 0.75, B=50\% &    0.79  &  0.15 & \quart{14}{17}{26}{49} & 190\\
+  2 &   0.5,  &    0.81  &  0.14 & \quart{21}{16}{28}{49} & 195\\
+\hline  3 & 0.5, B=50\% &    0.9  &  0.11 & \quart{30}{13}{38}{49} & 217\\
+  3 &  0.25,  &    0.91  &  0.05 & \quart{36}{6}{39}{49} & 219\\
+\hline  4 & 0.75, B=25\% &    0.94  &  0.05 & \quart{39}{6}{43}{49} & 226\\
+  4 & 0.25, B=50\% &    0.94  &  0.06 & \quart{39}{7}{43}{49} & 226\\
+\hline  5 & 0.25, B=25\% &    0.96  &  0.03 & \quart{44}{3}{45}{49} & 231\\
+  5 & 0.5, B=25\% &    0.96  &  0.03 & \quart{44}{3}{45}{49} & 231\\
+\hline  6 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 240\\
 \hline \end{tabular}}
 %\end{minipage}
-\caption{Results on  Jureczko   data sets. Baseline values shown at bottom. All other values
-are ratios of baselines.}
-\label{tab:ant}
+\caption{Results on  Jureczko   data sets. Same format as \fig{jur}.}
+\label{fig:ant}
 \end{figure}
-
-   \subsection{Procedures}
-   The procedure used to build and test HOW's plans was shown above in \fig{work}.
-The    Seigmund and Jureczko data sets have continuous and discrete classes (respectively).
-Hence, when building a predictor, we used (1)~Random Forest Regressors for the Seigmund data and (2)~Random Forests
-for the Jureczko data.
-
-   For both the Siegmind and Jureczko, we designed a procedure such we had at least
-   20 samples from the \fig{work} procedure for  each data set (the value of 20 was choosen as the minimum use sample size via the central limit theorem):
-   \bi
-   \item
-  For the Siegmind data set of \fig{cpm}, 
-  25 times, 
-  we randomized the order of the data, trained on the first half (using
-  Random Forest Regressor), then tested on the second half.
-  \item
-  For the Jureczko, if we just  used the training and test sets of  \fig{j}, that would only
-  give us sample per data set. Such a singleton sample could hide important details since the methods
-  used for parameter tuning (SMOTE and differential evolution) use some stochastic sub-routines.
-  Hence, for each  of the training sets of \fig{j}, we ran SMOTE+differential evolution 25 times to learn
-  parameters for Random Forests.
-  \ei
-\fig{where} defined two control parameters for HOW:
-\bi
-\item The $F$ variable controls the size of the displacement;
-\item The $B$ variable controls how many of the attributes are displaced;
-\ei
-The   25 repeats defined above were executed for various values of $F,B$ and for each data set.
-Those results, summarized below, are presented as horizontal quartile charts. For example,
-the following horizontal quartile chart   shows one result for ``some treatment'' where  the median performance was 20\% and
-the interquartile range (25th to 70th percentile) as 30\%:
- \begin{center}
- some treatment 0\%:\quart{0}{29}{18}{49}:100\%
- \end{center}
-We take all the quartile charts for one data set, sort them on their median value,
-then apply a Scott-Knott procedure to rank each one. 
-The Scott-Knott
-procedure recommended by Mittas \& Angelis in their 2013
-IEEE TSE paper~\cite{mittas13}.  This method
-sorts a list of $l$ treatments with $ls$ measurements by their median
-score. It then
-splits $l$ into sub-lists $m,n$ in order to maximize the expected value of
- differences  in the observed performances
-before and after divisions. E.g. for lists $l,m,n$ of size $ls,ms,ns$ where $l=m\cup n$:
- $E(\Delta)=\frac{ms}{ls}abs(m.\mu - l.\mu)^2 + \frac{ns}{ls}abs(n.\mu - l.\mu)^2$.
-Scott-Knott then applies some statistical hypothesis test $H$ to check
-if $m,n$ are significantly different. If so, Scott-Knott then recurses on each division.
 
@@
 see Shepperd\&MacDonell~\cite{shepperd12a}; Kampenes~\cite{kampenes07}; and
-Kocaguenli et al.~\cite{kocharm13}. These researchers
+Kocaguenli et al.~\cite{Kocaguneli2013:ep}. These researchers
 warn that even if an
@@
 the performance differences 
-we first must rule out small effects.
-This test was recently 
+we first must rule out small effects using A12, 
+a test   recently 
 endorsed by Arcuri and Briand
@@
 \subsection{Results}
-The results for each data set, for different ranges of $(F,B)$ are shown in \fig{ant} and \fig{xxx}.
+The results for each data set, for different ranges of $(F,B)$ are shown in \fig{jur} and \fig{ant}.
 Also included are a {\em baseline} figure which is taken from the cases in the test data
@@
 
+ All the results of \fig{jur} and \fig{ant} show that in $\frac{10}{11}$ of our
+ datasets, the baseline results are ranked significantly worse than the results seen
+ after planning (evidence: the staistical ranking assigned by Scott-Knott is shown in the left-hand-side columns and most baselines get larger, i.e. worse, ranks
+ that the treated data). The exception to this is SQL in  \fig{jur}. which
+ seems to
+ be resistant to our planning methods.
+
+ By comparing the top and bottom line of results from each data set, we can see how much HOW's
+ plans effect the predicted values. While the  size of the change varies from data set to data set:
+ \bi
+ \item The median change is down to 72\% and 75\%  of the original baseline values for Seigmund and Jureczko, respectively;
+ \item The best change is down to 20\% and 66\% of the original baseline values for Seigmund and Jureczko, respectively;
+ \ei
+ As to the impact of changing how far we mutate (the $F$ value) or how many attributes
+ we mutate (the $B$ value), the results are different for the data sets with discrete and continuous attributes:
+ \bi
+ \item For data sets with continuous objectives (the Jureczko data of \fig{jur}),
+ best results are obtained by taking the fewest attributes (minimize $B$) 
+ while moving close to the exemplar (maximize $F$).
+ \item For data sets with discrete objectives (the Seigmund data  of \fig{ant}),
+ best results are obtained by maximizing both $F$ and $B$.
+ \ei
+  From these differences, we conclude that the more specific the  information used for exemplar
+ generation, the better the planning. Recall that for the discrete
+ attributes, the exemplar is the mean position of all cases in the cluster.
+ However,  for continuous
+ objectives, the exemplar is much more specific and is the  single  best case in a cluster
+
 % \section{Discussion}
@@
 
-{\em 1. Sampling bias} threatens any data mining experiment; i.e., what matters
+{\em 1. Evaluation bias:} The biggest threat to validity of this work is our use
+of predictors learned on the training data to assess the impact of HOW's plans
+on the test data.
+If we believe the outputs of those predictors, then we can also believe that
+\fig{jur} and \fig{ant} are showing true effects.
+
+%XXX begin rahul
+One way to assess the validity of our predictions is to consider the space that generates
+them. \fig{xxx} shows (1)~the training cases and (2)~the test cases and (3)~the
+test cases displaced after applying HOW's plans for the {\em ant} data set.
+In this figure, all the cases are projected onto two dimensions after (a)~creating one
+data set with all of 1+2+3, finding their $x,y$ positions in the top-level {\tt cluster},
+as generated by \fig{howcode}. Note that the both the test cases and the displaced test
+cases all fall into nearly the same regions as the training data. This is to say that
+predictors learned from the {\em ant} training data have some authority in the regions
+used to generate our results\footnote{If the reader is concerned that this 2d projection
+losses important information, then they should note that two separate  studies~\cite{papa13,divya15}
+have confirmed that building defect predictors from this 2d space are just as effective
+as predictors learned using all the defect attributes of \fig{ck}.}
+
+\begin{figure}
+\includegraphics
+\end{figure}
+%XXX end
+
+That said, one thing to be said here
+is that we {\em strongly} recommend that predictors are assessed prior to planning.
+We showed above the results of one such planning exercise- we noted that half
+our defect data sets are not clear enough to support planning. On the other hand,
+the predictors from the configuration domain are extraordinarily accurate (recall
+their near perfect predictions seen in \tion{notplan}).
+
+{\em 2. Learner bias: } For building the defect predictors in this study, we elected
+to use  Random Forest  and Random Forest Regressors .
+We chose this approach,  based on its reputation for having the better  performance of 
+21 other learners for defect prediction~\cite{lessmann}.
+Data mining is a
+large and active field and any single study can only use a small
+subset of the known classification algorithms.
+
+{\em 3. Sampling bias} threatens any data mining experiment; i.e., what matters
 there may not be true here. For example, the data sets used here comes from two sources
@@
 
-{\em 2. Learner bias: } For building the defect predictors in this study, we elected
-to use  Random Forest  .
-We chose Random Forest based on its reputation for having the better  performance of 
-21 other learners for defect prediction~\cite{lessmann}.
-Data mining is a
-large and active field and any single study can only use a small
-subset of the known classification algorithms.
-
-{\em 3. Evaluation bias:} The issue was discussed above in \tion{assess} where
-we asserted that plans can be assessed via predictors-- with the all important
-proviso that the planning should {\em not} be attempted if the predictors
-are performing poorly.
-
 %%\footnote{LL: It seems to me that $privacy$ in LACE approach could be compromised in the case of extremes if I had some knowledge of the parties.
@@
 
+In summary, this paper makes five contributions:
+\be
+\item The HOW  case-based planner (which has not been presented before).
+\item The experiments of this paper showing that HOW planner is useful for real-world tasks;
+e.g. reducing the
+expected values of the Jureczko software defects and the Seigmund software runtimes.
+\item Apart from HOW, we  also offers a general framework for using  predictive system to build planners;
+\item Further, we offer a  test to recognizes  when we should {\em not}  plan: specifically,
+planning is
+not recommended in domains with  poorly performing predictors;
+\item Last, we  offer a general verification rig for assessing the value of plans generated within this rig.
+\ee
+
+\section*{Acknowledgments}
+
+The work has partially funded by a National Science Foundation CISE CCF award \#1506586.
+
 \bibliography{how}{}

### 2015-05-12 how.tex
Updates from ShareLaTeX

@@
 \usepackage{alltt}
+\usepackage{balance}
 \newcommand{\eq}[1]{Equation~\ref{eq:#1}}
@@
 Rahul Krishna, Tim Menzies, Xipeng Shen\\
-        Computer Science, NcState, USA\\
-       \{i.m.ralk, tim.menzies, xipengshen\}\@gmail.com
-% 3rd. author
+        Computer Science, North Carolina State University, USA\\
+       \{i.m.ralk, tim.menzies\}\@gmail.com, xshen5@ncsu.edu
  % use '\and' if you need 'another row' of author names
@@
        Computer Science, UtDallas, USA \\
-       amarcus\@utdallas.edu }
+       amarcus@utdallas.edu }
 
@@
 For example, in one remarkable recent study, Bente et al. report results
-were the same specification was developed into a product by four different organizations~\cite{Anda2009}. Given those kind of resources, it would be possible
+were the same specification was developed  by four different organizations~\cite{Anda2009}. Given those kind of resources, it would be possible
 to (say) take a code base, assign it to $N$ different teams, apply
@@
 
-The planner explored in this paper is the ``HOW'' case-based planner.
+The planner explored in this paper is the ``HOW'' case-based reasoner (CBR).
 HOW's  ``plans'' are  set of changes
@@
 
-However, not all domains come with ready-to-use models.
-For   several problems where models are hard to obtain, or the input and output are related by complex connections that simply cannot be modeled in a reliable manner~\cite{Ludewig2003}. For example, 
-consider software defect prediction and all the intricate issues that may lead defects in a product. A odel that includes {\em all} those
-potential issues would be very large and unweliding. Further,
+However, not all domains come with ready-to-use models. For example, 
+consider software defect prediction and all the intricate issues that may lead defects in a product. A model that includes {\em all} those
+potential issues would be very large and complex. Further,
 the empirical data required to validate any/all parts
@@
 developed by Boehm's group at the University of Southern California.
+Those models inputted project descriptors to output predictors
+of development effort, project risk, and defects.
 Some of those models took decades to develop and mature (from 1981~\cite{boehm81} to 2000~\cite{boehm00b}).
@@
 \subsection{Planning and AI}
-HOW is a {\em probablistic} planner, which is a different approach to that taken by
+HOW is a {\em probabilistic} planner, which is a different approach to that taken by
 classical AI. 
@@
 (where it has also bee called
- reasoning via anology or instance-based reasoning).
+ reasoning via analogy or instance-based reasoning).
 CBR seeks to emulate human recollection and adaptation
@@
 That is, CBR does not offer some trite generalization over multiple
-exmaples. Rather, the advice it gives is specialized to the particular
+examples. Rather, the advice it gives is specialized to the particular
 case being considered at the current time.  This is particularly attractive
@@
 IDEA and HOW use the    same recursive clustering
-method but IDEA made the mistake of  summarize those
+method but IDEA made the mistake of  summarizing those
 recursive divisions into a tree structure. Initial results with IDEA were weak, but somewhat
@@
 Turning now to the displacement {\em direction},
-our experiments show that it useful to  carefully reflect on exactly where HOW should  push each test case.
+our experiments show that it is useful to  carefully reflect on exactly where HOW should  push each test case.
 HOW replaces each cluster   with one {\em exemplar} that best
@@
 For the Jureczko data, the objective score
-is a boolean variable is true if defects have been noted
+is a Boolean which is  ``true'' if defects have been noted
 for that class.  For this kind of data (with discrete objectives),
@@
 \ei
-Note that using the best as the exemplar does better than useing the mean.
+Note that using the best as the exemplar does better than using the mean.
 The general pattern shown of \fig{pp} has been seen in all the Seigmund data sets;
@@
 Data   marked with ``$\star$'' show large improvements in performance, after tuning.
-Data   marked with ``$\times$'' are not ``good'' since their test suites  have so few undefective examples (less than 5\% of the total sample) that it becomes harder to find better data towards which we can displace test data.
+Data   marked with ``$\times$'' are not ``good'' since their test suites  have so few non-defective examples (less than 5\% of the total sample) that it becomes harder to find better data towards which we can displace test data.
 }\label{fig:j}
@@
 project data  into two disjoint sets {\em train} and {\em test}
-(so \mbox{{\em train} $\cup$ {\em test} $=\;\emptyset$}).
+(so \mbox{{\em train} $\cap ${\em test} $=\;\emptyset$}).
 Next, from the train set, we build both a {\em planner} as well
@@
 
- All the results of \fig{jur} and \fig{ant} show that in $\frac{10}{11}$ of our
- datasets, the baseline results are ranked significantly worse than the results seen
- after planning (evidence: the staistical ranking assigned by Scott-Knott is shown in the left-hand-side columns and most baselines get larger, i.e. worse, ranks
+ The   results of \fig{jur} and \fig{ant} show that in $\frac{10}{11}$ of our
+ data sets, the baseline results are ranked significantly worse than the results seen
+ after planning (evidence: the statistical ranking assigned by Scott-Knott is shown in the left-hand-side columns and most baselines get larger, i.e. worse, ranks
  that the treated data). The exception to this is SQL in  \fig{jur}. which
@@
 One way to assess the validity of our predictions is to consider the space that generates
-them. \fig{xxx} shows (1)~the training cases and (2)~the test cases and (3)~the
+them. \fig{howxy} shows (1)~the training cases and (2)~the test cases and (3)~the
 test cases displaced after applying HOW's plans for the {\em ant} data set.
-In this figure, all the cases are projected onto two dimensions after (a)~creating one
-data set with all of 1+2+3, finding their $x,y$ positions in the top-level {\tt cluster},
-as generated by \fig{howcode}. Note that the both the test cases and the displaced test
-cases all fall into nearly the same regions as the training data. This is to say that
-predictors learned from the {\em ant} training data have some authority in the regions
-used to generate our results\footnote{If the reader is concerned that this 2d projection
+In this figure, all the cases are projected onto two dimensions by   finding their $x,y$ positions in the top-level {\tt cluster},
+as generated by \fig{howcode}. Note that the  the   displaced test
+cases   fall into nearly the same regions as the training data.
+
+This pattern of \fig{howxy} (where the displaced test cases are found in the same
+region as the training data) has been observed in all the other data sets studied in this
+paper. Hence, the
+predictors learned from thse training data have some authority in the regions
+used to generate our predictions regarding the effects of planning\footnote{If the reader is concerned that this 2d projection
 losses important information, then they should note that two separate  studies~\cite{papa13,divya15}
 have confirmed that building defect predictors from this 2d space are just as effective
-as predictors learned using all the defect attributes of \fig{ck}.}
+as predictors learned using all the defect attributes of \fig{ck}.}.
 
 \begin{figure}
-\includegraphics
+\begin{center}\includegraphics[width=3in]{figs/2d.png}\end{center}
+\caption{Training cases (in gray), test cases (in red) and 
+test cases displaced by HOW (in green). Note how the green and the gray occupy
+the same regions; i.e. predictors trained on the training cases can be applied
+to the displaced test cases.}\label{fig:howxy}
 \end{figure}
@@
 
-In summary, this paper makes five contributions:
+This paper has explored the problem of assess changes to a project without
+extensive field studies. We have proposed using predictors learned from domain data
+to serve as the oracle that judges the effectiveness of those changes.
+
+The novel features of this paper are
 \be
-\item The HOW  case-based planner (which has not been presented before).
-\item The experiments of this paper showing that HOW planner is useful for real-world tasks;
-e.g. reducing the
-expected values of the Jureczko software defects and the Seigmund software runtimes.
-\item Apart from HOW, we  also offers a general framework for using  predictive system to build planners;
-\item Further, we offer a  test to recognizes  when we should {\em not}  plan: specifically,
+\item A general framework for using  predictive system to build planners (see \fig{work}).
+For this paper, we used Random Forests as our predictor, but other predictors could
+serve just as well.
+\item A  test to recognizes  when we should {\em not}  plan: specifically,
 planning is
-not recommended in domains with  poorly performing predictors;
-\item Last, we  offer a general verification rig for assessing the value of plans generated within this rig.
+not recommended in domains with  poorly performing predictors. In this paper, that
+test excluded certain problematic defect data sets.
+\item The HOW  case-based planner, which has not been presented before. HOW
+is a significant improvement on our two prior implementations~\cite{6600685,me12c} that both
+suffered
+from {\em optimization failure}; i.e. when their recommendations were applied,
+the resulting behavior actually got worse. We recommend HOW over that prior work
+since none of our results exhibited such optimization failures.
+\item The experiments of this paper, which showed that 
+the HOW planner is useful for real-world tasks;
+e.g. significantly reducing the
+predicted values of the Jureczko software defects and the Seigmund software runtimes.
+For those data sets, HOW
+reduce
+ the predicted values of defect counts and  runtimes to    
+ 72\%,75\%  (median) and 66\%,20\% (best case) of the initial values.
 \ee 
+As to when we would {\em not} use HOW, if  a domain has an accessible
+and certified and well-maintained
+domain model, then we would go beyond CBR and apply algorithms that can take
+full advantage of the domain knowledge in those models; e.g. GALE, NSGA-II, NSGA-III, SPEA2, IBEA, particle swarm optimization, MOEA/D, etc.~\cite{krall14,deb00a,zit02,zit04,%
+deb14,Cui2005a,zhang07:TEC}.
+
+That said, one clear future direction would be explore
+combinations of CBR tools with other approaches. 
+One way to view HOW is a {\em local patch operator} that could be applied within 
+GALE, NSGA*, etc (so in that combination, we would be trying to use   HOW's local patches to 
+to optimize those optimizers).
 
@@
 \bibliographystyle{IEEEtran}
+\balance
 \end{document}

### 2015-05-14 how.tex
Updates from ShareLaTeX

@@
  for learning optimizations to software, HOW does not require
- an underlying of the domain. Also, HOW's plans
+ an underlying model of the domain. Also, HOW's plans
  are designed to result in {\em minimal displacement}
@@
 \section{Introduction}
-Suppose someone suggests a change to your project. How might you assess the effectiveness of that change?
+Suppose someone wants changes that can improve their software project. How would you propose
+sensible changes? And how would you assess the effectiveness of those changes?
 
@@
 \ei
-How to assess such {\em plans}?
-Some organizations have the resources to 
-run repeated trials to assess  different treatments.
-For example, in one remarkable recent study, Bente et al. report results
-were the same specification was developed  by four different organizations~\cite{Anda2009}. Given those kind of resources, it would be possible
-to (say) take a code base, assign it to $N$ different teams, apply
-HOW's plans the code used by  $N/2$ teams, then check in 12 months time
-if those halves of the teams have fewer defects than the other.
-
-Very few industrial or research groups have access
-to the kinds of resources using by Bente et al. (evidence: in the size years since the
-publication of that work, we know of only one of two similar studies). Also, given the
-diversity of modern software projects, it might be unreasonable to demand that all
-proposed changes for all projects are always evaluated by something like the Bente et al. study.
-
-This paper proposes another, less resource intensive,  method for assessing the effectiveness of proposed
-changes to a project.  
-We propose using prediction systems (built by data mining) as a verification
-tool for planners. In domains where  data miners can build
-predictors of adequate performance, then those predictors can assess the value
-of proposed changes.
-
-The planner explored in this paper is the ``HOW'' case-based reasoner (CBR).
+To generate those plans, we propose the ``HOW'' case-based reasoner (CBR).
 HOW's  ``plans'' are  set of changes
@@
   adjust   attributes $Z_j$:
-\begin{equation}\label{eq:one}
+\[
 Z_j = Z_j + \delta_j
-\end{equation}
+\]
 For example, to simplify a  large bug-prone  method, HOW might suggest
@@
 two simpler functions).
-
 HOW's  plans displace the test case into some region
@@
 \begin{quote}{\em ``I may not know too much about that, but once you change into something like
-what I've already seen, then I can suggest how to change it''.}
+what I've already seen, then I can suggest how to improve it''.}
 \end{quote}
-This paper shows experimentally  that   HOW's plans can be quite effective and 
+After generating the plans, the next question is ``how to assess them?''.  
+Some organizations have the resources to 
+run repeated trials to assess  different treatments.
+For example, in one remarkable recent study, Bente et al. report results
+were the same specification was developed  by four different organizations~\cite{Anda2009}. Given those kind of resources, it would be possible
+to (say) take a code base, assign it to different teams, make these teams  adopt different polices,
+then check in 12 months time
+ which teams have fewer defects than the others.
+
+Very few industrial or research groups have access
+to the kinds of resources needed for this kind study  (evidence: in the six years since the
+publication of that work, we know of only one   similar study to Bente et al.). Also, given the
+diversity of modern software projects, it might be unreasonable to demand that all
+proposed changes for all projects are always evaluated by something like the Bente et al. study.
+
+This paper proposes another, less resource intensive,  method for assessing the effectiveness of proposed
+changes to a project.  
+We  use a prediction system (built by data mining) as a verification
+tool for planners. In domains where  data miners can build
+predictors of adequate performance, then those predictors can assess the value
+of proposed changes.
+This paper applies this proposal to show that   HOW's plans are quite effective and  can
  significantly reduce the  predicted
@@
 The rest of this paper presents the background to this work in Section~2; the design of HOW in Section~3;
-then our experimental results  in Section~4. Those experiments show that HOW can   reduce the expected
-value of defects in Jureczko   data sets by 72\% to 66\%  (median,best).
-Also, in the Seigmund data sets, HOW can   reduce the expected value of the runtimes by  75\% to 20\% (median,best).
+then our experimental results  in Section~4.  Our conclusion is that we can plan for the future in
+software engineering, provided the domain data supports adequate predictors.
 
@@
   {\scriptsize \textbf{Ant}\\[0.1cm]}
-  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~~~~}c@{}r}}
+  {\scriptsize  \begin{tabular}{{l@{~~~~}l@{}r@{~~~~}r@{~~}c@{}r}}
       \arrayrulecolor{darkgray}
@@
 
-%XXX begin rahul
 One way to assess the validity of our predictions is to consider the space that generates
-them. \fig{howxy} shows (1)~the training cases and (2)~the test cases and (3)~the
-test cases displaced after applying HOW's plans for the {\em ant} data set.
-In this figure, all the cases are projected onto two dimensions by   finding their $x,y$ positions in the top-level {\tt cluster},
-as generated by \fig{howcode}. Note that the  the   displaced test
-cases   fall into nearly the same regions as the training data.
+them. \fig{howxy} is from the {\em ivy} data
+set. It shows (1)~the training cases and (2)~the test cases and (3)~the
+test cases displaced after applying HOW's plans.
+To generate that figure, we placed all of 1+2+3 into the same data set then computed the first
+two  components (using PCA). Note that the  the   displaced test
+cases  (shown in green)  fall closer to the training cases (shown in gray) than
+the test cases (shown in red).  That is, if we believe
+that the gray data is  suitable for assessing
+the test cases (as indicated by the {\em ivy} results from \fig{j}), then it follows
+that we believe even more in the predictions
+generated from the displaced data).
 
@@
 paper. Hence, the
-predictors learned from thse training data have some authority in the regions
+predictors learned from these training data have some authority in the regions
 used to generate our predictions regarding the effects of planning\footnote{If the reader is concerned that this 2d projection
@@
 \caption{Training cases (in gray), test cases (in red) and 
-test cases displaced by HOW (in green). Note how the green and the gray occupy
-the same regions; i.e. predictors trained on the training cases can be applied
-to the displaced test cases.}\label{fig:howxy}
+test cases displaced by HOW (in green). Note how the green (displaced) cases are closer to the  training
+date than the original test data
+i.e. predictors trained on the training cases and
+applied to the test cases should
+work just as well, or better, on the displaced test cases.}\label{fig:howxy}
 \end{figure}

### 2015-05-15 how.tex
Updates from ShareLaTeX

@@
 
+%XXX begin rahul 
 One way to assess the validity of our predictions is to consider the space that generates
@@
 
-This pattern of \fig{howxy} (where the displaced test cases are found in the same
-region as the training data) has been observed in all the other data sets studied in this
-paper. Hence, the
+This pattern of \fig{howxy} (where the displaced test cases are found closer to  the training cases than the test cases) has been observed in all the other data sets studied in this
+paper. Hence,  we can assert that
 predictors learned from these training data have some authority in the regions
-used to generate our predictions regarding the effects of planning\footnote{If the reader is concerned that this 2d projection
+used to generate the plans\footnote{If the reader is concerned that this 2d projection
 losses important information, then they should note that two separate  studies~\cite{papa13,divya15}

### 2015-08-20 how.tex
Updates from ShareLaTeX

@@
  the expected values of defect counts and  runtimes to    
- 72\%,75\%  (median) and 66\%,20\% (best case) of the initial values.
+ 72\%,75\%  (median) and 66\%,20\% (best case) of the initial values, respectively.
   \end{abstract}
@@
 For example, in one remarkable recent study, Bente et al. report results
-were the same specification was developed  by four different organizations~\cite{Anda2009}. Given those kind of resources, it would be possible
+were the same for specification that was developed  by four different organizations~\cite{Anda2009}. Given those kind of resources, it would be possible
 to (say) take a code base, assign it to different teams, make these teams  adopt different polices,
@@
 We  use a prediction system (built by data mining) as a verification
-tool for planners. In domains where  data miners can build
-predictors of adequate performance, then those predictors can assess the value
+tool for planners. If for certain domains data miners can build
+predictors with adequate performance, then those predictors can assess the value
 of proposed changes.
@@
 However, not all domains come with ready-to-use models. For example, 
-consider software defect prediction and all the intricate issues that may lead defects in a product. A model that includes {\em all} those
+consider software defect prediction and all the intricate issues that may lead to defects in a product. A model that includes {\em all} those
 potential issues would be very large and complex. Further,
@@
 the kinds of tools that are widely used in the search-based
-software engineering community such as GALE,NSGA-II, NSGA-III, SPEA2, IBEA, particle swarm optimization, MOEA/D, etc.~\cite{krall14,deb00a,zit02,zit04,%
+software engineering community such as GALE, NSGA-II, NSGA-III, SPEA2, IBEA, particle swarm optimization, MOEA/D, etc.~\cite{krall14,deb00a,zit02,zit04,%
 deb14,Cui2005a,zhang07:TEC}. Otherwise, we recommend tools like HOW.
@@
 HOW's commitment to minimal displacement (and the fully-automated
-modeling approach) of this paper makes it stand apart from, say,
-  the Bayesian/Markov chain approach to planning of Dean et al.~\cite{dean1995planning}.
+modeling approach of this paper) makes it stand apart from, say,
+  the Bayesian/Markov chain approach to planning by Dean et al.~\cite{dean1995planning}.
 
@@
 explored in the AI literature
-(where it has also bee called
+(where it has also been called
  reasoning via analogy or instance-based reasoning).
@@
 Researchers have found that, in some domains, they are competitive with  closed form mathematical models or other modeling methods such as regression \cite{keung2008analogy}. 
-CBR is also useful when dealing with spare data sets~\cite{1438374} of with 
+CBR is also useful when dealing with sparse data sets~\cite{1438374} or with 
 partial knowledge  at, for example,  an early stage of a project)~\cite{walkerden1999empirical}.
@@
 Secondly, HOW   limits displacement
-to very small regions in the space of the training data (never more that the separation
+to very small regions in the space of the training data (never more than the separation
 of the two closest clusters).  HOW's clusterer divides  data into many   small clusters containing
@@
 test data towards that exemplar, as shown in \fig{howcode}, line 20. In summary, 
-If  $Z_j$ is an independent variable within the
+if  $Z_j$ is an independent variable within the
 test case $Z$ and  $X$ is the exemplar found at training time,
@@
     On the right-hand-side, we show the {\em results from learning}.
-    Data is ``good'' if it has   recalls over 60\% and false alarms under 40\%
+    Data is ``good'' if it has recall over 60\% and false alarm under 40\%
 (and note that, after tuning, there are more ``good'' than before).
 Data   marked with ``$\star$'' show large improvements in performance, after tuning.
-Data   marked with ``$\times$'' are not ``good'' since their test suites  have so few non-defective examples (less than 5\% of the total sample) that it becomes harder to find better data towards which we can displace test data.
+Data   marked with ``$\times$'' are ``not good'' since their test suites  have so few non-defective examples (less than 5\% of the total sample) that it becomes harder to find better data towards which we can displace test data.
 }\label{fig:j}
@@
 Else, we (1)~apply the { planner} to alter the {\em test} data;
-then (2)~apply the { predictor} to the altered data {\em test'};
+then (2)~apply the { predictor} to the altered data $test'$;
 then (3)~return data on the {\em before,after} predictions.
@@
 is that our assessment of the plans is only as good as the predictor. To 
-mitigate for this {\em problem of poor predictors}, it is hence wise to demand certain standards for the {\em
+mitigate for this {\em problem of poor predictors}, it is wise to demand certain standards for the {\em
 satisfactory} threshold used in this \fig{work}.
 
-For example, this study's data from two types of domains: the Jureczko   object-oriented data  
+For example, this study's data arise from two types of domains: the Jureczko   object-oriented data  
 and the Seigmund configuration data. 
@@
 using  $s= 100*(1- \frac{abs(a - p)}{a})$.
-This paper  explores    six Seigmund configuration data sets:  Berkeley DB (Java and Windows versions), Apache, SQLite, LLVM, and
+This paper  explores    six Seigmund configuration data sets:  Berkeley DB (Java and C versions), Apache, SQLite, LLVM, and
   x264\footnote{Available from the performance prediction section of PROMISE
@@
 One important detail to be stressed here is that, when we applied    SMOTE-ing and
-parameter tunings, those techniques should be applied the training data and {\em not}
+parameter tunings, those techniques should be applied to the training data and {\em not}
 the test data;  
@@
 We applied HOW's plans to all  Seigmund data, and the five ``good''
-  Jureczko   data sets {\em jedit, ivy, ant, lucene} and {\em poi}.
+  Jureczko   data sets {\em jedit, ivy, ant, lucene,} and {\em poi}.
   The training and tests used for Jurecko were display in \fig{j}. For these data
-  sets, training was managed by a Random Forest (tuned in the SMOTED training data using differential
+  sets, training was managed by a Random Forest (with tuning the SMOTED training data using differential
   evolution). \fig{ck} shows Jureczko data attributes.
@@
    \fig{cpm} shows the  Seigmund data attributes.
-   There were more diverse than the 
+   They were more diverse than the 
     Jurecko data since they
    contain the results of applying many  mutators
-  to the configuration options of the Makefiles of  BerkeleyDB (the Java  and  Windows  versions),  Apache,  SQLite,  LLVM, and x264.
+  to the configuration options of the Makefiles of  BerkeleyDB (the Java  and  C versions),  Apache,  SQLite,  LLVM, and x264.
 
@@
 
-   For both the Siegmind and Jureczko, we designed a procedure such we had at least
+   For both the Siegmind and Jureczko, we designed a procedure such that we had at least
    20 samples from the \fig{work} procedure for  each data set (the value of 20 was choosen as the minimum use sample size via the central limit theorem):
@@
       \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 & F=0.75, B=25 &    0.79  &  0.06 & \quart{0}{11}{7}{49} \\
-\hline  2 & F=0.75, B=50 &    0.82  &  0.07 & \quart{7}{14}{13}{49} \\
-\hline  3 &  F=0.75, B=100  &    0.85  &  0.06 & \quart{11}{12}{19}{49} \\
-  3 & F=0.5, B=25 &    0.87  &  0.03 & \quart{19}{6}{23}{49} \\
-  3 & F=0.5, B=50 &    0.87  &  0.07 & \quart{17}{14}{23}{49} \\
-\hline  4 &   F=0.5, B=100  &    0.91  &  0.07 & \quart{21}{14}{31}{49} \\
-\hline  5 & F=0.25, B=25 &    0.92  &  0.05 & \quart{29}{10}{33}{49} \\
-  5 & F=0.25, B=50 &    0.94  &  0.04 & \quart{35}{8}{37}{49} \\
-  5 &  F=0.25,B=100   &    0.95  &  0.04 & \quart{35}{8}{39}{49} \\
+  1 & F=0.75, B=25\% &    0.79  &  0.06 & \quart{0}{11}{7}{49} \\
+\hline  2 & F=0.75, B=50\% &    0.82  &  0.07 & \quart{7}{14}{13}{49} \\
+\hline  3 &  F=0.75, B=100\% &    0.85  &  0.06 & \quart{11}{12}{19}{49} \\
+  3 & F=0.5, B=25\% &    0.87  &  0.03 & \quart{19}{6}{23}{49} \\
+  3 & F=0.5, B=50\% &    0.87  &  0.07 & \quart{17}{14}{23}{49} \\
+\hline  4 &   F=0.5, B=100\% &    0.91  &  0.07 & \quart{21}{14}{31}{49} \\
+\hline  5 & F=0.25, B=25\% &    0.92  &  0.05 & \quart{29}{10}{33}{49} \\
+  5 & F=0.25, B=50\% &    0.94  &  0.04 & \quart{35}{8}{37}{49} \\
+  5 &  F=0.25,B=100\% &    0.95  &  0.04 & \quart{35}{8}{39}{49} \\
 \hline  6 &     Baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
@@
 \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 & F=0.75, B=50 &    0.2  &  0.03 & \quart{0}{1}{1}{49} \\
-  1 & F=0.75, B=25 &    0.2  &  0.05 & \quart{0}{3}{1}{49} \\
-\hline  2 &  F=0.75, B=100  &    0.22  &  0.07 & \quart{1}{5}{2}{49} \\
-\hline  3 & F=0.5, B=25 &    0.39  &  0.06 & \quart{11}{4}{12}{49} \\
-  3 & F=0.5, B=50 &    0.4  &  0.05 & \quart{12}{3}{13}{49} \\
-\hline  4 &   F=0.5,B=100   &    0.45  &  0.08 & \quart{14}{4}{16}{49} \\
-\hline  5 & F=0.25, B=25 &    0.65  &  0.05 & \quart{27}{3}{28}{49} \\
-  5 & F=0.25, B=50 &    0.66  &  0.05 & \quart{27}{3}{29}{49} \\
-\hline  6 &  F=0.25,B=100   &    0.69  &  0.05 & \quart{29}{3}{31}{49} \\
+  1 & F=0.75, B=50\% &    0.2  &  0.03 & \quart{0}{1}{1}{49} \\
+  1 & F=0.75, B=25\% &    0.2  &  0.05 & \quart{0}{3}{1}{49} \\
+\hline  2 &  F=0.75, B=100\% &    0.22  &  0.07 & \quart{1}{5}{2}{49} \\
+\hline  3 & F=0.5, B=25\% &    0.39  &  0.06 & \quart{11}{4}{12}{49} \\
+  3 & F=0.5, B=50\% &    0.4  &  0.05 & \quart{12}{3}{13}{49} \\
+\hline  4 &   F=0.5,B=100\% &    0.45  &  0.08 & \quart{14}{4}{16}{49} \\
+\hline  5 & F=0.25, B=25\% &    0.65  &  0.05 & \quart{27}{3}{28}{49} \\
+  5 & F=0.25, B=50\% &    0.66  &  0.05 & \quart{27}{3}{29}{49} \\
+\hline  6 &  F=0.25,B=100\% &    0.69  &  0.05 & \quart{29}{3}{31}{49} \\
 \hline  7 &     Baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
@@
 \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 & F=0.75, B=25 &    0.64  &  0.1 & \quart{1}{12}{6}{49} \\
-  1 & F=0.75, B=50 &    0.68  &  0.14 & \quart{0}{17}{10}{49} \\
-\hline  2 &  F=0.75, B=100   &    0.74  &  0.1 & \quart{12}{12}{18}{49} \\
-  2 & F=0.5, B=25 &    0.76  &  0.09 & \quart{15}{11}{20}{49} \\
-  2 & F=0.5, B=50 &    0.78  &  0.17 & \quart{15}{21}{23}{49} \\
-  2 &   F=0.5,B=100   &    0.8  &  0.07 & \quart{20}{9}{25}{49} \\
-\hline  3 & F=0.25, B=25 &    0.85  &  0.05 & \quart{30}{6}{31}{49} \\
-\hline  4 & F=0.25, B=50 &    0.89  &  0.09 & \quart{30}{11}{36}{49} \\
-  4 &  F=0.25, B=100  &    0.9  &  0.06 & \quart{35}{7}{37}{49} \\
+  1 & F=0.75, B=25\% &    0.64  &  0.1 & \quart{1}{12}{6}{49} \\
+  1 & F=0.75, B=50\% &    0.68  &  0.14 & \quart{0}{17}{10}{49} \\
+\hline  2 &  F=0.75, B=100\% &    0.74  &  0.1 & \quart{12}{12}{18}{49} \\
+  2 & F=0.5, B=25\% &    0.76  &  0.09 & \quart{15}{11}{20}{49} \\
+  2 & F=0.5, B=50\% &    0.78  &  0.17 & \quart{15}{21}{23}{49} \\
+  2 &   F=0.5,B=100\% &    0.8  &  0.07 & \quart{20}{9}{25}{49} \\
+\hline  3 & F=0.25, B=25\% &    0.85  &  0.05 & \quart{30}{6}{31}{49} \\
+\hline  4 & F=0.25, B=50\% &    0.89  &  0.09 & \quart{30}{11}{36}{49} \\
+  4 &  F=0.25, B=100\% &    0.9  &  0.06 & \quart{35}{7}{37}{49} \\
 \hline  5 &     Baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
@@
 \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 & F=0.75, B=25 &    0.92  &  0.02 & \quart{0}{11}{5}{49} \\
-  1 & F=0.75, B=50 &    0.93  &  0.02 & \quart{5}{11}{11}{49} \\
-  1 &  F=0.75, B=100   &    0.93  &  0.02 & \quart{11}{11}{11}{49} \\
+  1 & F=0.75, B=25\% &    0.92  &  0.02 & \quart{0}{11}{5}{49} \\
+  1 & F=0.75, B=50\% &    0.93  &  0.02 & \quart{5}{11}{11}{49} \\
+  1 &  F=0.75, B=100\% &    0.93  &  0.02 & \quart{11}{11}{11}{49} \\
 \hline  2 & F=0.5, B=25 &    0.95  &  0.01 & \quart{16}{6}{22}{49} \\
-  2 & F=0.5, B=50 &    0.95  &  0.01 & \quart{16}{6}{22}{49} \\
-  2 &   F=0.5, B=100   &    0.96  &  0.01 & \quart{22}{5}{27}{49} \\
-\hline  3 & F=0.25, B=25 &    0.97  &  0.01 & \quart{33}{5}{33}{49} \\
-  3 & F=0.25, B=50 &    0.98  &  0.0 & \quart{38}{0}{38}{49} \\
-  3 &  F=0.25, B=100  &    0.98  &  0.01 & \quart{38}{6}{38}{49} \\
+  2 & F=0.5, B=50\% &    0.95  &  0.01 & \quart{16}{6}{22}{49} \\
+  2 &   F=0.5, B=100\% &    0.96  &  0.01 & \quart{22}{5}{27}{49} \\
+\hline  3 & F=0.25, B=25\% &    0.97  &  0.01 & \quart{33}{5}{33}{49} \\
+  3 & F=0.25, B=50\% &    0.98  &  0.0 & \quart{38}{0}{38}{49} \\
+  3 &  F=0.25, B=100\% &    0.98  &  0.01 & \quart{38}{6}{38}{49} \\
 \hline  4 &     Baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
@@
 \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 & F=0.75, B=25 &    0.98  &  0.0 & \quart{0}{0}{0}{49} \\
-  1 & F=0.75, B=50 &    0.98  &  0.0 & \quart{0}{0}{0}{49} \\
-  1 & F=0.75, B=100 &   0.99  &  0.01 & \quart{0}{24}{24}{49} \\
-  1 & F=0.5, B=25 &    0.99  &  0.0 & \quart{24}{0}{24}{49} \\
-  1 & F=0.5, B=50 &    0.99  &  0.0 & \quart{24}{0}{24}{49} \\
-  1 & F=0.5, B=100 &    0.99  &  0.01 & \quart{24}{25}{24}{49} \\
-  1 & F=0.25, B=50 &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-  1 & F=0.25-weight-B=25 &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
-  1 & F=0.25, B=100 &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
+  1 & F=0.75, B=25\% &    0.98  &  0.0 & \quart{0}{0}{0}{49} \\
+  1 & F=0.75, B=50\% &    0.98  &  0.0 & \quart{0}{0}{0}{49} \\
+  1 & F=0.75, B=100\% &   0.99  &  0.01 & \quart{0}{24}{24}{49} \\
+  1 & F=0.5, B=25\% &    0.99  &  0.0 & \quart{24}{0}{24}{49} \\
+  1 & F=0.5, B=50\% &    0.99  &  0.0 & \quart{24}{0}{24}{49} \\
+  1 & F=0.5, B=100\% &    0.99  &  0.01 & \quart{24}{25}{24}{49} \\
+  1 & F=0.25, B=50\% &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
+  1 & F=0.25-weight-B=25\% &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
+  1 & F=0.25, B=100\% &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
   1 &     Baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
@@
 
-\vspace{2mm}\noindent {\scriptsize \textbf{X264}\\[0.1cm]}
+\vspace{2mm}\noindent {\scriptsize \textbf{x264}\\[0.1cm]}
   {\scriptsize  \begin{tabular}{{llrrc}}
@@
 \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
-  1 & F=0.75, B=25 &    0.72  &  0.04 & \quart{0}{6}{3}{49} \\
-  1 & F=0.75, B=50 &    0.74  &  0.04 & \quart{3}{6}{6}{49} \\
-\hline  2 & F=0.5, B=50 &    0.82  &  0.04 & \quart{16}{7}{19}{49} \\
-  2 &  F=0.75, B=100  &    0.82  &  0.06 & \quart{13}{10}{19}{49} \\
-  2 & F=0.5, B=25 &    0.82  &  0.03 & \quart{19}{5}{19}{49} \\
-\hline  3 &   F=0.5, B=100   &    0.88  &  0.03 & \quart{26}{5}{29}{49} \\
-\hline  4 & F=0.25, B=50 &    0.91  &  0.02 & \quart{33}{3}{34}{49} \\
-  4 & F=0.25, B=25 &    0.91  &  0.02 & \quart{34}{4}{34}{49} \\
-\hline  5 &  F=0.25, B=100 &    0.93  &  0.02 & \quart{36}{3}{38}{49} \\
+  1 & F=0.75, B=25\% &    0.72  &  0.04 & \quart{0}{6}{3}{49} \\
+  1 & F=0.75, B=50\% &    0.74  &  0.04 & \quart{3}{6}{6}{49} \\
+\hline  2 & F=0.5, B=50\% &    0.82  &  0.04 & \quart{16}{7}{19}{49} \\
+  2 &  F=0.75, B=100\% &    0.82  &  0.06 & \quart{13}{10}{19}{49} \\
+  2 & F=0.5, B=25\% &    0.82  &  0.03 & \quart{19}{5}{19}{49} \\
+\hline  3 &   F=0.5, B=100\% &    0.88  &  0.03 & \quart{26}{5}{29}{49} \\
+\hline  4 & F=0.25, B=50\% &    0.91  &  0.02 & \quart{33}{3}{34}{49} \\
+  4 & F=0.25, B=25\% &    0.91  &  0.02 & \quart{34}{4}{34}{49} \\
+\hline  5 &  F=0.25\%, B=100\% &    0.93  &  0.02 & \quart{36}{3}{38}{49} \\
 \hline  6 &     Baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} \\
@@
 are ratios of baselines.
-Recall that $B$ denotes how what {\em percent} of the attributes are displaced
-and $F$ denotes how {\em far} the test cases are mutated (so at $F=0.75,B=100$, all
+Recall that $B$ denotes what {\em percent} of the attributes are displaced
+and $F$ denotes how {\em far} the test cases are mutated (so at $F=0.75, B=100\%$, \textit{all}
 attributes are displaced 75\% of the distance to the exemplar).
 For each of the  tables in this figure, better methods appear higher up.
-In these tables, median and IQR are the 50th and the (75-25)th percentiles.
+In these tables, median and IQR are the 50\textsuperscript{th} and the (75-25)\textsuperscript{th} percentiles.
 The IQR ranges are shown in the right column with black dot at the median.
@@
       \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} && \textbf{Bugs}\\
-   1 &  F=0.75, B=100 &    0.71  &  0.19 & \quart{0}{25}{10}{49} & 62 \\
-\hline  2 &   F=0.5, B=100  &    0.88  &  0.14 & \quart{20}{19}{33}{49} & 77\\
+   1 &  F=0.75, B=100\% &    0.71  &  0.19 & \quart{0}{25}{10}{49} & 62 \\
+\hline  2 &   F=0.5, B=100\% &    0.88  &  0.14 & \quart{20}{19}{33}{49} & 77\\
 \hline  3 & F=0.5, B=50\% &    0.91  &  0.08 & \quart{32}{11}{37}{49} & 80\\
   3 & F=0.75, B=50\% &    0.92  &  0.09 & \quart{31}{12}{39}{49} & 82\\
-  3 &  F=0.25, B=100  &    0.92  &  0.04 & \quart{36}{5}{39}{49} & 81\\
+  3 &  F=0.25, B=100\% &    0.92  &  0.04 & \quart{36}{5}{39}{49} & 81\\
   3 & F=0.75, B=25\% &    0.94  &  0.09 & \quart{36}{12}{41}{49} & 82\\
@@
 \hline  5 &F= 0.25, B=25\% &    0.99  &  0.01 & \quart{48}{1}{48}{49} & 87\\
-\hline  6 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 90\\
+\hline  6 &         Baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 90\\
 \hline \end{tabular}}
@@
 \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & & \textbf{Bugs}\\
-  1 &  F=0.75,  B=100 &    0.75  &  0.18 & \quart{0}{29}{8}{49} & 50\\
-\hline  2 &   F=0.5,B=100   &    0.84  &  0.08 & \quart{14}{14}{23}{49} & 56\\
-  2 & F=0.75, B=50 &    0.84  &  0.09 & \quart{18}{15}{23}{49} & 56\\
-\hline  3 & F=0.5, B=50 &    0.91  &  0.05 & \quart{29}{9}{34}{49} & 61\\
-\hline  4 & F=0.25, B=50 &    0.96  &  0.01 & \quart{43}{1}{43}{49} & 64\\
-  4 & F=0.75, B=25 &    0.96  &  0.05 & \quart{39}{9}{43}{49} & 65\\
-  4 &  F=0.25, B=100  &    0.97  &  0.05 & \quart{39}{9}{44}{49} & 65\\
-  4 & F=0.5, B=25 &    0.97  &  0.03 & \quart{43}{5}{44}{49} & 65\\
-\hline  5 & F=0.25, B=25 &    0.99  &  0.01 & \quart{48}{1}{48}{49} & 66\\
-\hline  6 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 67\\
+  1 &  F=0.75,  B=100\% &    0.75  &  0.18 & \quart{0}{29}{8}{49} & 50\\
+\hline  2 &   F=0.5, B=100\% &    0.84  &  0.08 & \quart{14}{14}{23}{49} & 56\\
+  2 & F=0.75, B=50\% &    0.84  &  0.09 & \quart{18}{15}{23}{49} & 56\\
+\hline  3 & F=0.5, B=50\% &    0.91  &  0.05 & \quart{29}{9}{34}{49} & 61\\
+\hline  4 & F=0.25, B=50\% &    0.96  &  0.01 & \quart{43}{1}{43}{49} & 64\\
+  4 & F=0.75, B=25\% &    0.96  &  0.05 & \quart{39}{9}{43}{49} & 65\\
+  4 &  F=0.25, B=100\% &    0.97  &  0.05 & \quart{39}{9}{44}{49} & 65\\
+  4 & F=0.5, B=25\% &    0.97  &  0.03 & \quart{43}{5}{44}{49} & 65\\
+\hline  5 & F=0.25, B=25\% &    0.99  &  0.01 & \quart{48}{1}{48}{49} & 66\\
+\hline  6 &         Baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 67\\
 \hline \end{tabular}}
@@
 \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & & \textbf{Bugs}\\
-  1 &  F=0.75,  &    0.76  &  0.21 & \quart{0}{28}{17}{49} & 130\\
-  1 &   0.5,  &    0.76  &  0.16 & \quart{9}{22}{17}{49} & 131\\
-\hline  2 & 0.75, B=50\% &    0.85  &  0.12 & \quart{22}{17}{29}{49} & 146\\
-\hline  3 &  0.25,  &    0.87  &  0.07 & \quart{28}{9}{32}{49} & 152\\
-\hline  4 & 0.5, B=50\% &    0.93  &  0.05 & \quart{37}{7}{40}{49} & 162\\
-\hline  5 & 0.25, B=50\% &    0.97  &  0.03 & \quart{43}{4}{45}{49} & 167\\
-  5 & 0.75, B=25\% &    0.97  &  0.02 & \quart{44}{3}{45}{49} & 168\\
-\hline  6 & 0.5, B=25\% &    0.98  &  0.02 & \quart{45}{3}{47}{49} & 170\\
-  6 & 0.25, B=25\% &    0.98  &  0.01 & \quart{47}{1}{47}{49} & 171\\
-\hline  7 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 175\\
+  1 &  F=0.75, B=100\%  &    0.76  &  0.21 & \quart{0}{28}{17}{49} & 130\\
+  1 &   F=0.5, B=100\%  &    0.76  &  0.16 & \quart{9}{22}{17}{49} & 131\\
+\hline  2 & F=0.75, B=50\% &    0.85  &  0.12 & \quart{22}{17}{29}{49} & 146\\
+\hline  3 &  F=0.25, B=100\% &    0.87  &  0.07 & \quart{28}{9}{32}{49} & 152\\
+\hline  4 & F=0.5, B=50\% &    0.93  &  0.05 & \quart{37}{7}{40}{49} & 162\\
+\hline  5 & F=0.25, B=50\% &    0.97  &  0.03 & \quart{43}{4}{45}{49} & 167\\
+  5 & F=0.75, B=25\% &    0.97  &  0.02 & \quart{44}{3}{45}{49} & 168\\
+\hline  6 & F=0.5, B=25\% &    0.98  &  0.02 & \quart{45}{3}{47}{49} & 170\\
+  6 & F=0.25, B=25\% &    0.98  &  0.01 & \quart{47}{1}{47}{49} & 171\\
+\hline  7 &         Baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 175\\
 \hline \end{tabular}}
@@
 \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & & \textbf{Bugs}\\
-  1 &  0.75,  &    0.66  &  0.2 & \quart{0}{21}{13}{49} & 97\\
-\hline  2 & 0.75, B=50\% &    0.7  &  0.1 & \quart{14}{10}{17}{49} & 103\\
-\hline  3 & 0.75, B=25\% &    0.8  &  0.09 & \quart{21}{10}{28}{49} & 117\\
-  3 &   0.5,  &    0.81  &  0.09 & \quart{26}{9}{29}{49} & 119\\
-\hline  4 & 0.5, B=50\% &    0.88  &  0.07 & \quart{34}{8}{36}{49} & 128\\
-  4 & 0.25, B=25\% &    0.89  &  0.07 & \quart{36}{8}{38}{49} & 130\\
-  4 &  0.25,  &    0.92  &  0.04 & \quart{39}{4}{41}{49} & 133\\
-\hline  5 & 0.25, B=50\% &    0.95  &  0.04 & \quart{42}{4}{44}{49} & 139\\
-  5 & 0.5, B=25\% &    0.96  &  0.03 & \quart{43}{3}{45}{49} & 141\\
-\hline  6 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 146\\
+  1 &  F=0.75, B=100\% &    0.66  &  0.2 & \quart{0}{21}{13}{49} & 97\\
+\hline  2 & F=0.75, B=50\% &    0.7  &  0.1 & \quart{14}{10}{17}{49} & 103\\
+\hline  3 & F=0.75, B=25\% &    0.8  &  0.09 & \quart{21}{10}{28}{49} & 117\\
+  3 &   F=0.5, B=100\% &    0.81  &  0.09 & \quart{26}{9}{29}{49} & 119\\
+\hline  4 & F=0.5, B=50\% &    0.88  &  0.07 & \quart{34}{8}{36}{49} & 128\\
+  4 & F=0.25, B=25\% &    0.89  &  0.07 & \quart{36}{8}{38}{49} & 130\\
+  4 &  F=0.25, B=100\% &    0.92  &  0.04 & \quart{39}{4}{41}{49} & 133\\
+\hline  5 & F=0.25, B=50\% &    0.95  &  0.04 & \quart{42}{4}{44}{49} & 139\\
+  5 & F=0.5, B=25\% &    0.96  &  0.03 & \quart{43}{3}{45}{49} & 141\\
+\hline  6 &         Baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 146\\
 \hline \end{tabular}}
@@
 \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & & \textbf{Bugs}\\
-  1 &  0.75,  &    0.72  &  0.26 & \quart{0}{29}{18}{49} & 173\\
-\hline  2 & 0.75, B=50\% &    0.79  &  0.15 & \quart{14}{17}{26}{49} & 190\\
-  2 &   0.5,  &    0.81  &  0.14 & \quart{21}{16}{28}{49} & 195\\
-\hline  3 & 0.5, B=50\% &    0.9  &  0.11 & \quart{30}{13}{38}{49} & 217\\
-  3 &  0.25,  &    0.91  &  0.05 & \quart{36}{6}{39}{49} & 219\\
-\hline  4 & 0.75, B=25\% &    0.94  &  0.05 & \quart{39}{6}{43}{49} & 226\\
-  4 & 0.25, B=50\% &    0.94  &  0.06 & \quart{39}{7}{43}{49} & 226\\
-\hline  5 & 0.25, B=25\% &    0.96  &  0.03 & \quart{44}{3}{45}{49} & 231\\
-  5 & 0.5, B=25\% &    0.96  &  0.03 & \quart{44}{3}{45}{49} & 231\\
-\hline  6 &         Base &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 240\\
+  1 &  F=0.75, B=100\% &    0.72  &  0.26 & \quart{0}{29}{18}{49} & 173\\
+\hline  2 & F=0.75, B=50\% &    0.79  &  0.15 & \quart{14}{17}{26}{49} & 190\\
+  2 &  F=0.5, B=100\% &    0.81  &  0.14 & \quart{21}{16}{28}{49} & 195\\
+\hline  3 & F=0.5, B=50\% &    0.9  &  0.11 & \quart{30}{13}{38}{49} & 217\\
+  3 &  F=0.25, B=100\% &    0.91  &  0.05 & \quart{36}{6}{39}{49} & 219\\
+\hline  4 & F=0.75, B=25\% &    0.94  &  0.05 & \quart{39}{6}{43}{49} & 226\\
+  4 & F=0.25, B=50\% &    0.94  &  0.06 & \quart{39}{7}{43}{49} & 226\\
+\hline  5 & F=0.25, B=25\% &    0.96  &  0.03 & \quart{44}{3}{45}{49} & 231\\
+  5 & F=0.5, B=25\% &    0.96  &  0.03 & \quart{44}{3}{45}{49} & 231\\
+\hline  6 &         Baseline &    1.0  &  0.0 & \quart{49}{0}{49}{49} & 240\\
 \hline \end{tabular}}
@@
 The results for each data set, for different ranges of $(F,B)$ are shown in \fig{jur} and \fig{ant}.
-Also included are a {\em baseline} figure which is taken from the cases in the test data
-and  Since we wish to demonstrate
+Also included is a {\em baseline} figure which is taken from the cases in the test data
+and since we wish to demonstrate
 improving defects
@@
  data sets, the baseline results are ranked significantly worse than the results seen
- after planning (evidence: the statistical ranking assigned by Scott-Knott is shown in the left-hand-side columns and most baselines get larger, i.e. worse, ranks
- that the treated data). The exception to this is SQL in  \fig{jur}. which
+ after planning (evidence: the statistical ranking assigned by Scott-Knott is shown in the left-hand-side columns and most baselines get larger, i.e.
+worse, ranks consistently higher that than the treated data).
+The exception to this is SQL in  \fig{jur}.
+which
  seems to
@@
  \bi
- \item For data sets with continuous objectives (the Jureczko data of \fig{jur}),
+ \item For data sets with continuous objectives (the Seigmund  data of \fig{jur}),
  best results are obtained by taking the fewest attributes (minimize $B$) 
  while moving close to the exemplar (maximize $F$).
- \item For data sets with discrete objectives (the Seigmund data  of \fig{ant}),
+ \item For data sets with discrete objectives (the Jureczko data  of \fig{ant}),
  best results are obtained by maximizing both $F$ and $B$.
@@
 them. \fig{howxy} is from the {\em ivy} data
-set. It shows (1)~the training cases and (2)~the test cases and (3)~the
+set. It shows: (1)~the training cases, (2)~the test cases, and (3)~the
 test cases displaced after applying HOW's plans.
@@
 
-This paper has explored the problem of assess changes to a project without
+This paper has explored the problem of assessing changes to a project without
 extensive field studies. We have proposed using predictors learned from domain data
